### 2018-01-28 Algebra/Homework/Homework.tex
init commit

\documentclass{article}

\input{../../definitions.tex}
\input{../algebra.tex}

\title{Algebra Homework}

\begin{document}
\maketitle
\tableofcontents

\section{Chapter 1}
\subsection{Section 1}
\subsubsection{Question 1}

Choose $a,b\in S$. We find $$a = a * b = b * a = b$$, and thus all elements in $S$ must be the same element, so there is most one element of $S$.

\subsubsection{Question 2}
Let us choose $a,b,c \in S$.

\question{(a)} We have $$a*b = a - b = -(b-a) = -(b*a)$$, thus iff $0 = a*b = a-b$ we have $a*b = b*a$ as $0=-0$, however for any other value of $a*b$, $a*b\not=b*a$. We also may notice that iff $a=b$, then $a*b=a-b=0$. Thus for all $a\not= b$, $a*b \not=b*a$.

\question{(b)} We have
\begin{align*}
a*(b*c) &= a-(b-c) \\
&= a+(c-b) \\
&= a+c-b \\
&= a-b+c \\
&= a-b-(-c) \\
&= (a-b)-(-c) \\
&= (a*b)*-c
\end{align*} so $a*(b*c) = (a*b)*c$ iff $c=-c$ which is only true if $c = 0$.

\question{(c)} We have $a*0 = a-0 = a$.

\question{(d)} We have $a*a = a-a = 0$.

\subsection{Section 2}

\subsubsection{Question 8}

Let $x \in (A\setminus B) \union (B\setminus A)$ then either $x \in A \setminus B$ or $x \in B\setminus A$. If $x \in A\setminus B$ then we get that $x \in A$ and $x \not\in B$, thus $x \in A\union B$ and $x \not\in A \inter B$, which would mean $x \in (A\union B)\setminus(A\inter B)$. If $x\in B\setminus A$ then we get that $x\in B$ and $x\not\in A$, thus $x\in A \union B$ and $x\not\in A\inter B$, which would mean $x \in (A\union B)\setminus(A\inter B)$. It has now been demonstrated that $(A\setminus B) \union (B\setminus A) \subset (A \union B) \setminus (B\inter A)$.

Now let $x\in(A\union B)\setminus(A\inter B)$. We have that $x \in A\union B$ and $x \not\in A\inter B$. It follows that either $x \in A$ or $x\in B$, however, $x$ is not in both $A$ and $B$. This may be written as: $x \in A$ and $x \not\in B$, or $x\in B$ and $x\not\in A$. This then translates to $x \in A\setminus B$ or $x\in B\setminus A$, therefore, $x\in (A\setminus B) \union (B\setminus A)$. It has now been demonstrated that $(A\union B) \setminus (B\inter A) \subset (A\setminus B)\union (B\setminus A)$.

Now it has been shown that both sets are subsets of each-other, thus $(A\setminus B)\union(B\setminus A) = (A\union B) \setminus (A\inter B)$.

This may be displayed pictorially as follows:

%TODO figure out pictures

\def\secondcircle{(210:0.95cm) circle (1.5cm)}
\def\thirdcircle{(330:0.95cm) circle (1.5cm)}
\begin{tikzpicture}
	\begin{scope}
		\clip \secondcircle;
		\fill[cyan] \thirdcircle;
	\end{scope}
	\draw \secondcircle node [text=black,below left] {$A$};
	\draw \thirdcircle node [text=black,below right] {$B$};
\end{tikzpicture}

\subsubsection{Question 9}

Let $x \in A \inter (B \union C)$, thus $x \in A$ and $x\in B\union C$. We then have that $x \in B$ or $x \in C$. Now as we already know that $x\in A$ then we get that either $x \in B \inter A$ or $x \in C \inter A$ and therefore $x \in (A\inter B) \union (A \inter C)$. Thus it has been shown that $A \inter (B\union C) \subset (A\inter B)\union (A\inter C)$.

Let $x \in (A\inter B) \union (A\inter C)$, thus $x \in (A\inter B)$ or $x\in (A\inter C)$. We then get that either $x \in A$ and $x \in B$ or that $x\in A$ and $x\in C$, either way $x\in A$, thus we may write that $x \in A$ and either $x\in B$ or $x\in C$. This would be the same as $x\in A$ and $x\in B\union C$, which then translates to $x \in A \inter (B\union C)$. Thus it has been shown that $(A\inter B)\union (A\inter C) \subset A\inter (B\union C)$.

We have now shown that both sets are subsets of each-other, thus $A\inter(B\union C) = (A\inter B)\union (A\inter C)$.

\subsubsection{Question 10}

Let $x\in A\union (B\inter C)$, assume then for the sake of contradiction that $x\not\in(A\union B)\inter (A\union C)$. Because $x \in A\union (B\inter C)$ we have that $x \in A$ or $x\in B\inter C$. Because $x\not\in (A\union B)\inter (A\union C)$ we have that $x\not\in A\union B$ or $x\not\in A\union C$. We then get that either $x \not\in A$ and $x\not\in B$ or $x\not\in A$ and $x\not\in C$, either way $x\not\in A$, so we have $x\in B\inter C$. We know that $x\not\in B$ or $x\not\in C$, however we also have that $x\in B$ and $x\in C$ due to $x\in B\inter C$, thus we have a contradiction. Thus $A\union(B\inter C) \subset (A\union B)\inter(A \union C)$.

Let $x\in (A \union B) \inter (A\union C)$ and assume for the sake of contradiction that $x\not\in A\union(B \inter C)$. We then get that $x\not\in A$ and $x\not\in B\inter C$. We also have that $x\in A \union B$ and $x\in A \union C$, so if $x\not\in A$ then we get $x\in B$ and $x\in C$. This is then translated to $x\in B\inter C$ which is a direct contradiction with $x\not\in B\inter C$ and again we have a contradiction. Thus $(A\union B)\inter(A\union C)\subset A\union (B\inter C)$.

We have now shown that both sets are subsets of each other, thus $A\inter(B\union C) = (A\union B)\inter(A\union C)$.

\subsubsection{Question 12}

\question{(a)}
\begin{align*}
	\setcomp{(A\union B)} &= \setbuilder{x\in S}{x\not\in A\union B} \\
	&= \setbuilder{x\in S}{x\not\in A \And x\not\in B} \\
	&= \setbuilder{x\in S}{x \in \setcomp A \And x\in \setcomp B} \\
	&= \setcomp A \inter \setcomp B
\end{align*}

\question{(b)}
\begin{align*}
	\setcomp{(A\inter B)} &= \setbuilder{x\in S}{x\not\in A\inter B} \\
	&= \setbuilder{x\in S}{x\not\in A \Or x\not\in B} \\
	&= \setbuilder{x\in S}{x \in \setcomp A \Or x\in \setcomp B} \\
	&= \setcomp A \union \setcomp B
\end{align*}

\subsubsection{Question 13}
\question{(a)}
\begin{align*}
	A + B &= (A\setminus B) \union (B\setminus A) \\
	&= (B\setminus A) \union (A\setminus B) \\
	&= B + A
\end{align*}

\question{(b)}
First notice that for any set $X$, $X\setminus \emptyset = A$ and that $\emptyset \setminus X = \emptyset$.
\begin{align*}
	A + \emptyset &= (A \setminus \emptyset) \union (\emptyset \setminus A)\\
	&= A \union \emptyset \\
	&= A \\
\end{align*}

\question{(c)}
\begin{align*}
	A\cdot A &= A\inter A\\
	&= A
\end{align*}

\question{(d)}
\begin{align*}
	A + A &= (A\setminus A)\union (A\setminus A) \\
	&= \emptyset \union \emptyset \\
	&= \emptyset
\end{align*}

\question{(e)} To simplify this question let me introduce the logical operation, $a \lxor b$ which is defined as either $a$ or $b$ but not both, and we will show that $a \lxor (b\lxor c) = (a\lxor b)\lxor c$ using truth tables.

\begin{center}
	\begin{tabular}{c|c|c|c|c|c|c}
		$a$&$b$&$c$&$a\lxor b$&$b\lxor c$&$a\lxor(b\lxor c)$&$(a\lxor b)\lxor c$ \\
		\false&\false&\false&\false&\false&\false&\false\\
		\false&\false&\true&\false&\true&\true&\true\\
		\false&\true&\false&\true&\true&\true&\true\\
		\false&\true&\true&\true&\false&\false&\false\\
		\true&\false&\false&\true&\false&\true&\true\\
		\true&\false&\true&\true&\true&\false&\false\\
		\true&\true&\false&\false&\true&\false&\false\\
		\true&\true&\true&\false&\false&\true&\true
	\end{tabular}
\end{center}

Now we wish to show that $A + B = \setbuilder{x\in S}{x \in A \lxor x \in B}$. To do this we will first show that $a\lxor b = (a\land\lnot b) \lor (b\land\lnot a)$, where $\lnot$ is a logical not, $\land$ is a logical and, and $\lor$ is a logical or. We again show this by the following truth table:
\begin{center}
	\begin{tabular}{c|c|c|c|c|c|c|c}
		$a$&$b$&$\lnot b$&$a\land\lnot b$&$\lnot a$&$b\land\lnot a$&$(a\land\lnot b)\lor(b\land\lnot a)$&$a\lxor b$\\
		\false&\false&\true&\false&\true&\false&\false&\false\\
		\false&\true&\false&\false&\true&\true&\true&\true\\
		\true&\false&\true&\true&\false&\false&\true&\true\\
		\true&\true&\false&\false&\false&\false&\false&\false\\
	\end{tabular}
\end{center}
Now we find
\begin{align*}
A + B &= \setbuilder{x\in S}{x\in A+B} \\
&= \setbuilder{x\in S}{x \in (A\setminus B)\union(B\setminus A)}\\
&= \setbuilder{x\in S}{x\in (A\setminus B) \lor x\in(B\setminus A)}\\
&=\setbuilder{x\in S}{(x\in A \land x\not\in B)\lor(x\in B\land x\not\in A)}\\
&=\setbuilder{x\in S}{x\in A\lxor x\in B}\\
\end{align*}
so we then have
\begin{align*}
A+(B+C)&=\setbuilder{x\in S}{x\in A\lxor x\in B+C} \\
&=\setbuilder{x\in S}{x\in A\lxor(x\in B\lxor x\in C)}\\
&=\setbuilder{x\in S}{(x\in A \lxor x\in B)\lxor x\in C}\\
&=\setbuilder{x\in S}{x \in A + B\lxor x \in C}\\
&=(A+B)+C
\end{align*}

\question{(f)}
Suppose $B\not= C$. Because $B\not= C$ there exists some $x\in S$ such that either $x\in B$ and $x\not\in C$ or $x\in C$ and $x\not\in B$, we will assume without loss of generality that $x\in B$ and $x\not\in C$. Now if $x\in A$ then we would find $x\not\in A+B$ and $x\in A+C$. If $x\not\in A$ we would find that $x\in A+B$ and $x\not\in A+C$. We now have shown that $B\not= C\implies A+B\not=A+C$, thus by contrapositive we have $A+B=A+C \implies B=C$.

\question{(g)}
First we will want to show logical equivalence between the statement $a\land(b\lxor c)$ and $(a\land b)\lxor(a\land c)$.
\begin{center}
	\begin{tabular}{c|c|c|c|c|c|c|c}
		$a$&$b$&$c$&$b\lxor c$&$a\land b$&$a\land c$&$a\land(b\lxor c)$&$(a\land b)\lxor(a\land c)$\\
		\false&\false&\false&\false&\false&\false&\false&\false\\
		\false&\false&\true&\true&\false&\false&\false&\false\\
		\false&\true&\false&\true&\false&\false&\false&\false\\
		\false&\true&\true&\false&\false&\false&\false&\false\\
		\true&\false&\false&\false&\false&\false&\false&\false\\
		\true&\false&\true&\true&\false&\true&\true&\true\\
		\true&\true&\false&\true&\true&\false&\true&\true\\
		\true&\true&\true&\false&\true&\true&\false&\false
	\end{tabular}
\end{center}
now we may show
\begin{align*}
A\cdot(B+C) &= A\inter(B+C)\\
&=\setbuilder{x\in S}{x \in A\inter(B+C)}\\
&= \setbuilder{x\in S}{x\in A\land x\in(B+C)} \\
&= \setbuilder{x\in S}{x\in A\land (x\in B \lxor x\in C)}\\
&=\setbuilder{x\in S}{(x\in A\land x\in B)\lxor(x\in A\land x\in C)}\\
&=\setbuilder{x\in S}{x\in A\inter B\lxor x\in A\inter C}\\
&=\setbuilder{x\in S}{x\in (A\inter B)+(A\inter C)}\\
&=(A\inter B)+(A\inter C)\\
&=(A\cdot B)+(A\cdot C)
\end{align*}

\subsubsection{Question 14}
First notice that if $A$ and $B$ are disjoint then $m(A\union B) = m(A) + m(B)$. So now we get the three disjoint sets $A\setminus B$, $A\inter B$, and $B\setminus A$, notice that $A =( A\setminus B) \union (A\inter B)$, that $B =(B\setminus A)\union(A\inter B)$, and $A\union B = (A\setminus B)\union (A\inter B)\union (B\setminus A)$. Now we get $m(A) = m(A\setminus B) + m(A\inter B)$, $m(B) = m(B\setminus A) + m(A\inter B)$, and $m(A\union B) = m(A\setminus B)+(A\inter B)+m(B\setminus A)$. We then get \begin{align*}
m(A) + m(B) &= m(A\setminus B)+m(A \inter B)+m(B\setminus A)+m(A\inter B)\\
&= m(A\union B) + m(A\inter B)\\
m(A) + m(B) - m(A \inter B) &= m(A \union B)
\end{align*}

\subsubsection{Question 22}
\question{(a)} To construct a subset of any set we go through each element and choose to include it or not to, this gives us two possibilities per element. For a set of size $n$ then there are $n$ independent choices to be made in constructing a subset, thus $2^n$ subsets.

\question{(b)} There are exactly $\binom nm = \frac{n!}{m!(n-m)!}$ subsets of a set with $n$ elements that have $m$ elements.

\begin{proof}
	Let us start by defining $\binom nm$ as the number of ways to choose a subset with $m$ elements from a set with $n$ elements. Now we must recognize that $k!$ is the number of ways to order a set with $k$ elements. Then we get that $\binom nmm!(n-m)! = n!$ as we may order our set with $n$ elements by choosing the first $m$ elements in our order ($\binom nm$ possible ways), then ordering those elements ($m!$ ways), and finally ordering the rest of the elements ($(m-n!)$ ways). This gives us $\binom nmm!(n-m)!=n!$ and from there we divide and get $\binom nm=\frac{n!}{m!(n-m)!}$.
\end{proof}

\subsection{Section 3}
\subsubsection{Question 7}
Let $g:S\to T$, $h:S\to T$ and $f:T\to U$ be functions such that $f$ is 1-1 and $f\composed g = f\composed h$. Assume for the sake of contradiction that $g\not=h$, then there exists some $s \in S$ such that $g(s) \not= h(s)$. We know that $f\composed g(s) = f\composed h(s)$, thus $f(g(s)) = f(h(s))$ so $g(s) = h(s)$ by $f$ being 1-1. Thus we have a contradiction and we know that $g=h$.

\subsubsection{Question 8}
\question{(a)} Yes, as all integers are either even or odd and none are both even and odd.

\question{(b)} Let us break this into cases:
\begin{itemize}
	\item If $s_1$ and $s_2$ are even, then there exists $k_1\in\mathbb Z$ and $k_2\in\mathbb Z$ such that $2k_1 = s_1$ and $2k_2 = s_1$. Thus $s_1 + s_2 = 2k_1 + 2k_2 = 2(k_1 + k_2)$, thus $f(s_1 + s_2) = 1$. We also find that $f(s_1) \cdot f(s_2) = 1 \cdot 1 = 1$.
	\item If $s_1$ is even and $s_2$ is odd, then there exists $k_1\in\mathbb Z$ and $k_2\in\mathbb Z$ such that $s_1 = 2k_1$ and $s_2 = 2k_2 + 1$. Thus $s_1 + s_2 = 2k_1 + 2k_2 + 1 = 2(k_1 + k_2) + 1$ so $f(s_1 + s_2) = -1$. We also find that $f(s_1) f(s_2) = 1\cdot -1 = -1$.
	\item If $s_1$ is odd and $s_2$ is even we may write that $f(s_1 + s_2) = f(s_2 + s_1)$ and that $f(s_1)f(s_2) = f(s_2)f(s_1)$ because both addition and multiplication are commutative. Now we see that we have reproduced our previous case and thus in this case the equality holds.
	\item If $s_1$ and $s_2$ are odd, then there exists $k_1\in\mathbb Z$ and $k_2\in\mathbb Z$ such that $2k_1 + 1 = s_1$ and $2k_2 + 1 = s_2$, thus $s_1 + s_2 = 2k_1 + 1 + 2k_2 + 1 = 2(k_1 + k_2 + 1)$ so $f(s_1 + s_2) = 1$. We also find that $f(s_1)f(s_2) = -1\cdot -1 = 1$.
\end{itemize}
Thus for all possible integers $s_1$ and $s_2$, we have $f(s_1 + s_2) = f(s_1)f(s_2)$.

This tells us that even integers are closed under addition. that odd integers added together always are even, and finally that an odd added to an even is odd.

\question{(c)} No, as $f(1\cdot 2) = f(2) = 1$ and $f(1)f(2) = -1 \cdot 1 = -1$.

\subsubsection{Question 12}

\question{(a)} No $f$ is not a function as $2/3 = 4/6$ and $f(2/3) = 2^23^3 \not= 2^43^6 = f(4/6)$.

\question{(b)} We may define $f(m/n) = 2^m3^n$ iff $m$ and $n$ are coprime.

\subsubsection{Question 19}

Let $a,b\in\mathbb R$ be given. Now let us investigate the derivative of $x^2 + ax + b$ with respect to $x$. Any student of calculus can tell you $\derivative{x^2+ax+b}{x} = 2x+a$. Now consider that when $x < \frac a2$

\subsubsection{Question 23}
\subsubsection{Question 28}
\subsubsection{Question 29}

\end{document}

### 2018-01-28 Astronomy/Homework/HW6.tex
init commit

\documentclass{article}
\input{../../definitions.tex}

\usepackage{ wasysym }
\usepackage{enumitem}

\title{Astronomy\\Homework 6}

\begin{document}
	\maketitle

	\section{Chapter 13}
	\question{1.} A large cloud of $H_2$ (molecular hydrogen) where stars are able to form. Protostars will form when gas in a molecular cloud clumps together due to gravity and this clump is the protostar, eventually it will get enough pressure to start fusion and become a star.

	\question {2.} Once the sun runs out of hydrogen to fuse it will start to fuse heavier elements like helium, this will give off more energy, causing the sun to expand into a red giant. Hydrogen shell fusion refers to hydrogen around the core of the sun being fused into helium. Helium fusion refers to fusing helium atoms into heavier elements. Double shell fusion refers to when helium is fused in an inner shell and hydrogen is fused around that in an outer shell.

	\question{3.} A high mass star burns through it's supply of hydrogen much faster (and brighter) then a low mass star. Thus high mass stars die quickly and low mass stars die slowly. A high mass star may go out in a spectacular super-nova, whereas low mass stars aren't quite as flashy.

	\question{4.} Iron when fused together creates an atom that has an atomic mass more then twice Iron's, thus some energy must be lost in the fusion.

	\question{5.} Let $r = 1 \text{ AU}$, thus $V = \frac43\pi r^3 = \frac43\pi\text{ AU}^3 \approx 4.189 \text{ AU}^3 \approx 1.402\cdot10^{34}\text{ m}^3$ where $V$ is the volume of a sphere with radius $1 \text{ AU}$. The density of this sphere, if it has mass $m = 1\text{ M}_{\astrosun}$, would then be $d = \frac mV \approx 1.418\cdot 10^{-4} \text{ kg}\text{ m}^{-3}$, which is less dense then water and the atmosphere at sea level on earth which are $1000 \text{ kg}\text{ m}^{-3}$ and $1\text{ kg}\text{ m}^{-3}$ respectively.

	\question{6.} Let us define $\circ$ to be the `fuse with' operator
	\begin{enumerate}[label=\alph*)]
		\item Magnesium
		\item Sulfur
		\item Nickel
	\end{enumerate}

\end{document}

### 2018-01-28 Combinatorics/CatalanNumbers/document.tex
init commit

\documentclass{macjourn}
\usepackage{latexsym,amssymb}
\usepackage{url, tikz}
\usepackage{array}
\usepackage{multicol}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{amsthm,amsmath}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{makecell}

\def\useLim{}
\let\union\cup
\let\inter\cap
\let\emptyset\varnothing
\let\bigunion\bigcup
\let\biginter\bigcap
\let\composed\circ
\let\cross\times
\def\And{\textit{ and }}
\def\Or{\textit{ or }}
\def\Return{\State\textbf{return}\par}
\newcommand{\setcomp}[1]{{#1}^{\mathsf{c}}}
\newcommand{\prodfrom}[3]{\prod\useLim_{#1}^{#2}\left( #3 \right)}
\newcommand{\sumfrom}[3]{\sum\useLim_{#1}^{#2} \left( {#3} \right)}
\newcommand{\unionfrom}[3]{\bigunion\useLim_{#1}^{#2} \left( {#3} \right)}
\newcommand{\interfrom}[3]{\biginter\useLim_{#1}^{#2} \left( {#3} \right)}
\newcommand{\interacross}[2]{\interfrom{#1}{}{#2}}
\newcommand{\unionacross}[2]{\unionfrom{#1}{}{#2}}
\newcommand{\sumacross}[2]{\sumfrom{#1}{}{#2}}
\newcommand{\prodacross}[2]{\prodfrom{#1}{}{#2}}
\newcommand{\set}[1]{\left\{ {#1} \right\}}
\newcommand{\setbuilder}[2]{\set{#1 | #2}}
\newcommand{\derivative}[2]{\frac{d}{d{#2}}\left( {#1} \right)}
\newcommand{\Exists}[2]{\exists_{#1}\left( {#2} \right)}
\newcommand{\All}[2]{\forall_{#1}\left( #2 \right)}
\newcommand{\abs}[1]{\left|{#1}\right|}
\newcommand{\cardinality}[1]{\left| #1 \right|}
\newcommand{\range}[1]{\textit{\textbf{Rng}}\left( #1 \right)}
\newcommand{\domain}[1]{\textit{\textbf{Dom}}\left( #1 \right)}
\newcommand{\pair}[2]{\left( #1 , #2 \right)}
\newcommand{\ooint}[2]{\left( #1 , #2 \right)}
\newcommand{\ocint}[2]{\left( #1 , #2 \right]}
\newcommand{\coint}[2]{\left[ #1 , #2 \right)}
\newcommand{\ccint}[2]{\left[ #1 , #2 \right]}
\newcommand{\ceil}[1]{\left\lceil #1 \right\rceil}
\newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
\def\true{\text{True}}
\def\false{\text{False}}

\raggedbottom

\newtheorem{theorem}{Theorem}[subsection]

\theoremstyle{definition}
\newtheorem{definition}{Definition}[subsection]

\begin{document}

	%%%%%%%%%%%%%
	% keep everything above this line as is
	%
	% you MUST have the file macjourn.cls in the same directory as this file!!!
	%%%%%%%%%%%%%

	\title{Beveridge Sequences}
	\author{Benji Altman, Nam Phung, Joseph Wriedt\\featuring Amanda Doan}

	\maketitle

	\section{Introduction to the sequence}
	Our Catalan group is defined as a sequence of $a_1, \ldots, a_n+1$ of non-negative integers such that $\sumfrom{i=1}{n+1}{2^{-a_i}} = 1$ and for all $2 \leq j \leq n+1$ the number
	$2^{a_j} \sumfrom{i=1}{j-1}{2^{-a_i}}$ is an integer.  We will call any sequence that fits these rules a beveridge sequence.

	\section{Examples}
	\subsection{Enumerations for $0 \leq n \leq 4$}
	We enumerate all possible sequences for $0\leq n\leq 4$. 
	\begin{center}
		\begin{tabular}{|c|c|c|}

			\hline $n$ & \textbf{Beveridge Sequences of length $n + 1$} & \textbf{Number of Sequences} \\ \hline
			0 & 0 & 1 \\ \hline
			1 & 1,1 & 1 \\ \hline
			2 & 1,2,2 \quad 2,1,1 & 2 \\ \hline
			3 & 1,2,3,3 \quad 1,3,3,2 \quad 2,2,2,2 \quad 2,3,3,1 \quad 3,3,2,1 & 5 \\ \hline
			4 & \makecell{3,3,2,2,2 \quad 4,4,3,2,1 \quad 3,4,4,2,1 \quad 2,4,4,3,1 \quad 2,3,4,4,1 \\ 1,4,4,3,2 \quad 1,3,4,4,2 \quad 1,2,4,4,3 \quad 1,2,3,4,4 \quad 3,3,3,3,1 \\ 1,3,3,3,3 \quad 2,3,3,2,2 \quad 2,2,3,3,2 \quad 2,2,2,3,3} & 14 \\ \hline
		\end{tabular}
	\end{center}

	\subsection{Visualization of the Sequence}
	In the course of studying this sequence, we have noticed that the values in a sequence correspond to the depth of the leaves in a plane binary tree with $2n+1$ vertices. A \emph{binary tree} is a tree data structure in the field of computer science in which each vertex has at most two children (referred to as the left child and right child. A \emph{plane binary tree} (or full binary tree) is a binary tree where every vertex has either \emph{zero} of \emph{two} children. We noted that the \emph{Beveridge} sequence offers a way to represent plane binary trees with $2n + 1$ vertices. \\

	Below is a visualization of the sequence as plane binary trees when $n = 3$, in which case there are 5 possible sequences.

	\begin{center}
		\begin{tikzpicture}[scale = .7]
		\begin{scope}
		\draw[fill] (-1,0) circle (3pt);
		\draw[fill] (0,1) circle (3pt);
		\draw[fill] (0,-1) circle (3pt);
		\draw[fill] (1,0) circle (3pt);
		\draw[fill] (1,-2) circle (3pt);
		\draw[fill] (2,-1) circle (3pt);
		\draw[fill] (3,-2) circle (3pt);
		\draw[thick] (-1,0) -- (0,1) -- (1,0) -- (2,-1) -- (3,-2);
		\draw[thick] (0,-1) -- (1,0);
		\draw[thick] (1,-2) -- (2,-1);
		\draw[fill] (6,0) circle (3pt);
		\draw[fill] (6,-2) circle (3pt);
		\draw[fill] (7,1) circle (3pt);
		\draw[fill] (7,-1) circle (3pt);
		\draw[fill] (8,0) circle (3pt);
		\draw[fill] (8,-2) circle (3pt);
		\draw[fill] (9,-1) circle (3pt);
		\draw[thick] (6,0) -- (7,1) -- (8,0) -- (9,-1);
		\draw[thick] (7,-1) -- (8,0);
		\draw[thick] (6,-2) -- (7,-1) -- (8,-2);
		\draw[fill] (13,-1) circle (3pt);
		\draw[fill] (14,0) circle (3pt);
		\draw[fill] (15,1) circle (3pt);
		\draw[fill] (14.5,-1) circle (3pt);
		\draw[fill] (15.5,-1) circle (3pt);
		\draw[fill] (16,0) circle (3pt);
		\draw[fill] (17,-1) circle (3pt);
		\draw[thick] (13,-1) -- (14,0) -- (15,1) -- (16,0) -- (17,-1);
		\draw[thick] (14.5,-1) -- (14,0);
		\draw[thick] (15.5,-1) -- (16,0);
		\draw[fill] (-1,-7) circle (3pt);
		\draw[fill] (0,-6) circle (3pt);
		\draw[fill] (1,-7) circle (3pt);
		\draw[fill] (1,-5) circle (3pt);
		\draw[fill] (2,-6) circle (3pt);
		\draw[fill] (2,-4) circle (3pt);
		\draw[fill] (3,-5) circle (3pt);
		\draw[thick] (-1,-7) -- (0,-6) -- (1,-5) -- (2,-4) -- (3,-5);
		\draw[thick] (1,-7) -- (0,-6);
		\draw[thick] (2,-6) -- (1,-5);
		\draw[fill] (6,-6) circle (3pt);
		\draw[fill] (7,-7) circle (3pt);
		\draw[fill] (7,-5) circle (3pt);
		\draw[fill] (8,-6) circle (3pt);
		\draw[fill] (8,-4) circle (3pt);
		\draw[fill] (9,-7) circle (3pt);
		\draw[fill] (9,-5) circle (3pt);
		\draw[thick] (6,-6) -- (7,-5) -- (8,-4) -- (9,-5);
		\draw[thick] (7,-5) -- (8,-6) -- (7,-7);
		\draw[thick] (8,-6) -- (9,-7);
		\end{scope}

		\end{tikzpicture}

	\end{center}

	Each binary tree above corresponds to one of the Beveridge sequence with $n = 3$, from left to right: $(1,2,3,3), (1,3,3,2), (2,2,2,2), (3,3,2,1), (2,3,3,1).$

	\section{Proof}
	\subsection{Groundwork}
	Let us start by laying down a few theorems and definitions that will be used throughout the rest of the paper. Some theorems will be left unproven as their proof will be left for a real analysis student to complete.

	%%% DEFINITION OF SEQUENCE, can be included if desired, however it's a bit much %%%
	%\begin{definition}{Sequence}
	%A sequence is defined as a function $S:[n]\to\mathbb R$. We will write $S_i = S(i)$ for any $i \le n$. Additionally we say that $\cardinality S = n$ and that $i$ is an index in $S$ if $i \in [n]$. We may also define a function by saying $S = (S_1, S_2, S_3, \ldots, S_n)$. An index $i$ is said to come later than $j$ if $i > j$ and thus $j$ would be said to come earlier.
	%\end{definition}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	\begin{definition}{Beveridge}
		A beveridge sequence is any sequence, $S$, of non-negative integers for which both the following two properties hold.
		\begin{enumerate}
			\item $\sumfrom{i=1}{\cardinality{S}}{2^{-S_i}} = 1$
			\item For all indices $j \in \set{2,3,\ldots,\cardinality{S}}$, $2^{S_j}\sumfrom{i=1}{j-1}{2^{-S_i}}$ is an integer.
		\end{enumerate}
	\end{definition}

	\begin{theorem} \label{increasing}
		For any sequence $S$ of real numbers \[\sumfrom{n=1}{k}{2^{-S_n}} > \sumfrom{n=1}{k-1}{2^{-S_n}}\]
		for any integer $k > 1$.
	\end{theorem}

	\begin{theorem}	\label{positive}
		If a sequence $S$ is beveridge and $\cardinality{S} > 1$ then all elements in $S$ are positive.
	\end{theorem}

	\begin{proof}
		Let $S$ be a beveridge sequence. Thus all elements in $S$ must be non-negative integers. Assume that $S$ contains some index $i$ for which $S_i$ is not positive. Zero is the only non-negative, non-positive integer, thus $S_i = 0$. We know that $2^{-0} = 1$, thus $S$ must only contain $0$ as otherwise \[\sumfrom{n=1}{\cardinality{S}}{2^{-S_n}} > 2^{-S_i} = 1\] which is impossible as $S$ is beveridge. Thus if $S$ contains a non-positive element, then that may be it's only element, making $\cardinality{S} = 1$. If $\cardinality{S} > 1$ then $S$ may only contain non-negative and non-zero integers, which is the same as only containing positive integers.
	\end{proof}

	\subsection{Midpoint}

	\begin{theorem}	\label{one}
		If a sequence $S$ is beveridge and $\cardinality{S} > 1$ then there exists exactly one index $p(S)$ such that \[\sumfrom{i=1}{p(S)}{2^{-S_i}} = \frac12\]
	\end{theorem}
	\begin{proof}
		Let $S$ be a beveridge sequence with $\cardinality{S} > 1$. Assume for the sake of contradiction that there does not exist an index $p$ such that $\sumfrom{i=1}{p}{2^{-S_i}} = \frac12$. Because of theorem \ref{increasing}, we know that there is some index, $j$ such that \[\sumfrom{i=1}{j}{2^{-S_i}} > \frac12 > \sumfrom{i=1}{j-1}{2^{-S_i}}\] Because $2^{S_j}$ must be positive regardless of $j$ or $S$, we may multiply it through and our inequality will hold, giving us
		\begin{align*}
			2^{S_j}\sumfrom{i=1}{j}{2^{-S_i}}& \\
			= 1 + &2^{S_j}\sumfrom{i=1}{j-1}{2^{-S_i}}
			> 2^{S_j}\frac12 
			> 2^{S_j}\sumfrom{i=1}{j-1}{2^{-S_i}}
		\end{align*} 
		At this point we must observe that $j > 1$. To prove this we will assume that $j = 1$ (note that $j < 1$ makes no sense as it would be a sum of $0$ things, thus resulting in a result of $0$ which is less then $\frac12$), and we find
		\[
		\sumfrom{i=1}{j}{2^{-S_i}} = \sumfrom{i=1}{1}{2^{-S_i}} = 2^{-S_1} > \frac12
		\]
		and the only non-negative integer value for $S_1$ that satisfies this is $S_1 = 0$, which by theorem \ref{positive} means that $\cardinality{S} = 1$, which is a contradiction as we defined $S$ to have $\cardinality{S} > 1$. We thus know that $j > 1$, and because of that we know that $2^{S_j}\sumfrom{i=1}{j-1}{2^{-S_i}}$ is an integer. Now to finally finish this off we know that for any integer $k$ there are no integers in the interval $\ooint k{k+1}$, thus we know that $2^{S_j}\frac12 = 2^{S_j-1}$ is not an integer. As $S_j$ must be an integer this means that $S_j - 1 < 0$ or alternatively $S_j < 1$ which would mean that $S_j$ is not positive, however by theorem \ref{positive} we know that $S_j$ is positive and thus we have our contradiction.

		Finally we notice that there is only one possible point for any beveridge sequence $p$ via theorem \ref{increasing}, any index before $p$ must yield a sum less than $\frac12$ and any index after $p$ must yield a sum greater than $\frac12$.\footnote{When I say sum I really mean a sum in the form $\sumfrom{i=0}{k}{2^{-S_i}}$, where $k$ is some index in $S$.}

		Now we have shown that for all beveridge sequences $S$ of length greater than one, there exists a unique index $k$, such that $\sumfrom{i=1}{k}{2^{-S_i}} = \frac12$. Thus we may define a function $p(S) = k$ where \[\sumfrom{i=1}{k}{2^{-S_i}} = \frac12\]
	\end{proof}

	\begin{theorem}\label{edge}
		For any beveridge sequence $S$ with $\cardinality S > 1$, $p(S) < \cardinality S$.
	\end{theorem}

	\begin{proof}
		$S$ is beveridge thus, $\sumfrom{i=1}{\cardinality S}{2^{-S_i}} = 1 > \frac12$, and by theorem    \ref{increasing} we know that $p < \cardinality S$.
	\end{proof}

	\subsection{Decomposition}

	In this section we will show that using the index $p(S)$ we may break any beveridge sequence $S$ into two smaller beveridge sequences, in exactly one way, as long as $\cardinality S \not= 1$.

	\begin{theorem} \label{decompose}
		For any beveridge sequence $S$, of length greater than $1$, there exists two sequences
		\begin{align*}
			L(S) &= (S_1 - 1, S_2 - 1, \ldots, S_{p(S)} - 1) \\
			R(S) &= (S_{p(S)+1} - 1, S_{p(S)+2} - 1, \ldots, S_{\cardinality S} - 1)
		\end{align*}
		both of which are beveridge.
	\end{theorem}

	\begin{proof}
		Let $S$ be a beveridge sequence with $\cardinality S > 1$. First notice that $\cardinality{L(S)} \ge 1$ and that $\cardinality{R(S)} \ge 1$. $L(S)$ always contains $S_{p(S)}-1$ as an element, thus must contain at least one element. By theorem \ref{edge} we know that $p(S) + 1 < \cardinality S$, thus $S_{p(s)+1}-1$ is always in $R(S)$, so $R(S)$ may also not be empty. Second we would also like to notice that $L(S)$ and $R(S)$ contain only non-negative integers, as $S$ contains only positive integers (see theorem \ref{positive}).

		Now that we have shown that $L(S)$ and $R(S)$ are non-empty sequences of non-negative integers, we can start to show that they fit the requirements to be beveridge, this is simply a fair amount of fairly simple manipulation.

		First we want to show that $\sumfrom{i=1}{\cardinality{L(S)}}{2^{-L(S)_i}} = 1$.
		\begin{align*}
			\sumfrom{i=1}{\cardinality{L(S)}}{2^{-L(S)_i}} 
			&= \sumfrom{i=1}{p}{2^{-(S_i-1)}}\\
			&= \sumfrom{i=1}{p}{2^{-S_i+1}} \\
			&= 2\sumfrom{i=1}{p}{2^{-S_i}}
			= 2\cdot\frac12
			= 1
		\end{align*}

		Next we wish to show that $\sumfrom{i=1}{\cardinality{R(S)}}{2^{-R(S)_i}} = 1$.
		\begin{align*}
			\sumfrom{i=1}{\cardinality{R(S)}}{2^{-R(S)_i}}
			&= \sumfrom{i=p+1}{\cardinality{S}}{2^{-(S_i-1)}} \\
			&= \sumfrom{i=p+1}{\cardinality S}{2^{-S_i+1}} \\
			&= 2\sumfrom{i=p+1}{\cardinality S}{2^{-S_i}} \\
			&= 2\left[\sumfrom{i=1}{\cardinality S}{2^{-S_i}} - \sumfrom{i=1}{p}{2^{-S_i}}\right]
			= 2\left[1-\frac12\right]
			= 1
		\end{align*}

		Next we will show that for any $j \in \set{2, 3, \ldots, \cardinality{L(S)}}$, $\sumfrom{i=1}{j-1}{2^{L(S)_j-L(S)_i}}$ is an integer. Let us start by choosing $j \in \set{2, 3, \ldots, \cardinality{L(S)}}$.
		\begin{align*}
			\sumfrom{i=1}{j-1}{2^{L(S)_j - L(S)_i}}
			&= \sumfrom{i=1}{j-1}{2^{(S_j - 1) - (S_i - 1)}} \\
			&= \sumfrom{i=1}{j-1}{2^{S_j - S_i}} \in \mathbb Z
		\end{align*}
		We know this is an integer as $S$ is beveridge, thus we have shown that $L(S)$ is beveridge.

		Finally we will show that for any $j \in \set{2, 3, \ldots, \cardinality{R(S)}}$, $\sumfrom{i=1}{j-1}{2^{R(S)_j-R(S)_i}}$ is an integer.
		\begin{align*}
			\sumfrom{i=1}{j-1}{2^{R(S)_j-R(S)_i}}
			&= \sumfrom{i=p+1}{j-1 + p}{2^{(S_j - 1) - (S_i - 1)}} \\
			&= \sumfrom{i=p + 1}{j-1 + p}{2^{S_j - S_i}}\\
			&= \sumfrom{i=1}{j-1+p}{2^{S_j-S_i}} - \sumfrom{i=1}{p}{2^{S_j-S_i}}\\
			&= \sumfrom{i=1}{j-1+p}{2^{S_j - S_i}} - 2^{S_j}\cdot\frac12
		\end{align*}
		Now we notice that $\sumfrom{i=1}{j-1+p}{2^{S_j-S_i}}$ is an integer as $S$ is beveridge and $j\not= 1$. Additionally we know that $S_j$ is positive via theorem \ref{positive} and thus $S_j-1 \ge 0$. Also notice that $2^{S_j}\cdot\frac12 = 2^{S_j - 1}$, and as $S_j-1$ is non-negative, $2^{S_j-1}$ must be an integer. Finally the integers are closed on addition so we know $\sumfrom{i=1}{j-1+p}{2^{S_j - S_i}} - 2^{S_j}\cdot\frac12$ is an integer. Now we have shown that $R(S)$ is beveridge.
	\end{proof}

	%Consider the Beveridge Sequence $a_1, a_2, \ldots , a_{n}$, where $n > 1$. Theorem \ref{one} has it that there exists some index $k$, for whichdd
	%\[dd
	%\sum_{i=1}^k 2^{-a_i} = \frac{1}{2}.dd
	%\]dd
	%We will prove that this index breaks the sequence into two subsequences such that if we subtract one from every element of each subsequence, we get a valid Beveridge Sequence. Let the sequence $L = (a_1 - 1, a_2 - 2, \ldots, a_p - 1)$ and the sequence $R = (a_{p+1} - 1, a_{p+2} - 1, \ldots, a_{n} - 1)$. Now we wish to show that both $L$ and $R$ are beveridge.dd
	%dd
	%\begin{enumerate}dd
	%\item[(1)] First, we need to prove thatdd
	%\[dd
	%\sum_{i=1}^k 2^{-(a_i-1)} = 1dd
	%\]dd
	%anddd
	%\[dd
	%\forall j: 2 \leq j \leq k, \text{ we have } 2^{a_j-1} \sum_{i=1}^{j-1} 2^{-(a_i-1)} \in \mathbb{Z}.dd
	%\]dd
	%dd
	%\begin{itemize}dd
	%\item We have:dd
	%\begin{align*}dd
	%\sum_{i=1}^k 2^{-(a_i-1)} &= \sum_{i=1}^k \frac{1}{2^{a_i -1}} \\dd
	%&= \sum_{i=1}^k \frac{1}{2^{a_i}\cdot 2^{-1}} \\dd
	%&= \sum_{i=1}^k \frac{1}{2^{a_i}} \cdot 2 \\dd
	%&= \sum_{i=1}^k 2^{-a_i} \cdot 2  \\dd
	%&= \frac{1}{2} \cdot 2 = 1.dd
	%\end{align*}dd
	%\item Now we prove the second part, i.e. for all $j$, where $2\leq j \leq k+1$ such that dd
	%\[dd
	%2^{a_j} \sum_{i=1}^{j-1} 2^{-(a_i-1)} \in \mathbb{Z}.dd
	%\]dd
	%dd
	%We have:dd
	%\begin{align*}dd
	%2^{a_j-1} \sum_{i=1}^{j-1} 2^{-(a_i-1)} &= \frac{2^{a_j}}{2} \sum_{i=1}^{j-1} \frac{1}{2^{a_i -1}} \\dd
	%&= \frac{2^{a_j}}{2} \sum_{i=1}^{j-1}\frac{1}{2^{a_i}} \cdot 2 \\dd
	%& = 2^{a_j} \sum_{i=1}^{j-1} \frac{1}{2^{a_i}}.dd
	%\end{align*}dd
	%The second property of the Beveridge Sequence has it that this value is an integer.dd
	%\end{itemize}dd
	%dd
	%Thus, we have proved that the part on the left of the "dividing" index $k$ is a valid Beveridge Sequence.dd
	%dd
	%\item[(2)] Similarly, we can prove that the part on the right of the "dividing" index $k$ is also a valid Beveridge Sequence. In order to do that, we will prove that dd
	%\[dd
	%\sum_{i=k+1}^{n+1} 2^{-(a_i-1)} = 1dd
	%\]dd
	%and dd
	%\[dd
	%\forall j: k+2 \leq j \leq n+1, \text{ we have } 2^{a_j-1} \sum_{i=1}^{j-1} 2^{-(a_i-1)} \in \mathbb{Z}.dd
	%\]dd
	%dd
	%\begin{itemize}dd
	%\item We have:dd
	%\begin{align*}dd
	%\sum_{i=k+1}^{n+1} 2^{-(a_i-1)} &= \sum_{i=k+1}^{n+1} \frac{1}{2^{a_i}} \frac{1}{2^{-1}} \\dd
	%&= \sum_{i=k+1}^{n+1} \frac{1}{2^{a_i}} \cdot 2 \\dd
	%&= \frac{1}{2} \cdot 2 = 1.dd
	%\end{align*}dd
	%dd
	%\item We now prove the second part, i.e. for all $j$, where $2 \leq j \leq k+1$ such that dd
	%\[dd
	%2^{a_j-1} \sum_{i=1}^{j-1} 2^{-(a_i-1)} \in \mathbb{Z}.dd
	%\]dd
	%dd
	%We have:dd
	%\begin{align*}dd
	%2^{a_j-1} \sum_{i=1}^{j-1} 2^{-(a_i-1)} &= \sum_{i=1}^{j-1} 2^{a_j-a_i} \\dd
	%&= \sum_{i=k+1}^{k+j-1} 2^{a_j-a_i} \\dd
	%&= 2^{a_j} \sum_{i=1}^{k+j-1} 2^{-a_i} - 2^{a_j}\sum_{i=1}^k \\dd
	%&= 2^{a_j} \sum_{i=1}^{k+i-1} - 2^{a_j-1} \in \mathbb{Z}.dd
	%\end{align*}dd
	%\end{itemize}dd
	%\end{enumerate}dd
	%Thus, we have proved that the index $k$ divides the sequence into two subsequences that satisfy the conditions.

	\subsection{Composition}
	In the last section we showed that one could decompose any beveridge sequence $S$ of length greater than $1$ into two smaller beveridge sequences. We now want to show that if we take two beveridge sequences $L$ and $R$ we can compose them to construct a larger beveridge sequence. Let us start by defining a composition function \[C(L,R) = (L_1 + 1, L_2 + 1, \ldots, L_{\cardinality L} + 1,\quad R_1 + 1, R_2 + 1, \ldots, R_{\cardinality R} + 1)\]

	\begin{theorem} \label{compose}
		If $L$ and $R$ and beveridge sequences then $C(L,R)$ is also beveridge.
	\end{theorem}

	\begin{proof}
		Let $L$ and $R$ be beveridge sequences. First let us notice that $C(L,R)$ is a sequence of positive integers, as $L$ and $R$ are both sequences of non-negative integers.

		Next we would like to show that $\sumfrom{i=1}{\cardinality{C(L,R)}}{2^{-C(L,R)_i}}=1$.
		\begin{align*}
			\sumfrom{i=1}{\cardinality{C(L,R)}}{2^{-C(L,R)_i}}
			&= \sumfrom{i=1}{\cardinality{L}}{2^{-(L_i + 1)}} + \sumfrom{i=1}{\cardinality{R}}{2^{-(R_i+1)}} \\
			&= \frac12\left[\sumfrom{i=1}{\cardinality L}{2^{-L_i}} + \sumfrom{i=1}{\cardinality{R}}{2^{-R_i}}\right] \\
			&= \frac12\left[1 + 1\right]
			= 1
		\end{align*}

		Finally we would like to show that for any $j \in \set{2, 3, \ldots, \cardinality{C(L,R)}}$, $\sumfrom{i=1}{j-1}{2^{C(L,R)_j-C(L,R)_i}}$ is an integer. To do this we must do a proof by cases. Let us consider the three possible cases:
		\begin{enumerate}
			\item$j < \cardinality L + 1$
			\item$j = \cardinality L + 1$
			\item$j > \cardinality L + 1$
		\end{enumerate}

		First if $j < \cardinality L + 1$, this is the same as saying $j \in \set{2, 3, \ldots, \cardinality L}$.
		First we should notice that
		\[
		\sumfrom{i=1}{j-1}{2^{C(L,R)_j-C(L,R)_i}} = \sumfrom{i=1}{j-1}{2^{(L_j+1)-(L_i+1)}}
		\]
		as we are never referencing any index in $C(L,R)$ after the $j^\text{th}$ index which we know is at most $\cardinality L$. Now we simplify and find
		\[
		\sumfrom{i=1}{j-1}{2^{(L_j+1)-(L_i+1)}} = \sumfrom{i=1}{j-1}{2^{L_j-L_i}} \in \mathbb Z
		\]
		as $L$ is beveridge.

		Second if $j = \cardinality L + 1$, this means that we want to show that $\sumfrom{i=1}{\cardinality L}{2^{C(L,R)_{\cardinality L}-C(L,R)_i}}$ is an integer. Let us start by rewriting this as $2^{C(L,R)_{\cardinality L + 1}}\sumfrom{i=1}{\cardinality L}{2^{-C(L,R)_i}}$. Now we notice that $\sumfrom{i=1}{\cardinality L}{2^{-C(L,R)_i}} = \sumfrom{i=1}{\cardinality L}{2^{-(L_i + 1)}}$. Well we now show that
		\[\sumfrom{i=1}{\cardinality L}{2^{-(L_i + 1)}} = \frac12\sumfrom{i=1}{\cardinality L}{2^{-L_i}} = \frac12\cdot 1 = \frac12\]
		We now look at the $2^{C(L,R)_{\cardinality L + 1}}$ part. Notice that $C(L,R)_{\cardinality L + 1} = R_1 + 1$, thus $2^{C(L,R)_{\cardinality L + 1}} = 2^{R_1 + 1}$. Now we may put the parts together and we find that
		\[\sumfrom{i=1}{\cardinality L}{2^{C(L,R)_{\cardinality L}-C(L,R)_i}} = 2^{R_1 + 1}\cdot\frac12 - 2^{R_1}\]
		which is an integer as $R$ is composed of non-negative integers.

		Finally if $j > \cardinality L + 1$ we may do the following manipulation.
		\begin{align*}
			\sumfrom{i=1}{j-1}{2^{C(L,R)_j-C(L,R)_i}}
			&= 2^{C(L,R)_j}\sumfrom{i=1}{j-1}{2^{-C(L,R)_i}} \\
			&= 2^{R_{j-\cardinality L}+1}\left[ \sumfrom{i=1}{\cardinality L}{2^{-(L_i + 1)}} + \sumfrom{i=1}{j-1-\cardinality{L}}{2^{-(R_i + 1)}} \right] \\
			&= 2^{R_{j-\cardinality L} + 1}\cdot\frac12\left[1 +  \sumfrom{i=1}{j-1-\cardinality{L}}{2^{-R_i}}\right] \\
			&= 2^{R_{j-\cardinality L}} + 2^{R_{j-\cardinality L}}\sumfrom{i=1}{j-\cardinality{L}-1}{2^{-R_i}}
		\end{align*}
		Now $j-\cardinality L$ must be a member of $\set{2,3,\ldots,\cardinality R}$ and so we know that $2^{R_{j-\cardinality L}}\sumfrom{i=1}{j-\cardinality{L}-1}{2^{-R_i}}$ is an integer as $R$ is beveridge, thus we have the sum of two integers, and that must be an integer.

		Now we have demonstrated that for any pair of beveridge sequences $L$ and $R$, $C(L,R)$ is beveridge.
	\end{proof}

	We now must demonstrate that if we have two separate pairs of beveridge sequences we can't possibly compose both pairs respectively and get the same sequence

	\begin{theorem} \label{unique}
		If $A$, $B$, $\bar A$ and $\bar B$ are beveridge sequences such that $A \not= \bar A$ or $B \not= \bar B$  then $C(A,B) \not= C(\bar A, \bar B)$.
	\end{theorem}
	\begin{proof}
		This will be a proof by contra-positive. First we state
		\[\sumfrom{i=1}{\cardinality L}{2^{-C(L,R)_i}} = \sumfrom{i=1}{\cardinality L}{2^{-L_i - 1}} = \sumfrom{i=1}{\cardinality L}{2^{-L_i}}\cdot \frac 12 = \frac12\]
		and we find that the sum across the first $\cardinality L$ terms of $2^{-C(L,R)}$ is $\frac12$, thus $L = L(C(L,R))$, and thus there is exactly one way to construct $L$ from $C(L,R)$ and further there will be exactly one way to construct $R$. Thus we know that compositions are unique.
	\end{proof}

	\section{Complete induction}
	Here we will finally prove that there are $C_n$ beveridge sequences of length $n+1$, where $C_n$ is the $n^\text{th}$ Catalan number defined as \begin{align*}C_0& = 1 \\ C_n& = \sum_{i=0}^{n-1}C_i\cdot C_{n-i-1}\end{align*}

	\begin{proof}
		First we wish to show that there is exactly one beveridge sequence of length $1$. If a sequence is beveridge and of length one then we know that $\sumfrom{i=1}1{2^{-A_i}} = 1$, where $A$ is our beveridge sequence. We may rewrite this without the sigma as $2^{-A_1} = 1$. There is only one possible non-negative integer value for $A_1$, and this is $0$. Thus the sequence $(0)$ is the only sequence of length $1$ that is beveridge.\footnote{Technically I haven't shown that $(0)$ is beveridge, however it is rather trivial.} Now we have shown a base case

		Now choose $k \in \mathbb N$, let us assume that for all non-negative integers $n < k$, the number of beveridge sequences of length $n + 1$ is $C_n$. Now we wish to show that there are exactly $C_{k}$ beveridge sequences of length $k + 1$. First by theorem \ref{decompose} we know that all beveridge sequences of length $k+ 1$ can be decomposed into two shorter beveridge sequences. Next by theorem \ref{compose} and \ref{unique} we know that each composition of two beveridge sequences produces a unique beveridge sequence with length $l+r$ where $l$ and $r$ are the lengths of the two sequences being composed respectively. Thus for every beveridge sequence of length $t<k + 1$ (of which there are $C_{t-1}$) we may compose it with a beveridge sequence of length $k + 1 - t$ (of which there are $C_{k-t}$) to get a unique beveridge sequence of length $k + 1$. Thus we find that there are $\sumfrom{t=1}{k}{C_{t-1}\cdot C_{k-t}} = \sumfrom{i=0}{k-1}{C_{i}\cdot C_{k-i-1}}$ beveridge sequences of length $k + 1$ that can be composed of smaller beveridge sequences, this is of course all of them as we have already stated.

		Now by the principle of complete induction we know there are $C_n$ beveridge sequences of length $n + 1$.
	\end{proof}

	%\section{Weak Induction}
	%Assume that the there are $c_n$ beveridge sequences of length $n+1$.  That being said $c_0=1$ because there are only one sequence of length 1, $0$.  Now we prove that there are $c_{k-1}$ sequences of length $k$.  We can split these sequences, of length $k$, into two sub-sequences that are still sequences (proof from above).  We define these sub-sequences as 
	%$$
	%a_1, \ldots, a_j\quad a_{j+1}, \ldots, a_k$$
	%where the lengths of the subsections are $j$ and $k-j$ respectively, where $1\le j \le k$.  Using our assumption about beveridge sequences, there are $c_{j-1}$ sequences of length $j$ and $c_{k-j-1}$ of length $n-j$ where $1\le j \le k$.  The total number of possible sequences for length $k$ are $c_{j-1}\cdot c_{k-j-1}$ where $1\le j \le k-1$.
	%
	%\begin{eqnarray*}
	%\sum_{j=1}^{k-1} c_j \cdot c_{k-j-1} \\
	%\sum_{i=0}^{k-2} c_i \cdot c_{k-i-2}
	%\end{eqnarray*}
	%Notice that the summation is very similar to the Catalan recurrence:
	%\begin{eqnarray*}
	%C_0 &=& 1 \\
	%C_{n+1} &=& \sum_{i=0}^n C_i C_{n-i-1} \mbox{ for } n \geq 0.
	%\end{eqnarray*}
	%Therefore there are $c_{k-1}$ beveridge sequences for length $k$.
	%
	%

\end{document}

### 2018-01-28 Combinatorics/Exam2/document.tex
init commit

\documentclass{article}
\input{../../definitions}

\title{Combinatorics E
	xam 2}
\renewcommand{\thesubsection}{\thesection.\alph{subsection}}
\newtheorem{theorem}{Theorem}[section]

\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

\begin{document}
	\maketitle
	\section{}
	\subsection{What is the OGF for integer partitions where each part occurs an even number of times?}
	Any integer partition, $p$ on $n$ may be written as a sequence $(a_1, a_2, a_3, \ldots, a_k)$. If $p$ has the property that every part in it appears an even number of times then we may order it's sequence representation such that $a_i = a_{i+k/2}$ for all $i\in\cannonicalSet{k/2}$. Now look at the partition composed of $(a_1, a_2, a_3, \ldots, a_{k/2})$ and we find that this is a partition on $\frac n2$. Additionally if $(a_1, a_2, a_3, \ldots, a_k)$ is a partition on $\frac n2$ then $(a_1, a_2, a_3, \ldots, a_k, a_1, a_2, a_3, \ldots, a_k)$ will be a partition with an even number of each part on $n$. Now we have constructed a bijection from partitions on $n$ to partitions on $2n$ with an even number of each part. We know that the number of partitions on $n$ has an OGF of $$f(x) = \prodacross{i\in\mathbb N}{\frac1{1-x^i}}$$ thus the number of partitions on $2n$ with only even parts would have the same OGF and the number of partitions on $n$ with only even parts would have an OGF of $$A(x) = f(x^2) = \prodacross{i\in\mathbb N}{\frac{1}{1-x^{2i}}}$$

	\subsection{What is the OGF for integer partitions where each part is even?}
	We know the OGF for integer partitions on $n$ using only parts of size $k$ is $\frac1{1-x^k}$ as it is only doable one way and only if $n$ is a multiple of $k$. Thus to get the number of partitions on $n$ using only parts that are even in size we get $$B(x) = \frac1{1-x^2} + \frac1{1-x^4} + \frac1{1-x^6} \ldots = \prodacross{i \in\mathbb N}{\frac1{1-x^{2i}}}$$

	\subsection{What conclusions may be drawn?}
	Notice that $A(x) = B(x)$ where $A(x)$ is the number of partitions on $n$ where each part occurs an even number of times and $B(x)$ is the number of partitions on $n$ where each part is even. This means that there are the same number of partitions on $n$ that are composed solely of even parts as there are if each part occurs an even number of times.

	\section{}
	\begin{definition}{Words}
		are formed using the letters $A, B, C$ and digits $1,2,3,4$. Set $a_0= 0$ and for $n\ge1$, let $a_n$ be the number of words made up of $n$ of these symbols in which there are not two letters in succession. (Two numbers in succession are okay.)
	\end{definition}

	\subsection{find $a_1$ and $a_2$}
	For a word of length $1$ we simply may choose any valid symbol to be the first character and there are $7$ of them and then we are done, thus $a_1 = 7$.

	For a word of length $2$ we simply find all words of length two where we allow for any string of symbols to be valid and the remove the bad ones. There are $7^2$ strings on our $7$ symbols and $3^2$ strings containing two letters. Thus we have $a_2 = 7^2-3^2=40$.

	\subsection{Show that $a_n = 4a_{n-1} + 12a_{n-2}$ for $n\ge3$}
	For any word with length $n > 2$ we may either end with a number or letter.

	If it ends in a number then it may be composed by taking a word of length $n-1$ and appending a number. There are $4$ numbers that may be appended $a_{n-1}$ words of length $n-1$ thus we have $4a_{n-1}$ words of length $n$ that end in a number.

	If the word ends with a letter then the character before it must be a number giving use a $4$ numbers followed by $3$ letters that are possible and then before the number we may have any word of length $n-2$, which there are $a_{n-2}$ of. Thus we have $3\cdot4\cdot a_{n-2}$ words of length $n$ that end with a letter.

	Now we may put this together and we find $a_n = 4a_{n-1}+12a_{n-2}$.

	\subsection{Show that the OGF, $A(x) = \frac{7x+12x^2}{1-4x-12x^2}$}

	\def\tail{a_2x^2 + a_1x+a_0}

	\begin{align*}
		a_0 &= 0 \\ a_1 &= 7 \\ a_2 &= 40 \\
		A(x) &= \sumfrom{n=0}{\infty}{a_nx^n} \\
		&= \sumfrom{n=3}{\infty}{a_nx^n} + \tail \\
		&= \sumfrom{n=3}{\infty}{(4a_{n-1}+12a_{n-2})x^n} + \tail \\
		&= \sumfrom{n=3}{\infty}{4a_{n-1}x^n + 12a_{n-2}x^n} + \tail \\
		&= \sumfrom{n=3}{\infty}{4a_{n-1}x^n}+\sumfrom{n=3}{\infty}{12a_{n-2}x^n} + \tail \\
		&= 4x\sumfrom{n=2}{\infty}{a_nx^n} + 12x^2\sumfrom{n=1}{\infty}{a_nx^n} + \tail \\
		&= 4x(A(x) - a_1x - a_0) + 12x^2(A(x) - a_0) + \tail \\
		&= 4xA(x) - 4a_1x^2 - 4a_0x + 12x^2A(x) - 12a_0x^2 + \tail \\
		&= A(x)(4x+12x^2) + (-4a_1-12a_0+a_2)x^2+(-4a_0+a_1)x+a_0 \\
		&= A(x)(4x + 12x^2) + (-4(7)-12(0)+40)x^2+(-4(0)+7)x+0 \\
		&= A(x)(4x + 12x^2) + 12x^2 + 7x \\
		A(x) - A(x)(4x+12x^2) &= 12x^2 + 7x\\
		A(x)(-4x-12x^2+1) &= 12x^2+7x \\
		A(x) &= \frac{12x^2+7x}{-4x-12x^2+1} = \frac{7x+12x^2}{1-4x-12x^2}
	\end{align*}

	\subsection{Determine a simple cosed formula for $a_n$}

	\begin{align*}
		A(x) + 1 &= \frac{7x+12x^2 + 1 -4x-12x^2}{1-4x-12x^2} \\
		&= \frac{1+3x}{(-6x+1)(2x+1)} \\
		&= \frac a{-6x+1} + \frac b{2x+1} \\
		&= \frac {a(2x+1) + b(-6x+1)}{(-6x+1)(2x+1)}
	\end{align*}

	Thus $2a - 6b = 3$ and $a + b = 1$. Mathematica then is nice enough to tell us that $a = \frac98$ and $b = -\frac18$. Now armed with that we find

	\begin{align*}
		A(x) + 1 &= \frac{9/8}{-6x+1} + \frac{-1/8}{2x+1} \\
		&= \frac98\sumfrom{n=0}{\infty}{(6x)^n} - \frac18\sumfrom{n=0}{\infty}{(-2x)^n} \\
		&= \sumfrom{n=0}{\infty}{\left(\frac98(6)^n-\frac18(-2)^n\right)x^n}
	\end{align*}

	We only need find $a_n$ for $n \ge 1$ thus we don't care that we added $1$ to $A(x)$ as that would only effect the $x^0$ term. Thus $$a_n = \frac98(6)^n-\frac18(-2)^n$$ for all $n\ge 1$.

	\section{Vandermonde's formula}
	\begin{definition}{Vandermonde's formula}
		$$\sumfrom{j=0}{k}{\binom{m}{j}\binom{n}{k-j}}=\binom{m+n}{k}$$
	\end{definition}
	\subsection{Show that both sides of Vandermonde's formula are $0$ if $k > m + n$}

	Let $k > m + n$.

	First $\binom{m+n}k = 0$ as $k > m+n$.

	Now for all $j \in \ccint0m$ we find that $\binom n{k-j} = 0$ as $m \ge j$ thus $k - j \ge k - m > n$. For all $j > m$ we find that $\binom mj=0$ and thus for all $j \in \ccint0k$, $\binom mj\binom n{k-j} = 0$ and by extension $\sumfrom{n=0}{j}{\binom mj\binom n{k-j}} = 0$.

	\subsection{Give a combinatorial proof for Vandermode's formula}

	You have $n$ blue marbles, numbered $1$ through $n$, and $m$ red marbles, numbered $1$ through $m$, all in a bin. You want to take out $k$ marbles. Well you have a set of $n+m$ unique objects and you wish to choose $k$ of them, then this must simply be $\binom{n+m}k$.

	You also however could break this up into cases. You could pick $j$ of the red marbles, and thus would have picked $k-j$ of the blue marbles, where $0 \le j \le k$ (as you can not pick less than $0$ red marbles or more than $k$ red marbles and result in $k$ marbles at the end). Thus we would find that you have $\binom mj$ ways to pick red marbles and $\binom n{k-j}$ ways to pick blue marbles for a fixed $j$. We thus must take the sum for all possible $j$ and we find you have $\sumfrom{n=0}{k}{\binom mj\binom n{k-j}}$ ways to do this.

	Thus Vandermonde's formula must be true as we found that the right hand side and left hand side are both counting the same thing.

	\subsection{Prove using OGF}

	Let our task $\mathcal{H}$ be choosing some number of elements from a set of cardinality $m+n$. We obviously have $h_k = \binom {m+n}k$ ways of doing this, and thus a generating function $$H(x) = \sumfrom{k=0}{\infty}{h_kx^k} = \sumfrom{k=0}{\infty}{\binom{m+n}kx^k}$$

	We may also split $\mathcal H$ into two tasks by first doing task $\mathcal F$ (choosing some number of elements from a set of size $m$) and $\mathcal G$ (choosing some number of elements from a set of size $n$). There are $f_k = \binom nk$ ways to do task $\mathcal F$, where $k$ is the number of elements being chosen.  There are $g_k = \binom mk$ ways to do task $\mathcal G$, where $k$ is the number of elements being chosen. Thus $\mathcal F$ has OGF $$\sumfrom{k=0}{\infty}{\binom nkx^k}$$ and $\mathcal G$ has OGF $$\sumfrom{k=0}{\infty}{\binom mkx^k}$$ By the product formula for OGF we know that 
	\begin{align*}
		H(x) &= F(x)G(x) \\
		\sumfrom{k=0}{\infty}{\binom{m+n}kx^k}	&= \sumfrom{k=0}{\infty}{\sumfrom{j=0}{k}{\binom mk\binom n{k-j}}x^k}
	\end{align*}
	Thus Vandermonde's theorem must be true.

\section{Find the exponential generating function for the number of partitions of $\cannonicalSet{n}$ into an even number of odd-sized blocks. (You can only use odd-sized blocks. So the number of even-sized blocks is zero.}

%LOOK in notebook and bestarium generandi and use composition

First let us have a zero-indexed sequence $a = (0,1,0,1,0,1,\ldots)$, which has EGF $A(x) = \sinh x$. This sequence can be thought of as 'accepting' any set with odd cardinality and 'rejecting' a set of even cardinality.

Second let us have another zero-indexed sequence $b = (1,0,1,0,1,0,\ldots)$, which has EGF $B(x) = \cosh x$. This sequence can be thought of as 'accepting' any set with even cardinality and 'rejecting' any other finite set.

Now we can use the composition rule for EGF and find $H(x) = B(A(x)) = \cosh(\sinh x)$ and it would represent splitting a set into any number of blocks, if a block is even in size then the configuration is 'rejected' and otherwise do nothing to it. Then on the set of blocks reject it if it is not an even sized set and accept if it is even sized.

\[\cosh(\sinh x)\]

\section{Let $r_n$ be the number of ways to partition $\cannonicalSet{n}$ without any singleton blocks}
\subsection{Give combinatorial proof that $r_n=\sumfrom{k=0}{n-2}{\binom{n-1}kr_k}$}

The element $n$ will be in a block with some number of other elements. Let $k$ be the number of elements not in the block with $n$. Thus $k\in\ccint0{n-2}$ as $n$ must be joined by at least $1$ other element. Now choose the $k$ elements out of $\cannonicalSet n\setminus \set n = \cannonicalSet{n-1}$ to not be in a block with $n$ (n must be in it's own block, and thus is excluded from this), and partition them such that there are no singleton blocks. There are $\binom{n-1}k$ ways to make the choice and $r_k$ ways to partition them, thus we have $\binom{n-1}kr_k$ ways to partition when there are exactly $k$ elements not in the block with $n$.

Now sum across all possible values for $k$ and find $r_n=\sumfrom{k=0}{n-2}{\binom{n-1}{k}r_k}$

\subsection{Prove that $r_{n+1}$ counts the number of partitions on $\cannonicalSet{n}$ with at least $1$ singleton block.}
Let $t=n+1$. Now to partition $\cannonicalSet{n}$ such that it has some number of singleton sets we find that there must be some number of elements, $k \in \ccint0{n-1}$, not in singleton blocks. We simply choose those $k$ elements and then partition them into a set without any singleton blocks and find that we $\binom nkr_k$ ways to do this for a fixed $k$. We have only $1$ way of distributing the remaining elements as they all go into singletons. Thus we simply sum across all possible values of $k$ and find that we have $\sumfrom{k=0}{n-1}{\binom nk r_k}$ ways to partition $\cannonicalSet{n}$ such that it has at least one singleton block. If we change over to using $t=n+1$ we find $\sumfrom{k=0}{t-2}{\binom {t-1}kr_k}$ and that is the equation for $r_t = r_{n+1}$ thus $r_{n+1}$ is the number of ways to partition $\cannonicalSet{n}$ such that there is at least one singleton block.

\subsection{Show that $B(n) = r_n + r_{n+1}$.}
$B(n)$ is the number of partitions on $\cannonicalSet{n}$. Now either there is or there is not a singleton block in a partition. If there is at least one singleton block we have $r_{n+1}$ ways to partition as shown above, and if there are no singleton sets then we have $r_n$ ways to do this by definition of $r_n$. Thus $B(n) = r_n + r_{n+1}$.

\subsection{Find a closed formula for the EGF for $r_n$.}
Consider the zero-indexed sequence $a = (1,0,1,1,1, \ldots)$ for task $\mathcal A$, which may be thought of 'accepting' any finite set whose cardinality is non-empty and it has EGF of $A(x) = e^x-x$. We now use theorem 3.30 from the book and set $a_0 = 0$ thus changing our EGF to $\hat A(x) = e^x-x-1$. Then we would find that $\exp(e^x-x-1)$ would be the EGF for splitting a set $\cannonicalSet{n}$ into as many blocks as we like and then doing task $\mathcal A$ to it. This thus must be the EGF for $r_n$ it would split a set into any number of blocks and reject any singleton blocks.

\[R(x) = \exp\left(e^x-x-1\right)\]

\subsection{Use the EGF to show that $r_n = \sumfrom{k=0}{n}{\binom nk (-1)^{n-k}B(k)}$}

Let us denote the $n^{\text{th}}$ bell number as $B(n)$ and let $\mathcrl B(x)$ be the EGF for $B(n)$. We find that $\mathcrl B(x)$ by using the exponential rule for EGF and we end with \[\mathcrl B(x) = \exp(e^x-1)\] We also will denote

Now we do the following work
\begin{align*}
	R(x) &= \exp(e^x-x-1) \\
	&= \exp(e^x-1)e^{-x} \\
	&= \mathcrl B(x)e^{-x} \\
	&= \sumfrom{n=0}{\infty}{ B(n)\frac{x^n}{n!}}\sumfrom{n=0}{\infty}{(-1)^n\frac{x^n}{n!}}
\end{align*}

By proposition 3.18 from the book we find that $R(x) = \sumacross{n\ge0}{\sumfrom{k=0}{n}{\binom{n}{k}B(k)(-1)^{n-k}}\frac{x^n}{n!}}$ and thus we find \[r_n = \sumfrom{k=0}{n}{\binom{n}{k}B(k)(-1)^{n-k}}\]
\end{document}

### 2018-01-28 Combinatorics/Final/document.tex
init commit

\documentclass{article}
\input{../../definitions}

\title{Combinatorics Final Exam}
\renewcommand{\thesubsection}{\thesection.\alph{subsection}}
\newtheorem{theorem}{Theorem}[section]

\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

\begin{document}
	\maketitle
	\section{}
	\subsection{Let $G$ be an $r$-regular graph on $n$ vertices, meaning that we have $\deg(v) = r$ for every vertex $v$. Prove that $\chi(G) \ge n/(n-r)$}

	First we color $G$ minimally and we can now split the vertices into color sets, which would be the set of all vertices in $G$ with a specific color. Now as there are $\chi(G)$ color sets, and $n$ vertices, then there must exist some color set $B$, such that $$\cardinality{B} \ge \frac{n}{\chi(G)}$$. We also know that each vertex in $B$ connects to $r$ vertices outside of $B$ (as $B$ is an independent set), thus there must be at least $r$ vertices outside of $B$. $$n-\cardinality B \ge r$$

	We now will do some algebraic manipulation:
	\begin{align*}
		\frac n{\chi(G)} \le \cardinality B \;\And\; n-\cardinality B \ge r &\implies n-\frac n{\chi(G)} \ge n-\cardinality B \ge r\\
		&\implies r-n \le -\frac n{\chi(G)} \\
		&\implies n-r \ge \frac n{\chi(G)} \\
		&\implies \frac 1{n-r} \le \frac{\chi(G)}n \\
		&\implies \frac n{n-r} \le \chi(G) \\
		&\iff \chi(G) \ge \frac n{n-r}
	\end{align*}

	\subsection{Instead of coloring the vertices of  graph, we could color the \textbf{edges}. A proper edge coloring is one where any edges that share a vertex must get different colors. The \textbf{edge chromatic number} $\chi'(G)$ of a graph is the minimum number of colors needed to properly edge-color the graph. Prove that $$\Delta(G) \le \chi'(G) \le 2\Delta(G) - 1$$ where $\Delta(G) = \max_{v\in V(G)}\deg(v)$}

	Let us start by considering $V$ to be the vertex in $G$ with greatest degree (or at least one tied for the title).
	$V$ must have $\Delta(G)$ edges, each of those edges are going to have a different color, thus $\chi'(G) \ge \Delta(G)$.

	Now we can also try and color these edges with a greedy algorithm, that was for an edge to given the $k^{\text{th}}$ color it would need to share a vertex with $k-1$ other edges. Well any edge can at most be connected to two vertices and each of those vertices has at most $\Delta(G) - 1$ other edges. Then any edge may share a vertex with at most $2(\Delta(G) - 1)$ and then we would at most get that edge colored with color $2(\Delta(G) -1) + 1 = 2\Delta(G) - 1$, resulting in an upper bound of $\chi'(G) \le 2\Delta(G) - 1$.

	Now finally: $$\Delta(G) \le \chi'(G) \le 2\Delta(G) -1$$

	\section{}
	\subsection{Let $\mathcal F_n$ denote the set of permutations of the multiset $\set{1,1,2,2,3,3,\ldots,n,n}$ with the following special property: for $1 \le m \le n$, all numbers between the two occurrences of $m$ are greater than $m$, For example, $\mathcal F_1 = \set{11}$ and $\mathcal F_2 = \set{1122,1221,2211}$. Let $F_n = \cardinality{\mathcal F_n}$. Prove that for $n\ge 2$, we have $$F_n = (2n-1)\cdot F_{n-1}$$}

	We can construct any element of $\mathcal F_{n+1}$ using an element of $\mathcal F_{n}$. For any element in $\mathcal F_n$ we have $2n$ indices and thus $2n+1$ places we may add an element. To go from something in $\mathcal F_n$ to something in $\mathcal F_{n+1}$ we have to add two elements, but they must be next to each-other, as otherwise there would be some element between and all the elements other then $n+1$ are less then $n+1$, thus breaking our rule that between to same elements everything must be greater than it. We also can put it anywhere as it is greater then anything else. Additionally all constructions produce a unique element of $\mathcal F_{n+1}$. Now we have $(2n+1)$ ways to construct unique elements in $\mathcal F_{n+1}$ from any element of $\mathcal F_{n}$, thus we get the equation: $$F_{n+1} = (2n+1)F_n$$ and this will work for all $n\ge 1$. This is logically equivalent to the statement we are trying to prove, to show this simply replace $n$ with $\eta$ and then let $\eta = n-1$ and we find: $$F_{\eta + 1} = (2\eta + 1)F_\eta \iff F_{n} = (2n-1)F_{n-1}$$ and because before this would have worked for $\eta \ge 1$ now it would be $n-1 \ge 1$, thus $n\ge 2$

	\subsection{Use part (a) to explain why $F_n = (2n-1)!!$}

	Now we just do some weak induction. It is trivial that $F_1 = 1 = (2\cdot 1 -1)!!$, especially because it's given to us in part (a). Now we will assume that this holds for some $n \in\mathbb N$ and show that it also holds for $\eta = n+1$.

	\begin{align*}
		F_\eta &= F_{n+1} \\
		&= (2n+1)F_n \\
		&= (2n+1)(2n-1)!! \\
		&= (2n+1)!! \\
		&= (2\eta-1)!!
	\end{align*}

	\textbf{Ta-dah!} Now by the powers of weak induction we are confident that $F_n = (2n-1)!!$ for all $n\in\mathbb N$.

	\subsection{Let $\mathcal F_{n,k} \subset \mathcal F_n$ be the set of such permutations that have $k$ ascents. For example $$\mathcal F_{3,1} = \set{113322, 133221, 221331, 221133, 223311, 233211, 331122, 331221}$$ Let $F(n,k) = \cardinality{\mathcal F_{n.k}}$. Prove that $$F(n,k) = (k+1)F(n-1,k)+(2n-1-k)F(n-1,k-1)$$}

	Now to construct something in $\mathcal F_{n,k}$ we may take an element of $\mathcal F{n-1,k}$ and then insert a pair of $n$ in at any viable indices. The viable indices in this case are going to be any place in which we don't add a new assent and the two elements must be adjacent for reasons discussed in part (a). This means we can put the new elements at the beginning of the string or we may put them anywhere there is already an assent, this gives us $k+1$ places, thus yielding $(k+1)F(n-1,k)$ ways to create an element of $\mathcal F_{n,k}$ so far.

	We also may construct this element by taking a string missing $n+1$ and that needs one more assent, so an element of $\mathcal F_{n-1,k-1}$ and adding in the new element to create a new assent, this would be anywhere that it was not viable last time, so anywhere that is not already an assent and not the beginning. We have $k-1$ assents this time and $2n-2$ spots so we have $2n-2-(k+1) = 2n-1-k$ spots to put our new elements this time. Now we get our recursive equation of:

	$$F(n,k) = (k+1)F(n-1,k)+(2n-1-k)F(n-1,k-1)$$

	The only issue left to show this is true is to show that each thing created is different, that is that there is no double counting. To show this simply consider two distinct strings in $\mathcal F_{n-1,k} \union \mathcal F_{n-1,k-1}$ these strings can't possible both generate the same string when a pair of $n$ is added as simply removing the $n$ would get back to the distinct strings. Additionally notice that $\mathcal F_{n-1,k} \inter \mathcal F_{n-1,k-1} = \emptyset$.

	\section{}

	\subsection{Given $2\le k \le n-1$, let $T(n,k)$ be the number of labeled trees on $n$ vertices with exactly $k$ leaves. Find a simple formula for $T(n,k)$.}

	Consider the Pr\"ufer codes for these trees. If a vertex is a leaf then there will be no other vertices going to that element, with the exception of if $1$ is a leaf, in which case there would only be one vertex going to it, however in the simplified Pr\"ufer codes this isn't an issue as we remove a $1$ at the end. In the Pr\"ufer codes for trees counted by $T(n,k)$ means that there will be $k$ numbers that do not appear in the Pr\"ufer code. The valid Pr\"ufer codes will then be a string of length $n-2$ on the symbol set $[n]$ that does not include $k$ of the symbols. Well first choose those $k$ symbols from $[n]$ (done in $\binom nk$ ways), and second create a string on the remaining symbols (done in $(n-k)^{n-2}$ ways). This results in $$T(n,k) = \binom nk(n-k)^{n-2}$$

	\subsection{How many rooted trees are there on $[n]$ vertices such that the root is \textbf{not} a leaf?}

	Here we will use beveridge's theorem. There are $n^{n-2}$ non-rooted trees on $[n]$ and thus we simply choose a root to get the number of rooted trees giving us $n^{n-2}\cdot n = n^{n-1}$ rooted trees on $[n]$.

	To find the number of trees with a root that is a leaf we simply choose an element of $[n]$ to be the root and then create all the Pr\"ufer codes that don't have that element giving us $n(n-1)^{n-2}$ different trees with a leaf as a root.

	Now $n^{n-1} - n(n-1)^{n-2}$ is the solution for how many rooted trees there are on $[n]$ such that the root is not a leaf.

	\section{Suppose that we have a set of $n$ building blocks with height $[n]$. How many ways can we line up the blocks so that we see exactly $r$ blocks when looking from the right, and we can se exactly $s$ blocks when looking from the left?}

	First we notice that the tallest block (one with height $n$) divides this problem into two separate, but identical subproblems. That is once we place the tallest block somewhere, no mater what is to the right or left of it, it can be seen from both sides; additionally nothing on the left of it can be seen from the right and vice-versa.

	To tackle this problem we are first going to fix where the tallest block is and put and say there are $k$ blocks 'in-front' of it, and in-front depends on what way we are looking at it from, so this way when this is solved we may use this on both sides of the building. Now if there are $k$ blocks in-front of the tallest building then we must start by choosing which $k$ they are, notice that when we choose which $k$ blocks are on one side of the building we uniquely choose what is on the other side. Because the tallest block is already placed we have $\binom{n-1}k$ different blocks to choose to put in-front of the tallest building.

	Now that we have the block set we may re-label it with labels from $[k]$, and just make sure that we maintain the order between blocks. This is because we don't really care how tall a block is, just if it's taller or shorter then the other blocks in the set, and this will maintain that property. Now if we wanted to see $p+1$ blocks from whatever direction we are looking (we do the plus one because we already know that we can see the tallest building), then we can place a valid arrangement for this by permuting the blocks now with labels from $[k]$ such that there are $p$ cycles, we write these cycles in our canonical cycle notation, then remove parentheses and we will find a new permutation that has exactly $p$ indices with the greatest element so far in the permutation. Now we have $c(k,p)$ valid orderings of our blocks, where $c$ is the signless Sterling number of the first kind.

	Now to bring this all home we have bounds on $k$ of $r-1 \le k \le n-s+1$ and then choose the $k$ elements on one side (I go with the right side in this) and then permute with $s-1$ and $r-1$ cycles on both sides and we get:

	$$\sumfrom{k=r-1}{n-s+1}{\binom{n-1}{k} c(k,r-1) \cdot c(n-1-k,s-1)}$$

	\section{The stars and stripes graph EGF question}

	Alright, to make a star graph we just choose a vertex to be the center and then everything else is determined, thus there are always $n$ ways for this to be done on an $n$ vertex star graph, however when $n=2$ you get an odd case as no mater which vertex you choose you get the same graph, thus we get the EGF:$$ \sumfrom{n=1}{\infty}{n\frac{x^n}{n!}} - \frac{x^2}2 $$, all stars are the same color so we are now done.

	Now we make all our stripes which are just paths, a path on $[n]$ can be made in $\frac{n!}2$ ways as you may put any permutation but then you double count as a complete reversal of an ordering generates the same path so just divide by two. Now because we don't like that we divides by two we simply multiply back by two to account for the choice of a color between red or white. Also we must account for the issue of the case on one vertex as there is only one possible graph not $\frac{1!}2 = \frac 12$ graphs, thus meaning there are two when colored. This gives us an EGF: $$2x + \sumfrom{n=2}{\infty}{n!\frac{x^n}{n!}}$$

	Now each of these we exponentiate then multiply together as we are choosing two subsets, one to be stars and one to be stripes, then we create as many stars one one as we like and then we create as many red and white stripes on the other as we like, this gives us an EGF of: \begin{align*}
		\exp\left(\sumfrom{n=1}{\infty}{n\frac{x^n}{n!}}-\frac{x^2}2\right)\cdot\exp\left(2x+\sumfrom{n=2}\infty{n!\frac{x^n}{n!}}\right)
	\end{align*}

	This can be simplified, but I'll leave that as an exercise for the reader.

\end{document}

### 2018-01-28 Compilers/ContextFreeGrammars.tex
init commit

\documentclass{article}
\input{../definitions.tex}
\title{Context Free Gramers}
\begin{document}
\maketitle

\question{4.2.1:a)} $S \Rightarrow SS* \Rightarrow SS+S* \Rightarrow aS+S* \Rightarrow aa+S* \Rightarrow aa+a*$

\question{b)} $S \Rightarrow SS* \Rightarrow Sa* \Rightarrow SS+a* \Rightarrow Sa+a* \Rightarrow aa+a*$

\question{c)}
\Tree
[.$S$
	[.$S$
		[.$S$ $a$ ]
		[.$S$ $a$ ]
		$+$
	]
	[.$S$ $a$ ]
	$*$
]

\question{d)} This is unambiguous, because you can always match with whatever character is on the right side of the string, and work your way back. That is to say if one starts at the end of the string and works your way back you may create a production for any string in the language by following these rules:
\begin{enumerate}
\item If you see $*$, then convert your rightmost $S$ to $SS*$.
\item If you see $+$, then convert your rightmost $S$ to $SS+$.
\item If you see $a$, then convert your rightmost $S$ to $a$.
\end{enumerate}

\question{e)} This language will be the subset of the language given by the regular expression $a(a\vert*\vert+)^*$ such that the following two conditions are met.
\begin{enumerate}
\item $a_i - +_i - *_i \ge 1$ for all $i \in \coint0{\mathscr L}$.
\item $a_{\mathscr L} - +_{\mathscr L} - *_{\mathscr L} = 1$.
\end{enumerate}
Where $k_i$ is the number of times that a character $k$ appears in the string in any index in the range $\ccint0k$, given $0$ based indexing on the string, and $\mathscr L$ is the number of symbols in the string. For example $+_{\mathscr L}$ is the number of times $+$ appears in the string in the range of indicies $\ccint0{\mathscr L}$, a set that includes all indicies the given string, thus $+_{\mathscr L}$ is the number of times $+$ apears in the entire string.

\question{4.2.2:a)a)} $S \Rightarrow 0S1 \Rightarrow 00S11 \Rightarrow 000111$

\question{b)} $S \Rightarrow 0S1 \Rightarrow 00S11 \Rightarrow 000111$

\question{c)}
\Tree
[.$S$
	$0$
	[.$S$
		$0$
		[.$S$ $0$ $1$ ]
		$1$
	]
	$1$
]

\question{d)} This language is unambigous as you must always make $n - 1$ conversions from $S$ to $0S1$ followed by a conversion from $S$ to $01$, where $n$ is the number of $0$s there are in the string. There is only ever $1$ $S$, and thus this is trivially unambigous.

\question{e)} This language is $\setbuilder{0^n1^n}{n \ge 1}$

\question{b)a)} $S \Rightarrow +SS \Rightarrow +*SSS\Rightarrow +*aSS\Rightarrow +*aaS\Rightarrow+*aaa$

\question{b)} $S\Rightarrow +SS \Rightarrow +Sa\Rightarrow +*SSa\Rightarrow+*Saa\Rightarrow+*aaa$

\question{c)}
\Tree
[.$S$
	$+$
	[.$S$
		$*$
		[.$S$ $a$ ]
		[.$S$ $a$ ]
	]
	[.$S$ $a$ ]
]

\question{d)} This is unambigious for much the same reason as in question 4.2.1, although this time we parse through the string in the opposite direction and the conversions must be changed to the corrosponding conversions for this grammer.

\question{e)} This language is the set of all strings that are in the language given by the grammer in question 4.2.1, but the ordering of all the characters in the string is flipped.

\question{d)a)} $S \Rightarrow SS\Rightarrow S*S\Rightarrow (S)*S\Rightarrow(S+S)*S \Rightarrow(a+S)*S\Rightarrow(a+a)*S\Rightarrow(a+a)*a$

\question{b)} $S \Rightarrow SS \Rightarrow Sa \Rightarrow S*a \Rightarrow (S)*a \Rightarrow (S+S)*a \Rightarrow (S+a)*a \Rightarrow (a+a)*a$

\question{c)}
\Tree
[.$S$
	[.$S$
		[.$S$
			$($
			[.$S$
				[.$S$ $a$ ]
				$+$
				[.$S$ $a$ ]
			]
			$)$
		]
		$*$
	]
	[.$S$ $a$ ]
]

\question{d)} This grammer is ambigious, due to the equivlency of these two valid parse trees:

\Tree
[.$S$
	[.$S$
		[.$S$ $a$ ]
		[.$S$ $a$ ]
	]
	$*$
]
\Tree
[.$S$
	[.$S$ $a$ ]
	[.$S$
		[.$S$ $a$ ]
		$*$
	]
]

\question{e)} Think of $*$ as a postfixed unary opperator. Think of nothing between two terms as a binary operator on them, like multiplication in normal mathematical notation. Think of $+$ as an infixed binary operation, like it normally is. Think of parentheses as one normally does. Think of $a$ as the only allowed value, and then any well formed formula with these rules is valid in this language and this language is the set of all of these well formed formulas.

\question{4.2.3:a)}
\begin{align*}
S \quad &\to \quad 1\ S\ \vert\ 0\ 1\ S\ \vert\ \lambda
\end{align*}

\question{b)}
\begin{align*}
S \quad &\to \quad 1\ S\ 1\ \vert\ 0\ S\ 0\ \vert\ \lambda
\end{align*}

\question{c)}
\begin{align*}
S \quad &\to \quad 0\ S\ 1\ S\ \vert\ 1\ S\ 0\ S\ \vert\ \lambda
\end{align*}

\end{document}

### 2018-01-28 Topology/Homework/hw5.tex
init commit

\documentclass{article}

\input{../../definitions.tex}
\def\useLim{}
\def\sbSeperator{\ |\ }

\title{Topology Homework 5}

\begin{document}
\maketitle

\question{18.2.} Suppose that $f:X\to Y$ is continuous. If $x$ is a limit point of the subset $A$ of $X$, is it necessarily true that $f(x)$ is a limit point of $f(A)$?

No, it is not true. Suppose $X = Y = \mathbb R$ and we give $X$ and $Y$ the standard topology on $\mathbb R$. Then define $f$ to be the zero function and let $A = \ooint89$. Then we can choose $x$ to be a limit point of $A$, for example $x = 9$, and then $f(A) = \set0$ and $f(x) = 0$ and $0$ is not a limit point of $\set 0$.

\question{6.} Find a function $f:\mathbb R \to \mathbb R$ that is continuous at precisely one point.

We assume the standard topology on $\mathbb R$. Now consider $$f(x) = \begin{cases}0 & x \not\in \mathbb Q\\x & x \in \mathbb Q\end{cases}$$

Let us first show that $f$ is continuous at $0$. $f(0) = 0$, so let $V$ be an open set containing $0$. Now because $V$ is an open set in the standard topology on $\mathbb R$ containing $0$ there will some $a > 0$ such that the interval $\ooint {-a}{a} \subset V$. Now let $U = \ooint{-a}{a}$, then find that $f(U) \subset V$ as for any $x\in U$, $f(x) = 0 \in V$ or $f(x) = x \in U \subset V$. Thus by our definition of point continuity $f$ is continuous at the point $0$.

Let us now consider a point $x\not=0$ in $\mathbb R$. We will show that there exists some nhood $V$ of $f(x)$, such that for any nhood $U$ of $x$, we have $U \not\subset V$. Now if $x\in\mathbb Q$ then we will let $V$ be an nhood of $x$ not containing $0$ and because the irrational's are dense on $\mathbb R$ there exists some irrational number in any nhood $U$ of $x$, thus $0 \in f(U)$. If $x\not\in\mathbb Q$ then $f(x) = 0$ so we may let $V= \ooint{-\abs x}{\abs x}$. Now we will find that any nhood, $U$, of $x$ contains some rational, $q$, such that $\abs{q} > \abs{x}$ and thus $f(q) = q \not\in V$ and thus $f(U)\not\subset V$.

\question{7.(a)} First before we embark upon this little adventure let us give a rigorous definition for the limit from above, as I could not find any in this book. This definition is not complete as it does not deal with function of subsets of $\mathbb R$ and it does not deal with limits that tend to $\infty$ or $-\infty$, however it will be all we need.

\begin{definition}[Limit from above]
	Let $f:\mathbb R \to\mathbb R$, then $$\Lim x{c^+}{f(x)} = a \in\mathbb R$$ if for every $\epsilon > 0$ there exists some $\delta > 0$ such that for any $x \in\ooint c{c+\delta}$, $f(x) \in\ooint{a-\epsilon}{a+\epsilon}$.
\end{definition}

Now let $f:\mathbb R \to \mathbb R$ be continuous from above. Now choose $r\in\mathbb R$, and let $V$ be a nhood of $f(r)$. Because $V$ is open in $\mathbb R$ and contains $f(r)$, there must be some $\epsilon > 0$ such that $\ooint{f(r)-\epsilon}{f(r)+\epsilon} \subset V$. Now by definition of continuity from above we know that $\Lim{x}{r^+}{f(x)} = f(r)$, thus we have some $\delta > 0$ such that for any $x \in\ooint r{r+\delta}$, $f(x)\in\ooint{f(r)-\epsilon}{f(r)+\epsilon}$; this may also be written as $f(\ooint r{r+\delta}) \subset \ooint{f(r) - \epsilon}{f(r)+\epsilon}$. It is also trivial that $f(r) \in \ooint{f(r) - \epsilon}{f(r)+\epsilon}$ so we may say that $f(\coint{r}{r+\delta}) \subset \ooint{f(r) - \epsilon}{f(r)+\epsilon} \subset V$. If we consider $f$ then as a map from $\mathbb R_\ell$ to $\mathbb R$ we get that for any point $r\in\mathbb R$ and any nhood of $V$ of $f(r)$, there exists a nhood $U = \coint r{r+\delta}$ of $r$ such that $f(U) \subset f(V)$. Now by the powers vested in me by theorem 18.1 part 4 in the book I hereby declare $f$ continuous when thought of as a map from $\mathbb R_\ell$ to $\mathbb R$.

\question{(b)} Notice how this section merely asks for conjectures, not proofs nor even for the conjectures to be correct.

Now I state this without proof as I really do not know how to prove it, but from what I can tell it seems to be right. First there are no continuous function from $\mathbb R$ to $\mathbb R_\ell$, in some sense there seems to be 'to many' open sets in $\mathbb R_\ell$ for each one to have an inverse that is open in $\mathbb R$. My next statement I have less of a feel for, but I feel that continuous functions from $\mathbb R$ to $\mathbb R$ are the same as continuous function from $\mathbb R_\ell$ to $\mathbb R_\ell$. I would like to talk to you more about this and see if we can't come up with a proof or a disproof of either of these statements.

\question{19.2.} Let $A_\alpha$ be a subspace of $X_\alpha$, for each $\alpha \in J$. Show that that $\prod A_\alpha$ is a subspace of $\prod X_\alpha$ if both products are given the box topology, or if both products are given the product topology.

\textbf{Box topology:}

Let $B$ be a basis element of $\prod A_\alpha$ as a box topology, then for each $\alpha \in J$ there exists $B_\alpha$ open in $A_\alpha$ such that $\prod B_\alpha = B$. For any given $\alpha\in J$ there must be some open $C_\alpha$ in $X_\alpha$ such that $B_\alpha = C_\alpha \inter A_\alpha$ because $B_\alpha$ is open in $A_\alpha$ which is a subspace of $C_\alpha$. Now we find that $B = \prod B_\alpha = \prod\left[C_\alpha \inter A_\alpha\right] = \prod C_\alpha \inter \prod A_\alpha$ which is a basis element in $\prod A_\alpha$ as a subspace of $\prod X_\alpha$.

Let $B$ now be a basis element of $\prod A_\alpha$ as a subspace of $\prod X_\alpha$, then there exists an open $C \in \prod X_\alpha$ such that $\prod A_\alpha \inter C = B$. By virtue of $C$ being open in $\prod X_\alpha$ there exists some open $C_\alpha \subset X_\alpha$ for each $\alpha \in J$ such that $\prod C_\alpha = C$ Thus we have $B = \prod A_\alpha \inter C = \prod A_\alpha \inter \prod C_\alpha = \prod\left[A_\alpha \inter C_\alpha\right]$, which is a basis element of $\prod A_\alpha$ as the box topology of all $A_\alpha$.

\textbf{Product topology:}

Let $B$ be an open set in $\prod A_\alpha$ as a product topology, then (by theorem 19.1) for each $\alpha \in J$ there exists some $B_\alpha$ that is open in $A_\alpha$, such that $\prod B_\alpha = B$. We also know (by theorem 19.1) that for only finitely many $\alpha \in J$, $B_\alpha \not= A_\alpha$. Now for any $\alpha \in J$ such that $B_\alpha = A_\alpha$ we let $C_\alpha = X_\alpha$ and for all other $\alpha \in J$ there must be some open set, $C_\alpha$ in $X_\alpha$ such that $A_\alpha \inter C_\alpha = B_\alpha$. Now for all but finitely many $\alpha \in J$, $C_\alpha = X_\alpha$, thus $\prod C_\alpha$ is an open set in $\prod X_\alpha$. Finally we say $B = \prod B_\alpha = \prod\left[C_\alpha \inter X_\alpha\right] = \prod C_\alpha \inter \prod X_\alpha$, thus $B$ would be open in $\prod A_\alpha$ as a subspace topology.

Now let $B$ be an open set in $\prod A_\alpha$ as a subspace of $\prod X_\alpha$, then there exists some open $C\subset\prod X_\alpha$ such that $C \inter \prod A_\alpha = \prod B_\alpha$. Because $C$ is open in $\prod X_\alpha$ then for each $\alpha\in J$ there exists $C_\alpha$ open in $X_\alpha$ such that $\prod C_\alpha = C$ and for all but finitely many $\alpha \in J$, $C_\alpha = X_\alpha$. Now for each $\alpha \in J$ we let $B_\alpha = C_\alpha \inter A_\alpha$, thus $B_\alpha$ will be open in $A_\alpha$ and there may be only finitely many $B_\alpha \not= A_\alpha$. Finally we say that $B = C\inter\prod A_\alpha = \prod C_\alpha \inter \prod A_\alpha = \prod\left[C_\alpha \inter A_\alpha\right] = \prod B_\alpha$ which must be open in $\prod A_\alpha$ with a product topology.

\question{3.} Show that if for all $\alpha\in J$, $X_\alpha$ is Hausdorff then $\prod X_\alpha$ is Hausdorff given either a box or product topology.

First we will state and prove a theorem to help us in this proof.

\begin{theorem} \label{Comparable Hausdorff}
	Let a space $X$ has two topologies $\mathscr T$ and $\mathscr S$ with $\mathscr S$ finer than $\mathscr T$. If $\mathscr T$ is Hausdorff then so must $\mathscr S$ be.
\end{theorem}

\begin{proof}
	Let us choose $x,y\in X$ such that $x\not=y$. As $\mathscr T$ is Hausdorff there exists a nhood $U$ of $x$ and nhood $V$ of $y$ in $\mathscr T$ such that $U$ and $V$ are disjoint. $\mathscr S$ is finer than $\mathscr T$ so $U$ and $V$ must also be in $\mathscr S$, thus for arbitrary point $x,y\in X$ there is are disjoint nhoods of them in $\mathscr S$.
\end{proof}

First we notice that the box topology is finer then the product topology, thus because of theorem \ref{Comparable Hausdorff} if we show that the product topology on $\prod X_\alpha$ is Hausdorff then so is the box topology on $\prod X_\alpha$.

Consider $\prod X_\alpha$ given the product topology, with $X_\alpha$ Hausdorff for all $\alpha \in J$. Let $x,y\in \prod X_\alpha$ be given with $x\not=y$. For each $\alpha\in J$ there exists some $x_\alpha,y_\alpha \in X_\alpha$ such that $\prod x_\alpha = x$ and $\prod y_\alpha = y$. There then must be some $\beta \in J$ for which $x_\beta \not= y_\beta$ as if there was not then we would have $x=y$. We have that $X_\beta$ is Hausdorff, thus we may choose an nhoods of $U_\beta$ of $x_\beta$ and $V_\beta$ of $y_\beta$ such that $U_\beta \inter V_\beta = \emptyset$. Now for all $\alpha \in J\setminus\set\beta$ let us define $U_\alpha = V_\alpha = X_\alpha$. Now we have $\prod U_\alpha$ and $\prod V_\alpha$ open in $\prod X_\alpha$ with $\prod U_\alpha$ disjoint from $\prod V_\alpha$, and $x \in \prod U_\alpha$ and $y \in \prod V_\alpha$. Thus $\prod X_\alpha$ is Hausdorff.

Now by theorem \ref{Comparable Hausdorff} we have $\prod X_\alpha$ with the box topology as Hausdorff.

\question{5.}
If $f$ is continuous then all $\alpha \in J$,  $f_\alpha$ is continuous.

\begin{proof}
	Let there be some $\beta \in J$ such that $f_\beta$ is not continuous. Let us also define $B_\alpha = X_\alpha$ for all $\alpha\not= \beta$, and let $B_\beta$ an open set in $X_\beta$ such that $f_\beta^{-1}(B_\beta)$ is not open in $A$. Now for each $\alpha \not= \beta$ we have $f_\alpha^{-1}(B_\alpha) = A$ by definition of a function (it must be defined at all points on $A$). Now we have
	\def\LB{\left[}
	\def\RB{\right]}
	\begin{align*}
		f^{-1}\left(\prod B_\alpha\right) &= \setbuilder{a\in A}{f(a) \in \prod B_\alpha} \\
		&= \setbuilder{a \in A}{\prod f_\alpha(a) \in \prod B_\alpha} \\
		&= \setbuilder{a \in A}{\All {\alpha \in J}{f_\alpha(a) \in B_\alpha}} \\
		&= \interacross{\alpha\in J}{\setbuilder{a\in A}{f_\alpha(a) \in B_\alpha}} \\
		&= \interacross{\alpha\in J}{f_\alpha^{-1}(B_\alpha)} \\
		&= \interacross{\alpha \in J\setminus \set\beta}{f_\alpha^{-1}(B_\alpha)} \inter f_\beta^{-1}(B_\beta) \\
		&= A \inter f_\beta^{-1}(B_\beta) \\
		&= f_\beta^{-1}(B_\beta)
	\end{align*}
	and we know that $f_\beta^{-1}(B_\beta)$ is closed, thus $f$ is not continuous. Now by contrapositive we have shown that for $f$ to be continuous $\prod f_\alpha$ must be continuous for each $\alpha \in J$ when we consider the box topology. 
\end{proof}

\end{document}

### 2018-01-28 Topology/Midterm/Midterm.tex
init commit

\documentclass{article}
\input{../../definitions.tex}
\input{../topology.tex}

\title{Topology Midterm}

\begin{document}
\maketitle

In \question{17.5} order to show that, for any order topology, $\closure{\ooint ab} \subset \ccint ab$ we first notice that $\ccint ab \supset \ooint ab$ and that $\ccint ab$ is closed. By definition we know $\closure{\ooint ab} = \biginter \text{all closed supersets of }\ooint ab$. We now notice that $\ccint ab$ is one such closed superset of $\ooint ab$, thus $\closure{\ooint ab} \subset \ccint ab$.

We now will look to see when $\closure{\ooint ab} = \ccint ab$. We already know that $\closure{\ooint ab} \subset \ccint ab$, and to have equality we only need $\ccint ab \subset \closure{\ooint ab}$. Let us start by noticing that $\ccint ab$ is the union of disjoint sets $\ooint ab$ and $\set{a,b}$. Now if $\ccint ab$ is to be a subset of $\closure{\ooint ab}$ then that would be the same as saying $\ooint ab\union\set{a,b}\subset\closure{\ooint ab}$ thus both $\ooint ab$ and $\set{a,b}$ must be subsets of $\closure{\ooint ab}$. We know that $\ooint ab\subset\closure{\ooint ab}$ as $\closure{\ooint ab} = \ooint ab \union \limpts{\ooint ab}$, and because we know that $\set{a,b}$ is disjoint from $\ooint ab$ we can then say $\ccint ab \subset \closure{\ooint ab} \implies \set{a,b} \subset \limpts{\ooint ab}$. We also can say
\begin{align*}
\set{a,b} \subset \limpts{\ooint ab} &\implies \set{a,b} \subset \closure{\ooint ab} \\
&\implies \set{a,b} \union \ooint ab \subset \closure{\ooint ab} \\
&\implies \ccint ab \subset \closure{\ooint ab}
\end{align*}
and thus, iff $a$ and $b$ are limit points for the interval $\ooint ab$, then our equality ($\ccint ab = \closure{\ooint ab}$) holds.

\bigskip

\question{17.17}Consider the lower limit topology on $\mathbb R$, and the topology given by the basis $\mathscr C$ of Exercise 8 \S 13. Determine the closures of the intervals $A = \ooint0{\sqrt{2}}$ and $B=\ooint{\sqrt2}3$ in these two topologies.

Basis $\mathscr C$ of Exercise 8 \S 13:\[\mathscr C = \setbuilder{\coint ab}{a<b \And a,b\in\mathbb Q}\]
\medskip

First we will consider our topology to be $\mathbb R_{\ell}$:
\smallskip

Let $C$ be an interval in the form $\ooint ab$, where $a,b\in\mathbb R$. By definition we know that $\closure C $ is the intersection of all closed sets that contain $C$. We know that $\ooint{-\infty}a\union\coint b\infty \in \mathbb R_\ell$ and thus $\coint ab$ is closed in $\mathbb R_\ell$, thus $\closure C \subset \left[a,b\right)$.

Now if we can show that $[a,b)\subset\closure C$ then we will know that $[a,b)=\closure C$.

First we note that by theorem 17.6 $\closure C = C \union \limpts C$, now because we know $C \subset \closure C$ then we can say if $\coint ab\setminus C\subset \closure C \setminus C$ then $ [a,b) = \closure C$. We also know that $\closure C \setminus C \subset \limpts C$, thus we can say that if $\coint ab \setminus C \subset \limpts C$ then $[a,b) = \closure C$. Next we find that $[a,b) \setminus C = \set a$ so if $a \in \limpts C$ then $[a,b) = \closure C$. We will show $a\in\limpts C$ by contradiction.

Let us assume $a \not\in\limpts C$ then there is an interval $[x,y)$, where $x,y\in \mathbb R$, that contains $a$ but no elements in $C$. By definition $[x,y) = \setbuilder{k}{x\le k<y}$, so if $a\in[x,y)$ then $x\le a<y$. Now we can construct an interval $(a,y) \subset [x,y)$ which is not empty as $y > a$ and thus it will contain some elements of $C$. We now have a contradiction, thus $a \in \limpts C$, thus
\[
[a,b) = \closure C
\]

Now if we let $a = 0$ and $b = \sqrt2$ then we know $\closure{\ooint{0}{\sqrt2}} = \closure A = \coint{0}{\sqrt2}$.

Now if we let $a = \sqrt2$ and $b = 3$ then we know $\closure{\ooint{\sqrt2}3} = \closure B = \coint{\sqrt2}3$.
\medskip

Now we will to continue on to the topology $\mathcrl C$, which is given by basis $\mathscr C$.

Let us first attempt to find $\closure{\ooint{0}{\sqrt2}}$. We will consider the set $\ccint0{\sqrt2}$, and attempt to show that it is closed by showing it's compliment is open.
\begin{align*}
\setcomp{\ccint0{\sqrt2}} &= \ooint{-\infty}0 \union \ooint{\sqrt2}{\infty} \\
&= \left(\unionacross{a<b<0 \And a,b \in \mathbb Q}{\coint ab} \union \unionacross{\sqrt2<a<b \And a,b \in \mathbb Q}{\coint ab}\right) \in \mathcrl C
\end{align*}
Thus $\ccint 0{\sqrt2}$ is closed, and thus $\closure{\ooint0{\sqrt2}}\subset\ccint0{\sqrt2}=\ooint{0}{\sqrt2}\union\set{0,\sqrt2}$. Now to find $\closure{\ooint{0}{\sqrt2}}$ we simply must determine if $0$ is a limit point of $\ooint 0{\sqrt2}$ and if $\sqrt2$ is a limit point of $\ooint 0{\sqrt2}$.

Any open interval around $0$ must have an upper bound greater then $0$, and thus $0$ is a limit point for $\ooint 0{\sqrt2}$.

Any open interval around $\sqrt2$ must have a lower bound that is a rational number, $\sqrt2$ is not rational, thus there must be a rational number less then $\sqrt2$ in the interval, and thus $\sqrt2$ is a limit point for $\ooint 0{\sqrt2}$.

Thus we have shown \[\ccint{0}{\sqrt2} = \closure{\ooint{0}{\sqrt2}}\]

Next we will find $\closure{\ooint{\sqrt2}3}$. We first will check if $\sqrt2$ and $3$ are limit points of $\ooint{\sqrt2}3$.

For an open interval in $\mathcrl C$ to include $\sqrt2$ there must a rational number greater then $\sqrt2$ as the upper bound, thus there is some value between $\sqrt2$ and that upper bound that is in $\ooint{\sqrt2}3$. Thus $\closure{\ooint{\sqrt2}3} \supset \coint{\sqrt2}3$.

The interval $\coint34$ includes $3$ and is in $\mathscr C$, thus it is a nood\footnote{nood = neighborhood} of $3$ which contains no values in $\ooint{\sqrt2}3$. Thus we know $3 \not\in \closure{\ooint{\sqrt2}3}$.

Now we wish to show that $\coint{\sqrt2}3$ is closed, if we can do that then we know that $\coint{\sqrt2}3 \subset \closure{\ooint{\sqrt2}3} \subset \coint{\sqrt2}3$ or $\coint{\sqrt2}3 = \closure{\ooint{\sqrt2}3}$.
\begin{align*}
\setcomp{\coint{\sqrt2}3} &= \ooint{-\infty}{\sqrt2} \union \coint3\infty \\
&= \left( \unionacross{a<b<\sqrt2 \And a,b\in\mathbb Q}{\coint ab} \union \unionacross{3 \le a < b \And a,b \in \mathbb Q}{\coint ab} \right) \in \mathcrl C
\end{align*}
Thus we have shown $\coint{\sqrt2}3$ is closed, and thus have shown
\[\coint{\sqrt2}3 = \closure{\ooint{\sqrt2}3}\]

\bigskip
Consider \question{18.5}the linear function $f:\mathbb R \to \mathbb R$ defined as $f(x) = \frac{x-a}{b-a}$. We know all linear functions are continuous, we have the homeomorphisms
\begin{align*}
f(\ooint ab) &= \ooint{\frac{a-a}{b-a}}{\frac{b-a}{b-a}} \\
&= \ooint01
\end{align*}
\begin{align*}
f(\ccint ab) &= \ccint{\frac{a-a}{b-a}}{\frac{b-a}{b-a}} \\
&= \ccint01
\end{align*}
thus we have shown homeomorphism between $\ooint ab$ and $\ooint01$, and between $\ccint ab$ and $\ccint01$ for any $a<b\in\mathbb R$.

\bigskip
\question{18.8(a)} Consider first $\setcomp{\setbuilder{x\in X}{f(x)\le g(x)}} = \setbuilder{x\in X}{f(x)>g(g)} = S$. Let us now choose $x\in S$.

By theorem 17.11 we know that $Y$ is Hausdorff, thus there exists disjoint open sets $\mathfrak A$ and $\mathfrak B$ such that $f(x)\in\mathfrak A$ and $g(x)\in\mathfrak B$. Let $A \subset\mathfrak A$ be a basis element in $Y$'s order topology such that $f(x)\in A$ and let $B\subset\mathfrak B$ be a basis element in $Y$'s order topology such that $g(x)\in B$. Now we have $\All{a\in A}{\All{b\in B}{[a>b]}}$ due to the definition of the order topology.

Next we notice that $\inv{g}(B)$ is open by continuity of $g$ and $\inv{f}(A)$ is open by continuity of $f$. Finite intersections are open so $\inv g(B) \inter \inv f(A)$ must be open. Now for any $\hat x\in \inv g(B) \inter \inv f(A)$ we have $g(\hat x) \in B$ and $f(\hat x) \in A$ thus $g(\hat x) < f(\hat x)$. We now have shown that for every $x \in S$ there exists a nood of $x$ that is completely contained in $S$. We may now take the union of a nood for each $x$ and we get that $S$ is the union of open sets, thus $S$ is open. We now conclude that $\setbuilder{x\in X}{f(x)\le g(x)}$ is closed.

\medskip
\question{(b)}
Let $A = \setbuilder{x\in X}{f(x) \le g(x)}$ and $B = \setbuilder{x\in X}{g(x) \le f(x)}$, thus $\All{a \in A}{f(a) = h(a)}$ and $\All{b \in B}{g(b) = h(b)}$; additionally $X = A \union B$. Notice that if $x\in A\inter B$ then $f(x) \le g(x)$ and $g(x) \le f(x)$, thus $g(x) = f(x)$. Now the final thing we must show is that $A$ and $B$ are both closed, however we just showed that in part a of this problem, so we may use the pasting lemma and we know that $h(x)$ is continuous.

\bigskip
\question{19.7}
\textbf{Box topology:} Let $x\in \mathbb R^\omega\setminus\mathbb R^\infty$, therefore $x = (x_\alpha)_{\alpha\in J}$ where $x_a\not=0$ for infinitely many $\alpha\in J$. For each $\alpha\in J$ such that $x_\alpha\not=0$ let $A_\alpha$ be a nood of $x_\alpha$ that does not include $0$, for all other $\alpha\in J$ let $A_\alpha$ be a nood of $0$. We find that $\prodacross{\alpha\in J}{A_\alpha}$ is open in $\mathbb R^\omega$ as it is a basis element. We have now shown that for any $x \in\mathbb R^\omega\setminus\mathbb R^\infty$ there is an open set $A(x)$ such that $x \in A(x) \subset\mathbb R^\omega\setminus\mathbb R^\infty$, thus we may take the union and find $\unionacross{x\in\mathbb R^\omega\setminus\mathbb R^\infty}{A(x)} =\mathbb R^\omega\setminus\mathbb R^\infty$, thus $\mathbb R^\omega\setminus\mathbb R^\infty$ is open, and thus $\mathbb R^\infty$ is closed so $\mathbb R^\infty = \closure{\mathbb R^\infty}$.

\textbf{Product topology:} Let $x \in\mathbb R^\omega$ and let $N$ be a nood of $x$, thus there exists some basis element of $\mathbb R^\omega$, $A$ such that $x \in A \subset N$. There must then exists $(x_\alpha)_{\alpha\in J} = x$ and $\prodacross{\alpha \in J}{A_\alpha} = A$ with $x_\alpha \in \mathbb R$ for all $\alpha \in J$ and $A_\alpha$ open in $\mathbb R$ for all $\alpha \in J$. We also know that for only finitely many $\alpha\in J$, $A_\alpha \not= \mathbb R$. We will now let $y_\alpha = 0$ for all $\alpha \in J$ where $A_\alpha=\mathbb R$, and let $y_\alpha = x_\alpha$ for all $\alpha\in J$ where $A_\alpha\not= \mathbb R$, thus $y = (y_\alpha)_{\alpha\in J} \in A$. We also notice that there are at most finitely many $\alpha \in J$ such that $y_\alpha\not=0$ thus $y \in \mathbb R^\infty$. This means that for any $x\in\mathbb R^\omega$ and any nood of $x$, there is some point $y\in\mathbb R^\infty$ such that $y$ is in the chosen nood of $x$, thus all points in $\mathbb R^\omega$ are limit points of $\mathbb R^\infty$. Finally we conclude that $\closure{\mathbb R^\infty} = \mathbb R^\omega$.

\bigskip

\question{20.4} 
\begin{center}
	\begin{tabular}{r|c c c}
		&box topology&uniform topology &product topology\\
		\hline\question{(a)}
		$f$&not continuous&not continuous&continuous \\
		$g$&not continuous&continuous&continuous\\
		$h$&not continuous&continuous&continuous\\
		\hline\question{(b)}
		$\mathbf w$&does not converge&does not converge&converges\\
		$\mathbf x$&does not converge&converges&converges\\
		$\mathbf y$&does not converge&converges&converges\\
		$\mathbf z$&converges&converges&converges
	\end{tabular}
\end{center}
\end{document}

### 2018-01-28 Topology/Paper/glossary.tex
init commit

\usepackage[toc,xindy]{glossaries}

\makenoidxglossaries

\newglossaryentry{set}
{
	name={set},
	description={A collection of objects}
}
\newglossaryentry{vertex}
{
	name={vertex},
	description={A point or node in a graph},
	plural={verticies}
}
\newglossaryentry{edge}
{
	name={edge},
	description={A connection or line between points in a graph}
}
\newglossaryentry{connected}
{
	name={connected},
	description={A graph where one may start at any point and could follow edges and eventually get to any other point}
}
\newglossaryentry{multigraph}
{
	name={multigraph},
	description={Like a graph, but multiple \glspl{edge} may connect the same \gls{vertex} pair, and an edge may connect a \glx{vertex} to itself}
}
\newglossaryentry{complete}
{
	name={complete graph},
	description={A graph with all possible \glspl{edge} included, the notation $k_n$ is used to denote the \gls{complete} with $n$ \glspl{vertex}}
}
\newglossaryentry{face}
{
	name={face},
	description={An section of the space we are embedding our graph in that is separated from the rest of the space by \glspl{edge}}
}
\newglossaryentry{contraction}
{
	name={contraction},
	description={A graph operation where one removes an edge by fusing two \glspl{vertex} together}
}
\newglossaryentry{subgraph}
{
	name={subgraph},
	description={$A$ is a \gls{subgraph} of $B$ if $A$'s \gls{vertex} \gls{set} and \gls{edge} \gls{set} are subsets of $B$'s \gls{vertex} \gls{set} and \gls{edge} \gls{set} respectively}
}

### 2018-01-28 Topology/Paper/paper.tex
init commit

\documentclass{article}
\input{../../definitions}
\input{glossary}
\title{Topological Graph Theory}
\begin{document}
\maketitle
\tableofcontents

\section{Introduction}
Topological graph theory is an entire field within topology and as such this paper is by no means meant to cover all of topological graph theory in any depth. This paper instead will first cover a rather shallow overview of the field, followed by a more in depth study of graphs and their genus. The overview will mainly be focused on giving a thorough understanding of what topological graph theory is as well as to briefly cover the history of the field. In giving an overview of the field we will cover some of the basic concepts and definitions needed for the more rigorous part of the paper; as this may be confusing, all definitions will be provided in a glossary at the end. After the overview we will dive into Kuratowski's Theorem, We will go through and attempt to have an intuitive understanding of a Kuratowski's Theorem and it's proof. After proving Kuratowski's Theorem, we will continue onto talking about generalizations of the theorem and map colorings, however their coverage will be rather shallow and lacking proofs.

\section{Overview}
\subsection{Graphs}
Before we talk about topological graph theory with any level of understanding we must first understand what a graph is.

A graph is generally defined as a \gls{set} of \glspl{vertex} combined with a \gls{set} of \glspl{edge} between \glspl{vertex}, however here it may be more useful to think about them visually with a simple representation.

Consider first a \gls{set} of points, this may be thought of as just drawing dots on a sheet of paper. Each of these points will be called a \gls{vertex}. Now we may start drawing lines between \glspl{vertex}. Lines may cross over each other and need not be straight. There is no requirement that all \glspl{vertex} have a line going to it. Each of these lines are called an \gls{edge}. We will simply insist that no \gls{edge} connects two \glspl{vertex} and that we do not have multiple \glspl{edge} between the same pair of \glspl{vertex}.

Once we have drawn this we have a representation of a graph. If we were to move the \glspl{vertex} around on the paper but leave them having the same \glspl{edge} (the same \glspl{vertex} are connected to the point as they were before). we would be left with the same graph. That is to say, it doesn't mater where we put a \gls{vertex} on our sheet, the graph exists independently of the representation we draw.

\subsection{K\"onigsberg, and it's seven bridges}

Consider the following photo-realistic drawing of the city of K\"onigsberg.

\input{Konigsberg.pdf_tex}

Now the question is, if we get to choose where we start, can we go for a stroll and cross every bridge exactly once?

I first came across this question in the 8\textsuperscript{th} grade, and it was presented to us during geometry class. While undoubtedly an interesting problem, it is quite misleading to try and think of this as a geometry problem. Instead we will try and reduce it to a graph problem.

Let us start by thinking of every island as a \gls{vertex} and every bridge as an \gls{edge}. We find the following graph.

\begin{center}
\begin{tikzpicture}[auto, node distance=3cm, every loop/.style={},
                    thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries}]

  \node[main node] (1) {$A$};
  \node[main node] (2) [below of=1] {$B$};
  \node[main node] (3) [below of=2] {$C$};
  \node[main node] (4) [right of=2] {$D$};

  \path[every node/.style={font=\sffamily\small}]
    (1) edge node [right] {$1$} (4)
        edge [bend right] node[left] {$2$} (2)
    (2) edge [bend right] node [right] {$3$} (1)
        edge node {$4$} (4)
        edge [bend right] node[left] {$5$} (3)
    (3) edge [bend right] node [right] {$6$} (2)
    (4) edge node [right] {$7$} (3);
\end{tikzpicture}
\end{center}

It is worth noting two things about the above diagram. First that the labels on the \glspl{vertex} and \glspl{edge} are unrelated to the problem, but have been added simply to make referring to parts of the graph much easier. Second that whatever the above image depicts, does not fit our definition of a graph. %TODO add glossary entry for graph.

Notice that \gls{edge} $2$ and \gls{edge} $3$ both connect \gls{vertex} $A$ to $B$, as well \glspl{edge} $5$ and $6$ do for $B$ and $C$. This is a strict violation of our definition for a graph. The issue of course then comes to what would one call such a beast as this where, presumably, one is able to have as many connections between any pair of \glspl{vertex} and could even have connections from a \gls{vertex} to itself.

I am particularly glad that you're paying enough attention to notice that the diagram does not depict a graph. This is what we will refer to as a \gls{multigraph}. It is worth noting that graphs are a type of \gls{multigraph}, so anything we show to be true for all \glspl{multigraph}, is also true for all graphs.

Now to solve this problem we need to make one simple observation about how we walk. If we are to go to island (or vertex) we must also leave that island, unless it is the last island we arrive on. This means, that with the exception of the island we start on and end on, each island must have an even number of bridges connected to it. On the \gls{multigraph} we would say that we need all \glspl{vertex} but a start and end \gls{vertex} to have an even number of edges. If we look at the \gls{multigraph} above, we have four \glspl{vertex} that have an odd number of \glspl{edge} connected to them.

\subsection{History}
%TODO add more to section
The seven bridges of K\"onigsberg problem was solved by Euler %TODO Citation (wikipedia for seven bridges of konigsberg)
in 1736. In mathematics this problem is of great historical significance as it is considered to be the beginning of graph theory as well as a sort of precursor to topology. %TODO Citation

\section{Planar Graphs}

Consider the following graph.

\begin{center}
\begin{tikzpicture}[auto, node distance=3cm, every loop/.style={},
                    thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries}]

  \node[main node] (1) {$A$};
  \node[main node] (2) [below of=1] {$B$};
  \node[main node] (3) [right of=2] {$C$};
  \node[main node] (4) [right of=1] {$D$};

  \path[every node/.style={font=\sffamily\small}]
    (1) edge node {} (4)
    	edge node {} (3)
    (2) edge node {} (1)
        edge node {} (4)
    (3) edge node {} (2)
    (4) edge node {} (3);
\end{tikzpicture}
\end{center}

This graph is called a \gls{complete} as every \gls{vertex} is connected to every other \gls{vertex} by an \gls{edge}; in fact this graph in particular is called $K_4$ as it is the complete four vertex graph. We would like to find out if we can draw this above graph without having any lines crossing. We can in fact draw this graph without any intersections and for any skeptics who may being reading this, the below is $k_4$ without any \glspl{edge} intersecting.

\begin{center}
\begin{tikzpicture}[auto, node distance=3cm, every loop/.style={},
                    thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries}]

  \node[main node] (1) {$A$};
  \node[main node] (2) [below of=1] {$B$};
  \node[main node] (3) [below right of=2] {$C$};
  \node[main node] (4) [below right of=1] {$D$};

  \path[every node/.style={font=\sffamily\small}]
    (1) edge node {} (4)
    	edge [bend right = 100]node {} (3)
    (2) edge node {} (1)
        edge node {} (4)
    (3) edge node {} (2)
    (4) edge node {} (3);
\end{tikzpicture}
\end{center}

So if this graph can be drawn without intersection, can any graph be drawn without intersections? If some can and some can't how do we tell which can be drawn and which can not?

\subsection{Kuratowski's Theorem}
Kuratowski's theorem tell us exactly what graphs can be drawn on a plane or sphere. We say either a plane or sphere as it turns out to be the same question. %TODO prove that drawing on plane and sphere is same question
Now before we tackle the theorem let's lay down some terminology.

\subsubsection{Terminology: face}

Consider the following graph.

\begin{center}
	\begin{tikzpicture}[auto, node distance=3cm, every loop/.style={},
	thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries}]

	  \node[main node] (1) {$A$};
	  \node[main node] (2) [below left of=1] {$B$};
	  \node[main node] (3) [below right of=1] {$C$};

	  \path[every node/.style={font=\sffamily\small}]
	  (1) edge node {} (2)
		  edge node {} (3)
	  (2) edge node {} (3);

	\end{tikzpicture}
\end{center}

We say this graph has two \glspl{face}. One \gls{face} is easy to see and contained within triangle $ABC$. The other \gls{face} is a bit harder to see, however it is all the space outside of the triangle $ABC$. We may call this second face the outer \gls{face} for this drawing of the graph, however it is also possible to draw it such that the inner face may be the outer face. You can think of this as kind of turning the triangle inside out.

A face only makes sense to talk about for a graph that can be embedded in a certain space. For example the graph $K_4$ may look like it has $5$ faces in the following drawing.

\begin{center}
	\begin{tikzpicture}[auto, node distance=3cm, every loop/.style={},
	thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries}]

	\node[main node] (1) {$A$};
	\node[main node] (2) [below of=1] {$B$};
	\node[main node] (3) [right of=2] {$C$};
	\node[main node] (4) [right of=1] {$D$};

	\path[every node/.style={font=\sffamily\small}]
	(1) edge node {} (4)
	edge node {} (3)
	(2) edge node {} (1)
	edge node {} (4)
	(3) edge node {} (2)
	(4) edge node {} (3);
	\end{tikzpicture}
\end{center}
This would be wrong as a face assumes a drawing without \glspl{edge} intersecting. This can be rectified if the graph can be drawn without intersection and thus we find this drawing.
\begin{center}
	\begin{tikzpicture}[auto, node distance=3cm, every loop/.style={},
	thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries}]

	\node[main node] (1) {$A$};
	\node[main node] (2) [below of=1] {$B$};
	\node[main node] (3) [below right of=2] {$C$};
	\node[main node] (4) [below right of=1] {$D$};

	\path[every node/.style={font=\sffamily\small}]
	(1) edge node {} (4)
	edge [bend right = 100]node {} (3)
	(2) edge node {} (1)
	edge node {} (4)
	(3) edge node {} (2)
	(4) edge node {} (3);
	\end{tikzpicture}
\end{center}
This means there are actually $4$ \glspl{face} in $k_4$.

\subsubsection{Terminology: contraction}

Let us consider the following graph.

\begin{center}
	\begin{tikzpicture}[auto, node distance=3cm, every loop/.style={},
	thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries}]

	\node[main node] (1) {$r$};
	\node[main node] (2) [below right of=1] {$B$};
	\node[main node] (3) [left of=1] {$A$};
	\node[main node] (4) [below left of=2] {$s$};
	\node[main node] (5) [left of=4] {$C$};

	\path[every node/.style={font=\sffamily\small}]
	(1) edge node {$R$} (4)
	edge node {$a$} (3)
	(2) edge node {$b_r$} (1)
	edge node {$b_s$} (4)
	(4) edge node {$c$} (5);
	\end{tikzpicture}
\end{center}

We wish to preform a \gls{contraction} on \gls{edge} $R$. To be clear all graph \glspl{contraction} are on \glspl{edge}. So we will make a new \gls{vertex}, $r\cdot s$ which has all the \glspl{edge} of $r$ and all the \glspl{edge} of $s$ except the \gls{edge} we are contracting across. In this case the \gls{edge} we are contracting across is $R$ and thus we get the following \gls{multigraph}.

\begin{center}
	\begin{tikzpicture}[auto, node distance=3cm, every loop/.style={},
	thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries}]

	\node[main node] (1) {$r\cdot s$};
	\node[main node] (2) [right of=1] {$B$};
	\node[main node] (3) [above left of=1] {$A$};
	\node[main node] (4) [below left of=1] {$C$};

	\path[every node/.style={font=\sffamily\small}]
	(1)	edge node {$a$} (3)
	(2) edge [bend right] node {$b_r$} (1)
		edge [bend left] node {$b_s$} (1)
	(4) edge node {$c$} (1);
	\end{tikzpicture}
\end{center}

This can then be reduced into a graph again by simply treating $b_r$ and $b_s$ as the same edge. This operation is particularly important as we will prove that if a graph is planar, then so is any graph or \gls{multigraph} obtained by contracting an \gls{edge}. The proof for this will be provided.
%TODO put refrence to proof for contraction of planar graph is planar

\subsubsection{Terminology: subgraph}
We can say that a graph $A$ is a subgraph of another graph $B$, if all \glspl{vertex} in $A$ are also in $B$ and each \glspl{edge} in $A$ is also in $B$.

\subsubsection{Groundwork}
Here we would like to prove some lemmas that we would like to use while proving Kuratowski's theorem.

First we would like to add a single limit point to

\printnoidxglossaries

\bibliographystyle{unsrt}
\bibliography{bibliography}

\end{document}

### 2018-03-20 Algebra/Homework/Homework.tex
what da hell

@@
 
-Let $a,b\in\mathbb R$ be given.
-Now let us investigate the derivative of $x^2 + ax + b$ with respect to $x$.
-Any student of calculus can tell you $\derivative{x^2+ax+b}{x} = 2x+a$.
-Now consider that when $x < \frac a2$
+Let $f(x) = x^2+ax+b$, thus $f'(x) = 2x+a$.
+$f'(x)$ is linear so there exists only one $x\in\mathbb R$ for which $f'(x) = 0$, and thus this $x$ is a global extrema for $f$, so $f$ can not be surjective.
+Now consider $x_1 = -\frac a2-1$ and $x_2=-\frac a2+1$, thus
+\begin{align*}
+f(x_1) &= \left(-\frac a2-1\right)^2+a\left(-\frac a2-1\right)+b \\
+&= \frac{a^2}4+2\frac a2+1-\frac{a^2}2-a+b\\
+&=\frac{a^2}4+1+b\\
+f(x_2) &= \left(-\frac a2+1\right)^2+a\left(-\frac a2+1\right)+b \\
+&= \frac{a^2}4-2\frac a2+1-\frac{a^2}2+a+b\\
+&= \frac{a^2}4+1+b
+\end{align*}
+
+so $f$ must be 1-1.
 
 \subsubsection{Question 23}
+
+\def\RB{}
+\def\LB{}
+
+\marginnote{Ugly proof:}
+First let us show that there exists some bijection from $\mathbb N$ to $\ZNonNegative^2$.
+Consider the 1 norm on $\ZNonNegative^2$, defined as $\norm{(a,b)}_1 = a + b$.
+Then we may partition $\ZNonNegative^2$ into subsets $P_n = \setbuilder{x\in\ZNonNegative^2}{\norm x_1 = n}$, for any $n\in \ZNonNegative$.
+Notice that for $(a,b)\in P_n$ then $a \le n$ and $b \le n$, thus forcing $P_n$ to be finite.
+Now we can construct a function mapping from $\mathbb N$ to $\ZNonNegative^2$ by giving each element of $P_1$ a number from $1$ to $\card{P_0}$ (inclusive), then the next $\card{P_1}$ will be given to elements of $P_1$ and so on infinitely.
+Notice that by construction $x\not= y \implies f(x) \not= f(y)$, so we get this being 1-1, additionally for any $(a,b) \in \ZNonNegative^2$, $(a,b)\in P_{a+b}$ and thus receives a number greater than $\sumfrom{n=0}{a+b-1}{\card{P_n}}$ and less than or equal to $\sumfrom{n=0}{a+b}{\card{P_n}}$.
+This means that we can label each element of $\ZNonNegative$ with a single natural number and thus have a bijection.
+
+Now we can also construct a trivial bijection, $h:\ZNonNegative^2\to S$ as $h(a,b) = 2^a3^b$. Now we may compose the bijections to get a 1-1 correspondence $\mathbb N = S$ onto $T$.
+
+\bigskip
+
+\marginnote{Nice proof:}
+First notice that $T \subset S$ so there exists the trivial injective function from $T$ to $S$.
+Second notice that $f:S\to T$ defined as $f(s)=2^s$ is both well defined as injective.
+By the  \href{https://en.wikipedia.org/wiki/Schr\%C3\%B6der\%E2\%80\%93Bernstein_theorem}{Schr\"oder-Bernstein theorem} there must be some bijection from $S$ to $T$.
+
 \subsubsection{Question 28}
+
+Let $S$ be a finite set, with $f:S\to S$.
+Now let $f(x) = f(y)$, for some $x\not=y$, then there remain $\card S - 2$ elements in $S\setminus\set{x,y}$ and $\card S - 1$ elements in $S\setminus\set{f(x)}$.
+This means that for any definition of $f$ on $S\setminus\set{x,y}$ it can not possibly be onto $S\setminus\set{f(x)}$.
+We have now shown $f$ not being 1-1 implies $f$ not being onto, by contrapositive $f$ being onto implies $f$ is 1-1.
+
 \subsubsection{Question 29}
 
+Let $S$ be a finite set, with $f:S\to S$ injective.
+Now as $f$ is 1-1 each $s\in S$ has a unique $f(s)\in S$, so $f(S)$ must have exactly $\card S$ unique elements, thus $f(S) \subset S$ with exactly $\card S$ elements.\footnote{$f(A)$ is defined as $\setbuilder{y\in\range{f}}{\Exists{x\in \domain{f}}{f(x) = y}}$ when $A \subset \domain{f}$ and $A\not\in\domain{f}$.} Because $S$ is finite, this implies $f(S) = S$.
+
+\subsection{Section 4}
+
+\subsubsection{Question 5}
+
+\question{(a)} First identity:
+\begin{align*}
+f^2g^2&=ffgg\\
+&=f(fg)g\\
+&=f(gf)f\\
+&=(fg)^2
+\end{align*}
+
+\question{(b)} Second Identity: Let $i$ be the identity function.
+\begin{align*}
+\inv f\inv ggf &= i\\
+\inv f\inv ggf\inv{(gf)} &= i\inv{(gf)}\\
+=\inv f\inv g i&=i\inv{(fg)}\\
+=\inv f\inv g&=\inv{(fg)}
+\end{align*}
+
+\subsubsection{Question 9}
+\subsubsection{Question 10}
+\subsubsection{Question 14}
+\subsubsection{Question 21}
+\subsubsection{Question 27}
+\subsubsection{Question 30}
+\subsubsection{Question 32}
+
 \end{document}

### 2018-03-20 ComputationalLinearAlgebra/Homework/Homework1.tex
what da hell

\documentclass{article}
\input{../../definitions.tex}

\renewcommand{\thesubsection}{\thesection.\alph{subsection}}

\title{Computational Linear Algebra\\ Homework 1}
\author{Benji Altman}

\begin{document}
	\maketitle
	\tableofcontents

	\section{Question 1}
	See attached R code.

	\section{Question 2}
	\subsection{}
	See attached R code.

	\subsection{}
	See attached R code.
	\subsection{}
	Let $f(x) = \cos(x)^2 + \sin(x) - 1$, then we find that $f'(x) = - 2\sin(x)\cos(x) + \cos(x)$. Then the tangent line at $x_0$ for any $x_0\in\mathbb R$ to $f$ is 
	\begin{align*}
	\ell(x) &= f'(x_0)(x-x_0) + f(x_0)\text{.}
	\end{align*}
	We now solve for $x$ when $\ell(x) = 0$.
	\begin{align*}
	\ell(x) &= 0 \\
	f(x_0)(x-x_0)+f'(x_0) &= 0\\
	f(x_0)(x-x_0) &= -f'(x_0) \\
	x-x_0 &= -\frac{f'(x_0)}{f(x_0)}\\
	x  &= x_0-\frac{f'(x_0)}{f(x_0)}\\
	&=x_0+\frac{2\sin(x_0)\cos(x_0)-\cos(x_0)}{\cos(x_0)^2 + \sin(x_0)-1}
	\end{align*}

	This means that in newton's method for $f$,
	\[
	x_{i+1} = x_i+\frac{2\sin(x_i)\cos(x_i)-\cos(x_i)}{\cos(x_i)^2 + \sin(x_i)-1}\text{.}
	\]
	\subsection{}
	See attached R code.
	\subsection{}
	See attached R code.
	\section{Question 3}
	We have the matrix
	\[
	A = 
	\begin{bmatrix}
	1&2&3&x\\
	4&5&x&6\\
	7&x&8&9\\
	x&10&11&12
	\end{bmatrix}
	\]
	and we wish to solve for $x$ when $\det A = 1000$. We will then let $f(x) = \det A - 1000$ and we may solve for some roots.

	The rest of this problem will be doe in R; see attached R code.

	\section{Question 4}
	See attached R code.
\end{document}

### 2018-03-20 ComputationalLinearAlgebra/Homework/Homework3.Rmd
what da hell

---
title: "Homework 3"
author: "Benji Altman"
date: "February 19, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1

### Part a

So first notice that $L_k = I - E_k$ for some $n\times n$ matrix $E_k$. Notice that $$E_k = 
\begin{bmatrix}
0 \\
 & \ddots \\ 
 & & 0 \\
 & & \ell_{k+1,k} & 0 \\
 & & \ddots& & \ddots \\
 & & \ell_{n,k} & & & 0
\end{bmatrix}
$$

Notice now that $\ell_ke_k^T = E_k$ as $f(\vec v) = e_k^T \vec v$ will take a column vector $\vec v$ and put it into the $k^{\text{th}}$ column of a matrix. Additionally we would like to notice that ${E_k}^2 = 0$ as $E_k$ has zeros on the diagonal and all indicies above it, thus for any index $i,j$ in ${E_k}^2$ the dot product that gives it would contain a zero in either the first or second vector in every index.

Now let $A$ be the matrix that we would like to show is $T_k^{-1}$
\begin{align*}
L_k &= I-E_k \\
A &= I+E_k \\
L_k A &= (I-E_k)(I+E_k) \\
&= I^2-(E_k)^2 \\
&= I
\end{align*}
And now by definition $A$ is the inverse of $T_k$.

### Part b

Now notice that 
\begin{align*}
\prod_{k=1}^nT_k^{-1} &= \prod_{k=1}^n (I+E_k) \\
&= (I+E_1)\cdot(I+E_2)\cdots(I+E_n) \\
&= (I^2+E_1 + E_1 + E_2 + E_1\cdot E_2)(I+E_3)\cdots(I+E_n) \\
&= (I + E_1 + E_2)(I+E_3)\cdots(I+E_n) \\
&= \ldots \\
&= I + E_1 + E_2 + \ldots + E_n
\end{align*}

Again notice that $E_aE_b = 0_{n\times n}$ as $E_a$ and $E_b$ have zeros on the diagonal and everywhere above it.

## Question 2

### Part a

$$A = 
\begin{bmatrix}
4&-1&-1&0&0&0&0&0 \\
-1&4&0&-1&0&0&0&0 \\
-1&0&4&-1&-1&0&0&0\\
0&-1&-1&4&0&-1&0&0\\
0&0&-1&0&4&-1&-1&0\\
0&0&0&-1&-1&4&0&-1\\
0&0&0&0&-1&0&4&-1\\
0&0&0&0&0&-1&-1&4\\
\end{bmatrix}
$$
 and

$$ 
b = 
 \begin{bmatrix}
 5 \\ 15 \\ 0 \\ 10 \\ 0 \\ 10 \\ 20 \\ 30
 \end{bmatrix}
$$

### Part b
```{r}
#Takes in matrix, A, and does a L-U decomposition
#Complete, tested
LUDecompose = function(A)
{
  if(nrow(A) != ncol(A))
    return(NULL)
  out = new.env()
  out$U = A
  out$L = diag(nrow(A))

  #now lets start getting to it
  i = 1
  while(i < nrow(A))
  {
    #make ith column 0
    row = i + 1
    while(row <= nrow(A))
    {
      #set row
      op = out$U[row, i] / out$U[i, i]
      out$L[row, i] = op
      out$U[row,] = out$U[row,] - out$U[i,] * op
      row = row + 1
    }
    i = i + 1
  }
  return(out)
}
#Now to type in A
A = matrix(
  c(4,-1,-1,0,0,0,0,0,
    -1,4,0,-1,0,0,0,0,
    -1,0,4,-1,-1,0,0,0,
    0,-1,-1,4,0,-1,0,0,
    0,0,-1,0,4,-1,-1,0,
    0,0,0,-1,-1,4,0,-1,
    0,0,0,0,-1,0,4,-1,
    0,0,0,0,0,-1,-1,4),
  nrow = 8, ncol = 8, byrow = TRUE)

factorization = LUDecompose(A)
print(factorization$U)
print(factorization$L)
```

### Part c

```{r, echo=FALSE}
mySolve=function(L,U,b,tol=1e-10){

  n=nrow(L)

  # First solve Ly=b 
  y = rep(0,n)        # pre-allocate a vector y with 0s in it.
  if(abs(L[1,1])<tol) stop('There is a zero on the diagonal of L')
  y[1] = b[1]/L[1,1]  # Fill in the 1st value of y
  for (j in 2:n ) {
    if(abs(L[j,j])<tol) stop('There is a zero on the diagonal of L')
    y[j] = (b[j] - L[j,1:(j-1)]%*%y[1:(j-1)])/L[j,j]
  }

  # Then solve Ux=y 
  x = rep(0,n)        # pre-allocate a vector x with 0s in it.
  if(abs(U[n,n])<tol) stop('There is a zero on the diagonal of U')
  x[n] = y[n]/U[n,n]  # Fill in the nth value of x
  for (j in (n-1):1 ) {
    if(abs(U[j,j])<tol) stop('There is a zero on the diagonal of U')
    x[j] = (y[j] - U[j,(j+1):n]%*%x[(j+1):n])/U[j,j]
  }
  return(x)
}
```

```{r}
mySolve(factorization$L, factorization$U, c(5,15,0,10,0,10,20,30))
```

### Part d

```{r}
mySolve(factorization$L, factorization$U, c(5,15,0,10,0,10,30,40))
```

### Part e

```{r}
solve(A)
```

## Question 6

Take a matrix $A$, one may define $x_i$ such that $x_i$ maximizes the $i^{\text{th}}$ value in $Ax_i$. One does this by letting ${x_i}_j = \begin{cases} 1 & A_{i,j}\ge0\\-1&A_{i,j}<0\end{cases}$. Now we may maximize $||Ax_i||_\infty$, by letting $i$ be the row in $A$'s sum of absolute values is greatest. This means that $|| A||_\infty$ is the maximum sum of absolute values of rows

## Question 7

let
$$
A=\begin{bmatrix}
-1 & 0 & 1 \\
3 & 1 & 1 \\
2 & 0 & 1 
\end{bmatrix} 
$$
Now we will do this in steps

$$
P_1 = \begin{bmatrix}
0&1&0\\
1&0&0\\
0&0&1
\end{bmatrix}
$$
$$
A_1 = \begin{bmatrix}
3&1&1\\
-\frac13&\frac13&\frac43\\
\frac23&-\frac23&\frac13
\end{bmatrix}
$$
$$
P_2 = \begin{bmatrix}
0&1&0\\
0&0&1\\
1&0&0
\end{bmatrix}
$$
$$
A_2 = \begin{bmatrix}
3&1&1\\
\frac23&-\frac23&\frac13\\
-\frac13&-\frac12&\frac32
\end{bmatrix}
$$
Thus we have 
$$
\begin{bmatrix}
0&1&0\\0&0&1\\1&0&0
\end{bmatrix}
\begin{bmatrix}
-1 & 0 & 1 \\
3 & 1 & 1 \\
2 & 0 & 1 
\end{bmatrix}
=
\begin{bmatrix}
1&0&0\\\frac23&1&0\\-\frac13&-\frac12&1
\end{bmatrix}
\begin{bmatrix}
3&1&1\\0&-\frac23&\frac13\\0&0&\frac32
\end{bmatrix}
$$

### 2018-03-20 MathPapers/Seminar/DFAs.tex
what da hell

\documentclass{article}
\input{../../definitions}
\title{Deterministic Finite Automata}
\begin{document}
	\maketitle

	\question{1.} Make a DFA for the language of all binary integers.

	\bigskip
	\bigskip
	\bigskip
	\bigskip
	\bigskip
	\bigskip

	\question{2.} Make a DFA for the language of all binary numbers with finite representation (only rational numbers that do not need repeating representation).
	\bigskip
	\bigskip
	\bigskip
	\bigskip
	\bigskip
	\bigskip

	\question{3.} Make a DFA for numbers written in scientific notation.
	\bigskip
	\bigskip
	\bigskip
	\bigskip
	\bigskip
	\bigskip

	\question{4.} Make a DFA for the language on $\set{a,b}$ with no two $b$'s in a row.
	\bigskip
	\bigskip
	\bigskip
	\bigskip
	\bigskip
	\bigskip

	\question{5.} Make a DFA for the language on $\set{a,b}$ with no $b$ by itself.
	\bigskip
	\bigskip
	\bigskip
	\bigskip
	\bigskip
	\bigskip

	\question{6.} Make a DFA for the language $\set{\lambda, a, aa, aab, aaba, aabaa, aabaab, \ldots}$
\end{document}

### 2018-03-20 Topology/Homework/hw6.tex
what da hell

\documentclass{article}
\input{../../definitions.tex}
\input{../topology.tex}

\title{Homework 6}

\begin{document}
\maketitle

\question{23.8} First we will use a theorem from real analysis

\begin{theorem}
	Let $(a_n)$ be a convergent sequence in $\mathbb R$ with standard topology and $(b_n)0$ be a sequence in $\mathbb R$. The sequence $(a_n+b_n)$ converges iff $(b_n)$ converges.
\end{theorem}

A proof for this may be provided if desired, however this is considered to be outside the scope of this course.

Let us choose $x\in\mathbb R^\omega$ and let us consider this to be $(b_n)$. Let us also choose $\epsilon\in\ooint 01$, then the open ball around $x$ is defined as $\setbuilder{(s_n)}{\All{n\in\mathbb N}{\abs{s_n-b_n} < \frac\epsilon n}}$. This means that any element $s$ in our open ball may be written as $\left( b_n + \frac\delta n \right)$ for some $\delta \in \ooint 0\epsilon$. We now use our theorem from above consider $\frac\delta n$ to be our sequence $(a_n)$. Thus we may cover $\mathbb R^\omega$ with two open non-intersecting sets, The set of all convergent sequences in $\mathbb R$ with standard topology and the set of all non-convergent sequences in $\mathbb R$ with the standard topology.

\question{23.11}

\end{document}

### 2018-03-20 Topology/Paper/glossary.tex
what da hell

@@
 	name={edge},
-	description={A connection or line between points in a graph}
+	description={A connection or line between verticies in a graph}
 }
@@
 	name={multigraph},
-	description={Like a graph, but multiple \glspl{edge} may connect the same \gls{vertex} pair, and an edge may connect a \glx{vertex} to itself}
+	description={Like a graph, but multiple edges may connect the same vertex pair, and an edge may connect a vertex to itself}
 }
@@
 	name={complete graph},
-	description={A graph with all possible \glspl{edge} included, the notation $k_n$ is used to denote the \gls{complete} with $n$ \glspl{vertex}}
+	description={A graph with all possible edges included, the notation $K_n$ is used to denote the complete with $n$ verticies}
 }
@@
 	name={face},
-	description={An section of the space we are embedding our graph in that is separated from the rest of the space by \glspl{edge}}
+	description={An section of the space we are embedding our graph in that is separated from the rest of the space by edges}
 }
@@
 	name={contraction},
-	description={A graph operation where one removes an edge by fusing two \glspl{vertex} together}
+	description={A graph operation where one removes an edge by fusing two verticies together}
 }
@@
 	name={subgraph},
-	description={$A$ is a \gls{subgraph} of $B$ if $A$'s \gls{vertex} \gls{set} and \gls{edge} \gls{set} are subsets of $B$'s \gls{vertex} \gls{set} and \gls{edge} \gls{set} respectively}
+	description={$A$ is a subgraph of some graph $\mathcal G$ iff you could add verticies and edges to $A$ and somehow get $\mathcal G$}
 }
+\newglossaryentry{graph}
+{
+	name={graph},
+	description={A set of verticies and edges}
+}

### 2018-03-20 Topology/Paper/paper.tex
what da hell

@@
 \input{../../definitions}
+\input{../topology}
 \input{glossary}
@@
 \subsection{Graphs}
-Before we talk about topological graph theory with any level of understanding we must first understand what a graph is.
+Before we talk about topological graph theory with any level of understanding we must first understand what a \gls{graph} is.
 
-A graph is generally defined as a \gls{set} of \glspl{vertex} combined with a \gls{set} of \glspl{edge} between \glspl{vertex}, however here it may be more useful to think about them visually with a simple representation.
+A \gls{graph} is generally defined as a \gls{set} of \glspl{vertex} combined with a \gls{set} of \glspl{edge} between \glspl{vertex}, however here it may be more useful to think about them visually with a simple representation.
 
@@
 
-Once we have drawn this we have a representation of a graph.
+Once we have drawn this we have a representation of a \gls{graph}.
 If we were to move the \glspl{vertex} around on the paper but leave them having the same \glspl{edge} (the same \glspl{vertex} are connected to the point as they were before).
-we would be left with the same graph.
-That is to say, it doesn't mater where we put a \gls{vertex} on our sheet, the graph exists independently of the representation we draw.
+we would be left with the same \gls{graph}.
+That is to say, it doesn't mater where we put a \gls{vertex} on our sheet, the \gls{graph} exists independently of the representation we draw.
 
@@
 While undoubtedly an interesting problem, it is quite misleading to try and think of this as a geometry problem.
-Instead we will try and reduce it to a graph problem.
+Instead we will try and reduce it to a \gls{graph} problem.
 
-Let us start by thinking of every island as a \gls{vertex} and every bridge as an \gls{edge}. We find the following graph.
+Let us start by thinking of every island as a \gls{vertex} and every bridge as an \gls{edge}. We find the following \gls{graph}.
 
@@
 It is worth noting two things about the above diagram.
-First that the labels on the \glspl{vertex} and \glspl{edge} are unrelated to the problem, but have been added simply to make referring to parts of the graph much easier.
-Second that whatever the above image depicts, does not fit our definition of a graph.
-%TODO add glossary entry for graph.
+First that the labels on the \glspl{vertex} and \glspl{edge} are unrelated to the problem, but have been added simply to make referring to parts of the \gls{graph} much easier.
+Second that whatever the above image depicts, does not fit our definition of a \gls{graph}.
 
 Notice that \gls{edge} $2$ and \gls{edge} $3$ both connect \gls{vertex} $A$ to $B$, as well \glspl{edge} $5$ and $6$ do for $B$ and $C$.
-This is a strict violation of our definition for a graph.
+This is a strict violation of our definition for a \gls{graph}.
 The issue of course then comes to what would one call such a beast as this where, presumably, one is able to have as many connections between any pair of \glspl{vertex} and could even have connections from a \gls{vertex} to itself.
 
-I am particularly glad that you're paying enough attention to notice that the diagram does not depict a graph.
+I am particularly glad that you're paying enough attention to notice that the diagram does not depict a \gls{graph}.
 This is what we will refer to as a \gls{multigraph}.
-It is worth noting that graphs are a type of \gls{multigraph}, so anything we show to be true for all \glspl{multigraph}, is also true for all graphs.
+It is worth noting that \glspl{graph} are a type of \gls{multigraph}, so anything we show to be true for all \glspl{multigraph}, is also true for all \glspl{graph}.
 
@@
 
-Consider the following graph.
+Consider the following \gls{graph}.
 
@@
 
-This graph is called a \gls{complete} as every \gls{vertex} is connected to every other \gls{vertex} by an \gls{edge}; in fact this graph in particular is called $K_4$ as it is the complete four vertex graph.
-We would like to find out if we can draw this above graph without having any lines crossing.
-We can in fact draw this graph without any intersections and for any skeptics who may being reading this, the below is $k_4$ without any \glspl{edge} intersecting.
+This \gls{graph} is called a \gls{complete} as every \gls{vertex} is connected to every other \gls{vertex} by an \gls{edge}; in fact this \gls{graph} in particular is called $K_4$ as it is the complete four vertex \gls{graph}.
+We would like to find out if we can draw this above \gls{graph} without having any lines crossing.
+We can in fact draw this \gls{graph} without any intersections and for any skeptics who may being reading this, the below is $K_4$ without any \glspl{edge} intersecting.
 
@@
 
-So if this graph can be drawn without intersection, can any graph be drawn without intersections? If some can and some can't how do we tell which can be drawn and which can not?
+So if this \gls{graph} can be drawn without intersection, can any \gls{graph} be drawn without intersections? If some can and some can't how do we tell which can be drawn and which can not?
 
-\subsection{Kuratowski's Theorem}
-Kuratowski's theorem tell us exactly what graphs can be drawn on a plane or sphere.
+\section{Kuratowski's Theorem}
+Kuratowski's theorem tell us exactly what \glspl{graph} can be drawn on a plane or sphere.
 We say either a plane or sphere as it turns out to be the same question.
@@
 
+\subsection{Terminology}
+
 \subsubsection{Terminology: face}
 
-Consider the following graph.
+Consider the following \gls{graph}.
 
@@
 
-We say this graph has two \glspl{face}.
+We say this \gls{graph} has two \glspl{face}.
 One \gls{face} is easy to see and contained within triangle $ABC$.
 The other \gls{face} is a bit harder to see, however it is all the space outside of the triangle $ABC$.
-We may call this second face the outer \gls{face} for this drawing of the graph, however it is also possible to draw it such that the inner face may be the outer face.
+We may call this second face the outer \gls{face} for this drawing of the \gls{graph}, however it is also possible to draw it such that the inner face may be the outer face.
 You can think of this as kind of turning the triangle inside out.
 
-A face only makes sense to talk about for a graph that can be embedded in a certain space. For example the graph $K_4$ may look like it has $5$ faces in the following drawing.
+A face only makes sense to talk about for a \gls{graph} that can be embedded in a certain space. For example the \gls{graph} $K_4$ may look like it has $5$ faces in the following drawing.
 
@@
 \end{center}
-This would be wrong as a face assumes a drawing without \glspl{edge} intersecting. This can be rectified if the graph can be drawn without intersection and thus we find this drawing.
+This would be wrong as a face assumes a drawing without \glspl{edge} intersecting. This can be rectified if the \gls{graph} can be drawn without intersection and thus we find this drawing.
 \begin{center}
@@
 \end{center}
-This means there are actually $4$ \glspl{face} in $k_4$.
+This means there are actually $4$ \glspl{face} in $K_4$.
 
@@
 
-Let us consider the following graph.
+Let us consider the following \gls{graph}.
 
@@
 
-This can then be reduced into a graph again by simply treating $b_r$ and $b_s$ as the same edge.
-This operation is particularly important as we will prove that if a graph is planar, then so is any graph or \gls{multigraph} obtained by contracting an \gls{edge}.
+This can then be reduced into a \gls{graph} again by simply treating $b_r$ and $b_s$ as the same edge.
+This operation is particularly important as we will prove that if a \gls{graph} is planar, then so is any \gls{graph} or \gls{multigraph} obtained by contracting an \gls{edge}.
 The proof for this will be provided.
@@
 \subsubsection{Terminology: subgraph}
-We can say that a graph $A$ is a subgraph of another graph $B$, if all \glspl{vertex} in $A$ are also in $B$ and each \glspl{edge} in $A$ is also in $B$.
+We can say that a \gls{graph} $A$ is a \gls{subgraph} of another \gls{graph} $B$, if all \glspl{vertex} in $A$ are also in $B$ and each \glspl{edge} in $A$ is also in $B$.
 
-\subsubsection{Groundwork}
+\subsection{Groundwork}
 Here we would like to prove some lemmas that we would like to use while proving Kuratowski's theorem.
 
-First we would like to add a single limit point to
+\begin{theorem}[Spherical and Planar graphs are the same] \label{sphere=plane}
+	If and only if a \gls{graph} may be drawn on a plane with no \glspl{edge} intersection then it may be drawn on a sphere without self intersection.
+\end{theorem}
 
-\printnoidxglossaries
+\begin{proof}
+	First we know from topology that the punctured sphere is homeomorphic to the plane, planarity of a graph is the same as saying that the graph may be drawn on a punctured sphere without any self intersection.
+Now it's trivial to say that anything drawn on a punctured sphere may be drawn on the sphere.
+Now it will suffice to show only that a graph drawing will never cover the entire sphere as then there exists some at which to puncture.
+\end{proof}
+
+\printnoidxglossary
 

### 2018-03-20 ComputationalLinearAlgebra/Homework/Homework1.R

@@ -1,0 +1,257 @@
+#Homework 1 for computational Linear Algebra
+#
+#Offie space problem
+#Problem 1
+print("Problem 1:")
+accounts=floor(runif(10000,10000,10000000))#deal with cents, should work better
+mysecretaccount = 0
+days = 0
+while(mysecretaccount < 100000000)
+{
+  days = days + 1
+  tmpBal = accounts * (1 + .05 / 365)
+  accounts = floor(tmpBal)
+  funnledMoney = tmpBal - accounts
+  mysecretaccount = mysecretaccount + sum(funnledMoney)
+}
+print(sprintf("%d days to millionare status.", days))
+print('')
+print("Problem 2:")
+print("  Part A")
+print(sprintf("Should take %d bisections to get 8 decimal digits of percision", ceiling(log2(10 ^ 8))))
+
+print("  Part B")
+#Benji's bisection function
+#Finds a zero (within certain error) in a function given some bounds using bisection method
+# f is a function, f: R-> R where R is the set of real numbers (it should work on some other functions but be careful)
+# lowerBound is a bound, doesn't really mater if it's lower then upperBound
+# upperBound is another bound
+#   There is a reqiurement that f(upperBound) * f(lowerBound) <= 0
+# a maximal number of iterations (optional)
+# desired error (defaults to 10^-10)
+#Output of function is a data enviroment with the following paramaters
+# $value is a dataframe with $x and $y containing an x and y value of my guess for a root respecivly
+# $iterations is an non-negative integer, representing the number of bisections used
+# $error is the amount of error (upper bound - lower bound) for my guess
+BenjiBisect = function(f, lowerBound, upperBound, iterations=Inf, targetError = 10^-10)
+{
+  #helper function to handle points in R^2 more easily and avoid possibly costly calls of the f function
+  #Returns a data frame with x and y component, both of which will be floating point numbers
+  get = function(p){
+    out = new.env()
+    out$x = p
+    out$y = f(p)
+    return(out)
+  }
+  
+  #set l and u to lower and upper bound so they may be easier to use
[…]

### 2018-03-20 Cryptography/Crypto/Crypto/Program.cs

@@ -1,0 +1,46 @@
+﻿using System;
+using System.Numerics;
+
+namespace crypto
+{
+	static class Program
+	{
+		static void Main(string[] args)
+		{
+			uint b;
+			if(args.Length < 1 || !uint.TryParse (args [0], out b))
+				Console.WriteLine ("Need to pass in a positive integer followed by as many textual messages as you like");
+			else {
+				Console.WriteLine ($"Base: {args[0]}");
+				for(int i = 1; i < args.Length; i++)
+					Console.WriteLine ($"{args[i]} -> {encrypt(args[i], b)}");
+			}
+		}
+
+		static BigInteger encrypt(string str, uint b)
+		{
+			BigInteger msg = 1;
+			foreach (char c in str) {
+				msg *= 100;
+				if(c >= 'a' && c <= 'z')
+					msg += c - 'a';
+				else if(c >= 'A' && c <= 'Z')
+					msg += c - 'A';
+			}
+			msg *= 10;
+			msg += 1;
+			return msg.flip (b);
+		}
+
+		static BigInteger flip(this BigInteger number, BigInteger b)
+		{
+			BigInteger output = 0;
+			while(number != 0) {
+				output *= b;
+				output += number % b;
+				number /= b;
+			}
+			return output;
+		}
+	}
+}

### 2018-03-20 Cryptography/Crypto/Crypto/Properties/AssemblyInfo.cs

@@ -1,0 +1,27 @@
+﻿using System.Reflection;
+using System.Runtime.CompilerServices;
+
+// Information about this assembly is defined by the following attributes.
+// Change them to the values specific to your project.
+
+[assembly: AssemblyTitle ("Crypto")]
+[assembly: AssemblyDescription ("")]
+[assembly: AssemblyConfiguration ("")]
+[assembly: AssemblyCompany ("")]
+[assembly: AssemblyProduct ("")]
+[assembly: AssemblyCopyright ("bendy")]
+[assembly: AssemblyTrademark ("")]
+[assembly: AssemblyCulture ("")]
+
+// The assembly version has the format "{Major}.{Minor}.{Build}.{Revision}".
+// The form "{Major}.{Minor}.*" will automatically update the build and revision,
+// and "{Major}.{Minor}.{Build}.*" will update just the revision.
+
+[assembly: AssemblyVersion ("1.0.*")]
+
+// The following attributes are used to specify the signing key for the assembly,
+// if desired. See the Mono documentation for more information about signing.
+
+//[assembly: AssemblyDelaySign(false)]
+//[assembly: AssemblyKeyFile("")]
+

### 2018-03-20 NetworkScience/Random/HW2.js

@@ -1,0 +1,118 @@
+
+//original (with x and y disconnected)
+const ADJ_LIST = [
+	[], //a 0
+	[], //b 1
+	[1], //c 2
+	[1], //d 3
+	[0, 1], //e 4
+	[0], //f 5
+	[], //x 6
+	[]		//y 7
+];
+var opt1 = JSON.parse(JSON.stringify(ADJ_LIST));
+opt1[7].push(6);
+var opt2 = JSON.parse(JSON.stringify(ADJ_LIST));
+opt2[7].push(0, 1, 6);
+
+// function convertAdjListToMatrix(adj)
+// {
+// 	var size = adj.length;
+// 	var output = [];
+// 	for(var i = 0; i < size; i++)
+// 	{
+// 		var current = [];
+// 		current.length = size;
+// 		current.fill(false);
+// 		for(var j of adj[i])
+// 		{
+// 			current[j] = true;
+// 		}
+// 		output.push(current);
+// 	}
+// 	return output;
+// }
+
+function normalize(arr)
+{
+	var sum = arr.reduce((a, b) => a + b);
+	if (sum === 0)
+		return arr;
+	else
+		return arr.map(a => a / sum);
+}
+
+function authority(adj, hubScore)
+{
+	var output = [];
+	output.length = hubScore.length;
+	output.fill(0);
+	for (var i = 0; i < hubScore.length; i++)
+	{
+		for (var v of adj[i])
+		{
+			output[v] += hubScore[i];
+		}
+	}
+	return normalize(output);
+}
+
+function hub(adj, authorityScore)
+{
+	var output = [];
+	output.length = authorityScore.length;
+	output.fill(0);
+	for (var i = 0; i < authorityScore.length; i++)
+	{
+		for (var v of adj[i])
+		{
+			output[i] += authorityScore[v];
+		}
+	}
+	return normalize(output);
+}
+
+
+function simulate(graph, steps)
+{
+	var hubs = [];
+	var authorities = [];
+	hubs.length = authorities.length = graph.length;
+	hubs.fill(1 / hubs.length);
+	authorities.fill(1 / authorities.length);
+
+	console.log('\\begin{center}');
+	console.log("\\begin{tabular}{c|" + (function (c) {
+		var output = 'c';
+		while (c > 1) {
+			c--;
+			output += '|c';
+		}
+		return output;
+	})(graph.length) + '}');
+
+	console.log('name & a & b & c & d & e & f & x & y \\\\');
+	console.log('\\hline');
+
[…]

### 2018-03-23 Cryptography/MidTerm/cryptoMidterm.tex
done borked another computer

\documentclass{article}
\input{../../definitions}
\usepackage{csquotes}

\title{Cryptography and Number Theory\\Mid-Term writeup}

\begin{document}
	\maketitle
	\section{RSA, problems with small encryption exponents}
	This section will be handled backwards, in that part two of the question will be solved then part one. This is as part two is the general case of part one, so we will solve the general case then show it in action using part one as an example.

	\subsection{General case}
	Statement of Problem:
	\begin{displayquote}
		Suppose that $n$ people have RSA moduli $m_1, \ldots m_n$ and they all have encryption exponent $n$. Explain how a message (an integer less than each $m_i$) encrypted and sent to all $n$ people can be decrypted from the $n$ ciphertexts without factoring the $m_i$. This is why small encryption exponents should not be used.
	\end{displayquote}

	 Now it can be safely assumed that all $m_i$ are coprime. The reasoning for this is as follows. These are all just RSA moduli computed normally. If there was a significant chance that I would get two RSA moduli that share a divisor then an adversary, who is trying to crack my RSA modulus, would have a good shot if they keep generating their own RSA moduli and checking to see if either of the factors in their generated moduli are a factor in my modulus. So any reasonable assumption that RSA is secure must imply that the RSA moduli are coprime.

	 Now because they are coprime we may use Sunzi's theorem to compute $c$ such that $x^n \equiv c(\text{mod } \prodfrom{i=1}{n}{m_i})$. Notice that $\min(\setbuilder{m_i}{0<i\le n})^n < \prodfrom{i=1}{n}{m_i}$ and that $x < \min(\setbuilder{m_i}{0<i\le n})$, thus $$x ^ n < \min(\setbuilder{m_i}{0<i\le n})^n < \prodfrom{i=1}{n}{m_i}$$ so we know $x^n$ as an integer without any modulus and thus may calculate $x$.

	 \subsection{Application}
	 Statement of Problem:
	 \begin{displayquote}
	 	Suppose that Bob, Claire, and Dave all have RSA public keys with encryption exponent $3$. Bob's modulus is 161, Claire's is 209, and Dave's is 221. Alice sends the same message, an integer $x$ less than 161, to Bob, Claire, and Dave. You intercept all three ciphertexts. Bob's ciphertext is 29, Claire's is 144, and Dave's is 196. That is, you know $x^3 \equiv 29 \mod 161$, $x^3\equiv 144 \mod 209$, and $x^3 \equiv 196 \mod 221$. Solve for $x$ without factoring any of the moduli.
	 \end{displayquote}

	 Now we will employ what we stated in the last section. We first use sunzi's theorem to solve for $x^3 (\text{mod }161\cdot209\cdot221)$. This is easiest to be done via a simple program so I'll spare the reader tedious arithmetic; the solution is $x^3 \equiv 1000000 \mod 7436429$. Now $x < 161$ so $x^3 < 161^3 < 7436429 = 161 \cdot 209 \cdot 221$, so $x^3 = 1000000$, and thus $x = 100$.

	\section{Linear algebra euclidean algorithm}

	\subsection{Solutions}

	\question{(a)} If the $i^{\text{th}}$ quotient is $q_i$, then the matrix will be $$M_i = \left[\begin{matrix}0&1\\1&-q_i\end{matrix}\right]$$ and it is easy to see it's determinant is $0\cdot(-q_i) - 1\cdot 1 = -1$.

	To solve for it's inverse we concatenate the identity to $M_i$ and row reduce $M_i$ until it's the identity and the other side of the concatenated matrix will have the inverse. This is all rather basic linear algebra, for notational purposes, while solving fo the inverse $AB$ will be the matrix $A$ concatenated with $B$, not multiplication.
	\begin{align*}
	M_iI &= 
	\left[\begin{matrix}
	0&1&0&1\\
	1&-q_i&1&0
	\end{matrix}\right] \\
	I{M_i}^{-1}&=
	\left[\begin{matrix}
	0&1&0&1\\
	1&0&1&q_i
	\end{matrix}\right] \\
	{M_i}^{-1} &=
	\left[\begin{matrix}
	0&1\\
	1&q_i
	\end{matrix}\right]
	\end{align*}

	\question{(b)} Here the arithmetic is quite straight forward I will forgo showing it all, however note that it is made easy as if you solve $\left(\begin{matrix}0&1\\1&a\end{matrix}\right)\cdot\left(\begin{matrix}0&1\\1&b\end{matrix}\right) = \left(\begin{matrix}	1&b\\a&ab\end{matrix}\right)$ then we already know $M_1M_2$ and $M_3M_4$ and solving for $M_1M_2M_3M_4$ is simply one final multiplication, so the final solution is $$M_1M_2M_3M_4 = \left(\begin{matrix}
	26&-57\\-83&182
	\end{matrix}\right)$$

	\question{(c)} We have been given this sort of identity that $(a,b)M_1M_2\ldots M_r = (1,0)$. So $M_1M_2\ldots M_r$ is a $2\times 2$ matrix, thus we may write it as $$M_1M_2\ldots M_r=\left(\begin{matrix}
	\alpha&\gamma\\
	\beta&\delta
	\end{matrix}\right)$$ for some $\alpha,\beta,\gamma,\delta\in\mathbb Z$. It follows that $$(a,b)\left(\begin{matrix}
	\alpha&\gamma\\
	\beta&\delta
	\end{matrix}\right) = (1,0)$$ so we may break apart the multiplication and see $a\alpha+b\beta=1$. This reveals that $a\alpha \equiv 1 \mod b$ and $b\beta \equiv 1 \mod a$ so $\inv a \mod b \equiv \alpha$ and $\inv b \mod a \equiv \beta$.

	\section{Vigen\`ere extensions}
	\subsection{Large Language approach}
	The Friedman attack works on the fundamental idea that not all letters are equally common in texts. This leads naturally to the question, can we create a language where each letter it equally common in appearance? It would be a tremendous undertaking to create an entirely new language, where each letter is equally common, just so that we can defeat the Friedman attack. The approach I take here will instead add a sort of preprocessing step to our native language to map it into a larger language with equal distribution of letters.

	Now to stay language agnostic and for simplicity, we will think of our letters as being the numbers $0,1,\ldots,n-1$. Now each letter will have some rate of occurrence. For any letter $\ell$ in a language will have a probability of $p_\ell\in\ocint01$\footnote{If a letter were to have a probability of $0$ then we would simply omit it from the language, however a probability of $1$ is allowed if it is the only letter in a language.} of occurrence where $\sumfrom{n=0}{n-1}{p_\ell} = 1$. Now find some natural number, $n\not=0$, such that for all letters $\ell$, $np_\ell$ is within some specified $\epsilon$ of a positive integer, let us call this integer $z_\ell$. Now we will let there be a set $\phi(\ell)$ for each letter $\ell$ with the requirement that $\card{\phi(\ell)} = z_\ell$ and for letters $a\not=b$, $\phi(a)\inter \phi(b) =\emptyset$.

	Now if we have some string $M$ with letters $M_0, M_1, \ldots$ we will then let $M'$ consist of letters $M'_0,M'_1,\ldots$. where $M'_n$ is randomly chosen from the set $\phi(M_n)$.

	Now with a small $\epsilon$ chosen this will make it so that are letters occur with very nearly a uniform distribution in $M'$. We may now do a vigen\`ere cipher on this new text. Notice that the key must be consist of letters chosen from the large language $\bigunion\phi(\ell)$.

	Now depending on how $\phi$ is chosen then this may still be weak to modified Friedman attacks. For example if $\phi(0)=\set{0,1,\ldots, z_0-1}, \phi(1) = \set{z_0,z_0+1,\ldots,z_0+z_1-1}, \ldots$ then counting coincidences as having the same letter you said it was a near by number, then you would be able to break this. If however you choose $\phi$ in a more random fashion, this will not be possible.\footnote{A possible schema for choosing $\phi$ is to simply choose it randomly and publicly release your scheme, there is no need to change $\phi$ between usages so a common $\phi$ may be chosen once and used everywhere, as long as the randomizing of it's order is secure.}
	%TODO test this?

	\subsection{Diffusion}
	One of the nice things about a vigen\`ere cipher is that it can encrypt one character at a time without knowledge of characters around it, all that is needed is it's position in the text. This lends itself nicely to parallelization. We try and throw out this advantage to be able to mix data from surrounding parts of our message based on the key for the encryption. Before we even address how to do this one might worry about letters on the edge of the message (the first and last characters), to deal with this we will consider the message to be surrounded by an infinite number of a chosen letter, so $M_{-1}$ and $M_{\card{M}}$ may be used without causing any issue.

	For terminology's sake let us refer to our plain-text message as $M$ and our encrypted message as $E$.

	One possible implementation for this diffusion would be to have
	$
	E_i=\begin{cases}
	M_i+K_i+M_{i-1} &K_i\text{ is even}\\
	M_i+K_i+M_{i-2}&K_i \text{ is odd}
	\end{cases}
	$
	Now the Friedman attack is much weaker, as in order to get a coincidence to mean something you must have $i$ and $k$ such that $i\equiv k (\text{mod } K.\text{Length})$, $M_i = M_k$, and depending on if $K_i$ is even or odd $M_{i-1} = M_{k-1}$ or $M_{i-2} = M_{k-2}$. This however may still not cause a perfect uniform distribution, however with even this simple diffusion we will already have significantly decreased the chances to detect the key length.
	%TODO some testing would be very gooda

	\section{Mersenne Primes}

	\question{(a)} If $r$ is a prime factor of $2^q-1$ then $2^q-1 \equiv 0\mod r$, thus $2^q\equiv 1\mod r$.

	\question{(b)} It follows from $2^q \equiv 1 \mod r$ that the order of $2$ in modulus $r$ must divide $q$. To prove this, let $o$ be the order of $2$ in mod $r$. This means that there is no positive integer, $k < o$ such that $2^k\equiv1 \mod r$, then if $n \ge 1$ is not divisible by $o$, there must be some $a,b$ such that $bo+a = n$ with $0<a<o$ and thus 
	\begin{align*}
	2^n&=2^{bo+a}\\
	&= \left(2^o\right)^b\cdot 2^a \\
	&\equiv 1^b\cdot 2^a \mod r \\
	&\equiv 2^a\mod r \not\equiv 1
	\end{align*}

	Now additionally we are given that $q$ is prime, therefore $q$ must be the order of $2$ in mod $r$.

	\question{(c)} By Fermat's little theorem we know that for any prime $p$, $a^{p-1}\equiv 1\mod p$, and thus $2^{r-1}\equiv 1\mod r$. By our proof from above we then know that $r-1$ must be divisible by the order of $2$ in mod $r$. We know the order to be $q$, so $q$ must divide $r-1$. This means, that any prime divisor of $2^{q-1}$, $r$, must have the property that $r-1$ is divisible by $q$.

	\question{d}Now $127=2^7-1$, so to check for divisors we only need to check prime factors in the form $7n+1$.

	\begin{itemize}
		\item $7\cdot1+1 = 8$ is not prime
		\item $7\cdot2+1 = 15$ is not prime
		\item $7\cdot3+1 = 22$ is not prime
		\item $7\cdot4+1 = 29 < \sqrt{127}$, thus if $29$ was a prime factor of 127 it must not be the greatest prime of $127$. We know that there are no possible prime factors of $127$ less than $29$, thus $127$ has no prime factors and must be prime.
	\end{itemize}
\end{document}

### 2018-03-27 Algebra/Homework/Homework.tex
upd

@@
 \subsubsection{Question 9}
+
+\question{(a)} 
+\begin{align*}
+f^2&:x_1\to x_3, x_2 \to x_4, x_3 \to x_1, x_4 \to x_2\\
+f^3&:x_1\to x_4, x_2 \to x_1, x_3 \to x_2, x_4 \to x_1\\
+f^4&:x_1\to x_1, x_2 \to x_2, x_3 \to x_3, x_4 \to x_4
+\end{align*}
+
+\question{(b)}
+\begin{align*}
+g^2&:x_1\to x_1, x_2 \to x_2, x_3 \to x_3, x_4 \to x_4\\
+g^3&:x_1\to x_2, x_2 \to x_1, x_3 \to x_3, x_4 \to x_4
+\end{align*}
+
+\question{(c)}
+$$fg:x_1\to x_3, x_2\to x_2, x_3\to x_4, x_4\to x_1$$
+
+\question{(d)}
+$$gf:x_1\to x_1, x_2 \to x_3, x_3 \to x_4, x_4 \to x_2$$
+
+\question{(e)}
+\begin{align*}
+(fg)^3&:x_1\to x_1, x_2 \to x_2, x_3 \to x_3, x_4 \to x_4\\
+(gf)^3&:x_1\to x_1, x_2 \to x_2, x_3 \to x_3, x_4 \to x_4
+\end{align*}
+
+\question{(f)} No, $fg(x_1) \not= gf(x_1)$ as can be seen above, thus $fg\not=gf$.
+
 \subsubsection{Question 10}
+Consider the cycle structure of a permutation $f$.
+It is obvious that $f^k = i$ if $k$ is the greatest common divisor among all the cycle lengths in $f$.
+Now for any $f\in S_3$, cycles must be of length one, two, or three.
+Therefore, as $6 = \gcd(1,2,3)$ for any $f\in S_3$, $f^6=i$.
+
 \subsubsection{Question 14}
+
+Let $F$ be the mapping from $S_m\to S_n$ such that $F(f)$ is defined to be the same as $f$ where $f$ is defined, and acts as the identity elsewhere.
+Now $F$ is trivially 1-1, so let us show that it satisfies $F(fg) = F(f)F(g)$ for all $f,g \in S_m$.
+To start let us choose $x$ in the domain of $g$, then $F(g)$ takes $x \to g(x)$ and $F(f)$ takes $g(x) \to fg(x)$, which is obviously the same as what $F(fg)$ does.
+If $x$ is not in the domain of $g$ then $F(g)$ takes $x\to x$ and $F(f)$ takes $x \to x$ as does $F(fg)$, we can thus conclude that $F(fg) = F(f)F(g)$.
+
 \subsubsection{Question 21}
+
+Let $g_j$ swap $x_1$ and $x_{j+1}$.
+Now when $n = 1$ this is trivially true as we have $f = i$ which satisfies the definition of $f$.
+Let us now try and do an induction on this statement.
+Assume that $g_1g_2g_3\cdots g_{n-1} = f$ when $n$ is some specific fixed constant.
+Then it follows that for $f'\in S_{n+1}$ where $f'$ is defined just as $f$ was, that is $f': x_1\to x_2, x_2 \to x_3, \ldots, x_n \to x_{n+1}, x_{n+1} \to x_1$, then consider $g_1g_2g_3 \ldots g_n = fg_n$ and this will obviously give us $f'$, so by induction we have shown that this may be done for any $n$.
+
 \subsubsection{Question 27}
+For every $b$ in the domain of $f$ there must be exactly one $a$ and $c$ such that $f(a) = b$ and $f(b) = c$.
+As the domain of $f$ is finite then there must be some $n\in\mathbb N$ such that $f^n(b) = b$.
+It follows then that if there is some $n$ such that $f^n(s) = t$ then there must also be some $k$ such that $f^k(t) = s$.
+By symmetry we also know that the converse is true.
+This means that either $O(s) = O(t)$ or the two are disjoint.
+
 \subsubsection{Question 30}
+Each orbit must be exactly of size $1$. This is because otherwise all $n$ such that $f^n = i$, would have to be a multiple of a number that is not $1$, and thus could not be any prime number.
+
 \subsubsection{Question 32}
+$g\in A(S)$ commutes with $f$ iff $g$ is closed on the set $\set{x_1,x_2}$.
+\begin{proof}
+	First we will show by cases that any $g$ that is closed on $\set{x_1,x_2}$ commutes with $f$, then we will show that no other set does so.
+
+	\begin{itemize}
+		\item Let $s,t \in \set{x_1,x_2}$ with $s\not=t$
+		\begin{itemize}
+			\item If $g(s) = s$, then $fg(s) = g(t) = t$ and $gf(s) = f(s) = t$.
+			\item If $g(s) = t$, then $fg(s) = g(t) = s$ and $gf(s) = f(t) = s$.
+		\end{itemize}
+		\item Let $s \not\in\set{x_1,x_2}$, then $fg(s) = gf(s)$ as $f$ acts as the identity.
+	\end{itemize}
+
+	Now if $g$ is not closed on $\set{x_1,x_2}$ then lets say without loss of generality that $g(x_1) = s \not\in\set{x_1,x_2}$ it follows that $fg(x_1) = g(x_2)$ and $gf(x_1) = f(s) = s$.
+Now $g(x_2) \not= s$ as otherwise both $x_1$ and $x_2$ would map to the same element which is not possible.
+\end{proof}
+
+\subsection{Section 5}
+\subsubsection{Question 1}
+\subsubsection{Question 4}
+\subsubsection{Question 7}
+\subsubsection{Question 13}
+\subsubsection{Question 17}
 

### 2018-04-06 Algebra/Homework/Homework.tex
hi

@@
 \subsection{Section 5}
+
 \subsubsection{Question 1}
+For this we use the Euclidean algorithm, rather then do the somewhat tedious math, I will simply employ a program I have written in Python.
+\\
+\question{(a)} $(116, -84) = 4 = 8 \cdot 116 + 11 \cdot -84$.
+\\
+\question{(b)} $(85,65)=5=-3\cdot85+4\cdot65$.
+\\
+\question{(c)} $(72,26)=2=4\cdot72-11\cdot26$.
+\\
+\question{(d)} $(72,25)=1,8\cdot72-23\cdot25$.
+
 \subsubsection{Question 4}
+This shall be nothing but some simple arithmetic, most of these numbers are factorials making them particularly easy to compute.\\
+\question{(a)} $36 = 2^23^2$.\\
+\question{(b)} $120 = 2^33^15^1$.\\
+\question{(c)} $720 = 2^43^25^1$.\\
+\question{(d)} $5040 = 2^43^25^17^1$.
+
 \subsubsection{Question 7}
+
+\question{(a)}First, we write $m = k_1(m,n)$ and $n=k_2(m,n)$ for some $k_1,k_2\in\mathbb Z$. It follows $$\frac{mn}{(m,n)} = k_1k_2(m,n) = mk_2 = nk_1$$ so this satisfies $m|v$ and $n|v$.
+
+\newcommand{\factorize}[2]{\prodacross{{#2}\in\mathbb N}{{p_{#2}}^{{#1}_{#2}}}}
+
+\begin{lemma}
+	For $n = \factorize ni$ and $m = \factorize mi$, if $c_i = \min(n_i,m_i)$ then $$(n,m) = \factorize{c}{i}$$ where $p_i$ is the $i^{\text{th}}$ prime number. 
+\end{lemma}
+
+\begin{proof}
+	For convention we will let $p_i$ be the $i^{\text{th}}$ prime unless otherwise stated.
+We will also adopt the convention that for any natural number $x$, the sequence $x_i$ will be it's prime factorization, that is $\factorize{x}{i} = x$ unless otherwise stated.
+Furthermore we will also by convention assume that if a sequence of natural numbers $x_i$ has been defined then $x = \factorize{x}{i}$, unless otherwise stated.
+As a last note, we will define $\mathbb N = \set{0,1,2,\ldots}$ and $2 = p_0$.
+
+	Let $n$ and $m$ be natural numbers, and then let $c_i = \min{n_i,m_i}$ for all $i\in\mathbb N$. We would like to show $c=(n,m)$. First it is trivial that $c>0$.
+
+	Second we must show $c|n$ and $c|m$. To do this let $k_i = n_i - c_i$, notice that $n_i \ge c_i$ for all $i$, therefore $k_i$ is an integer for all $i$.
+	\begin{align*}
+	kc &= \factorize ki \factorize ci \\
+	&= \prodacross{i\in\mathbb N}{{p_i}^{n_i-c_i}}\factorize ci \\
+	&= \prodacross{i\in\mathbb N}{{p_i}^{n_i}} \\
+	&= n
+	\end{align*}
+	The same argument can be made to show that $c|m$.
+
+	Lastly we must show that if $d|n$ and $d|m$ then $d|c$, we will do this by contrapositive, so assume $d\nmid c$, therefore there does not exist any $k$ st.
+$dk = c$.
+Further there exists no sequence of natural numbers $k_i$ st.
+$d\factorize ki = c$.
+We know have
+	\begin{align*}
+	\factorize ki \factorize di &= \prodacross{i\in\mathbb N}{{p_i}^{d_i+k_i}} \\
+	&\not= \factorize ci
+	\end{align*}
+	for any sequence $k_i$, therefore there must exists some $i\in\mathbb N$ st. $d_i > c_i$. It follows then that either $d_i > n_i$ or $d_i > m_i$.
+\end{proof}
+
+Now note that $\min(a,b) + \max(a,b) = a + b$ for any $a,b$. Therefore if we define $v_i = \max(n_i,m_i)$ and $c_i = \min(n_i,m_i)$ we get
+\begin{align*}
+\frac{mn}{(m,n)} &= \frac{\factorize mi \factorize ni}{\factorize ci} \\
+&= \prodacross{i\in\mathbb N}{{p_i}^{m_i+n_i-c_i}} \\
+&= \factorize vi \\
+&= v
+\end{align*}
+
+Now we just need to show that $v$ is the least common multiple.
+If $r < v$ and $\factorize ri = r$, it follows that is some $i$ for which $r_i < v_i$, therefore either $m$ or $n$ can not possibly divide $r$ as either $m_i > r_i$ or $n_i > r_i$.
+
+We now know that $mn/(m,n)$ is the least common multiple of $m$ and $n$.
+
+\question{(b)} As we have already shown $v = \prodacross{i\in\mathbb N}{{p_n}^{\max(n_i,m_i)}}$.
+
 \subsubsection{Question 13}
+
+\question{(a)} If $p = 4n$ then $p$ is divisible by four an not prime. If $p = 4n + 2 = 2(2n + 1)$ then $p$ is divisible by two and not odd. Therefore either $p = 4n+1$ or $p = 4n+3$.
+
+\question{(b)} If $p = 6n$ then $p$ is divisible by six and not prime.
+If $p = 6n + 2 = 2(3n + 1)$ then $p$ is divisible by two and not odd.
+If $p = 6n + 3 = 3(2n + 1)$ then $p$ is divisible by three and is either the number 3 or is not prime.
+If $p = 6n + 4 = 2(3n + 2)$ then $p$ is divisible by two.
+Therefore if $p$ is an odd prime that is not $3$, then either $p = 6n+1$ or $p = 6n+5$.
+
 \subsubsection{Question 17}
 
+Let $p$ be the $n^{\text{th}}$ prime.
+Assume for the sake of contradiction that there is some $a,b\in\mathbb N$ st.
+$a^2=pb^2$, and let $\factorize ai = a$ and $\factorize bi = b$.
+It follows that $\factorize{2a}i=p\factorize{2b}i$.
+As $p$ is the $n^{\text{th}}$ prime then $$p^{2a_n}\prodacross{i\in\mathbb N\setminus\set n}{{p_i}^{2a_i}} = p^{2b_n+1}\prodacross{i\in\mathbb N\setminus\set n}{{p_i}^{2a_i}}$$ so the prime factorizations can not possibly be the same, so we have a contradiction.
+
+\subsection{Section 6}
+\subsubsection{Question 1}
+
+\question{(a)} $(6-7i)(8+i) = 48 - 56i + 6i + 7 = 55-50i$
+
+\question{(b)} $(\frac 23 + \frac 32i)(\frac23 - \frac 32i) = \frac49+\frac94=\frac{16+81}{36} = \frac{97}{36}$
+
+\question{(c)} $(6-7i)(8-i) = 48-56i-6i-7 = 41-62i$
+
+\subsubsection{Question 2}
+
+%TODO fix me
+
+\question{(a)} $z^{-1} = -\frac{6}{6^2+8^2} + \frac8{6^2+8^2}i$
+
+\question{(b)} $z^{-1} = -\frac{6}{6^2+8^2} - \frac8{6^2+8^2}i$
+
+\subsubsection{Question 8}
+\subsubsection{Question 14}
+
 \end{document}

### 2018-04-06 Seminar/PushDownAutomata.tex
hi

\documentclass{article}
\input{../definitions}
\title{Push Down Automata}

\begin{document}

	\maketitle
	\question{1.} Make a PDA for the language of $a^nb^n$ that is $n$ $a$'s followed by $n$ $b$'s for any $n$. So ${\lambda, ab, aabb, aaabbb,\ldots}$

	\bigskip
	\bigskip
	\bigskip
	\bigskip
	\bigskip
	\bigskip

	\question{2.} Make a PDA for a valid mathematical expression with symbols $+$, $-$, $*$, $/$, and $0$ through $9$.

	\bigskip
	\bigskip
	\bigskip
	\bigskip
	\bigskip
	\bigskip

	\question{3.} Make a PDA that accepts any word with correctly matching parentheses, on the alphabet, $\set{a,b,c,(,)}$

	\bigskip
	\bigskip
	\bigskip
	\bigskip
	\bigskip
	\bigskip

	\question{4.} Build up a language that you know as a grammer.

\end{document}

### 2018-04-06 Topology/Paper/paper.tex
abstract
hi

@@
 
+Now for some extensions of Kuratowski's theorem
+
 \begin{theorem}[Spherical and Planar graphs are the same] \label{sphere=plane}
@@
 
-\begin{proof}
-	First we know from topology that the punctured sphere is homeomorphic to the plane, planarity of a graph is the same as saying that the graph may be drawn on a punctured sphere without any self intersection.
-Now it's trivial to say that anything drawn on a punctured sphere may be drawn on the sphere.
-Now it will suffice to show only that a graph drawing will never cover the entire sphere as then there exists some at which to puncture.
-\end{proof}
+Now this we won't actually prove as it's quite difficult to do so, however notice that the plane is homeomorphic to the punctured sphere.
+Now it seems intuitive that if you can draw a finite graph, or even multi-graph on a sphere then it would not have to cover every single point on the sphere.
+This means that we could puncture the sphere at one point and thus we have the plane.
+
+This is not needed for our proof of Kuratowski's theorem, however it does help to think about drawing graphs on planes sometimes as well as helping to think about extensions beyond Kuratowski's theorem.
 

### 2018-04-30 Algebra/Homework/Homework.tex
final

@@
 \subsection{Section 6}
+
+\subsubsection{Question 1}
+
+\begin{proof}
+Base case, we have $\frac161(1+1)(2\cdot 1 + 1) = \frac166 = 1 = 1^2$, when $n = 1$.
+Inductive case we get 
+\begin{align*}
+\frac 16(n-1)((n-1)+1)(2(n-1)+1) + n^2 &=\frac16(n-1)n(2n-1) + n^2 \\
+&= \frac16\left(2n^3 - 3n^2+n\right) + n^2 \\
+&= \frac16\left(2n^3 + 3n^2+n\right) \\
+&= \frac16n(2n^2+3n + 1) \\
+&= \frac16n(n+1)(2n+1)
+\end{align*}
+\end{proof}
+
+\subsubsection{Question 2}
+
+\begin{proof}
+	Base case, we have $\frac141^2(1+1)^2 = \frac144 = 1 = 1^3$, when $n = 1$. Inductive case we get 
+	\begin{align*}
+	\frac14(n-1)^2((n-1)+1)^2 + n^3 &= \frac14n^2(n-1)^2 + n^3 \\
+	&= \frac14\left(n^4-2n^3+n^2\right)+n^3\\
+	&= \frac14\left(n^4+2n^3+n^2\right)\\
+	&= \frac14n^2(n+1)^2
+	\end{align*}
+\end{proof}
+
+\subsubsection{Question 8}
+
+\begin{proof}
+Our base case is trivial when $n=1$. In our inductive case we get
+\begin{align*}
+\frac{(n-1)}{n} + \frac1{n(n+1)} &= \frac{(n-1)(n+1) + 1}{n(n+1)}\\
+&= \frac{n^2}{n(n+1)} \\
+&= \frac n{n+1}
+\end{align*}
+\end{proof}
+
+\subsubsection{Question 14}
+%TODO Fermat's little theorem, I have combinatorial proof but inductive evades me
+
+\subsection{Section 7}
 \subsubsection{Question 1}
@@
 
-%TODO fix me
+In general $z^{-1} = \frac{\bar z}{\abs{z}^2}$
 
-\question{(a)} $z^{-1} = -\frac{6}{6^2+8^2} + \frac8{6^2+8^2}i$
+\question{(a)} $z^{-1} = \frac{6}{6^2+8^2} - \frac8{6^2+8^2}i$
 
-\question{(b)} $z^{-1} = -\frac{6}{6^2+8^2} - \frac8{6^2+8^2}i$
+\question{(b)} $z^{-1} = \frac{6}{6^2+8^2} + \frac8{6^2+8^2}i$
+
+\question{(c)} $z^{-1} = \frac1{\sqrt2} - \frac1{\sqrt 2}i$
 
 \subsubsection{Question 8}
+
+By lemma 1.7.3 from the book we know that $\abs{uv} = \abs u\abs v$, therefore, as $zz^{-1} = 1$ we also have $\abs{zz^{-1}} = 1$ so $\abs z\abs{z^{-1}} = 1$ and it follows $\abs {z^{-1}} = 1 / \abs z$.
+
 \subsubsection{Question 14}
 
+%Get help from Russos?
+By Euler's equation we know that $\cos\theta + i\sin\theta = e^{i\theta}$. We have ${\left(e^{i\theta}\right)}^m = e^{im\theta} = \cos (m\theta) + i\sin (m\theta)$
+
 \end{document}

### 2018-05-05 NetworkScience/Final/Final.tex
hi

\documentclass{article}

\title{So you want to build a search engine?}
\input{../../definitions.tex}
\begin{document}
	\maketitle

	\tableofcontents

	\begin{abstract}
		There are many different types of search engines, the most complicated of which are where you do not initially have knowledge of what is being searched and that information may change. In order to tackle this we need some way of discovering possible results, matching these results to a query and ranking possible results. %TODO come back to
	\end{abstract}

	\section{Introduction}
	So you want to build a search engine? Now there are a couple different types of search engines and not all search engines need work the same, however there are two steps that are absolutely necessary for any searching to make sense. First you are going to need to have some set $A$ to search through and second you will need a search function $s:Q\to\pset{A}$\footnote{$\pset A$ is the power set of $A$.} where $Q$ is the set of all possible search queries. If we step away from mathematical formalities this makes sense as we simply are finding a way to match a search query to set of possibly results.

	Now what one might notice is that none of this talks about ranking the results, and this is obviously an important part of any modern search engine. The problem of ordering may, in fact, be the most interesting part of a search engine. This paper however will spend very little time talking about ordering a search result as Page Rank is already well understood and after that most of the complexity really has more to do with understanding the query which we will cover when talking about our search function.

	Now this paper will mostly focus on the discovery of set $A$ and assumes and Internet like structure to $A$. That is to say that $A$ is a large set with a directed graph structure to it. Additionally $A$ is not static, edges in $A$'s graph structure may change, members of $A$ may be created or destroyed, as may the content of those members. Finally $A$ is not initially known to us.

	Now while I try to keep this paper in the abstract and I talk about $A$ as if it's a set and does not have to be the Internet, I think it's important to talk about some of the tools that we have built to help us work with constrains the Internet put on us. This is because the Internet is so well known and what most people have experience searching. Leaving out practical information, while it may take away from the abstractness, it is the authors opinion that it is too important to leave out. In this vein we will be focusing on Google's architecture as it is so well known and information is readily available on it.\footnote{This is not fully accurate, there is some very good information on Google's inner workings that comes from before 2000, however much of of modern Google's inner workings are kept as trade secrets or simply not released.}

	\section{}
	The discovery of $A$ is done through a process called web crawling. We will

\end{document}

### 2018-05-06 NetworkScience/Final/Final.tex
hi

@@
 \input{../../definitions.tex}
+\usepackage{listings}
+\usepackage{xcolor}
+
+\lstset{%
+	language=[LaTeX]TeX,
+%	backgroundcolor=\color{gray!25},
+	basicstyle=\ttfamily,
+	breaklines=true,
+	columns=fullflexible
+}
+
 \begin{document}
@@
 
-	\section{}
-	The discovery of $A$ is done through a process called web crawling. We will
+	\section{The Internet}
+
+	\subsection{How it works}
+	The Internet itself is a somewhat complex entity and a lot goes into making it work.
+For this we don't need to know everything  but it would be good to have a rough idea of what happens when you go to a web page.
+
+	Lets say you open your web browser and go to the \verb|www.google.com|.
+Now what happens is your computer sends a message out to \verb|www.google.com| and a response is sent back to you.
+The web browser that you use (ie: Mozilla Firefox, Internet Explorer, Google Chrome, \ldots) will then display that message in a way that makes most sense.
+
+	The message that is sent to \verb|https://www.google.com| ins't terribly complicated, however we aren't goint to deal with it's entire protocol, instead we will pretend that the message is simply the URL that you type in.
+Now you might see a somewhat more complicated URL then just \verb|https://www.google.com|, maybe you'll see \verb|https://www.google.com\mail| or even more complicated looking like
+	\begin{lstlisting}[breaklines]
+	https://www.google.com/search?ei=k1TuWuoH0pCaBcvOuIgC\&q=hello+world\&oq=hello+world\&gs\_l=psy-ab.3..0j0i20i264k1l2j0l5j0i10k1j0.2636.3822.0.3932.11.8.0.0.0.0.252.676.2-3.3.0....0...1c.1.64.psy-ab..8.3.676...46j0i67k1j0i46k1j0i131k1.0.2UY03D\_JQgE
+	\end{lstlisting}
+	we can think of this as simply sending that message to \verb|www.google.com|, and them sending back a reply.
+Now you can see the actual text of the response that is sent back to you, however what is important to note is that this is simply a response.
+This means that \verb|https://www.google.com| can send me any response it likes and it doesn't need to look like a web page and it does not need to be consistent.
+This means that there really ins't information on the Interent, just URLs and servers that give responses.
+
+	When we make a Internet search engine we are making some implicit assumptions about how websites like \verb|https://www.google.com| are going to act.
+First we assume that most urls will respond with relitivily consistant responses.
+What is meant by this is that if I have a URL $x$ that produces response $r_0$, the first time I made a request for it, then when I send another request to $x$ and get response $r_1$, then $r_1$ should be similar in content to $r_0$.
+
+	Now in practice, as of writing this paper, most responses (at least for important web pages) tend to be fairly static, often being exactly the same for a length of time and not changing by a large amount when they do change.
+For example think of the website \verb|https://www.wikipedia.com| that acts as a communally sourced encyclopedia.
+Now as anyone may make a change to any particular page on this site you might think it to be rather  volitile, however these changes tend to be very minimal and wont completley change the content of the page.
+When we talk about crawling we will useing and working within this constraint that pages change, but only gradually.
+
+	For this section we have thought of web pages simply a responses to a URL. Now that we have justified that these responses are mostly consistent, we will think of them rather as pages.
+
+	\subsection{Some terminology}
+	In order for us to understand how a search engine like Google operates, there is some terminology pertaining the Internet that we must understand.
+Admittedly the definitions here are not rigorous, however the quick overview of some ideas is all that is needed for our discussion.
+	\begin{itemize}
+
+		\item \textbf{Website} - A website might be best though of as a server.
+Each website has a single computer\footnote{In practice the single computer is actually multiple computers} that deals with incoming requests and makes responses.
+A website is denoted by \verb|www.google.com|, anything that is appended after that is still on the same website, that is that \verb|www.google.com| is still sending the responses.
+
+		\item \textbf{Web page} - A web page is a single page or URL on a web site.
+More precisely a web page is the response given to you by a website given a specific URL.
+In this we will think of the URL as being the name of the web page while the page itself being subject to change.
+That is to say if a page was to be moved from  URL $a$ to URL $b$ we would simply see it as $a$'s web page changing to not exist and $b$'s web page changing to whatever $a$ used to be.
+
+		\item \textbf{URL} - The URL is the `name' of a webpage and tells us how to get there.
+We have already seen some example URLs like \verb|https://www.google.com|.
+We see URLs come in a a few flavors, we will break them into two catagories.
+		\begin{itemize}
+			\item \textbf{absolute URL} - This a URL that has the whole name in it like the ones we have seen.
+This contains all the information we need to get to the specific page.
+These often look something like \verb|www.domainName.topLevelDomain/optionalExtraStuff|.
+			\item \textbf{relative URL} - This a URL that works within a website, for example if I'm at \verb|www.example.com/index| and I go to the URL \verb|/home| there is an agreement that this link really refers to \verb|www.example.com/home|.
+		\end{itemize}
+
+		%TODO maybe remove
+		\item \textbf{404 Error} - Sometimes web pages are removed.
+When we try to go to a URL that is not set to respond with anything, the website will respond with a 404 error.
+This becomes important as we may find that some pages that used to exist no longer do, and these must be handled in a meaningful way.
+
+		%TODO add more
+
+	\end{itemize}
+
+	\section{Discovery}
+	Now let us return to the abstract.
+You want to create a search engine that searches through some set $A$, however you do not have all of $A$, so you need some way to discover as much of $A$ as you can.
+Now for this we are going to assume you already know some $S\subset A$ and that $A$ has a directed graph structure to it that you may follow to discover new nodes.
 

### 2018-05-06 NetworkScience/Final/Final.tex
Hi'

@@
 	\end{abstract}
+
+	\section{Who this paper is for.}
+	This paper assumes the reader has no special knowledge of Mathematics, Graph theory, or the workings of the Internet.
+The paper does however use very common terminology from Mathematics and Graph theory without providing definitions.
+If a reader is unfamiliar with certain terms they are encouraged to look them up as otherwise the paper will spend to much time describing mathematical concepts that are outside the scope of this paper.
 
@@
 These often look something like \verb|www.domainName.topLevelDomain/optionalExtraStuff|.
-			\item \textbf{relative URL} - This a URL that works within a website, for example if I'm at \verb|www.example.com/index| and I go to the URL \verb|/home| there is an agreement that this link really refers to \verb|www.example.com/home|.
+			\item \textbf{relative URL} - This a URL that works within a website.
+If I'm at \verb|www.example.com/index| and I go to the URL \verb|/home| there is an agreement that this link really refers to \verb|www.example.com/home|.
 		\end{itemize}
@@
 
-		%TODO add more
+		%TODO add more maybe?
 
@@
 	\section{Discovery}
-	Now let us return to the abstract.
+
 	You want to create a search engine that searches through some set $A$, however you do not have all of $A$, so you need some way to discover as much of $A$ as you can.
 Now for this we are going to assume you already know some $S\subset A$ and that $A$ has a directed graph structure to it that you may follow to discover new nodes.
+In order to do this we will need a graph searching algorithm.
+There are two basic algorithms available: Depth-First search and Breadth-First search.
+
+	A depth-first search starts with a single vertex $v_0$, it finds all children of $v_0$ and then repeats the process recursively on them one at a time.
+Notice that if $v_1$ is $v_0$'s `first' child then we will find each $v_1$'s children, and then repeat on $v_1$'s first child continuing in this fashion until there are no more children and we are able to work back up to $v_0$'s second child.
+This is like searching by clicking the first link you find on a page until there is no links on some page and then going back to the last page and clicking it's second link.
+The obvious problem with this search is that it loop infinitely and to deal with this we make the slight adjustment that we never go to the same vertex twice.
+
+	A breadth-first search starts with a seed set $S$ and finds the neighborhood of $S$.
+In this context we define the neighborhood of a set, $S$, to be all verticies $v\not\in S$ for which there is some vertex $s\in S$ with an edge to $v$.
+In a breadth-first search, once we find the neighborhood of $S$ we then repeat the process on the union of $S$ with it's neighborhood and continue recursively until the neighborhood of $S$ is empty, at this point we have discovered as much of our graph as possible given our seed set.
+This is like going to a page and clicking all of it's links and opening them in a new tab, then going through each tab and continually opening links in new tabs.
+
+	The choice of which search to use is very situational and has much to do with the structure of the graph you are searching.
+Additionally with more information about the graph you may be able to do some more complicated algorithms that are more suited to your needs, or some combination between the above algorithms.
+
+	\subsection{On the Internet}
+	There are quite a few useful results that we already know about the structure of the Internet that will help us to explore it.
+The problem with the Internet however is that it is so large that no one could ever hope to discover all of it, so instead we must find some way of trying to get the most valuable parts discovered and we need to do so efficiently.
 

### 2018-05-06 NetworkScience/Final/Final.tex
Hi

@@
 	So you want to build a search engine?
-Now there are a couple different types of search engines and not all search engines need work the same, however there are two steps that are absolutely necessary for any searching to make sense.
+Now there are a couple different types of search engines and not all search engines need to work the same, however there are two steps that are absolutely necessary for any searching to make sense.
 First you are going to need to have some set $A$ to search through and second you will need a search function $s:Q\to\pset{A}$\footnote{$\pset A$ is the power set of $A$.} where $Q$ is the set of all possible search queries.
@@
 		\end{itemize}
+		If which type of URL is not specified it should be assumed that we are referring to an absolute URL.
 
@@
 	There are quite a few useful results that we already know about the structure of the Internet that will help us to explore it.
-The problem with the Internet however is that it is so large that no one could ever hope to discover all of it, so instead we must find some way of trying to get the most valuable parts discovered and we need to do so efficiently.
+The problem with the Internet however is that it is so large that no one could ever hope to discover all of it, so instead we must find some way of trying to get the most valuable parts of the Internet discovered.
+
+	The process we are talking about is often referred to as web crawling and a program that does this is called a web crawler or spider. Our first idea for building one might be as follows:
+	\begin{enumerate}
+		\item Start with some set of URLs $S$ as our seed. 
+		\item Enqueue each element of $S$ to a queue $Q$.
+		\item While $Q$ is not empty do the following:
+		\begin{enumerate}
+			\item Dequeue a URL from $Q$, let us call this URL $u$.
+			\item Make a request to URL $u$.
+			\item When a response is sent back, find all URLs (either absolute or relative) that one may find in that response, convert all relative URLs to absolute URLs.
+We will refer to this set of discovered URLs as $D$.
+			\begin{itemize}
+				\item On a webpage there are certain places to look, for example an anchor tag may be a link to another page.
+				\item One may also use a regular expression to try and find things anywhere on the page that look like URLs.
+Even if our system is perfect sometimes pages go away so we should expect not all URLs to be valid.
+			\end{itemize}
+			In practice we may want to use some or all of the information from the web page.
+This will be important in later sections, but for now just realize that we can keep track of the responses we get and deal with them how we choose.
+			\item For each URL $d\in D$, if $d \not\in S$ then add $d$ to $S$ and enqueue it onto $Q$.
+		\end{enumerate}
+	\end{enumerate}
+
+	Now this web crawler works perfectly well, however it's going to be incredibly slow. The first step in optimizing this is always looking at
 

### 2018-05-06 NetworkScience/Final/Final.tex
Hi

@@
 First you are going to need to have some set $A$ to search through and second you will need a search function $s:Q\to\pset{A}$\footnote{$\pset A$ is the power set of $A$.} where $Q$ is the set of all possible search queries.
-If we step away from mathematical formalities this makes sense as we simply are finding a way to match a search query to set of possibly results.
+If we step away from mathematical formalities, this makes sense, as we simply are finding a way to match a search query to set of possible results.
 
@@
 
-	Now this web crawler works perfectly well, however it's going to be incredibly slow. The first step in optimizing this is always looking at
+	Now this web crawler works perfectly well, however it's going to be incredibly slow.
+The first step in optimizing this is always looking at what the slowest part is.
+Without even testing this program there is going to be a clear winner.
 

### 2018-05-06 NetworkScience/Final/Final.tex
Hi

@@
 
-	\section{Who this paper is for.}
+	\section{Who this paper is for}
 	This paper assumes the reader has no special knowledge of Mathematics, Graph theory, or the workings of the Internet.
@@
 
-	Now what one might notice is that none of this talks about ranking the results, and this is obviously an important part of any modern search engine.
+	Now what one might notice is that none of this relates to ranking the results, and this is obviously an important part of any modern search engine.
 The problem of ordering may, in fact, be the most interesting part of a search engine.
@@
 Without even testing this program there is going to be a clear winner.
+When we measure
 

### 2018-05-07 NetworkScience/Final/Final.tex
hi

@@
 In order to tackle this we need some way of discovering possible results, matching these results to a query and ranking possible results.
-%TODO come back to
+This paper deals largely with the discovery and more specifically a process called web crawling.
 	\end{abstract}
@@
 	Now while I try to keep this paper in the abstract and I talk about $A$ as if it's a set and does not have to be the Internet, I think it's important to talk about some of the tools that we have built to help us work with constrains the Internet put on us.
-This is because the Internet is so well known and what most people have experience searching.
+This is because the Internet is so well known and the thing that most people have experience searching.
 Leaving out practical information, while it may take away from the abstractness, it is the authors opinion that it is too important to leave out.
@@
 
-	The message that is sent to \verb|https://www.google.com| ins't terribly complicated, however we aren't goint to deal with it's entire protocol, instead we will pretend that the message is simply the URL that you type in.
+	The message that is sent to \verb|https://www.google.com| ins't terribly complicated, however we aren't going to deal with its entire protocol, instead we will pretend that the message is simply the URL that you type in.
 Now you might see a somewhat more complicated URL then just \verb|https://www.google.com|, maybe you'll see \verb|https://www.google.com\mail| or even more complicated looking like
@@
 This means that \verb|https://www.google.com| can send me any response it likes and it doesn't need to look like a web page and it does not need to be consistent.
-This means that there really ins't information on the Interent, just URLs and servers that give responses.
+This means that there really ins't information on the Internet, just URLs and servers that give responses.
 
 	When we make a Internet search engine we are making some implicit assumptions about how websites like \verb|https://www.google.com| are going to act.
-First we assume that most urls will respond with relitivily consistant responses.
+First we assume that most urls will respond with relativly consistent responses.
 What is meant by this is that if I have a URL $x$ that produces response $r_0$, the first time I made a request for it, then when I send another request to $x$ and get response $r_1$, then $r_1$ should be similar in content to $r_0$.
@@
 
+		\item \textbf{Link} - A link is a URL (either absolute or relative) contained within a web page.
+A link's URL may be invalid, this we call a \textbf{dead link}.
+We will active links (ones that aren't dead) as the out edges in our graph model of the Internet
+
+		\item \textbf{Content} - The content of the page is the actual text and information that someone viewing it might see. This will be very important for matching a search query with a result.
+
 	\end{itemize}
@@
 Notice that if $v_1$ is $v_0$'s `first' child then we will find each $v_1$'s children, and then repeat on $v_1$'s first child continuing in this fashion until there are no more children and we are able to work back up to $v_0$'s second child.
-This is like searching by clicking the first link you find on a page until there is no links on some page and then going back to the last page and clicking it's second link.
+This is like searching by clicking the first link you find on a page until there is no links on some page and then going back to the last page and clicking its second link.
 The obvious problem with this search is that it loop infinitely and to deal with this we make the slight adjustment that we never go to the same vertex twice.
@@
 In this context we define the neighborhood of a set, $S$, to be all verticies $v\not\in S$ for which there is some vertex $s\in S$ with an edge to $v$.
-In a breadth-first search, once we find the neighborhood of $S$ we then repeat the process on the union of $S$ with it's neighborhood and continue recursively until the neighborhood of $S$ is empty, at this point we have discovered as much of our graph as possible given our seed set.
-This is like going to a page and clicking all of it's links and opening them in a new tab, then going through each tab and continually opening links in new tabs.
+In a breadth-first search, once we find the neighborhood of $S$ we then repeat the process on the union of $S$ with its neighborhood and continue recursively until the neighborhood of $S$ is empty, at this point we have discovered as much of our graph as possible given our seed set.
+This is like going to a page and clicking all of its links and opening them in a new tab, then going through each tab and continually opening links in new tabs.
 
@@
 
-	\subsection{On the Internet}
+	\subsection{On the Internet / Building a Web Crawler}
 	There are quite a few useful results that we already know about the structure of the Internet that will help us to explore it.
@@
 
+	\subsubsection{A First Web Crawler}
 	The process we are talking about is often referred to as web crawling and a program that does this is called a web crawler or spider. Our first idea for building one might be as follows:
@@
 Without even testing this program there is going to be a clear winner.
-When we measure
+When we measure the amount of time single instructions take in a computer we usually operate on the order of nanoseconds ($10^{-9} s$), whereas when we measure about the amount of time a web request takes we often operate in milliseconds ($10^{-3} s$).
+This means that the computer is going to very quickly go through steps 1 through 3b very quickly, then idles until a response is given and the program can continue on.
+
+	\subsubsection{Some Improvements}
+	To solve this problem we will use something called asynchronous programming.
+How this works we will have a response queue, $R$, where every time we receive a response we enqueue the response onto $R$.
+Now when we make a request to a URL instead of waiting for the response we call an \textit{empty queue} function where we dequeue each element of $R$ until it is empty, processing each one by finding its links and then adding the links to $S$ and enqueuing them to $Q$.
+Once we have emptied $R$, then we move onto the next element of $Q$ as we had before.\footnote{Implementing asynchronous programming is not a trivial problem, however many programming languages have built in or standardized support for asynchronous operations making this a fairly effective tool.}
+
+	The advantage of this new algorithm is that we no longer wait for the Internet's response to our requests, rather we just keep crawling and deal with responses as they get back to us.
+It is worth noting that there is some overhead cost incurred by this, however it will be insignificant compared to the cost of waiting for a response.
+There however is again an issue with this approach, scalability.
+While this algorithm is fast, the Internet is still magnitudes of orders larger then what this would be able to handle.
+If we want to make the program go faster, without changing it we have to keep investing in better and more expensive CPUs, and there is a limit to how far we can do that.
+Enter parallel programming.
+
+	\subsubsection{Scaling Up with Parallel Programming}
+	There are a few types of parallel programming.
+The differences all boil down to how expensive it is to communicate between processes; for example two threads running on different cores of the same CPU communicate very quickly as they share memory whereas programs running on hundreds of computers across the world will find it much slower to communicate with each other.
+In this paper we specifically deal with parallel computing where communication is costly, as this allows for the most scalability.
+
+	The most obvious way to parallelize this program is to simply run this program on many computers, each with a different seed set and sending the collected information to some central database.
+The issue however arises that the crawlers are going to be overlapping each other, so the benefit we get from running this on a greater number of processes is very small.
+To formalize the issue, every time a process goes to a page that another process has already gone to it creates a redundancy, which we consider a waste of resources.
+
+	There are three basic ways of reducing redundancy in our crawl.
+	\begin{itemize}
+		\item Have each process keep and updated list of what pages have already been visited by every other process.
+To optimize for the significant cost of communication, we may employ a buffer so that each process stores what it has crawled and only sends a message to each other process for them to update their list under some predetermined condition.
+This of course means that more redundancy could happen but the cost of communication is great enough that buffering becomes necessary.
+
+		\item Have a master process that tells all the crawler processes what to crawl.
+As with the last approach, buffering is important, however here the buffering does not hurt us.
+The master simply send each crawler a list of URLs to crawl, once they are done they send back their results, and the master sends them a new batch.
+This method has benefit that it does not incur any redundancy as the master can ensure this.
+The potential downside to this method however is scalability.
+If there are enough crawlers running the master may be overworked and not able to keep up with them.
+It may be possible to unload more of the master's work onto the crawlers, however eventually one would want to find a way to distribute the master's work.
+This however is speculative and a single master may in-fact be enough as it can handle a tremendous amount of crawlers.
+
+		\item Find a way to divide the Internet up into chunks that each crawler knows to stay within.
+Consider that we have a way to partition the Internet into $n$ subsets.
+We may give each of our $n$ processes a single one of these subsets to crawl.
+There are a couple ways to do this, for example the most simple is maybe each processes gets a specific character and if that character and it's job is to discover everything with that character being first in the URL.
+This is simply an example idea, however it closely relates to one of the three methods of partitioning the Internet we will consider.
+
+		\begin{itemize}
+			\item \textbf{Hash function} - An issue with using the first letter of the URL is that not all letters are equally likely (for example \verb|w| appears quite often at the beggining of a URL with \verb|www|).
+To solve this we instead introduce the idea of a Hash function.
+A Hash function is a function $H:\mathbb N\to\cannonicalSet{n}$\footnote{$\cannonicalSet{n}$ is the set $\setbuilder{x\in\mathbb N}{x \le n}$.} for some $n\in\mathbb N$ with the requirement that given any random inputs to $H$ the results should be uniformly distributed.
+An example that fits this definition is using a modulo, and much better and more complex hash functions exist, we will not cover them in this paper, rather we will simply assume their existance.
+
+			Now that we have a hash function we may take the hash of any URL\footnote{In a computer everything may be treated as an integer if desired, even strings like URLs, so we can in fact take the Hash of a URL.} and based on that determine which process should crawl that page.
+This ensures that each process has an equal chunk of the Internet to crawl but at the cost that a crawler will be finding many links outside it's partition.
+
+			\item \textbf{Graph structure (communities)} - Here we try and split the Internet up in a way that makes sense given the structure of it's graph.
+We want to try and break the Internet into communities and give each community to a different process.
+This becomes a difficult problem given that we don't already have the entire graph discovered.
+We aren't going to be going deep into this idea, however it does warrant further investigation and I will give two possible ways trying to go about this.
+
+			\begin{itemize}
+				\item Use the already discovered parts of the graph to try and guess what community a URL might belong to.
+There may be some machine learning involved in this and you may need a master process or some way to coordinate between processes so that they may use even more information to inform their guesses.
+This process would allow for some redundancy to happen as guesses will not always be correct.
+That being said the amount of communication needed in this will be very minimal.
+
+				\item Use the fact that pages have content and that content relates to the graph structure of the Internet.
+The idea here is that we should suspect that two sites dealing with the same topic will be closer on the graph than two topics that are unrelated.
+We try here to levy the actual content of the pages to try and guess what the content of a link might be, and based on this we can choose to crawl it or not.
+			\end{itemize}
+
+			If we were to actually implement this method, we would probably want some combination of both these methods, as they both are fundamentally trying to break the Internet graph into communities and guess what community a URL belongs to.
+
+			\item \textbf{Geographic Location} - We won't spend much time talking about this approach.
+The idea is simple, on the Internet messages must travel and websites are hosted somewhere.
+The idea is that we try and optimize response time by having crawlers all around the world dealing with websites in their geographic location.
+This isn't greatly scalable however and would be used in conjunction with another method.
+		\end{itemize}
+	\end{itemize}
+
+	For our purposes we are going to use the master process method as it will be easier to adjust for what is needed.
+Now we have a fairly scalable method of running an efficient crawling algorithm.
+So what is next?
+
+	\subsubsection{Age and Freshness}
+	The Internet is not a static entity.
+It is always changing and we need to have our crawler reflect this.
+If we were able to finish a crawl of the Internet in a month, then we could keep re-crawling every month.
+This might be okay for most resources, but imagine someone today entering in the search query ``\verb|Trump|'' Into Google and only getting results that were at least a couple weeks old, obviously we need some way to recrawl important parts quickly.
+
+	The first step in doing this is instead of our master process simply queuing everything that is found, it will use a priority queue and will have to have some protocol for adding in old pages that we want to have re-crawled.
+This is where Age and Freshness come in to play.
+
+	\textbf{Age} is the amount of time since a page has been crawled.
+\textbf{Freshness} is weather or not a page has been changed since it was last crawled.
+Both terms are widely used when talking about web crawling, however for our purposes we will only be dealing with age.
+We also can leverage the fact that different pages will have different requirements for how old they should be.
+
+	What we want to come up with is a priority function.
+This should take into account both age, content of a page some measure of importance, and possibly some other information such as how often this page has been updated in the past.
+We can calculate an importance by using something like PageRank, however we will not be covering any such algorithm in this paper.
+Once we have a priority function we can consider every page that we have discovered and already crawled to be included within our queue on the master process.
+When a crawler requests a new batch of pages to crawl, the master simply sends it the $n$ URLs with the highest priority.
+
+	This finally gives us an algorithm that is fast, largely scalable, and will deal with the changing Internet.
+The next step is what should we do with all this data we've been discovering.
+It's important to realize that we aren't actually discovering the entire Internet, many pages have no links going to them.
+There are some ways of dealing with even this.
+
+	\subsubsection{Utilizing Oddities of the Internet}
+	Now there are some problems that come up when you are doing a massive Internet crawl.
+Many websites may get a lot of traffic (requests) from crawlers quickly going through all their pages, and this can slow down websites and be unintentionally harmful.\footnote{This is the basic idea of a DDOS (Distributed Denial Of Service) attack and can be very harmful to a website.} To deal with this, often a website will provide a \verb|robots.txt| file that tells crawlers what they should and should not crawl.
+Follwing what this file tells you is purely up to you as a polite crawler.
+
+	These \verb|robots.txt| files often can be helpful in finding new webpages on a website, that may be otherwise impossible to find.
+Even more helpful however is something called a sitemap.
+A sitemap is a file that can more or less give you all the pages and links within a website, which makes your job quite easy.
+You may still want to validate that the sitemap is not lieing to you, but even so it can help to discover even more potentially impossible to find parts of the web.
+
+	The last idea on finding URLs that aren't linked to is by using some educated guessing based on how websites tend to be structured.
+For example consider you find the URL \verb|www.abc.com/home/index/text|, you then very reasonably may guess that \verb|www.abc.com/home/index|, \verb|www.abc.com/home|, and \verb|www.abc.com| are all good candidates for possible pages.
+
+	\section{Searching}
+
+	Now that we have discovered our graph, or at least enough of it, we need some way to query.
+This is a problem that isn't well generalized.
+Rather then talk about how one might do this for any abstract data we will look at how we can do it on the Internet, and this will be modifiable to be usable in many situations.
+
+	The vast majority of the complexity for this comes from understanding natural language and dealing with tremendously large amounts of data, neither of which we are going to be going into any depth on, as such this section is quite short.
+
+	\subsection{On the Internet}
+
+	Now as we are crawling the web we are continually downloading web pages and we need some way to process these.
+Once a page is downloaded we need to choose how and what information from it to store.
+We're going to store a large index of all the `keywords' found in each web page.
+
+	In order to search quickly we want to turn this into a reverse index where we pair each keyword with the URL it comes from.
+Now when a query comes in, you may pick it apart however you like, find keywords matching what was searched, the serve up those pages as the result.
+
+	The last big part of this is ordering the pages, and for this there are many good algorithms.
+The most famous of which, PageRank will give a good measure of how important a page is based on the graph structure of the Internet.
+In practice you'll want to combine this with some other data, so that less significant but more relevant pages are able to show up.\footnote{A result's relevance is how closely it's content is related to the search query, whereas it's significance is how good of a page a result is.
+We may measure significance with PageRank while relevance is somewhat harder to measure.}
+
+	\section{Conclusion}
+
+	Now we have all the building blocks to build a search engine.
+We can build a high quality web crawler and we know what to do with it's results.
+While there may be many details left to figure out, one should have a clear idea of what steps need to be done.
+
+	\section{Further Work}
+	The next step in this research is to actually implement and test a distributed web crawler and compare a few of the different models described here and see how they compare.
+So far this has been beyond my means as the sort of computing power needed to test this requires hundreds of computers running in parallel.
+That being said, testing such an algorithm on even one computer may give some interesting results.
+
+	\section{Sources}
+
+	\begin{itemize}
+		\item \textbf{A Review of Web Crawler Algorithms} -  \url{http://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.661.1511&rep=rep1&type=pdf}
+
+		\item \textbf{The Anatomy of a Large-Scale Hypertextual
+			Web Search Engine} - \url{http://infolab.stanford.edu/pub/papers/google.pdf}
+
+		\item \textbf{Graph structure in the Web} -  \url{https://dl.dropboxusercontent.com/content_link/k2RzpEomf92MtS9iavSTlhGvNq5GRZ2gAutGoQjiKn141VXbbpKukaGLeDS5POAN/file?_download_id=3820982252842405369605800197997434545937153422705510517394288281257&_notify_domain=www.dropbox.com&dl=1}
+
+		\item \textbf{Parallel Crawlers} - \url{http://ilpubs.stanford.edu:8090/733/1/2002-9.pdf}
+
+	\end{itemize}
 

### 2018-05-27 Algebra/Homework/Homework.tex
backup

@@
 \subsubsection{Question 14}
-%TODO Fermat's little theorem, I have combinatorial proof but inductive evades me
+
+Let $n = 0$, then it is trivial that $n^p - n$ is divisible by $p$ for any prime $p$.
+
+Now let $n$ be a fixed non-negative integer, and assume that $n^p-n$ is divisible by $p$ for any prime $p$. By the binomial theorem we have
+\begin{align*}
+(n+1)^p - (n+1)
+&= \sumfrom{i=0}{p}{\binom{p}{i}n^i}-n-1 \\
+&= \sumfrom{i=1}{p-1}{\binom{p}{i}n^i}+n^p+1-n-1 \\
+&= \sumfrom{i=1}{p-1}{\binom{p}{i}n^i}+\left(n^p-n\right)
+\end{align*}
+By our assumption we have $n^p-n$ is divisible by $p$. Additionally $\binom pi$ must be divisible by $p$ for all $0 < i < p$ because $\binom pi = \frac{p!}{i!(p-i)!}$ and $p$ is prime.
+
+By induction we then know that $n^p-n$ is divisible by $p$ for any prime $p$.
 
@@
 
-\subsubsection{Question 8}
+\subsubsection{Question 3}
+Using Lemma 1.7.1, the fact that $\overline 1 = 1$, and some group axioms, we get.
+\begin{align*}
+1 &= (\overline z)^{-1}\overline z \\
+\therefore \overline 1 &= \overline{(\overline z)^{-1}\overline z} \\
+&= \overline{(\overline z)^{-1}}\cdot\overline{(\overline z)} \\
+&= \overline{(\overline z)^{-1}} \cdot z \\
+\therefore z^{-1} &= \overline{(\overline z)^{-1}} \\
+\therefore \overline{z^{-1}} &= \overline{\left(\overline{(\overline z)^{-1}}\right)} \\
+&= (\overline z)^{-1}
+\end{align*}
 
-By lemma 1.7.3 from the book we know that $\abs{uv} = \abs u\abs v$, therefore, as $zz^{-1} = 1$ we also have $\abs{zz^{-1}} = 1$ so $\abs z\abs{z^{-1}} = 1$ and it follows $\abs {z^{-1}} = 1 / \abs z$.
+\subsubsection{Question 6}
 
-\subsubsection{Question 14}
+For any $z \in\mathbb C$, there exists $a,b\in\mathbb R$ such that $z = a+bi$.
+Now $\overline z = a-bi$ by definition.
+Therefore $z = \overline z$ iff $b=0$ as $a-bi = a+bi$ iff $b=0$.
+Finally if $b=0$ then $z = a$ and therefore $z$ is real, if $b\not=0$ then $z=a+bi$ for some non-zero $b\in\mathbb R$ so $z$ has an imaginary part and is not real.
+Therefore we have shown that $z = \overline z$ iff $z\in\mathbb R$.
+
+Now if $a=0$ the we say that $z$ is purely imaginary as there is no real part to $z$.
+So if $z$ is purely imaginary then $z = bi$ and $\overline z = -bi = -z$.
+If we start with $\overline z = -z$ then we get
+\begin{align*}
+-(a+bi) &= a-bi \\
+-a-bi &= a-bi \\
+-a = a\\
+a = 0
+\end{align*}
+so $z$ must be purely imaginary. Putting this all together we get that $-z=\overline z$ iff $z$ is purely imaginary.
+
+%\subsubsection{Question 8}
+
+%By lemma 1.7.3 from the book we know that $\abs{uv} = \abs u\abs v$, therefore, as $zz^{-1} = 1$ we also have $\abs{zz^{-1}} = 1$ so $\abs z\abs{z^{-1}} = 1$ and it follows $\abs {z^{-1}} = 1 / \abs z$.
+
+\subsubsection{Question 11}
+
+\question{(a)} $z = \cos\frac{7\pi}4 + i\sin\frac{7\pi}{4}$
+
+\question{(b)} $z = 4\left(\cos \frac\pi2 + i\sin \frac\pi2\right)$
+
+\question{(c)} $z = 36\left(\cos \frac\pi4 + i\sin \frac\pi4\right)$
+
+\question{(d)} $z = 13\left(\cos \frac{2\pi}3 + i \sin\frac{2\pi}3 \right)$
+
+\subsubsection{Question 13}
+\begin{align*}
+\left(\frac12 + \frac12\sqrt3i\right)^3 &= \left(\frac12\left(1+\sqrt3i\right)\right)^3 \\
+&= \frac18\left(1+\sqrt3i\right)^3 \\
+&= \frac18\left( 1 + 3\sqrt3i+ 3\left(\sqrt3i\right)^2 + \left(\sqrt3i\right)^3 \right) \\
+&= \frac18\left( 1 + 3\sqrt3i - 9 - 3\sqrt3i \right) \\
+&= \frac18\left(-8\right) \\
+&= -1
+\end{align*}
+
+%\subsubsection{Question 14}
 
 %Get help from Russos?
-By Euler's equation we know that $\cos\theta + i\sin\theta = e^{i\theta}$. We have ${\left(e^{i\theta}\right)}^m = e^{im\theta} = \cos (m\theta) + i\sin (m\theta)$
+%By Euler's equation we know that $\cos\theta + i\sin\theta = e^{i\theta}$. We have ${\left(e^{i\theta}\right)}^m = e^{im\theta} = \cos (m\theta) + i\sin (m\theta)$
+
+\subsubsection{Question 20}
+
+Let us adopt the notation that for any $c\in\mathbb C$, $$c = c_a + c_bi$$ where $c_a,c_b\in\mathbb R$.
+\begin{align*}
+\abs{z+w}^2+\abs{z-w}^2 &= \abs{z_a+z_bi + w_a+w_bi}^2 + \abs{z_a+z_bi - w_a-w_bi}^2 \\
+&= (z_a+w_a)^2+(z_b+w_b)^2+(z_a-w_a)^2+(z_b-w_b)^2 \\
+&= {z_a}^2+2z_aw_a+{w_a}^2 + {z_b}^2+2z_bw_b+{w_b}^2 +{z_a}^2-2z_aw_a+{w_a}^2 + {z_b}^2-2z_bw_b+{w_b}^2 \\
+&= 2\left({z_a}^2+{a_b}^2+{w_a}^2+{w_b}^2\right)\\
+&= 2\left( \abs{z}^2 + \abs{w}^2 \right)
+\end{align*}
+
+\subsubsection{Question 21}
+
+Our approach here is to partition $A$ into countably many finite sets, this will show that there is a 1-1 and onto correspondence from $A$ to $\mathbb N$ as they are both countably infinite.
+We define $\abs{a+bi}_1 = \abs a + \abs b$.
+Now we define the set $Z_k = \setbuilder{z\in A}{\abs{z} = k}$ for $k \in\mathbb N \union\set0$.
+Now for all $z\in A$, there exists some $k\in\mathbb N \union\set 0$ such that $z\in Z_k$ as for any $z\in A$, $z = a+bi$ for $a,b\in\mathbb Z$ and therefore $\abs{z} = \abs{a} + \abs{b} \in \mathbb N \union \set 0$ so there is some $k\in\mathbb N \union\set 0$ such that $z \in Z_k$.
+For any $k\in\mathbb N\union\set 0$ we also have $Z_k$ is finite as for all $a+bi \in Z_k$, $\abs a\le k$ and $\abs b \le k$, therefore there are only finitely many possibilities for $a$ and $b$.
+Now we have $\unionacross{k\in\mathbb N \union\set 0}{Z_k} = A$ with each $Z_k$ finite, so $A$ must be countable.
+
+\subsubsection{Question 22}
+
+First we will prove that $P(\overline x) = \overline{P(x)}$ for any polynomial $P:\mathbb C \to \mathbb C$ with real coefficients, $\alpha_0, \alpha_1,\ldots,\alpha_n$.
+Let $z \in \mathbb C$ such that $z = a+bi$ with $a$ and $b$ real.
+Notice that for any $\alpha\in\mathbb R$,
+\begin{align*}
+\alpha\overline z &= \alpha(a - bi) \\
+&= \alpha a - \alpha bi \\
+&= \overline{\alpha z}
+\end{align*}
+From lemma 1.7.1 we get $\overline{zw} = \overline z \overline w$, so it follows that $\overline{z^n} = \overline{z}^n$.
+Finally from lemma 1.7.1 we also get $\overline {z + w} = \overline z + \overline w$ so it follows that $\overline{\sum z_j} = \sum \overline{z_j}$.
+So if $P(x) = \sumfrom{j=0}{n}{\alpha_jx^j}$ then it follows
+\begin{align*}
+P(\overline{x}) &= \sumfrom{j=0}{n}{\alpha_j\overline x^j} \\
+&= \sumfrom{j=0}{n}{\alpha_j\overline{x^j}} \\
+&= \sumfrom{j=0}{n}{\overline{\alpha_jx^j}} \\
+&= \overline{\sumfrom{j=0}{n}{\alpha_jx^j}} \\
+&= \overline{P(x)}
+\end{align*}
+
+Therefore if we have any polynomial $P$ with real coefficients, and $P(x) = 0$ then $P(\overline x) = \overline 0 = 0$.
+
+\section{Chapter 2}
+\subsection{Section 1}
+\subsubsection{Question 8}
+Let us start with when $n=0$, then $(a*b)^n = e = a^n*b^n$.
+
+For $n > 0$ we will do induction, so let us assume that $(a*b)^{n-1} = a^{n-1}*b^{n-1}$, therefore 
+\begin{align*}
+(a*b)^n &= (a*b)^{n-1}*(a*b) \\
+&= (a^{n-1}*b^{n-1}) * (a * b) \\
+&= (a^{n-1} * a) * (b^{n-1} * b) \\
+&= a^n * b^n
+\end{align*}
+as we already have the case $n=0$ this induction proves the statement for $n\ge 0$.
+
+Now assume $n<0$, therefore $a^n = \left(a^{-1}\right)^{-n}$ and as $a^{-1} \in G$ and $-n > 0$ then we simply refer to our previous work and conclude that the statement still holds.
+
+\subsubsection{Question 9}
+
+Let $a,b\in G$.
+\begin{align*}
+e &= (a*b)^2 \\
+e &=  a^2 \\
+e &= b^2 \\
+e &= e * e \\
+&= a^2 * b^2\\
+a^2 * b^2 &= (a*b)^2\\
+a*a*b*b &= a*b*a*b \\
+a^{-1}*a*a*b*b*b^{-1} &= a^{-1}*a*b*a*b*b^{-1}\\
+a*b &= b*a
+\end{align*}
+
+\subsubsection{Question 19}
+
+We simply list off all elements of $S_3$ as $S_3$ is small.
+
+\begin{tabular}{c|c|c}
+	$x\in S_3$ & Does $x^2 = e$ & Does $x^3 = e$ \\
+	\hline
+	$(1,2,3)$ & Yes & Yes \\
+	$(1,3,2)$ & Yes & No \\
+	$(2,1,3)$ & Yes & No \\
+	$(2,3,1)$ & No & Yes \\
+	$(3,2,1)$ & Yes & No \\
+	$(3,1,2)$ & No & Yes \\
+\end{tabular}
+
+\subsubsection{Question 20}
+This is all elements $p\in S_4$ such that there does not exist exactly one $x$ such that $p(x) = x$.
+\begin{enumerate}
+	\item $(1,2,3,4)$
+	\item $(1,2,4,3)$
+	\item $(2,1,3,4)$
+	\item $(2,1,4,3)$
+	\item $(1,4,3,2)$
+	\item $(3,2,1,4)$
+	\item $(3,4,1,2)$
+	\item $(1,3,2,4)$
+	\item $(4,2,3,1)$
+	\item $(4,3,2,1)$
+	\item $(2,3,4,1)$
+	\item $(2,4,1,3)$
+	\item $(3,4,2,1)$
+	\item $(3,1,4,2)$
+	\item $(4,1,2,3)$
+	\item $(4,3,1,2)$
+\end{enumerate}
+\subsubsection{Question 26}
+
+Let $G$ be a finite group.
+Assume for the sake of contradiction that there is some $a\in G$ such that for all $n \in\mathbb N$, $a^n\not= e$.
+As $G$ is finite there then must be some $n_1\not=n_2$ such that $a^{n_1} = a^{n_2}$ by the pigeon hole principle.
+Let us assume without loss of generality that $n_2 > n_1$, it follows then that $a^{n_1}*a^{-n_1} = a^{n_2}*a^{-n_1}$ and therefore $e = a^{n_2 - n_1}$.
+This means we have a contradiction and therefore there exists some $n\in\mathbb N$ such that $a^n=e$ for any $a \in G$.
+
+\subsubsection{Question 27}
+
+We already have shown that each element $a\in G$ has some specific $n_a$ such that $a^n = e$. It follows then that if $m = {\prodacross{a\in G}{n_a}}$ then $a^m = e$ for all $a\in G$.
+\begin{proof}
+	Choose $a \in G$ and let $m = \prodacross{g\in G}{n_g}$. Now $a^m = a^{(m/n_a)(n_a)}$, and for notation let $m_a = \frac m{n_a}$. We now have
+	\begin{align*}
+	a^m &= a^{n_a\cdot m_a} \\
+	&= \left(a^{n_a}\right)^{m_a} \\
+	&= e^{m_a} \\
+	&= e
+	\end{align*}
+\end{proof}
+
+\subsubsection{Question 28}
+
+First we know that for any $a \in G$ there exists some $a^{-1} \in G$ such that $a^{-1} a = e$ We will adopt this notation as well as simply saying $ab = a * b$ for $a,b\in G$. Now we have
+\begin{align*}
+aa^{-1}aa^{-1} &= aea^{-1} \\
+&= aa^{-1} \\
+\therefore \left(aa^{-1}\right)^{-1}aa^{-1} &= \left(aa^{-1}\right)^{-1}aa^{-1}aa^{-1} \\
+\therefore e &= aa^{-1}
+\end{align*}
+
+Next we wish to prove some a lemma. If $ab = ac$ then $b = c$
+\begin{proof}
+	\begin{align*}
+	ab = ac &\implies a^{-1}ab = a^{-1}ac \\
+	&\implies eb=ec \\
+	&\implies b = c
+	\end{align*}
+\end{proof}
+
+Now with this we can say that for all $a \in G$, there exists exactly one inverse as if $ab = e = ac$, then $b = c$.
+We also can say an element $a\in G$ is the inverse of exactly one element by the exact same proof.
+
+Finally we get
+\begin{align*}
+aea^{-1} &= aa^{-1} \\
+&= e \\
+\therefore a^{-1} &= (ea)^{-1} \\
+\therefore a &= ea
+\end{align*}
+
+\subsection{Section 2}
+\subsubsection{Question 1}
+\subsubsection{Question 2}
+\subsubsection{Question 5}
+
+\subsection{Section 3}
+\subsubsection{Question 4}
+\subsubsection{Question 5}
+\subsubsection{Question 11}
+\subsubsection{Question 22}
+\subsubsection{Question 24}
+\subsubsection{Question 26}
+\subsubsection{Question 28}
+\subsubsection{Question 29}
+
+\subsection{Section 4}
+\subsubsection{Question 1}
+\subsubsection{Question 5}
+\subsubsection{Question 18}
+\subsubsection{Question 24}
+\subsubsection{Question 30}
+\subsubsection{Question 35}
+\subsubsection{Question 37}
+\subsubsection{Question 38}
+\subsubsection{Question 42}
+\subsubsection{Question 43}
+
+\subsection{Section 5}
+\subsubsection{Question 3}
+\subsubsection{Question 17}
+\subsubsection{Question 18}
+\subsubsection{Question 19}
+\subsubsection{Question 24}
+\subsubsection{Question 26}
+\subsubsection{Question 29}
+\subsubsection{Question 38}
+\subsubsection{Question 42}
 

### 2018-05-27 NetworkScience/Final/Final.tex
backup

@@
 	\begin{abstract}
-		There are many different types of search engines, the most complicated of which are where you do not initially have knowledge of what is being searched and that information may change.
-In order to tackle this we need some way of discovering possible results, matching these results to a query and ranking possible results.
+		There are many different types of search engines for many different use cases.
+In this paper will investigate how one may make a search engine for the Internet or a similar entity.
+In doing this we need some way of discovering possible results, matching these results to a query and ranking possible results.
 This paper deals largely with the discovery and more specifically a process called web crawling.

### 2018-06-15 Algebra/Homework/Homework.tex
hi

@@
 \subsubsection{Question 1}
+
+Let $a\in G$, therefore there is some $e\in G$ st.
+$ea = a$ by statement 1.
+Let $b \in G$ therefore there exists $c\in G$ such that $ca = b$.
+It follows $be = cae = ca = b$.
+It has now been shown that there exists $e \in G$ such that for all $x \in G$, $xe = x$.
+
+Now let $a\in G$ then there must exist a $b\in G$ such that $ba = e$. Now we shown that $G$ has the same properties as the set $G$ from Section 1, Question 28, and therefore must be a group.
+
 \subsubsection{Question 2}
+
+Choose $a \in G$, and let us define $f:G\to G$ as $f(x) = ax$ and $g:G\to G$ as $g(x) = xa$.
+Now the thing to notice is that $f$ is 1-1 as for any $u,v \in G$ we have $f(u) = au$ and $f(v) = av$, so $av = au$ iff $v=u$.
+The same statement may be made about $g$.
+As $f$ and $g$ are 1-1 on a finite set $G$ we then also have $f$ and $g$ are onto.
+This means that for any $a,y\in G$ there is some $x$ such that $ax = f(x) = y$ and for any $a,w\in G$ there is some $u$ such that $ua = g(u) = w$.
+Therefore we have the conditions from Question 1 and can conclude that $G$ is a group.
+
 \subsubsection{Question 5}
 
+All we need to show that $G$ is abelian is for all $a,b \in G$, $ab = ba$. To start let us choose $a,b \in G$. We know that $a^5b^5 = (ab)^5$ so we get
+\begin{align*}
+a^5b^5 &= (ab)^5 \\
+&= a(ba)^4b \\
+\therefore a^4b^4 &= (ba)^4
+\end{align*}
+and we make a similar argument with $a^3b^3 = (ab)^3$ so
+\begin{align*}
+a^3b^3 &= (ab)^3 \\
+&= a(ba)^2b \\
+\therefore a^2b^2 &= (ba)^2
+\end{align*}
+We combine these to get that
+\begin{align*}
+a^4b^4 &= (ba)^4\\
+ &= \left((ba)^2\right)^2 \\
+ &= \left(a^2b^2\right)^2 \\
+ &= a^2b^2a^2b^2 \\
+ \therefore a^2b^2 &= b^2a^2
+\end{align*}
+ and finally wrap up with
+ \begin{align*}
+ a^2b^2&= b^2a^2 \\
+ &= (ab)^2 \\
+ \therefore a^2b^2 &= (ab)^2 \\
+ &= abab \\
+ \therefore ab &= ba
+ \end{align*}
+
 \subsection{Section 3}
+\subsubsection{Question 4}\label{sec:question-4}
+$Z(G)$ is defined as $\setbuilder{z\in G}{x\in G \; \forall\; {zx=xz}}$. First let us choose $a,b\in Z(G)$ therefore for all $x \in G$ we have $ax = xa$ and $bx = xb$. It follows
+\begin{align*}
+(ab)x &= a(bx) \\
+&= a(xb) \\
+&= (ax)b \\
+&= (xa)b \\
+&= x(ab)
+\end{align*}
+so $ab \in Z(G)$.
+
+Now choose $a\in Z(G)$, therefore for all $x\in G$, $ax = xa$. It follows then that
+\begin{align*}
+(xa)a^{-1} &= x \\
+&= a^{-1}ax \\
+&= a^{-1}(xa) \\
+xaa^{-1}a^{-1} &= a^{-1}xaa^{-1} \\
+\therefore xa^{-1} &= a^{-1}x
+\end{align*}
+and by definition $a^{-1} \in Z(G)$. Now by lemma 2.3.1 $Z(G)$ is a subgroup of $G$.
+
+\subsubsection{Question 5}
+Let $x \in Z(G)$, it follows that for all $a \in G$, $ax = xa$, so therefore for all $a \in G$, $x \in C(a)$, thus $Z(G) \subset \interacross{a\in G}{C(a)}$.
+Let $x \in \interacross{a\in G}{C(A)}$, then $xa = ax$ for all $a \in G$, and thus $x \in Z(G)$ and therefore $\interacross{a\in G}{C(A)} \subset Z(G)$.
+By definition of set equality $Z(G) = \interacross{a\in G}{C(A)}$.
+
+\subsubsection{Question 11}
+Let $a,b \in H$, therefore $a^{n(a)} = e = b^{n(b)}$. Now it follows that
+\begin{align*}
+(ab)^{n(a)\cdot n(b)} &= a^{n(a)n(b)}b^{n(a)n(b)} \\
+&= e^{n(b)}e^{n(a)} \\
+&= e
+\end{align*}
+thus $ab \in H$.
+
+Let $a \in H$, therefore $a^{n(a)} = e$. It follows that $a^{n(a)-1}a = e$, so $a^{n(a)-1} = a^{-1}$ and as we have already shown $H$ to be closed, then $a^{-1}=a^{n(a)-1}\in H$.
+
+By lemma 2.3.1 it has been demonstrated that $H$ is a subgroup of $G$.
+
+\subsubsection{Question 22}
+
+Let us first show that $AB$ is a group.
+For any $x,y\in AB$, then let $x_a,y_a \in A$ and $x_b,y_b\in B$ such that $x_ax_b = x$ and $y_ay_b = y$.
+It follows that $xy = x_ax_by_ay_b = x_ay_ax_by_b \in AB$ as $G$ is abelian.
+Now for $x \in AB$ then there exists $a\in A$ and $b\in B$ such that $ab = x$.
+Therefore $a^{-1} \in A$ and $b^{-1}\in B$ as they are both groups, it then follows that $a^{-1}b^{-1} \in AB$ and $a^{-1}b^{-1}ab = e$ by commutativity, so $a^{-1}b^{-1}=(ab)^{-1}$.
+Thus it has been shown that $AB$ is a group.
+
+Next we will show that $\card{AB}= \frac{\card{A}\card{B}}{\card{A\inter B}}$.
+
+Let us choose $a \in A$ and $b \in B$ then notice that for all $c \in A\inter B$ then $ac \in A$ and $c^{-1}b \in B$ and therefore $(ac)(c^{-1}b) = ab$.
+Therefore there are at least as many $(a,b)$ pairs such that $ab$ is equal as there are elements in $A \inter B$.
+Now assume there is some other $\bar a \in A$ and $\bar b \in B$ such that there is no $\bar c \in A\inter B$ such that $\bar a \bar c = a$ and ${\bar c}^{-1}\bar b = b$.
+If $\bar a\bar b = ab$ then $a^{-1}\bar a = b\bar b^{-1} \in A\inter B$.
+We will let $\bar c^{-1} = b\bar b^{-1}$ as we then get $\bar c^{-1}\bar b = b\bar b^{-1}\bar b = b$ we then will also find that $\bar c= \bar a^{-1}a$ and thus $\bar a\bar c = \bar a\bar a^{-1}a = a$.
+Finally we conclude that for any element $ab \in AB$, there exists exactly $\card{A \inter B}$ pairs $(\bar a,\bar b) \in A\cross B$ such that $ab = \bar a\bar b$.
+
+Finally if $\bar A$ is relatively prime  to $\bar B$ then $A \inter B = \set e$ as for any $a \in A \inter B$ there would be a cyclic set generated by $a$ and that cyclic set's order must divide both $A$ and $B$.
+Only if the order is one is this possible so the only element may be the identity element.
+
+\subsubsection{Question 24}
+
+First we show $N$ to be a group.
+Let $n,k \in N$, so if we choose $x \in G$ then there exists $h_1\in H$ such that $n=x^{-1}h_1x$ and $h_2 \in H$ such that $k=x^{-1}h_2x$.
+It follows that $nk= x^{-1}h_1xx^{-1}h_2x = x^{-1}h_1h_2x$, and therefore is in $N$ as $h_1h_2 \in H$.
+Now let $n \in N$, and choose $x\in G$ then there exists $h\in H$ such that $n = x^{-1}hx$ then it follows that $n^{-1} = \left(x^{-1}hx\right)^{-1} = x^{-1}h^{-1}x$ and as $h^{-1} \in H$ then $n^{-1} \in N$.
+This proves $N$ to be a group.
+
+Now let us show that for all $y \in G$, $y^{-1}Ny = N$.
+Let us choose $n \in N$, and $y \in G$.
+By $n \in N$ we then choose $x \in G$ and there must exist $h \in H$ such that $n=x^{-1}hx$, then it follows that $y^{-1}ny= y^{-1}x^{-1}hxy$.
+Now we may choose $z \in G$ and let $x$ be such that $xy = z$ then we find that $y^{-1}x^{-1}hxy = z^{-1}hz$ and therefore $y^{-1}Ny=N$.
+
+\subsubsection{Question 26}
+
+If there exists $h_1, h_2 \in H$ such that $h_1a = h_2b$ then it follows that $ab^{-1} = {h_1}^{-1}h_2 \in H$.
+Now for any $\bar a \in Ha$ there is some $h \in H$ such that $ha = \bar a$.
+It then must be so that $hab^{-1}b \in B$ as we know that $ab^{-1} \in H$ and as $hab^{-1}b = ha = \bar a$ then $Ha \subset Hb$.
+By symmetry we also know that $Hb \subset Ha$, therefore $Ha = Hb$.
+
+We've now shown if $Ha \inter Hb \not= \emptyset$ then $Ha = Hb$ and otherwise obviously $Ha \inter Hb = \emptyset$.
+
+\subsubsection{Question 28}
+
+First let us reference the next question as it will prove that $M = x^{-1}Mx$ and $N = x^{-1}Nx$ for all $x\in G$. Now we will proceed to show that $MN$ is a group.
+
+Let $c \in MN$, therefore there is some $a \in M$ and $b \in N$ such that $ab = c$.
+Now as $N = x^{-1}Nx$ for all $x \in G$ then there exists some $\bar b \in N$ such that $a^{-1}\bar ba = b$, therefore $ab = aa^{-1}\bar ba = \bar ba$.
+We now get inverses as $c^{-1} = a^{-1}\bar b^{-1}$ and $a^{-1} \in M$ and $\bar b^{-1} \in N$.
+Now let $d \in MN$ as well, then there is some $m \in M$ and $n \in N$ such that $d = mn$.
+Now as $m \in M = x^{-1}Mx$ for all $x \in G$ then there is $\bar m \in M$ such that $b^{-1}\bar mb = m$.
+It follows that $cd = abmn = abb^{-1}\bar mbn = a\bar mbn\in MN$ as $a,\bar m \in M$ and $b,n \in N$.
+
+Now finally to show that $x^{-1}MNx \subset MN$ for all $x \in G$ we choose $x \in G$ and $d = mn \in MN$ with $m \in M$ and $n \in N$.
+We then find $x^{-1}mnx = (x^{-1}mx)(x^{-1}nx)$ and of course $x^{-1}mx \in M$ and $x^{-1}nx \in N$.
+
+\subsubsection{Question 29}
+
+Let $m \in M$ and let $x \in G$.
+We wish to show the existence of $n \in M$ such that $x^{-1}nx = m$.
+If we let $x^{-1}nx = m$ then we get $n=xmx^{-1}$ and as $x^{-1}\in G$ and $m\in M$ the we get $n \in x^{-1}Mx \subset M$ so $n \in M$.
+Now we have shown that $m \in x^{-1}Mx$ and thus $x^{-1}Mx = M$.
+
+\subsection{Section 4}
+\subsubsection{Question 1}
+
+\begin{enumerate}
+	\item $a ~ b$ for $a,b \in \mathbb R$ iff $a - b \in\mathbb Q$.
+	\begin{itemize}
+		\item \textbf{Reflexivity} $a - a = 0 \in \mathbb Q$, therefore $a \sim a$.
+		\item \textbf{Symmetry} If $a\sim b$ then $a-b =q \in\mathbb Q$, therefore $b-a=-q\in\mathbb Q$, so $b\sim a$.
+		\item \textbf{Transitivity} If $a\sim b$ and $b \sim c$ then $a-b = q \in\mathbb Q$ and $b - c = p \in\mathbb Q$, therefore $a-c = a-b+b-c = q + p \in\mathbb Q$, so $a \sim c$.
+	\end{itemize}
+	\item $a \sim b$ for $a,b\in\mathbb C$ iff $\abs a = \abs b$.
+	\begin{itemize}
+		\item \textbf{Reflexivity} $a \sim a$ is trivial.
+		\item \textbf{Symmetry} If $a\sim b$ then $\abs a = \abs b$. By symmetry of equality we have $\abs b = \abs a$ and therefore $a \sim b$.
+		\item \textbf{Transitivity} If $a\sim b$ and $b\sim c$ then $\abs a = \abs b = \abs c$ therefore $\abs a = \abs c$ so $a \sim c$.
+	\end{itemize}
+	\item $a \sim b$ for lines $a,b$ in the plane if $a$ is parallel to $b$.
+	\begin{itemize}
+		\item \textbf{Reflexivity} Any line $a$ is parallel to itself.
+		\item \textbf{Symmetry} If $a$ is parallel to $b$ then $b$ must also be parallel to $a$.
+		\item \textbf{Transitivity} If $a$ is parallel to $b$ and $b$ is parallel to $c$ then we would also have $a$ parallel to $c$.
+	\end{itemize}
+	\item $a \sim b$ for people $a,b$ if $a$'s eye color is the same as $b$'s eye color.
+	\begin{itemize}
+		\item \textbf{Reflexivity} You have the same eye color as yourself.
+		\item \textbf{Symmetry} If $a\sim b$ then $a$'s eye color is $b$'s eye color and therefore $b$'s eye color is $a$'s eye color so $b \sim a$.
+		\item \textbf{Transitivity} If $a\sim b$ and $b \sim c$ then $a$'s eye color is $b$'s eye color and $b$'s eye color is $c$'s eye color then it must be that $a$'s eye color is $c$'s eye color so $a \sim c$.
+	\end{itemize}
+\end{enumerate}
+
+\subsubsection{Question 5}
+
+Let us first show that $a\sim b$ is an equivalence relation.
+\begin{itemize}
+	\item \textbf{Reflexivity} For any $a \in G$, $a^{-1}a = e \in H$ therefore $a \sim a$.
+	\item \textbf{Symmetry} For any $a\sim b \in G$ we get $a^{-1}b \in H$. Now $\left(a^{-1}b\right)^{-1} = b^{-1}a$ must also be a member of $H$, so $b \sim a$.
+	\item \textbf{Transitivity} Let $a \sim b$ and $b \sim c$.
+We get then that $a^{-1}b \in H$ and $b^{-1}c \in H$.
+It follows then that $\left(a^{-1}b\right)\left(b^{-1}c\right) = a^{-1}c \in H$, so $a \sim c$.
+\end{itemize}
+Now we show that $\eqclass{a} = aH$.
+
+Let $\alpha \in \eqclass a$, therefore $a \sim \alpha$ so $a^{-1}\alpha \in H$. We then get that $aa^{-1}\alpha = \alpha \in aH$, so $\eqclass a \subset aH$.
+
+Now Let $\alpha \in aH$, therefore there is some $h \in H$ such that $\alpha = ah$.
+It follows then that $a^{-1}\alpha = a^{-1}ah = h \in H$ so $a \sim \alpha$, and therefore $\alpha\in\eqclass a$ so $\eqclass a \supset aH$.
+
+We now conclude $aH = \eqclass a$.
+
+\subsubsection{Question 18}
+
+Consider the group $U_p$ under multiplication.
+Notice that for all $0 < n < p$, $n$ is relatively prime to $p$, so all $0 < n < p$ is included.
+This yields $p-1$, an even number of elements so when we multiply them all together we get $(p-1)!$ and from problem 16 we know that this must be some $x \in U_p$ such that $x^2 \equiv 1 \mod p$.
+
+Now there are only two $n \in U_p$ such that $n^2 \equiv 1 \mod p$, $1, -1$.
+The proof for this is as follows.
+Obviously $1^2 = (-1)^2 = 1$.
+Now assume for some $n \in U_p$, $n^2 \equiv 1 \mod p$ therefore $n^2 -1 = (n+1)(n-1) \equiv 0 \mod p$ so $p$ divides $n+1$ or $p$ divides $n-1$ as $p$ is prime.
+This leaves only $n \equiv -1 \mod p$ or $n \equiv 1 \mod p$.
+
+Now as only $1^2$ and $(-1)^2$ are $1$ in $U_p$ we get that every element $x \in U_p$ that is not $1$ or $-1$ has a compliment in $U_p$, and therefore $(n-1)!
+\equiv 1\cdot -1 \mod p$ and this obviously leaves $(n-1) \equiv -1 \mod p$.
+
+\subsubsection{Question 24}
+
+Let $p = 4n+3$ and let $\mathbb Z/p$ be the set of integers mod $p$, and further let us adopt the notation that $\mathbb Z/p^* = \mathbb Z/p \setminus \set 0$.
+Now assume $x \in \mathbb Z/p$ such that $x^2 \equiv -1 \mod p$.
+Now we get $x^4 \equiv 1 \mod p$ so $o(x)$ must divide $4$, either 1, 2, or 4.
+If $o(x) = 1$ then $x=1$ and $x^2\not \equiv -1 \mod p$ unless $p = 2$ which violates $p = 4n+3$.
+If $o(x) = 2$ then $x^2 = 1 \not\equiv -1$ as $p\not=2$ again.
+So it must be that $o(x) = 4$.
+Now $\mathbb Z/p^*$ forms a group with order $p-1$ under multiplication as $p$ is prime, so if $o(x) = 4$ then the cyclic group generated by $x$ would be a subgroup of $Z/p^*$ with order 4.
+Now $p-1 = 4n+2$ which is not divisible by 4 so we have a contradiction due to Lagrange's theorem.
+
+This does overlook if $x = 0$, however then $x^2 = 0 \not = -1$.
+
+\subsubsection{Question 30}
+\begin{itemize}
+	\item $b^2 = aba^4$
+	\item $b^4 = \left(b^2\right)^2 = aba^4aba^4 = ab^2a^4 = a^2ba^3$
+	\item $b^8 = \left(b^4\right)^2 = a^2ba^3a^2ba^3 = a^2b^2a^3 = a^3ba^2$
+	\item $b^{16} = \left(b^8\right)^2 = a^3ba^2a^3ba^2 = a^3b^2a^2 = a^4ba$
+	\item $b^{32} = \left(b^{16}\right)^2 = a^4baa^4ba = a^4b^2a = ebe = b$
+\end{itemize}
+
+So we know $b^{32} = b$, then it follows that $b^{32}b^{-1} = bb^{-1} = e$ so $b^{31} = e$.
+This means $o(b)$ must be a divisor of $31$, however as $31$ is prime and we know $o(b)\not= 1$ as $b \not= e$ then $o(b) = 31$.
+\subsubsection{Question 35}
+
+For any permutation we may find it's order by looking at it's cycle structure and taking the least common multiple of all the cycles in the permutation.
+Now if a permutation has a prime order then it's cycles may either be length 1 or length $p$, where $p$ is that specific prime.
+Not all our cycles can be of length $p$ as $\card S$ is not a multiple of $p$.
+We conclude there must be some cycle of length 1 and thus some element maps to itself.
+
+\subsubsection{Question 37}
+Let $G$ be a cyclic group of order $n$ with $g$ as a primitive element.
+Choose $m$ such that $m$ is a divisor of $n$ and choose $k \le m$ such that $\gcd(k,m) = 1$.
+It follows that $\left(g^{k\frac nm}\right)^m = g^{k\frac nmm} = g^{kn} = e$ so $o\left(g^{k\frac nm}\right) | m$.
+Let us assume for the sake of contradiction now that $o\left(g^{k\frac nm}\right) \not= m$, therefore $o\left(g^{k\frac nm}\right) < m$.
+Let then $\bar m < m = o\left(g^{k\frac nm}\right)$, therefore we get $\left(g^{k\frac nm}\right)^{\bar m} = g^{k\frac nm \bar m} = e$ so we get that $k\frac nm\bar m \equiv 0 \mod n$ and therefore there is some $\bar k$ such that $k\frac nm\bar m = \bar kn$.
+Dividing by $n$ e get $\frac {k\bar m}m = \bar kn$.
+We know that $k$ is relatively prime to $m$ so $\frac{\bar m}m$ is an integer which yields a contradiction as $\bar m < m$ and therefore $\frac{\bar m}{m} < 1$.
+This means that for all $m$ divisible by $n$, and any $k \le m$ such that $\gcd(k,m) = 1$, we get $o\left(g^{k\frac nm}\right) = m$.
+
+Next we show that for all $a$ with $0 < a \le n$ there is some $m | n$ and $k$ with $\gcd(m,k) = 1$ such that $a = \frac nmk$.
+For notational sake let for all $x \in\mathbb N$, $x = \factorize{x}{i}$, where $p_i$ is the $i^{\text{th}}$.
+This means that we wish to show that $$\factorize ai = \frac{\factorize ni}{\factorize mi} \factorize ki$$, we may simplify this and show $$\factorize{a}{i} = \prodacross{i\in\mathbb N}{{p_i}^{n_i-m_i+k_i}}$$ and due to properties of primes we need only show that for all $i\in\mathbb N$, $a_i = n_i-m_i+k_i$.
+Now we have the restriction that $m|n$ which simply means that for all $i\in\mathbb N$, $m_i \le n_i$.
+We also have the restriction that $\gcd(m,k) = 1$ this can be taken to mean there are no prime divisors shared between $m$ and $k$ so $k_i\not=0\implies m_i = 0$ and $m_i\not=0\implies k_i=0$ for all $i\in\mathbb N$.
+With these restrictions we can construct $m$ and $k$.
+For all $i\in\mathbb N$ we follow these rules:
+\begin{itemize}
+	\item If $0\le a_i \le n_i$, then let $m_i = n_i - a_i$ and $k_i = 0$, therefore we get $n_i-m_i+k_i = n_i - (n_i-a_i) + 0 = a_i$.
+	\item If $n_i < a_i$ then let $k_i = a_i - n_i$ and $m_i = 0$ therefore we get $n_i-m_i+k_i = n_i-0+(a_i-n_i) = a_i$.
+\end{itemize}
+Notice also that $k \ge m$ as otherwise $a = \frac nmk = n \frac km < n$ and we know $a \le n$.
+
+Finally this means that for any $\alpha \in G$ we know that there exists $0 < a \le n$ such that $g^a = \alpha$ and therefore there is some $m |n$ such that there is a $k\le m$ where $\gcd(k,m) = 1$ and $\frac mnk = a$ so $\alpha = g^{\frac mnk}$ and therefore as we have already shown $o(\alpha) = m$.
+This means that for all $m | n$ there are exactly $\varphi(m)$ elements $\alpha \in G$ such that $o(\alpha) = m$.
+
+\subsubsection{Question 38}
+
+Let there be a cyclic group $G$ of order $n$.
+One must exist for all $n \in\mathbb N$ as the integers mod $n$ under addition are a cyclic group of order $n$ with 1 as their primitive root.
+For each divisor of $m$ of $n$ there are $\varphi(m)$ elements $\alpha \in G$ such that $o(\alpha) = m$.
+There can be no elements $\alpha\in G$ such that $o(\alpha)$ does not divide $n$ by Lagrange's theorem so we know that $n = \sumacross{m|n}{\varphi(m)}$.
+
+\subsubsection{Question 42}
+
+Let $p = 4n+1$.
+
+\begin{align*}
+\frac{p-1}2! = \frac{4n}2! &= (2n)! \\
+&= 1 \cdot 2 \cdots 2n \\
+&= (1\cdot (n+1))\cdot (2\cdot(n+2)) \cdots (n\cdot(n+n))\\
+&= (-1\cdot -(n+1)) \cdot (-2\cdot -(n+2)) \cdots (-n\cdot-(n+n))\\
+&\equiv ((p-1)\cdot(p-(n+1)) \cdot ((p-2) \cdot (p-(n+2)) \cdots ((p-n) \cdot (p-(n+n))) \mod p \\
+&\equiv (p - 1) \cdot (p - 2) \cdots (p - n) \cdot (p-(n+1)) \cdot (p - (n+2)) \cdots (p-(n+n)) \mod p \\
+&\equiv (p-1) \cdot (p-2) \cdots (p-2n) \mod p \\
+&\equiv (4n) \cdot (4n-1) \cdots (2n+1) \mod (p = 4n+1) \\
+&\equiv \frac{(4n)!}{(2n)!} \mod p \\
+\therefore \left(\frac{p-1}2!\right)^2 &\equiv (2n)! \cdot \frac{(4n)!}{(2n)!} \mod p \\
+&\equiv (4n)! \mod p \\
+&\equiv (p-1)! \mod p \\
+\end{align*}
+
+Now by wilson's theorem we may state that if $p$ is prime with $p = 4n+1$ then $\frac{p-1}2! \equiv -1 \mod p$
+
+\subsubsection{Question 43}
+
+Let $G$ be an abelian group with order $n$ and elements $a_1,a_2,\ldots,a_n$ and let $x = a_1a_2\cdots a_n$.
+
+\question{(a)} Suppose $G$ has exactly one element $b \not = e$ such that $b^2 = e$.
+Then it follows that for all elements $g \in G$ with $g \not = b$ and $g \not = e$ we have $g\not=g^{-1}$.
+This means that every element except $b$ and $e$ has it's inverse in the product that gives us $x$ so this reduces to $x = bee^{\frac{n-1}2} = b$.
+
+\question{(b)} Consider the $B = \setbuilder{b \in G}{b^2 = e} \subset G$.
+$B$ is a subgroup of $G$ as for any $a,b \in B$, $(ab)^2 = a^2b^2 = e$ and for any $a \in B$, $a = a^{-1}$.
+Now for our problem we suppose that $\card{B} > 2$ and as this is the case we may take some element $b_1 \in B$ and we get a cyclic subgroup $B_1 = \set{{b_1}^0,{b_1}^1} \subset B$.
+Now if $B_1 \not = B$ then there exists some $b_2 \in B\setminus B_1$ and this generates $B_2 = \set{{b_2}^0,{b_2}^1}$ and it follows that $B_1B_2 = \setbuilder{{b_1}^{i_1}{b_2}^{i_2}}{\All{k\in\set{1,2}}{i_k \in \set{0,1}}}$.
+Now by some sort of induction we will find that $B = B_1B_2\cdots B_k$ where $B_i = \set{e, b_i}$ and $b_i \not\in B_1B_2\cdots B_{i-1}$ This means that for all $b \in B$, $b = \prodfrom{r = 1}{k}{{b_r}^{i_r}}$ with $i_r \in \set{0,1}$ for all $r$ and for all $(i_1,i_2,\ldots, i_k)$ with $i_r \in \set{0,1}$, we get a unique $\prodfrom{r=1}{k}{{b_r}^{i_r}} \in B$.
+That is to say that $f:\set{0,1}^k \to B$ defined as $f(r) = \prodfrom{r=1}{k}{{b_r}^{i_r}}$ is 1-1 and onto.
+This means that if we take the product of all these elements we get
+\begin{align*}
+\prodacross{b \in B}b &= \prodacross{i \in \set{0,1}^k}{\left[\prodfrom{r=1}{k}{{b_r}^{i_r}}\right]} \\
+&= \prodfrom{r = 1}{k}{\left[\prodacross{i \in \set{0,1}^k}{{b_r}^{i_r}}\right]}\\
+&= \prodfrom{r = 1}{k}{\left[\left({b_r}^0\right)^{2^{k-1}}\left({b_r}^1\right)^{2^{k-1}}\right]} \\
+&= \prodfrom{r = 1}{k}{{b_r}^{2^{k-1}}}
+\end{align*}
+
+If $k=1$ we get the result from part (a) where $B = \set{b_1,e}$ and our product simplifies to just $b_1$.
+If $k > 1$ then we get ${b_r}^{2^{k-1}} = \left({b_r}^2\right)^{2^{k-2}} = e^{2^{k-2}}$.
+Now for any $G$ we would have $x = \prodacross{b\in B}{b}$ where $B = \setbuilder{g\in G}{g^2 = e}$ as all other elements will be paired up with inverses and cancel out.
+So if there is more than one element in $B$ then we get $x = \prodacross{b\in B}{b} = e$.
+
+\question{(c)} If $n$ is odd we get that there can be no subgroup of $G$ with order two, so if there is any element $b\in G$ such that $b = b^{-1}$ we would get the cyclic group $B$ formed by $b$ would be of order two as $b^2 = e$.
+This means that if $n$ is odd all elements in $G$ have an inverse that is not themselves, unless that element is $e$ itself so we end with $x = e$ after everything has canceled out.
+
+\subsection{Section 5}
+\subsubsection{Question 3}
+
+Let $L_a: G\to G$ be defined as $L_a(x) = xa^{-1}$.
+\question{(a)} Show that $L_a \in A(G)$, this is equivalent to showing that $L_a$ is 1-1 as we already know $L_a:G\to G$.
+
+Let $b,c \in G$ and if $L_a(b)=L_a(b)$ then $ba^{-1} = ca^{-1}$ and it follows by cancellation that $b=c$, therefore $L_a$ is 1-1 and $L_a\in A(G)$
+
+\question{(b)} Show that $L_aL_b = L_aL_b$
+
+Let $a,b,x\in G$. It follows that
+\begin{align*}
+L_aL_b(x) &= L_a(L_b(x)) \\
+&= L_a(xb^{-1})\\
+&=xb^{-1}a^{-1}\\
+&=x(ab)^{-1}\\
+&=L_{ab}(x)
+\end{align*}
+therefore $L_aL_b = L_{ab}$
+
+\question{(c)} Let $\psi:G\to A(G)$ be defined as $\psi(a) = L_a$. Show that $\psi$ is a monomorphism.
+
+\begin{proof}
+	We know $\psi$ is a homomorphism as if $a,b\in G$ then $\psi(a)\psi(b) = L_aL_b = L_{ab} = \psi(ab)$.
+
+	To show $\psi$ is 1-1 let $a,b\in G$ such that $\psi(a) = \psi(b)$, we then get $L_a=L_b$. If we choose $x\in G$ then
+	\begin{align*}
+	L_a(x) &= L_b(x) \\
+	\therefore xa^{-1}&=xb^{-1} \\
+	\therefore a^{-1}&=b^{-1} \\
+	\therefore a&=b
+	\end{align*}
+	so we may conclude that $\psi$ is 1-1 and thus a monomorphism.
+\end{proof}
+
+\subsubsection{Question 17}
+
+We already know that the intersection of subgroups is a group so we simply need show that $M\inter N$ is normal if $M$ and $N$ are normal subgroups of $G$.
+This means we need to show that for all $x\in M\inter N$ and for all $g \in G$, $g^{-1}xg \in M\inter N$.
+Let us start by choosing an arbitrary $x \in M\inter N$ and $g\in G$ We find that $g^{-1}xg \in M$ by the fact that $M$ is normal and $x \in M$ and the same argument goes for $g^{-1}xg \in N$ so $g^{-1}xg \in M\inter N$ and therefore $M\inter N\normsubgroup G$.
+
+\subsubsection{Question 18}
+
+Let $H$ be a subgroup of $G$ and $N = \interacross{a\in G}{a^{-1}Ha}$. We will show that $N\normsubgroup G$.
+
+Let $n\in N$, by definition on $N$ we have $\All{a\in G}{\Exists{h\in H}{\left(a^{-1}ha = n\right)}}$.
+Now if we choose $g\in G$ and we find that if we choose $a \in H\subset G$ then there exists $h \in H$ such that $n = a^{-1}ha \in H$ and therefore $g^{-1}ng \in N$.
+We now can conclude that for all $g \in G$, $g^{-1}Ng \subset N$ and therefore $N\normsubgroup G$.
+
+\subsubsection{Question 19}
+
+\question{(a)} First let us show $H\subset N(H)$.
+Let $h \in H$ and $\ell \in H$ then $h^{-1}\ell h \in H$ and therefore $h^{-1}Hh\subset H$.
+If $\ell \in h^{-1}Hh$ then there is $k \in H$ such that $\ell=h^{-1}Kh \in H$ and therefore $h^{-1}Hh \subset H$.
+It follows that $h^{-1}Hh = H$ and thus $H \subset N(H)$.
+
+Now let us show that $N(H)$ is a subgroup of $G$.
+If $n \in N(H)$ then $n \in a^{-1}Ha$ for all $a \in G$.
+This implies there is some $h \in H$ such that $n = a^{-1}ha$ and therefore $n^{-1} = \left(a^{-1}ha\right)^{-1} = a^{-1}h^{-1}a$.
+We then know that for all $n \in N(H)$, $n^{-1}\in N(H)$.
+If $n,m\in N(H)$ then for any $a\in G$ there is some $h,k\in H$ such that $n = a^{-1}ha$ and $m = a^{-1}ka$ and therefore $nm = a^{-1}haa^{-1}ka = a^{-1}hka$ and as $hk\in H$ then $nm \in N(H)$ so $N(H)$ must be a subgroup of $G$.
+
+\question{(b)} Let us choose an arbitrary $x \in N(H)$, therefore we get $x^{-1}Hx = H$. It follows by definition that $H\normsubgroup N$.
+
+\question{(c)} Let $K$ be a subgroup of $G$ such that $H\normsubgroup K$. If we choose $k \in K$ then we get $k^{-1}Hk = H$ and thus $k \in N(H)$. It follows that $K \subset N(H)$.
+
+\subsubsection{Question 24}
+
+For notation we will adopt the practice that if $x \in A\cross B$ then $x = \pair{x_1}{x_2}$ with $x_1 \in A$ and $x_2 \in B$.
+
+\question{(a)}
+Let $a,b \in G = G_1\cross G_2$, therefore $ab = \pair{a_1}{a_2}\pair{b_1}{b_2} = \pair{a_1b_1}{a_2b_2}$ and as $a_1b_1 \in G_1$ and $a_2b_2 \in G_2$ we get $ab \in G$, so $G$ has closure.
+
+Let $a,b,c\in G$, we find
+\begin{align*}
+(ab)c &= \left(\pair{a_1}{a_2}\pair{b_1}{b_2}\right)\pair{c_1}{c_2} \\
+&= \pair{a_1b_1}{a_2b_2}\pair{c_1}{c_2} \\
+&= \pair{a_1b_1c_1}{a_2b_2c_2} \\
+a(bc) &= \pair{a_1}{a_2}\left(\pair{b_1}{b_2}\pair{c_1}{c_2}\right) \\
+&= \pair{a_1}{a_2}\pair{b_1c_1}{b_2c_2} \\
+&= \pair {a_1b_1c_1}{a_2b_2c_2} \\
+\therefore (ab)c &= a(bc)
+\end{align*}
+so we have associativity.
+
+Consider $\pair{e_1}{e_2}$ where $e_1$ is the identity of $G_1$ and $e_2$ is the identity of $G_2$. Choose $a\in G$ and we find
+\begin{align*}
+a\pair{e_1}{e_2} &= \pair{a_1}{a_2}\pair{e_1}{e_2} \\
+&= \pair{a_1e_1}{a_2e_2} \\
+&= \pair{a_1}{a_2} \\
+&= a \\
+\pair{e_1}{e_2}a &= \pair{e_1}{e_2}\pair{a_1}{a_2} \\
+&= \pair{e_1a_1}{e_2a_2} \\
+&= \pair{a_1}{a_2} \\
+&= a \\
+\end{align*}
+therefore we have an identity $e = \pair{e_1}{e_2}$.
+
+Let $a \in G$.
+We find that $a\pair{{a_1}^{-1}}{{a_2}^{-1}} = \pair{a_1{a_1}^{-1}}{a_2{a_2}^{-1}} = \pair{e_1}{e_2} = e$ and $\pair{{a_1}^{-1}}{{a_2}^{-1}}a = \pair{{a_1}^{-1}a_1}{{a_2}^{-1}a_2} = \pair{e_1}{e_2} = e$ and therefore we have inverses with $a^{-1} = \pair{{a_1}^{-1}}{{a_2}^{-1}}$.
+
+\question{(b)} Let $x,y\in G_1$. We get $\varphi_1(x)\varphi_1(y) = \pair x{e_2}\pair y{e_2} = \pair{xy}{e_2} = \varphi_1(xy)$, so $\varphi_1$ is a homomorphism.
+
+Let $x,y \in G_1$ such that $\varphi_1(x) = \varphi_1(y)$. It follows that $\pair{x}{e_2} = \pair{y}{e_2}$ and thus $x=y$, so $\varphi_1$ is a monomorphism.
+
+\question{(c)} Let us define $\varphi_2:G_2\to G$ as $\varphi_2(x) = \pair{e_1}x$.
+Now we can make the exact same argument to show $\varphi_2$ is a monomorphism as we did for $\varphi_1$ and thus $\varphi_2$ is a monomorphism by symmetry.
+
+\question{(d)} It is trivial that $\varphi_1(G_1)\varphi_2(G_2) \subset G$ as $G$ is the co-domain of both $\varphi_1$ and $\varphi_2$ and additionally $G$ is closed.
+
+Choose $g \in G$, therefore $g = \pair{g_1}{g_2}$ with $g_1 \in G_1$ and $g_2 \in G_2$.
+It follows that $\pair{g_1}{g_2} = \pair{g_1e_1}{e_2g_2} = \pair{g_1}{e_2}\pair{e_1}{g_2} = \varphi_1(g_1)\varphi_2(g_2)$ and thus $G \subset \varphi_1(G_1)\varphi_2(G_2)$ so $G=\varphi_1(G_1)\varphi_2(G_2)$.
+
+Now consider $\pair{g_1}{g_2}\in\varphi_1(G_1)\inter\varphi_2(G_2)$.
+Now for all $x \in G_1$, $\varphi_1(x) = \pair{x}{e_2}$ and thus $g_2 = e_2$.
+For all $x \in G_2$, $\varphi_2(x) = \pair{e_1}{x}$ and thus $g_1 = e_1$ so we have $\pair{g_1}{g_2} = e$ for all $\pair{g_1}{g_2} \in \varphi_1(G_1)\inter\varphi_2(G_2)$.
+It follows that $\set e = \varphi_1(G_1)\inter\varphi_2(G_2)$.
+
+\question{(e)} Let us define $f: G_1\cross G2 \to G_2\cross G_1$ as $f(g) = f(\pair{g_1}{g_2}) = \pair{g_2}{g_1}$.
+We know $G_1\cross G_2$ is a group and by symmetry $G_2\cross G_1$ must also be a group.
+Now if we choose $a,b \in G_1\cross G_2$ then we get
+\begin{align*}
+f(a)f(b) &= f(\pair{a_1}{a_2})f(\pair{b_1}{b_2}) \\
+&= \pair{a_2}{a_1}\pair{b_2}{b_1} \\
+&= \pair{a_2b_2}{a_1b_1} \\
+&= f(\pair{a_1b_1}{a_2b_2}) \\
+&= f(ab)
+\end{align*}
+so $f$ is a homomorphism, however we may go a step further as if $f(a) = f(b)$ then we get $f(\pair{a_1}{a_2}) = f(\pair{b_1}{b_2})$.
+By definition of $f$ we get $\pair{a_2}{a_1} = \pair{b_2}{b_1}$ and therefore we get $a_2 = b_2$ and $a_1 = b_1$ so it must be that $a = b$ yielding $f$ to be a monomorphism.
+Now we cay say $G_1\cross G_2 \simeq G_2\cross G_1$.
+
+\subsubsection{Question 26}
+\question{(a)} Let $a,b,x \in G$ then
+\begin{align*}
+\sigma_a\sigma_b(x) &= \sigma_a(\sigma_b(x)) \\
+&= \sigma_a\left(bxb^{-1}\right) \\
+&= abxb^{-1}a^{-1} \\
+&= (ab)x(ba)^{-1} \\
+&= \sigma_{ab}(x)
+\end{align*} so it follows that $\psi(a)\psi(b) = \sigma_a\sigma_b = \sigma_{ab} = \psi(ab)$ so $\psi$ is a homomorphism.
+
+Now let us show that $\ker(\psi) = Z(G)$.
+
+First  let $x \in Z(G)$, and $a,y \in G$. We then get 
+\begin{align*}
+\sigma_y\sigma_x(a) &= yxax^{-1}y^{-1}\\
+& = yaxx^{-1}y^{-1}\\
+& = yay^{-1}\\
+& = \sigma_y(a)
+\end{align*}
+and therefore $\psi(y)\psi(x) = \psi(y)$, thus $x\in\ker(\psi)$ and $Z(G) \subset \ker(\psi)$.
+
+Now let $a \in \ker(\psi)$ It follows then that $\psi(a)\psi(e) = \psi(e)$.
+Therefore if we choose $x \in G$ we get $\sigma_a\sigma_e(x) = aexe^{-1}a^{-1} = exe^{-1} = \psi(e)$.
+If we simplify somewhat we get $axa^{-1} = x$ and therefore $ax=xa$.
+This implies $x \in Z(G)$ and thus $\ker(\psi) \subset Z(G)$.
+
+We are now finished with $Z(G) = \ker(\psi)$.
+\subsubsection{Question 29}
+\question{(a)}
+Let $m \in M$ and we must show that for all $a \in G$, $a^{-1}ma\in M$.
+
+We have $T_a(x) = a^{-1}xa$ is an automorphism as 
+\begin{align*}
+T_a(x)T_a(y) &= a^{-1}xaa^{-1}ya \\
+&= a^{-1}xya 
+&= T_a(xy)
+\end{align*}
+and if $T_a(x) = T_a(y)$ then $a^{-1}xa = a^{-1}ya$ and thus $x=y$ and for all $x \in G$ $T_a(axa^{-1})=a^{-1}axa^{-1}a=x$.
+
+It follows that if $m \in M$ then $a^{-1}ma = T_a(m) \in M$ by definition of $M$ and thus $M\normsubgroup G$.
+
+\question{(b)} If $a \in MN$ then $mn = a$ for some $m \in M$ and $n \in N$.
+Therefore for any automorphism $\varphi$ we have $\varphi(a) = \varphi(mn) = \varphi(m)\varphi(n)$ and we know $\varphi(m) \in M$ and $\varphi(n)\in N$ so $\varphi(a)=\varphi(m)\varphi(n) \in MN$.
+Thus $MN$ is a characteristic subgroup of $G$.
+
+\question{(c)} Let $A$ be a group.
+We already have shown then that $A\cross A = A^2$ is a group when $\pair ab\pair xy = \pair{ax}{by}$.
+We also get that $A\cross\set e$ is a subgroup of $A^2$ as for $\pair ae\in A\cross\set e$, and $\pair be \in A\cross\set e$, we have $\pair ae\pair be = \pair{ab}e\in A\cross\set e$ and $\pair{a^{-1}}e\pair ae = \pair ee$.
+Additionally $A$ is normal as for any $a =\pair xy\in G$ and $b = \pair ze\in A\cross\set e$ we have $a^{-1}ba = \pair{x^{-1}}{y^{-1}}\pair ze\pair xy = \pair{x^{-1}zx}{y^{-1}ey} = \pair{x^{-1}zx}{e} \in A\cross\set e$.
+However $A\cross\set e$ is not a characteristic subgroup of $A^2$ as for $\phi:A^2\to A^2$ defined as $\phi(\pair ab) = \pair ba$ we get $\phi(\pair ae) = \pair ea$ and if $A\not=\set e$ then there exists some $a$ for which $\pair ea \not \in A \cross \set e$.
+
+\subsubsection{Question 38}
+\question{(a)}
+Let $a,b \in G $ and $q \in S$ therefore there is some $x \in G$ such that $q = Hx$
+\begin{align*}
+T_aT_b(q) &= T_aT_b(Hx) \\
+&= T_a(T_b(Hx))\\
+&= T_a(Hxb) \\
+&= Hxba \\
+&= T_{ba}(Hx) \\
+&= T_{ba}(q)
+\end{align*}
+So $T_aT_b = T_{ab}$, so if we define $\psi: G\to A(S)$ as $\psi(x) = T_x$ then we get a homomorphism.
+
+\question{(b)} If $x \in \ker(\psi)$ we get $\psi(b) = \psi(ba)$ for all $b\in G$.
+It follows that $T_b(Hx)=T_{ba}(Hx)$ for all $x\in G$.
+We then get $Hxb = Hxba$ and therefore $T_{a}(Hxb) = Hxb$ for all $x,b$ so $T_a$ is the identity if $a \in \ker(\psi)$.
+We also get the converse as if $T_a(Hx) = Hx = T_e(Hx)$ then $\psi(a) = \psi(e)$.
+
+Further then that we may state that if $x \in \ker(\psi)$ then we get $T_x(Ha) = Ha$ as $T_x$ for all $a\in G$ as is the identity.
+It follows that $Hax = Ha$ and therefore $Haxa^{-1} = H$.
+Thus for any $h \in H$ there is $\bar h \in H$ such that $haxa^{-1} = \bar h$ and thus $axa^{-1}=h^{-1}\bar h \in H$.
+This also implies that $x \in a^{-1}Ha$ for all $a \in G$ and thus $\ker(\psi) \subset \interacross{a\in G}{a^{-1}Ha}$.
+Now if $x \in \interacross{a \in G}{a^{-1}Ha}$ then $x \in a^{-1}Ha$ for all $a \in G$ and therefore $axa^{-1} \in H$.
+We now can say that $Haxa^{-1} = H$ and thus $Hax = Ha$ so $T_x(Ha) = Ha$ for any $ a\in G$.
+This means that $T_x$ is the identity and thus $x \in \ker(\psi)$ and we can finish by stating $\ker(\psi) = \interacross{a \in G}{a^{-1}Ha}$
+
+\question{(c)} We know $\ker(\psi) = \interacross{a \in G}{a^{-1}Ha} \subset e^{-1}He = H$ so $\ker(\psi)$ is obviously a subset of $H$.
+We also know $\ker(\psi) \normsubgroup G$ as it is the kernel of a homomorphism.
+Now if there is a $K$ such that $K \normsubgroup G$ and $K\subset H$ then for all $k \in K$ and $g \in G$ we have $gkg^{-1} \in K$.
+It then follows that $gkg^{-1} \in H$, so $k \in g^{-1}Hg$ so $k \in\ker(\psi)$.
+
+\subsubsection{Question 42}
+
+As we did in the last problem let us define $S =\setbuilder{Ha}{a \in G}$ and $T_a:S\to S$ as $T_a(Hx) = Hxa$. We may also define $\psi:G\to A(S)$ as $\psi(a) = T_a$.
+
+Now first we need to show that $\card S = 4$.
+We know this as we may define $a\sim b$ if $Ha = Hb$.
+This is nearly trivially an equivalence relation so I won't bother showing that however we will find that $\eqclass{a} = \setbuilder{ha}{h\in G}$.
+The proof is as follows: Consider $x \in \eqclass{a}$, it then follows that $Hx = Ha$ so if we choose $h \in H$ then there is some $\bar h \in H$ such that $ha = \bar hx$ and therefore $a = (h^{-1}\bar h)x \in \setbuilder{ha}{h \in H}$.
+Consider $x \in \setbuilder{ha}{h \in H}$, therefore $x = ha$ for some $h\in H$ and thus $Hx = Hha = Ha$ so $x \sim a$.
+This means that for each $x \in G$, $\card{\eqclass{x}} = \card H = 9$, so there must be $4$ equivalence classes and as each equivalence class corresponds to a co-set of $H$ we get 4 co-sets of $H$.
+
+Now as $\card{S} = 4$ then it follows that $\card{A(S)} = 4!$. Now we need a lemma
+
+\begin{lemma}
+	Let $f:A\to B$ be a homomorphism. If $\ker(f) = (e)$ then $f$ is a monomorphism.
+\end{lemma}
+\begin{proof}
+	Suppose $f$ is not 1-1, therefore there is some $a\not=b \in A$ such that $f(a) = f(b)$.
+It follows then that $f(ab^{-1}) = f(a)f(b^{-1}) = f(b)f(b^{-1}) = f(bb^{-1}) = f(e)$ so $ab^{-1}\not=e$ is in $\ker(f)$.
+Therefore by contrapositive we get if $\ker(f) = (e)$ then $f$ is 1-1.
+\end{proof}
+
+We know our function $\psi$ is not a monomorphism as $\card G > \card{A(S)}$.
+This means that $\ker(\psi) \not= (e)$.
+Now the last thing we need to show is $\ker(\psi) \subset H$.
+We can show this by considering $x \in G \setminus H$ and we find that in order for $x\in \ker(\psi)$ we would expect $\psi(x)\psi(y) = \psi(y)$ for all $y\in G$ which therefore means $T_yT_x(Ha) = T_y(Ha)$ for all $a \in G$.
+Consider $a = e$ and we get $Hexe = Hee$ so $Hx = H$ and this would mean $x \in H$ contradicting our previous statement.
+So as we know $\ker(\psi) \subset H$ and $\ker(\psi) \not= (e)$ and we already know that the kernel of a homomorphism is a normal subgroup, so as it is contained in $H$ which is of order 9, then this subgroup must be of order 3 or 9.
+This concludes our proof that either $H\normsubgroup G$ or there is $N \subset H$ with $\card N = 3$ such that $N \normsubgroup G$.
+
+\subsection{Section 6}
+\subsubsection{Question 11}
+\subsubsection{Question 12}
+\subsubsection{Question 13}
+\subsubsection{Question 18}
+
+\subsection{Section 7}
 \subsubsection{Question 4}
 \subsubsection{Question 5}
+\subsubsection{Question 7}
+
+\subsection{Section 8}
+\subsubsection{Question 4}
+\subsubsection{Question 6}
+\subsubsection{Question 7}
+\subsubsection{Question 8}
 \subsubsection{Question 11}
-\subsubsection{Question 22}
-\subsubsection{Question 24}
-\subsubsection{Question 26}
-\subsubsection{Question 28}
-\subsubsection{Question 29}
-
-\subsection{Section 4}
+\subsubsection{Question 12}
+
+\subsection{Section 9}
 \subsubsection{Question 1}
-\subsubsection{Question 5}
-\subsubsection{Question 18}
-\subsubsection{Question 24}
-\subsubsection{Question 30}
-\subsubsection{Question 35}
-\subsubsection{Question 37}
-\subsubsection{Question 38}
-\subsubsection{Question 42}
-\subsubsection{Question 43}
-
-\subsection{Section 5}
+\subsubsection{Question 2}
 \subsubsection{Question 3}
-\subsubsection{Question 17}
-\subsubsection{Question 18}
-\subsubsection{Question 19}
-\subsubsection{Question 24}
-\subsubsection{Question 26}
-\subsubsection{Question 29}
-\subsubsection{Question 38}
-\subsubsection{Question 42}
 

### 2018-06-15 Algebra/Homework/Homework.tex
Hi

@@
 \subsubsection{Question 11}
+Suppose $G$ is a group and let $Z(G) = Z$.
+It is trivial to show that $Z \normsubgroup G$ so suppose further that $G/Z$ is cyclic.
+As $G/Z$ is cyclic it has some primitive element, $\eqclass g$.
+Now for any $x,y \in G$ we have $x \in Zg^n$ and $y \in Zg^m$ for some $n,m\in\mathbb N$ as all elements are in some coset of $Z$.
+We also have then that for some $z,w \in Z$ there is $x = zg^n$ and $y = wg^m$.
+We now do some manipulation
+\begin{align*}
+xy &= zg^nwg^m \\
+&= zwg^ng^m \\
+&= wzg^mg^n \\
+&= wg^mzg^n \\
+&= yz
+\end{align*}
+and we find $G$ is abelian. This means $Z = Z(G) = G$ so $G/Z = (e)$.
+
 \subsubsection{Question 12}
+If $G/N$ is abelian then we get $Nab = Nba$.
+This means there is some $n,m \in N$ such that $nab = mba$, and it follows that $(nab)^{-1} = (mba)^{-1} = a^{-1}b^{-1}m^{-1}$.
+We now get that $e = nab(nab)^{-1} = naba^{-1}b^{-1}m^{-1}$ so $n^{-1}m = aba^{-1}b^{-1}$.
+It follows from $N$ being a subgroup of $G$ that $aba^{-1}b^{-1} \in N$.
+
 \subsubsection{Question 13}
+Let $a,b\in G$.
+We get $aba^{-1}b^{-1}\in N$, and therefore $\eqclass e = \eqclass{aba^{-1}b^{-1}} = \eqclass{ab}\eqclass{a^{-1}b^{-1}}$.
+It follows then that $\eqclass{ab} = \eqclass{a^{-1}b^{-1}}^{-1} = \eqclass{\left(a^{-1}b^{-1}\right)^{-1}} = \eqclass{ba}$ so $G / N$ is abelian.
+
 \subsubsection{Question 18}
+Choose $a,b\in T$ then $a^n = e$ and $b^m = e$ and therefore $(ab)^{nm} = a^{nm}b^{nm} = e$ so $ab \in T$.
+Choose $a \in T$ and we get $a^n = e$ so $a^{n-1}a = e$ and thus $a^{n-1} = a^{-1} \in T$.
+We have now shown that $T$ is a subgroup of $G$.
+
+Now for any $\eqclass{a}\in G/T$ if $\eqclass{a}^n = \eqclass{e}$ for some $n > 0$ then we would get $Ta^n = T$ and further for some $u,v\in T$, $va^n = u$.
+Now we if we let $t =v^{-1}u$ then we get $a^n = t \in T$.
+By definition of $T$ we get $t^m = e$ for some $m > 1$ and thus $\left(a^n\right)^m = a^{nm} = e$ so $a \in T$.
+It follows then that $\eqclass{a} = \eqclass{e}$, so only the identity has a finite order in $G/T$.
 
@@
 \subsubsection{Question 4}
+We know that the kernel of a homomorphism is a normal subgroup, so let us construct $\varphi:G\to G_2$ as $\varphi(a,b) = b$.
+$\varphi$ is a homomorphism as $\varphi(a,b)\varphi(c,d) = ac = \varphi(ac,bd)$.
+Now we will show $\ker(\varphi) = \setbuilder{\pair{e_1}x}{x \in G_2}$.
+
 \subsubsection{Question 5}

### 2018-06-30 Algebra/Homework/Homework.tex
algebrah complet

@@
 \documentclass{article}
-
 \input{../../definitions.tex}
@@
 
-This may be displayed pictorially as follows:
+The pictures I will hand into you separately.
+
+%This may be displayed pictorially as follows:
 
@@
 
-\def\secondcircle{(210:0.95cm) circle (1.5cm)}
-\def\thirdcircle{(330:0.95cm) circle (1.5cm)}
-\begin{tikzpicture}
-	\begin{scope}
-		\clip \secondcircle;
-		\fill[cyan] \thirdcircle;
-	\end{scope}
-	\draw \secondcircle node [text=black,below left] {$A$};
-	\draw \thirdcircle node [text=black,below right] {$B$};
-\end{tikzpicture}
+%\def\secondcircle{(210:0.95cm) circle (1.5cm)}
+%\def\thirdcircle{(330:0.95cm) circle (1.5cm)}
+%\begin{tikzpicture}
+%	\begin{scope}
+%		\clip \secondcircle;
+%		\fill[cyan] \thirdcircle;
+%	\end{scope}
+%	\draw \secondcircle node [text=black,below left] {$A$};
+%	\draw \thirdcircle node [text=black,below right] {$B$};
+%\end{tikzpicture}
 
@@
 This concludes our proof that either $H\normsubgroup G$ or there is $N \subset H$ with $\card N = 3$ such that $N \normsubgroup G$.
-
+%
 \subsection{Section 6}
@@
 \subsubsection{Question 4}
-We know that the kernel of a homomorphism is a normal subgroup, so let us construct $\varphi:G\to G_2$ as $\varphi(a,b) = b$.
-$\varphi$ is a homomorphism as $\varphi(a,b)\varphi(c,d) = ac = \varphi(ac,bd)$.
-Now we will show $\ker(\varphi) = \setbuilder{\pair{e_1}x}{x \in G_2}$.
+\question{(a)}
+We know that the kernel of a homomorphism is a normal subgroup, so let us construct $\pi_2:G\to G_2$ as $\pi_2(a,b) = b$. $\pi_2$ is a homomorphism as $\pi_2(a,b)\pi_2(c,d) = ac = \pi_2(ac,bd)$.
+
+Now we will show $\ker(\pi_2) = N$.
+First let $\pair x{e_2} \in N$ and $\pair ab \in G$ and therefore $\pi_2(a,b)\pi_2(x,e_2) = be_2 = b = \pi_2(a,b)$ so $N \subset \ker(\pi_2)$.
+Now let $\pair xy\in\ker(\pi_2)$ and we get $\pi_2(x,y)\pi_2(a,b) = \pi_2(a,b)$ for $\pair ab \in G$.
+It follows then that $yb = b$ and therefore $y=e_2$ so $\ker(\pi_2) = N$.
+
+\question{(b)}
+Let $\pi_1:N\to G_1$ be defined as $\pi_1(a,{e_2}) = a$.
+We find that $\pi_1(a,e_2)\pi_1(b,e_2) = ab = \pi_1(ab,e_2)$ so it a homomorphism.
+If $\pi_1(a,e_2) = \pi_1(b,e_2)$ then $a =b$ so $\pi_1$ is a monomorphism.
+If $a \in G_1$ then $\pi_1(a, e_2) = a$ so $\pi_1$ is a isomorphism and thus $N \simeq G_1$.
+
+\question{(c)}
+Now let us define $\psi:G/N \to G_2$ as $\psi(N\pair ab) = b$.
+First we must show that this is a well defined function.
+Consider $N\pair ab = N\pair cd$, then it follows that $\pair ab = \pair n{e_2}\pair cd$.
+We get from this $b = e_2d = d$ so $\psi(N\pair ab) = b = d = \psi(N\pair cd)$.
+Before we show  We get for any $\pair ab, \pair cd \in G$,  $\psi(N\pair ab)\psi(N\pair cd) = bd = \psi(N\pair ab\pair cd)$ and therefore $\psi$ is a homomorphism.
+If $\psi(N\pair ab) = \psi(N\pair cd)$ then we get $b = d$.
+Now if $\pair xy \in N\pair ab$ then $x = na$ and $y = b$ for some $n \in G_1$, and thus $\pair xy \in N\pair cd$ as $x = na = nac^{-1}c$ and $b = d = ed$.
+This shows that $N\pair ab \subset N\pair cd$ and we get $N\pair cd \subset N\pair ab$ by symmetry so we conclude that if $\psi(N\pair ab)=\psi(N \pair cd)$ then $N\pair ab = N\pair cd$ so $\psi$ is a monomorphism.
+For any $g \in G_2$ I may construct $\pair ag$ with $a \in G_1$ and find that $\psi(N\pair ag) = g$ so $\psi$ is a isomorphism and thus $G_2 \simeq G/N$.
+
+%Now consider the set $N\pair abN$, where $\pair ab \in G$.
+We find that for any $\pair nm \in N \pair ab N$, $n = n_1an_2$ and $m=e_2be_2 = b$ therefore as $\pair {n_1an_2}{b} \in N\pair ab$ due to $\pair{n_1an_2a^{-1}}{e_2} \in N$ we have $N\pair ab N \subset N\pair ab$.
+$N\pair ab \subset N\pair abN$ is trivial as $e\in N$ so $N\pair abe = N\pair ab \subset N\pair ab N$ and thus we get $N\pair abN = N\pair ab$ for any $\pair ab \in G$.
 
 \subsubsection{Question 5}
+
+\question{(a)} We know that $H\inter N$ is a subgroup of $H$ as intersections form subgroups.
+Now consider $x \in H\inter N$ and $h \in H$.
+We wish to show that $h^{-1}xh \in H\inter N$.
+We know that $h^{-1}xh \in N$ as $N \normsubgroup G$, and as $h\in H$ and $n \in H$ we get $h^{-1}xh \in H$ so $h^{-1}xh \in H \inter N$ and thus $N\inter H \normsubgroup H$.
+
+\question{(b)} For $x,y \in HN$ we get $x=h_1n_1$ and $y = h_2n_2$ for some $h_1,h_2 \in H$ and $n_1,n_2 \in N$, so $xy = h_1n_1h_2n_2$.
+Now $N\normsubgroup G$ so for some $\bar n \in N$ we get $h_1h_2\bar n{h_2}^{-1}h_2n_2 = h_1h_2\bar nn_2 \in HN$.
+For $hn \in HN$ we also have $(hn)^{-1} = n^{-1}h^{-1} = h^{-1}\bar nhh^{-1} = h^{-1}\bar n$ for some $\bar n \in N$.
+Therefore $HN$ is a subgroup of $G$.
+
+\question{(c)} For all $n \in N$, we have $n = en \in HN$ as $e \in H$, therefore $N \subset HN$.
+Now as $N\normsubgroup G$ and $HN$ is a subgroup of $G$ then $N\normsubgroup HN$ is implied by $N\normsubgroup G$.
+
+\question{(d)} Let us define $Q = H\inter N$.
+We find $H/Q = \setbuilder{hQ}{h\in H}$ and $HN/N = \setbuilder{hnN}{h \in H\land n \in N} = \setbuilder{hN}{h \in H}$.
+Now we define $\phi:HN/N \to H/Q$ as $\phi(hN) = hQ$.
+First to show that $\phi$ is a function let $qN = hN$ with $h,q \in H$.
+Now choose $qn \in \phi(qN) = qQ$.
+As $n \in Q$ this implies $n \in N$.
+As $qn \in qN = hN$ there is some $m \in N$ such that $hm = qn$.
+We then have $m = h^{-1}qn$ and as all $h,q,n \in H$ we get $m \in H$, and therefore $m \in Q$.
+It follows then that $qn = hm \in hQ$ and therefore $\phi(qN) = qQ \subset hQ = \phi(hN)$.
+By symmetry we may make the same argument that $\phi(qN)\supset \phi(hN)$ and therefore $\phi$ is well defined.
+
+If we take $hN, qN \in HN/N$ we find $\phi(hN)\phi(qN) = (hQ)(qQ) = hqQ = \phi(hqQ)$.
+If $\phi(hN) = \phi(qN)$ then we find $hQ = qQ$.
+Now take $hn \in hN$ and as $hQ = qQ$ then there is some $v \in Q$ so that $he = h = qv$ and therefore $hn = qvn = q(vn) \in qN$.
+By symmetry we also know that for any $qn \in qN$, $qn \in hN$ so $hN = qN$.
+Finally for any $hQ \in H/Q$ we know $hN \in HN/N$ so that $\phi(hN) = hQ$ and therefore $\phi$ is a isomorphism giving $HN/N \simeq H/Q$.
+
 \subsubsection{Question 7}
+Let $\varphi: G\to G'$ be a homomorphism and onto and let $N \normsubgroup G$.
+Choose $a' \in G'$, and $n' \in \varphi(N)$.
+It follows that for some $a\in G$ and some $n \in N$, $\varphi(a) = a'$ and $\varphi(n) = n'$.
+Now if $a'^{-1}n'a' \in \varphi(N)$ then $\varphi(N) \normsubgroup G$.
+\begin{align*}
+a'^{-1}n'a' &= \varphi(a)^{-1}\varphi(n)\varphi(a) \\
+&= \varphi(a^{-1})\varphi(n)\varphi(a) \\
+&= \varphi(a^{-1}na)
+\end{align*}
+We know $a^{-1}na \in N$ and therefore $a'^{-1}n'a' \in \varphi(N)$ so $\varphi(N)\normsubgroup G'$.
 
@@
 \subsubsection{Question 4}
+Let $a$ and $b$ be elements with order 7 and 3 respectively. It follows that $b^{-1}ab = a^i$ for some $0 \le i < 7$. We then have 
+\begin{align*}
+a &= eae\\
+& = b^{-3}ab^3\\
+& = b^{-2}a^ib^2\\
+&= b^{-1}a^{i^2}b \\
+&= a^{i^3}
+\end{align*}
+and therefore $i^3 \equiv 1 \mod 7$.
+If we let $i = 2$ we find that $2^3=8\equiv1\mod7$ and additionally this is consistent with Fermat's little theorem so $2^6 \equiv 1^2 \equiv 1 \mod 7$.
+We go ahead then and define $b^{-1}ab = a^2$ so $ab=ba^2$.
+Now consider
+\begin{align*}
+a^nb^m &= a^{n-1}ba^2b^{m-1} \\
+&= a^{n-k}ba^{2k}b^{m-1} \\
+&= ba^{2k}b^{m-1} \\
+&= b^2a^{4n}b^{m-2} \\
+&= b^\ell a^{2^\ell n}b^{m-\ell} \\
+&= b^ma^{2^mn}
+\end{align*}
+Now we can show that $G= \setbuilder{a^nb^m}{n\in\mathbb Z\land m\in\mathbb Z}$ is closed under this operation.
+\begin{align*}
+a^nb^ma^ob^p &= b^ma^{2^mn+o}b^p \\
+&= b^{m+p}a^{2^p\left(2^mn+o\right)} \in G
+\end{align*}
+This is a group as it obviously has an identity $a^0b^0$ and gets inverses from it's closure with $(a^nb^m)^{-1} =b^{-m}a^{-n}= a^0b^{-m}a^{-n}b^0 \in G$.
+Finally it's order is 21 as we may make the bijection $f(a^nb^m) = (n\mod 7,m\mod 3) \in \mathbb Z/7\cross \mathbb Z/3$.
+This is well defined due to the assumed order of $a$ and $b$ in $G$.
+It is 1-1 as if $f(a^nb^m)=f(a^ob^p)$ then $n\equiv o\mod 7$ and $m\equiv p \mod 7$ so it follows that $a^nb^m = a^ob^p$.
+Finally $f$ is onto as for any $(n,m) = f(a^nb^m)$.
+
 \subsubsection{Question 6}
+Consider $\card{AB}$.
+From a previous problem we showed that $\card{AB}=\frac{\card{A}\card{B}}{\card{A\inter B}}$.
+$AB \subset G$ so $\card{AB}\le\card G$.
+From this it follows that $\card{A\inter B}= \frac{\card A\card B}{\card{AB}} \ge \frac{\card A\card B}{\card G} > \frac{\card{\sqrt G}\card{\sqrt G}}{\card G} = 1$, so $A\inter B$ must have more than just the identity.
+
 \subsubsection{Question 7}
+We know that $A\inter B$ is a subgroup of both $A$ and $B$ so $\card{A\inter B}|A$ and $\card{A\inter B} | B$ by Lagrange's theorem, which in turn implies that $\card{A\inter B} = 1$ as $\card A$ relatively prime to $\card B$ and therefore $A\inter B = (e)$.
+We also know that $\card{AB} = \frac{\card A\card B}{\card{A\inter B}} = \card A\card B$.
+
 \subsubsection{Question 8}
+
+99 has prime divisors $3$ and $11$ so there is some element $a \in G$ with $o(a) = 3$ and $b\in G$ with $o(b) = 11$. It follows then that $o(ab) = 33$ so $(ab)$ is a subgroup of $G$ with order 33.
+
+Now we construct as $S=\setbuilder{(ab)x}{x\in G}$ and $T_x:S\to S$ as $T_x((ab)y) = (ab)yx$, which we note is in $A(S)$.
+Now we construct $\psi:G\to A(S)$ as $\psi(x) = T_x$.
+We get that $\psi$ is homomorphism from our work chapter 2, section 4, and additionally that $\abs S = \frac{\card G}{\card{(ab)}} = 3$.
+Now $\psi$ is not a monomorphism as it's domain is larger then it's co-domain.
+We then conclude that $\ker(\psi)$ must be a non-trivial subgroup of $G$ as $\ker(\psi) \not = (e)$ and kernels are always normal subgroups.
+
 \subsubsection{Question 11}
+
+Let us choose $a \in A$ and $b \in B$ then notice that for all $c \in A\inter B$ then $ac \in A$ and $c^{-1}b \in B$ and therefore $(ac)(c^{-1}b) = ab$.
+Therefore there are at least as many $(a,b)$ pairs such that $ab$ is equal as there are elements in $A \inter B$.
+Now assume there is some other $\bar a \in A$ and $\bar b \in B$ such that there is no $\bar c \in A\inter B$ such that $\bar a \bar c = a$ and ${\bar c}^{-1}\bar b = b$.
+If $\bar a\bar b = ab$ then $a^{-1}\bar a = b\bar b^{-1} \in A\inter B$.
+We will let $\bar c^{-1} = b\bar b^{-1}$ as we then get $\bar c^{-1}\bar b = b\bar b^{-1}\bar b = b$ we then will also find that $\bar c= \bar a^{-1}a$ and thus $\bar a\bar c = \bar a\bar a^{-1}a = a$.
+Finally we conclude that for any element $ab \in AB$, there exists exactly $\card{A \inter B}$ pairs $(\bar a,\bar b) \in A\cross B$ such that $ab = \bar a\bar b$.
+
 \subsubsection{Question 12}
+
+If $G$ is of order 21 then let $a,b \in G$ such that $o(a) = 7$ and $o(b) = 3$ we then know that $b^{-1}ab = a^{i}$ for some $i$ and from this we get $i^3 \equiv 1 \mod 7$.
+Well for $i^3 \equiv 1\mod 7$ we need either $i =1$, $i= 2$, or $i = 4$.
+If $i = 1$ then we get $b^{-1}ab = a$ so $ab = ba$ and $G$ is abelian.
+So either $i = 2$ or $i = 4$.
+Now consider $c = b^2$, $o(c) = 3$ as we get $(c) = \set{b^2,b^4=b^1,b^3 = e}$.
+In question 4 we found that $a^nb^m=b^ma^{2^m+n}$ and here we find it more generally is $a^nb^m=b^ma^{i^mn}$.
+If $i = 2$ and we get
+\begin{align*}
+a^nc^m &= a^nb^{2m} \\
+&= b^{2m}a^{2^{2m}n} \\
+&= b^{2m}a^{\left(2^2\right)^mn}\\
+&= c^ma^{4^mn}
+\end{align*}
+and therefore we find that even if we set $i = 2$ then we also have the group that we would get if $i=4$.
+This means the two must be isomorphic with the isomorphism $f(a^nb^m) = a^n\left(b^2\right)^m$.
 
@@
 \subsubsection{Question 1}
+Let $f:G_1\cross G_2 \to G_2\cross G_1$ be defined as $f(\pair{a}{b}) = \pair ba$. We have 
+\begin{align*}
+f(\pair ab)f(\pair cd) &= \pair ba\pair dc\\
+& = \pair {bd}{ac} \\
+&= f(\pair{ac}{bd}) \\
+&= f(\pair ab\pair cd)
+\end{align*}
+so $f$ is a homomorphism.
+We have if $f(\pair ab) = f(\pair cd)$ then $\pair ba = \pair dc$ so $a = c$ and $b = d$, therefore $\pair ab=\pair cd$, so $f$ is a monomorphism.
+For any $\pair ab\in G_2\cross G_1$ we have $f(\pair ba) = \pair ab$ and $\pair ba \in G_1\cross G_2$ by definition so we have $f$ is an isomorphism.
+Therefore $G_1\simeq G_2$.
+
 \subsubsection{Question 2}
+Suppose $G_1$ and $G_2$ are cyclic groups of order $m,n$ respectively.
+The group $G_1\cross G_2$ has order $mn$ and therefore to say that $G_1\cross G_2$ is cyclic is equivalent to saying there is some element $\pair ab \in G_1\cross G_2$ with order $mn$.
+Now for any $\pair ab\in G_1\cross G_2$ we get $\pair ab^{mn} = \pair{a^{mn}}{b^{mn}} = \pair ee = e$, so therefore in order of $G_1\cross G_2$ not to be cyclic we need to show that for all elements there is some $i < mn$ such that $\pair ab = e$.
+Well this $i$ needs to be such that $n|i$ so that $b^i = e$ and $m|i$ so that $a^i = e$, and $i | ab$ by Lagrange's theorem.
+This exists if and only if $(m,n) \not = 1$ otherwise stated if and only if $m$ and $n$ are not relatively prime.
+
 \subsubsection{Question 3}
 
+\question{(a)}
+Consider $f:G\to T$ as $f(a) = \pair aa$.
+We get $f(a)f(b) = \pair aa\pair bb = \pair{ab}{ab} = f(ab)$.
+If $f(a) = f(b)$ we get $\pair aa = \pair bb $and therefore $a=b$.
+Finally if $\pair aa \in T$ then $f(a) = \pair aa$ so we know $f$ to be an isomorphism.
+
+\question{(b)} First iff $G$ is abelian is $G\cross G$ abelian.
+\begin{proof}
+	Let $G$ be abelian.
+It follows then that $\pair ab\pair cd = \pair{ac}{bd} = \pair{ca}{db} = \pair cd\pair ab$ so $G\cross G$ so $G$ is abelian implies $G\cross G$ is abelian.
+Let $G\cross G$ be abelian.
+Then as $G$ is isomorphic to the subgroup $\setbuilder{\pair gg}{g \in G}$ we get $G$ being abelian.
+\end{proof}
+
+So it follows that if $G$ is abelian then any subgroup is normal including $T$.
+If $T$ is a normal subgroup then we get for any $a,b,c \in G$ there exists $d\in G$ such that $\pair ab^{-1}\pair cc\pair ab = \pair dd$.
+This means  From this we get $a^{-1}ca = d = b^{-1}cb$, and further for any $g\in G$, $g^{-1}cg = d$.
+It logically follows then that $e^{-1}ce = d = c$.
+Now finally we have $a^{-1}ca = c$ for any $a,c\in G$ and by multiplying $a$ in the front we get $ca = ac$ for any $a,c\in G$ so $G$ is abelian.
+
+%and from that if we choose any $g \in G$ we still have $\pair ag^{-1}\pair cc\pair ag = \pair ff$, however from this we get $a^{-1}ca = f$ so $f= d$ and therefore $a^{-1}ca =d =f = g^{-1}cg$
+
+\subsection{Section 11}
+\subsubsection{Question 3}
+Let $ c\in C\left(x^{-1}ax\right)$.
+By definition we get $cx^{-1}ax=x^{-1}axc$.
+It follows from this that $x^{-1}ax = c^{-1}x^{-1}axc =(xc)^{-1}axc$, and therefore $xcx^{-1} \in C(a)$.
+This means $x^{-1}xcx^{-1}x  = c \in x^{-1}C(a)x$ so $C\left(x^{-1}ax\right) \subset x^{-1}C(a)x$.
+Going the other direction, let $x^{-1}cx \in x^{-1}C(a)x$, so $ca = ac$.
+We then get $\left(x^{-1}cx\right)\left(x^{-1}ax\right) = x^{-1}cax = x^{-1}acx = \left(x^{-1}ax\right)\left(x^{-1}cx\right)$.
+This means $x^{-1}cx \in C(x^{-1}ax)$ and we conclude our proof that $C\left(x^{-1}ax\right) = x^{-1}C(a)x$.
+
+\subsubsection{Question 4}
+Let $\varphi(b) \in \varphi(C(a))$ therefore $b \in C(a)$.
+Now we get $\varphi(a)\varphi(b) = \varphi(ab) = \varphi(ba) = \varphi(b)\varphi(a)$ so $\varphi(b) \in C(\varphi(a))$, and therefore $\varphi(C(a)) \subset C(\varphi(a))$.
+
+Let $b \in C(\varphi(a))$, and as $\varphi$ is 1-1 there is some $c$, such that $\varphi(c) = b$.
+Now we have $ac = \varphi^{-1}(\varphi(ac))$, which we can do again due to $\varphi$ being 1-1 and onto.
+This gives
+\begin{align*}
+ac &= \varphi^{-1}(\varphi(ac))\\
+& = \varphi^{-1}(\varphi(a)\varphi(c))\\
+& = \varphi^{-1}(\varphi(c)\varphi(a))\\
+&= \varphi^{-1}(\varphi(ca)) \\
+&= ca
+\end{align*}
+so $c \in C(a)$ and thus $\varphi(c) = b \in \varphi(C(a))$ so we finish with $\varphi(C(a)) = C(\varphi(a))$.
+
+\subsubsection{Question 11}
+
+For any subgroup $H$ of $G$ we have $H \subset N(H)$ as if we choose $h \in H$ we get $h^{-1}gh \in H$ if $g \in H$ due to closure and we get $g \in H$ if $h^{-1}gh \in H$ as we would have $g = hqh^{-1}$ for some $q\in H$.
+This simply shows that if $P$ is a $p$-Sylow subgroup of $G$ then it must also be a subgroup of $N(P)$ and as $N(P)$ is trivially a subgroup of $G$, by Lagrange's theorem we know if there was some $p$-Sylow subgroup of $N(P)$ larger then $H$ it would be a subgroup of $G$ and thus $P$ would no longer be a $p$-Sylow group, so therefore $P$ is a $p$-Sylow subgroup of $H$.
+
+let $Q$ be a subgroup of $N(P)$ such that $\card Q = \card P = p^n$ Now consider the set $PQ = \setbuilder{pq}{p \in P\land q\in Q}$, we wish to show this is a group.
+Consider $p_1q_1p_2q_2$ with $p_1,p_2 \in P$ and $q_1,q_2\in Q$.
+Now $p_1q_1p_2q_2 = p_1\left(q_1p_2{q_1}^{-1}\right)q_1q_2 = p_1p_3q_1q_2$ with $p_3 = q_1p_2{q_1}^{-1}$ and we know $p_3 \in P$ as $ Q \subset N(P)$.
+This shows closure of $PQ$.
+Now we get inverses as $(pq)^{-1} = q^{-1}p^{-1} = eq^{-1}p^{-1}e$ and $eq^{-1} \in PQ$ as is $p^{-1}e\in PQ$, considering that we already have $PQ$ is closed we have now shown $PQ$ to be a subgroup of $G$ and as both $P$ and $Q$ are subgroups of $N(P)$ this is also a subgroup of $N(P)$.
+Finally we consider the size of this group, $\card{PQ} = \frac{\card{P}\card{Q}}{\card{P\inter Q}}$.
+$\card{P\inter Q} = p^k$ for some $k \le n$ as it is a subgroup of both $P$ and $Q$ which have order $p^n$.
+$\card P\card Q = p^{2n}$, so $\card{PQ} = p^{2n-k}$.
+It follows that $k = n$ as otherwise $P$ would not be $p$-Sylow group.
+Therefore $\card{P\inter N}= 2^p$ so $P\inter N = P$.
+Finally we then conclude that $N = P$ and therefore $P$ is the only $p$-Sylow subgroup of $N(P)$.
+
+\subsubsection{Question 14}
+Suppose $a \sim b$ if $a^{-1}Pa = b^{-1}Pb$. We get that $\sim$ is an equivalence relation very quickly as
+\begin{itemize}
+	\item $a\sim a$ trivial
+	\item $a \sim b \implies a^{-1}Pa=b^{-1}Pb\implies b^{-1}Pb=a^{-1}Pa \implies b\sim a$.
+	\item if $a\sim b$ and $b\sim c$ then $a^{-1}Pa =b^{-1}Pb = c^{-1}Pc$ so $a\sim c$.
+\end{itemize}
+
+Now we may construct equivalence classes $\eqclass{a} = \setbuilder{x\in G}{x \sim a}$, and notice that the question of how many distinct $a^{-1}Pa$ there are is the same as how many equivalence classes there are.
+Now first consider $\eqclass e$.
+This is the set of all $x$ such that $x^{-1}Px = e^{-1}Pe = P$.
+This trivially contains all of $P$ and is in-fact itself a subgroup of $G$ as
+\begin{itemize}
+	\item If $a, b \in \eqclass e$ then $a^{-1}Pa = b^{-1}Pb = P$. It follows that $\left({ab}\right)^{-1}Pab = b^{-1}a^{-1}Pab = b^{-1}Pb = P$ and therefore $ab \in \eqclass e$.
+	\item If $a \in \eqclass e$ then $a^{-1}Pa = P$. It follows then that $aPa^{-1} = aa^{-1}Paa^{-1} = P$ so $a^{-1} \in \eqclass e$.
+\end{itemize}
+so this means it's order is a multiple of $\card P = p^n$.
+Finally we now wish to prove that for all $a,b \in G$, $\card{\eqclass{a}}=\card{\eqclass{b}}$.
+To do this we construct a bijection $f_a:\eqclass e\to\eqclass a$ as $f_a(x) = xa$.
+
+First to show this function is well defined.
+If $x\in \eqclass e$ then $x^{-1}Px = P$ and therefore $(xa)^{-1}Pxa = a^{-1}x^{-1}Pxa = a^{-1}Pa$ so $f_a(x)\in\eqclass a$ and our function is shown to be well defined.
+Next it is 1-1 as if $f_a(x) = f_a(y)$ then $ax = ay$ and $x=y$.
+Our function is also onto as if I choose $y\in \eqclass a$ then consider $x=ya^{-1}$, if $x\in \eqclass e$ then we get $f_a(x) = y$ and $f_a$ would be onto.
+To show $x\in\eqclass e$ we consider $x^{-1}Px=\left(ya^{-1}\right)^{-1}P\left(ya^{-1}\right) = ay^{-1}Pya^{-1}$.
+We know $y\sim a$ so $y^{-1}Py=a^{-1}Pa$ and therefore $ay^{-1}Pya^{-1} =aa^{-1}Paa^{-1} = P$ so $x \in \eqclass e$.
+We conclude then that $f_a$ is onto and therefore for any $a\in G$, $\card{\eqclass{a}} = \card{\eqclass e}$.
+It follows from this that the number of distinct $\eqclass a$ is $\frac{\card G}{\card{\eqclass e}}$ We know $\card G = p^nm$ and $\card{\eqclass{e}} =p^nk$ for some $k$, we then get the number of distinct equality classes to be $\frac mk$.
+Due to $m$ not being divisible by $p$ then $\frac mk$ must also not be divisible by $p$ as it is a divisor of $m$.
+Therefore we conclude that the number of distinct equivalence classes, also the number of distinct $x^{-1}Px$ can not be a multiple of $p$.
+
+\subsubsection{Question 18}
+Let $a \in N(N(P))$, with $P$, $p$-Sylow.
+It follows that $a^{-1}N(P)a\subset N(P)$.
+We know $P \subset N(P)$ so $a^{-1}Pa\subset a^{-1}N(P)a\subset N(P)$.
+Now we have $a^{-1}Pa$ as a $p$-Sylow subgroup of $N(P)$.
+$N(P)$ contains only one $p$-Sylow subgroup, $P$ (as we have already shown in a previous question) so $a^{-1}Pa = P$.
+Now we have that $a\in N(P)$ and therefore $N(N(P)) \subset N(P)$.
+We already had $N(P)\subset N(N(P))$ as this is true for any subgroup $H$ of $G$ that $H\subset N(H)$ and $N(P)$ is a subgroup of $G$.
+We now conclude $N(N(P)) = N(P)$.
+
+%We already know that $N(P) \subset N(N(P))$ as for any subgroup $H$ of $G$ we have $H \subset N(H)$ and $N(P)$ is a group in $G$.
+Next consider $x \in N(N(P))$, this implies that $x^{-1}N(P)x = N(P)$.
+Now consider $y \in N(P)$, this implies that $y^{-1}Py = P$ and $x^{-1}yx \in N(P)$.
+We follow this out to get that $\left(x^{-1}yx\right)^{-1}Px^{-1}yx = P = x^{-1}y^{-1}xPx^{-1}yx$.
+We extrapolate that $xPx^{-1}=y^{-1}xPx^{-1}y$ so $y \in N\left(xPx^{-1}\right)$.
+This implies that $N(P)\subset N\left(xPx^{-1}\right)$.
+It follows that $y = xpx^{-1}$ for some $p\in P$ and therefore $x^{-1}yx = p$ so $x^{-1}yx \in P$.
+We now get $x^{-1}N(P)x\subset P$ and as $P\subset N(P)$ we then have $x^{-1}Px\subset P$.
+From this it follows that $x^{-1}Px = P$ as we saw in the section on normal subgroups.
+We now conclude that $x\in N(P)$ so $N(P) = N(N(P))$.
+Note that at no point did this make use of $P$ being and special subgroup of $G$ so this holds for all subgroups of $G$.
+
+\subsubsection{Question 19}
+
+Obviously if $\card G = p^n$, then $G$ contains the trivial subgroup of order $p^n$, itself.
+Now assume that for some $m$ with $0 \le m \le n$ that there is a subgroup of $G$ with order $p^m$, from this and theorem 2.11.6, we get that there is a subgroup of this group (the one with order $p^m$) that has order $p^{m-1}$, so we get $G$ having a subgroup of order $p^m$ implies $G$ has a subgroup of order $p^{m-1}$.
+Now we finish by invoking induction and we have shown that for all $m$, $0\le m \le n$ that $G$ has a subgroup of order $p^m$.
+
+\subsubsection{Question 25}
+First a lemma from a previous problem that was not assigned.
+\begin{lemma}\label{Q25}
+	Suppose $a \in G$ such that $o(a) = p^m$, and $a^{-1}Pa = P$, with $P$ a $p$-Sylow subgroup of $G$ then $a\in P$.
+\end{lemma}
+\begin{proof}
+	First we get that for all $k$, $a^-kPa^k = P$, and it follows that $Pa^k=a^{-k}P$.
+It follows from this that $(a)P=P(a)$, so let us show that this is a subgroup of $G$.
+Any element will have the form $a^kp$, with $p\in P$ so
+	\begin{itemize}
+		\item $a^{k_1}p_1a^{k_2}p_2 = a^{k_1+k_2}\left(a^{-k_2}p_1a^{k_2}\right)p_2 \in (a)P$.
+		\item $\left(a^kp\right)^{-1}=p^{-1}a^{-m} = a^{-m}\left(a^mp^{-1}a^{-m}\right) \in (a)P$.
+	\end{itemize}
+	so we get $(a)P$ is a group.
+Now the order of $(a)P$ must be $\frac{\card{(a)}\card P}{\card{(a)\inter P}} = \frac{p^mp^n}{\card{(a)\inter P}}$.
+This must then be in the form $p^k$ for some $k$, so $k \le n$ as we have a $p$-Sylow group of order $p^n$.
+Now we then get that $\card{(a)\inter P} = p^m$ which is the order $(a)$ and thus $(a)\subset P$.
+\end{proof}
+Now let $P$ and $Q$ be $p$-Sylow subgroups of $G$ and $Q\not=P$.
+Consider $a\in P\inter N(Q)$ it follows that $a\in N(Q)$ so $a^{-1}Qa = Q$.
+By our lemma we have that $a \in Q$ and as $a \in P$ it's order must divide the order of $P$ so we get $a \in Q$.
+It follows then that $P\inter N(Q) \subset P\inter Q$ and as $P\not=Q$ then $P\inter Q \not=P$.
+Now $P\inter Q$ is a subgroup of $P$ and as $P\inter N(Q)$ is a subgroup of that we get $P\inter N(Q)$ is a subgroup of $P$ so its order must divide $p$ and not be $p^n$.
+Now we get $i_P(N(Q)\inter N) = p^k  > 1$, and as $i_G(N(H))$ is the number of double co-sets of $H$ in $G$ we get that the number of double co-sets of $Q$ in $P$ is in the form $p^k > 1$ so must be a multiple of $p$.
+
+\subsubsection{Question 26}
+Let $P$ be $p$-Sylow.
+For any $Q\not=P$ such that $Q$ is $p$-Sylow we get a multiple of $p$, $kp$ distinct double co-sets of $Q$, which in turn are all $p$-Sylow subgroups of $G$ and are not $P$.
+Therefore we get the number of distinct $p$-Sylow subgroups of $G$ must be 1 plus a multiple of $p$ as we have $P$ and a multiple of $p$ other $p$-Sylow groups.
+
+\subsubsection{Question 28}
+Suppose $H$ is a subgroup of $G$ with order $p^m$ and further assume that it is not contained in any $p$-Sylow subgroup of $G$.
+Now consider $Q$, a $p$-Sylow subgroup of $G$ and let $a \in H\inter N(Q)$ and we find that $a \in Q$ by our lemma $\ref{Q25}$ in my answers (part of question 25).
+Therefore it follows that $H\inter Q \supset H\inter N(Q)$.
+Now consider $i_H(H\inter N(Q)) = \frac{p^k}{p^m}\not=1$ and we know $k\not=p$ as that would imply that $H\subset Q$ and contradict the assumption that it is not contained in a $p$-Sylow group.
+Now we find that there is a multiple of $p$ double co-sets for any $p$-Sylow group, $Q$ and therefore a multiple of $p$, $p$-Sylow groups.
+This contradicts the fact that there is always $1$ plus a multiple of $p$, $p$-Sylow groups so $H$ must be contained in a $p$-Sylow group.
+
+\section{Chapter 3}
+\subsection{Section 1}
+\subsubsection{Question 1}
+\question{(a)} $(4, 5,2,1,3,6)$
+
+\question{(b)} $(3,1,2,4,5)$
+
+\question{(c)} $(1, 4, 3, 2, 5)$
+
+\subsubsection{Question 2}
+
+\question{(a)}
+\begin{enumerate}
+	\item $(2,3,4,5,6,1)$
+	\item $(3,4,5,6,1,2)$
+	\item $(4,5,6,1,2,3)$
+	\item $(5,6,1,2,3,4)$
+	\item $(6,1,2,3,4,5)$
+	\item $(1,2,3,4,5,6)$
+\end{enumerate}
+
+\question{(b)}
+\begin{enumerate}
+	\item $(2,1,3,4,6,5,7)$
+	\item $(1,2,3,4,5,6,7)$
+\end{enumerate}
+
+\question{(c)}
+\begin{enumerate}
+	\item $(6,4,5,2,1,3)$
+	\item $(3,2,1,4,6,5)$
+	\item $(5,4,6,2,3,1)$
+	\item $(1,2,3,4,5,6)$
+\end{enumerate}
+
+\subsubsection{Question 3}
+Consider $a = \left(\begin{smallmatrix}
+1&2&\cdots&n\\a_1&a_2&\cdots&a_n
+\end{smallmatrix}\right)$ and $b =  \left(\begin{smallmatrix}
+a_1&a_2&\cdots&a_n\\b_1&b_2&\cdots&b_n
+\end{smallmatrix}\right)$. We then get $ba = \left(\begin{smallmatrix}
+1&2&\cdots&n\\b_1&b_2&\cdots&b_n
+\end{smallmatrix}\right)$. So in order for $ba = e$ we need $k = b_k$ for all $k$. This implies that $a^{-1} = \left(\begin{smallmatrix}
+a_1&a_2&\cdots&a_n\\1&2&\cdots&n
+\end{smallmatrix}\right)$.
+
+\subsection{Section 2}
+\subsubsection{Question 3}
+
+\question{(a)} $\left(\begin{matrix}1&2&4\end{matrix}\right)\left(\begin{matrix}3&5&7&6\end{matrix}\right)$ has order 12.
+
+\question{(b)}
+$\left(\begin{matrix}1&4&3&2\end{matrix}\right)$ has order 4.
+
+\question{(c)}
+$\left(\begin{matrix}1&4&7&3&6&2&5\end{matrix}\right)$ has order 7.
+
+\question{(d)}
+$\left(\begin{matrix}1\end{matrix}\right)\left(\begin{matrix}2\end{matrix}\right)\left(\begin{matrix}3\end{matrix}\right)$ has order 1.
+
+\question{(e)}
+$\left(\begin{matrix}1&5&7&9\end{matrix}\right)\left(\begin{matrix}2\end{matrix}\right)$ has order 4.
+
+\question{(f)}
+$\left(\begin{matrix}1&4&2&5&3\end{matrix}\right)$ has order 5.
+
+\subsubsection{Question 9}
+When $\sigma = \left(\begin{matrix}2&3\end{matrix}\right)$.
+
+\subsubsection{Question 12}
+Let $p = \left(\begin{matrix}1&2&3\end{matrix}\right)$ and let $a \in\set{1,2,\ldots,7}$ and suppose $\sigma(a) = b$.
+Now if $a \not\in\set{1,2,3}$ then it follows that $p(a) = a$, and therefore $\sigma p\sigma^{-1}(b) = \sigma(p(\sigma^{-1}(b))) = \sigma(p(a)) = \sigma(a) = b$.
+From this we get that for any $\sigma^{-1}(b) \not\in\set{1,2,3}$ then $\sigma p\sigma^{-1}(b) = b$.
+Therefore there at most 3 $b$ such that $\sigma p\sigma^{-1}(b)\not=b$, and therefore $\sigma p\sigma^{-1}$ can not be $\left(\begin{matrix}1&2&4\end{matrix}\right)\left(\begin{matrix}5&6&7\end{matrix}\right)$.
+
+\subsubsection{Question 21}
+By the fact that $\sigma$ and $\tau$ have no letters in common we get that if $\sigma(a) \not= a$ then $\tau(a) = a$ and if $\tau(a) \not = a$ then $\sigma(a) = a$.
+Now if $\sigma\tau = e$ then for any $a$ we have $\sigma(\tau(a)) = a$.
+If for some $a$, $\tau(a)\not = a$ then $\sigma(a) =a$ and therefore $\sigma(\tau(a))\not = a$.
+If for some $a$, $\sigma(a)\not=a$, then we have $\tau(a) = a$ and therefore $\sigma(\tau(a)) = \sigma(a)\not= a$ so $\sigma$ and $\tau$ must both be the identity.
+
+\subsubsection{Question 23}
+For any of the disjoint cycles $a$ in $\sigma$ there is a corresponding cycle $\alpha$ with the same length in $\tau$.
+Now we can think of these cycles as finite sequences simply be choosing one element to fix at the beginning, and it does not mater which we fix, so we can say $a=(a_1,a_2,\ldots,a_k)$ and $\alpha = (\alpha_1,\alpha_2,\ldots,\alpha_k)$.
+Now we can set $p(a_i) = \alpha_i$ and therefore $p\sigma p^{-1}(\alpha_i) = p(\sigma(p^{_1}(\alpha_i))) = p(\sigma(a_i)) = p(a_{i+1}) = \alpha_{i+1}$ as we would want for $\tau$.
+Note we may need to think mod $k$ in order for this to work as we want $k+1 = 1$.
+Now we can construct this for all the cycles and we get $p\sigma p^{-1} = \tau$.
+
+\subsubsection{Question 24}
+\begin{theorem}
+The conjugacy class for any permutation is the set of permutations with the same cycle structure as it.
+\end{theorem}
+\begin{proof}
+	Suppose $f,g\in S_n$ and choose $a \in \set{1,2,\ldots,n}$.
+Every permutation is composed of distinct cycles so $g(a)$ is in some cycle in $f$,  $(c_1,c_2,\ldots,c_k)$, so let $g(a) = c_1$ (from this we also get that $a = c_k$).
+Note also this is a cycle in $f$, so $f(c_1) = c_2$ and $f(c_i) = c_{j}$ where $j \equiv i + 1 \mod k$ and $0<j\le k$.
+Now consider \begin{align*}
+	\left(g^{-1}fg\right)^i(a) &= g^{-1}f^ig(a) \\
+	&= g^{-1}f^i(c_1) \\
+	&= g^{-1}(c_i)
+	\end{align*}
+	therefore  if we let $g^{-1}(c_i) = b_i$ we find $g^{-1}fg$ contains a cycle $(b_1,b_2,\ldots,b_k)$.
+Notice that $g^{-1}fg$ is 1-1 and onto so if $g(\alpha) = c_i$ then $\alpha = b_i$ so cycles in $g^{-1}fg$ map to cycles of the same length in $f$, therefore $g^{-1}fg$ has the same cycle structure as $f$.
+\end{proof}
+
+From this we find that the conjugacy class for this permutation is the set of all single cycle permutations in $S_n$.
+
+The centralizer of our permutation is a little easier.
+If we let $f,g\in S_n$ such that $fg = gf$ then we suppose $(a_1,a_2,\ldots,a_k)$ is a cycle in $f$ then we know $f(a_i) = a_{i+1}$ so $g(a_i) = gf(a_{i-1}) = fg(a_{i-1})$ we then find that $f$ maps $g(a_{i}) \to g(a_{i+1})$ This means that $(g(a_1),g(a_2),\ldots,g(a_k))$ is a cycle in $f$.
+
+So for our permutation we are looking for any $g$ such that $g(k) + 1 \equiv g(k+1) \mod n$. In order for this to be true $g$ must must be a power of $f$.
+
+\subsubsection{Question 25}
+From our solution to the last problem we know that $\sigma$'s conjugacy class is the set of all permutations in $S_4$ with two cycles of size two.
+
+From our solution to the last problem we also know that in order for a permutation $g\in S_4$ to commute with $\sigma$ we need $f(g(1)) = g(2)$ and $f(g(2)) = g(1)$ and then the same with 3 and 4.
+
+\subsection{Section 3}
+\subsubsection{Question 1}
+\question{(a)} even
+
+\question{(b)} odd
+
+\question{(c)} even
+
+\question{(d)} even
+
+\subsubsection{Question 3}
+
+We have already shown that for any permutation $\sigma$ it's conjugacy class is the set of permutations with the same cycle structure as it. This means that it must have the same parity.
+
+Another proof is using our homomorphism $\theta$ to $\set{-1, 1}$.
+We have $\theta(\tau^{-1}\sigma\tau) = \theta(\tau)\theta(\sigma)\theta(\tau) = \theta(\tau)\theta(\tau)\theta(\sigma)$ and as in $\set{-1,1}$ 3very element squared gives the identity 1, we conclude that $\theta(\tau^{-1}\sigma\tau) = \theta(\sigma)$.
+
+\subsubsection{Question 5}
+We must have $4\to 5$ and $5\to 4$.
+
+\subsubsection{Question 6}
+$A_n$ is the set of permutations that are written as the product of an even number of transpositions, so let us show that the product of two transpositions can be written as the product of 3-cycles, from this we will get that any element of $A_n$ can be written in such a way as we could decompose a transposition representation into a product of 3-cycles.
+
+Consider $p = \left(\begin{matrix}
+a&b
+\end{matrix}\right)\left(\begin{matrix}
+c&d
+\end{matrix}\right)$ and insist that $a\not=b$ and $c\not=d$.
+If there is overlap between these two transpositions then the problem becomes nearly trivial.
+I'll go through all the cases: if there is only one overlap (any of $a=c,b=c,a=d,b=d$ and the remaining pair does not overlap then we have a 3-cycle and this is trivial, if there are two overlaps then we get the identity and this can be written as the product of any 3-cycle with it's inverse, which also will be a 3-cycle.
+So assume $a,b,c,d$ all to be distinct.
+Now consider the permutation  $ \rho = \left(\begin{matrix}
+a&d&c
+\end{matrix}\right)\left(\begin{matrix}
+a&b&c
+\end{matrix}\right) = \left(\begin{matrix}
+a&b
+\end{matrix}\right)\left(\begin{matrix}
+c&d
+\end{matrix}
+\right)$.
+
+\subsubsection{Question 8}
+
+\[
+\set{
+	e, \left(\begin{matrix}
+	1&2
+	\end{matrix}\right)\left(\begin{matrix}
+	3&4
+	\end{matrix}\right),\left(\begin{matrix}
+	1&3
+	\end{matrix}\right)\left(\begin{matrix}
+	2&4
+	\end{matrix}\right),\left(\begin{matrix}
+	1&4
+	\end{matrix}\right)\left(\begin{matrix}
+	2&3
+	\end{matrix}\right)
+	}
+\]
+
+\section{Chapter 4}
+\subsection{Section 1}
+\subsubsection{Question 9}
+Consider $A = \left(\begin{matrix}
+a&b\\c&d
+\end{matrix}\right)$ and suppose that for all $2\times 2$ matrices $ B =  \left(\begin{matrix}
+\alpha&\beta\\\gamma&\delta
+\end{matrix}\right)$, $AB = BA$. We get
+\[
+AB = \left(\begin{matrix}
+a\alpha+b\gamma&a\beta+b\delta \\
+c\alpha+d\gamma&c\beta+d\delta
+\end{matrix}\right) = BA = \left(\begin{matrix}
+a\alpha+c\beta&b\alpha+d\beta\\
+a\gamma+c\delta&b\gamma+d\delta
+\end{matrix}
+\right)
+\]
+
+From this we get first by looking in the top left entry that $a\alpha+b\gamma = a\alpha+c\beta$, and therefore $b\gamma = c\beta$.
+This means that for any $\gamma,\beta$ we need some $b,c$ such that this equality holds, and that only happens if $b=c=0$, so we already figured out half of $A$.
+Next look at the entry on the top right and we get $a\beta+b\delta = b\alpha+d\beta$.
+We already know $b=0$ so this reduces to $a\beta=d\beta$ and therefore it follows that $a=d$.
+
+So far we have shown that it is necessary for $a=d$ and $b=c=0$ for our matrix to commute with all $2\cross 2$ matrices, so now we need to show this is sufficient.
+Consider the matrix $ A= \left(\begin{matrix}
+\alpha&0\\0&\alpha
+\end{matrix}\right) $ and an arbitrary matrix $B = \left(\begin{matrix}
+a&b\\c&d
+\end{matrix}\right)$, we then have
+\[AB = \left(
+\begin{matrix}
+a\alpha&b\alpha\\c\alpha&d\alpha
+\end{matrix}
+\right) = BA\] so this must be sufficient as well as necessary.
+
+\subsubsection{Question 11}
+\question{(a)} Let $x = a + bi \in \mathbb C$ and $y = \alpha + \beta i\in\mathbb C$. We then get 
+\begin{align*}
+F(xy) &= F((a+bi)(\alpha+\beta i))\\
+&= F(a\alpha-b\beta+(a\beta+b\alpha)i) \\
+&= a\alpha-b\beta-(a\beta+b\alpha)i \\ \\
+F(x)F(y) &= F(a+bi)F(\alpha+\beta i) \\ 
+&= (a-bi)(\alpha-\beta i)\\
+&= a\alpha - b\beta - (a\beta +b\alpha) i
+\end{align*}
+
+\question{(b)}
+Remember that by definition $\sqrt{x\overline x} = \abs x$ for $x \in \mathbb C$, and as $F(x) = \bar x$ we can use what we proved in the previous part of this question and write $F(x\overline x) = F(x)F(\overline x) = \overline xx = \abs{x}^2$.
+
+\question{(c)} Suppose $x = a + bi$ and $y = c +di$.
+We get $F(x\overline x)F(y\overline y) = \abs x^2\abs y^2 = (a^2+b^2)(c^2+d^2)$ from part b.
+We also can say $F(x\overline x)F(y\overline y) = F(xy\overline{xy}) = \abs{xy}^2 = (ac-bd)^2+(bc+ad)^2$.
+
+\subsubsection{Question 13}
+
+\question{(a)}
+\begin{align*}
+(i+j)(i-j) &= i^2-ij+ji-j^2 \\
+&= -1-k-k+1\\
+& = -2k
+\end{align*}
+
+\question{(b)}
+\begin{align*}
+(1-i+2j-2k)(1+2i-4j+6k) &= 1+2+8+12 + (2-1+12-8)i+(-4+2+6-4)j+(6-2+4-4)k \\
+&= 23 + 5i+4k
+\end{align*}
+
+\question{(c)}
+\begin{align*}
+(2i-3j+4k)^2 &= -4-9-16+(-12+12)i+(8-8)j+(-6+6)k\\
+&= -29
+\end{align*}
+
+\question{(d)}
+\begin{align*}
+i(\alpha_0+\alpha_1i+\alpha_2j+\alpha_3k)-(\alpha_0+\alpha_1i+\alpha_2j+\alpha_3k)i &= \alpha_0i-\alpha_1+\alpha_2k-\alpha_3j-(\alpha_0i-\alpha_1-\alpha_2k+\alpha_3j) \\
+&= -\alpha_1+\alpha_0i-\alpha_3j+\alpha_2k+\alpha_1-\alpha_0i-\alpha_3j+\alpha_2k \\
+&= -2\alpha_3j+2\alpha_2k
+\end{align*}
+
+\subsubsection{Question 16}
+When using our definition for multiplication we find that if we let our solution take the form $\gamma_0+\gamma_1i+\gamma_2j+\gamma_3k$ then we get $\gamma_0 = {\alpha_0}^2+{\alpha_1}^2+{\alpha_2}^2+{\alpha_3}^2$ and $\gamma_1=\gamma_2=\gamma_3 = 0$ as all of these will haver alternating parts that cancel themselves out.
+
+\subsubsection{Question 23}
+For this question let $x = a+bi+cj+dk$ and $y = \alpha+\beta i+\gamma j + \delta k$.
+
+\def\sop{\textbf{*}}
+
+\question{(a)}\begin{align*}
+x\sop\sop &= (a-bi-cj-dk)\sop\\
+& = a+bi+ci+dk \\
+&= x
+\end{align*}
+
+\question{(b)}\begin{align*}
+(x+y)\sop &= (a+\alpha+(b+\beta)i+(c+\gamma)j+(d+\delta)k)\sop\\
+&= a+\alpha-(b+\beta)i-(c+\gamma)j-(d+\delta)k \\
+&= a-bi-ci-dk + \alpha-\beta i-\gamma j - \delta k \\
+&= x\sop+y\sop
+\end{align*}
+
+\question{(c)}\begin{align*}
+xx\sop &= (a+bi+cj+dk)(a-bi-cj-dk) \\
+&= a^2+b^2+c^2+d^2
+\end{align*}
+(see problem 16) Note this is real and non-negative
+\begin{align*}
+x\sop x&=(a-bi-cj-dk)(a+bi+cj+dk) \\
+&= a^2+b^2+c^2+d^2
+\end{align*}
+
+\question{(d)} As margins in this are rather limiting I will adopt the notation $$x = a+bi+cj+dk = \left[\begin{matrix}
+a\\b\\c\\d
+\end{matrix}\right]$$, note that despite this looking like a row vector it is simply a representation of a quaternion, I am going to stick to using this throughout the section and possibly the chapter.
+If there is any possibility for confusion I will state which is being used.
+
+\begin{align*}
+(xy)\sop &= \left[\begin{matrix}
+a\alpha - b\beta -c\gamma -d\delta\\
+a\beta+b\alpha+c\delta-d\gamma\\
+a\gamma+c\alpha+d\beta-b\delta\\
+a\delta+d\alpha+b\gamma-c\beta
+\end{matrix}\right]\sop \\
+&= \left[\begin{matrix}
+a\alpha - b\beta -c\gamma -d\delta\\
+-a\beta-b\alpha-c\delta+d\gamma\\
+-a\gamma-c\alpha-d\beta+b\delta\\
+-a\delta-d\alpha-b\gamma+c\beta
+\end{matrix}\right]
+\\ \\
+y\sop x\sop &= \left[\begin{matrix}
+\alpha\\-\beta\\-\gamma\\-\delta
+\end{matrix}\right]\left[\begin{matrix}
+a\\-b\\-c\\-d
+\end{matrix}\right]\\
+&= \left[\begin{matrix}
+a\alpha-b\beta-c\gamma-d\delta\\
+-a\beta-b\alpha+d\gamma-c\delta\\
+-a\gamma-c\alpha+b\delta-d\beta\\
+-a\delta-d\alpha+c\beta-b\gamma
+\end{matrix}\right]
+\end{align*}
+and therefore $(xy)\sop = y\sop x\sop$.
+
+\subsubsection{Question 36}
+We know that if some element is a zero-divisor then it does not have an inverse, so all we need to do in order to show that $H(\mathbb C)$ is not a division ring is to find $a,b\in H(\mathbb C)$ such that $ab=0$ and $a\not=0\not=b$.
+We will use the representation from the previous problem ans write elements of $H(\mathbb C)$ in the form \[\left[\begin{matrix}
+a_0+b_0i\\
+a_1+b_1i\\
+a_2+b_2i\\
+a_3+b_3i
+\end{matrix}\right]\] Now consider $a=\left[\begin{matrix}
+1\\i\\0\\0
+\end{matrix}\right]$ and $b=\left[\begin{matrix}
+1\\-i\\0\\0
+\end{matrix}\right]$. We then find 
+\begin{align*}
+ab&=\left[\begin{matrix}
+1-1\\
+-i+i\\
+0\\
+0
+\end{matrix}\right]\\
+&= 0
+\end{align*}
+
+\subsubsection{Question 37}
+
+Using again the notation from before, consider
+\begin{align*}
+x &= \left[\begin{matrix}
+0\\3\\4\\5i
+\end{matrix}\right]\\
+\therefore x^2&= \left[\begin{matrix}
+0^2-3^2-4^2-(5i)^2\\
+2\cdot0\cdot3\\
+2\cdot0\cdot4\\
+2\cdot0\cdot5i
+\end{matrix}\right] \\
+&= \left[\begin{matrix}
+5^2-3^2+4^2\\0\\0\\0
+\end{matrix}\right]\\
+&= 0
+\end{align*}
+
+\subsection{Section 2}
+
+\subsubsection{Question 2}
+Let $R$ be an integral domain ring and let $a,b,c\in R$ such that $ab=ac$ and $a\not=0$.
+\begin{align*}
+ab&=ac \\
+ ab-ab&=ac-ab \\
+ 0 &= a(c-b) \\
+ c-b &= 0 \\
+ c&=b
+\end{align*}
+
+We also get this from $ba = ca$ by doing analogous operations from the right.
+
+\subsubsection{Question 3}
+Consider some element of $R$, $\alpha\not=0$ and we find first that all powers of $\alpha$ are not $0$ by the integral domain axioms and second that as $R$ is finite there is some $n>k>0$ such that $\alpha^n=\alpha^k$ and therefore $\alpha^{n-k}\alpha^k=\alpha^k$.
+Now let us relabel a bit and suppose $a = \alpha^{n-k}$ and $b= \alpha^k=\alpha^n$.
+Now $aab = a(ab) = ab$ so we can infer from what we proved in the previous question that $aa = a$.
+Now let $c \in R$ and we find $ac = aac$ and thus $c = ac$ and from the other side $ca = caa$ so $c = ca$.
+From this we can infer that $a = 1$, and thus $R$ has a unit.
+Next we need inverses on our multiplication.
+Now for every $\alpha$ we have some $n(\alpha)> 1$ such that $\alpha^{n(\alpha)} = 1$, therefore it follows that $\alpha^{n(\alpha)-1}\alpha = \alpha\alpha^{n(\alpha)-1} = 1$ and therefore for any $\alpha$, we have $\inv{\alpha} = \alpha^{n(\alpha)-1}$.
+Finally we get commutativity from the fact that $R$ is an integral domain so we can now conclude that we have a commutative division ring, and thus a field.
+
+\subsubsection{Question 7}
+We know from lemma 4.2.1 that $(-a)(-b) = ab$ in any ring and therefore it follows that $(-a)^4 = a^4$, so in our ring $R$ we get for any $r\in R$, $r = r^4 = (-r)^4 = -r$.
+From this we get that $r + r = 0$.
+Now notice that in $R$ if we have $a^n = 0$ then $a = 0$, as $a^n = a^k$ for $k \equiv n\mod 3$ and $1 \le k < 4$ so either $a^1 = a = 0$, $a^2 = 0$ which means that $a = a^4 = 0\cdot a^{4-k} = 0$ so $a= 0$.
+Now consider an element in $t\in R$ such that $t^2 = t$ and choose $l\in R$.
+We find
+\begin{align*}
+(tl - tlt)^2 &= (tl)^2 - (tl)(tlt) - (tlt)(tl) + (tlt)^2\\
+&= tltl - tltlt - tlt^2l + tlt^2lt \\
+&= tltl - tltl - tltlt + tltlt \\
+&= 0
+\end{align*} and \begin{align*}
+(lt-tlt)^2 &= (lt)^2-(lt)(tlt)-(tlt)(lt) + (tlt)^2 \\
+&= ltlt-lt^2lt-tltlt+tlt^2lt \\
+&= ltlt-ltlt-tltlt+tltlt \\
+&= 0
+\end{align*}
+
+From this we find that $tl-tlt = 0$ and $lt - tlt = 0$ and so we can conclude that $tlt = -tl$ and $tlt = -lt$ so $lt = tl$.
+So from this we know that for any $x,y\in R$, $(x^2+x)y = y(x^2+x)$.
+From this we may choose $x,y \in R$ and we would find $z((x^2+y)^2+(x^2+y))=((x^2+y)^2+(x^2+y))z$ for all $z\in R$.
+We may expand out $(x^2+y)^2+(x^2+y)$ and get\begin{align*}
+(x^2+y)^2+x^2+y &= x^4+x^2y+yx^2+y^2+x^2+y \\
+&= x+x^2y+yx^2+y^2+x^2+y \\
+&= (x^2+x)+(y^2+y)+(x^2y+yx^2)\\
+\end{align*}
+and it follows then that
+\begin{align*}
+z((x^2+y)^2+(x^2+y))&=((x^2+y)^2+(x^2+y))z\\
+\therefore z((x^2+x)+(y^2+y)+(x^2y+yx^2))&=((x^2+x)+(y^2+y)+(x^2y+yx^2))z\\
+z(x^2+x) + z(y^2+y) + z(x^2y+yx^2) &= (x^2+x)z + (y^2+y)z + (x^2y+yx^2)z \\
+&= z(x^2+x) + z(y^2+y) + (x^2y+yx^2)z\\
+\therefore z(x^2y+yx^2)&=(x^2y+yx^2)z
+\end{align*}
+
+And now finally if we let $z = x^2$ we get \begin{align*}
+x^2(x^2y+yx^2)&=(x^2y+yx^2)x^2 \\
+x^4y+x^2yx^2&= x^2yx^2+yx^4\\
+\therefore xy&=yx
+\end{align*}
+
+and thus we conclude that $R$ is commutative.
+
+\subsubsection{Question 9}
+First we try and do our sum the traditional way, without simplification and we get $$\sumfrom{n=1}{p-1}{\frac 1n} = \frac{\sumfrom{n=1}{p-1}{(p-1)!\frac 1n}}{(p-1)!}$$ and we can let $a = \sumfrom{n=1}{p-1}{(p-1)!\frac 1n}$ and $b = (p-1)!$.
+Now notice that if $p|a$ so mus the simplified form of the fraction's numerator as that would be $\frac{a/\gcd(a,b)}{b/\gcd(a,b)}$ and $b$ is not a multiple of $p$ due to $p$ being prime so $p\not|\gcd(a,b)$ and therefore $p|\frac a{\gcd(a,b)}$.
+Further any possible numerator in a fraction equaling $\frac ab$ would be a multiple of the simplified forms fractions so if $p|a$ then $p$ must always divide the numerator of this fraction.
+Next we know that $(p-1)!
+\equiv -1\mod p$ as every element has an inverse other than itself which cancels itself out except $1$ and $p-1$ who's inverses are themselves.
+When we do divide this then by some $n$ with $0<n<p$ then we get $(p-1)!
+\equiv -\eqclass{n}^{-1}$, so when we take the sum we get
+\begin{align*}
+\sumfrom{n=1}{p-1}{(p-1)!\frac 1n} &\equiv \sumfrom{n=1}{p-1}{-\eqclass{n}^{-1}}
+\end{align*}
+Each negative inverse just simply becomes a separate element in $\mathbb Z/p$ and still never the 0 element as it has no inverse and is it's own negative, therefore this simply is the sum $\sumfrom{n=1}{p-1}{\eqclass{n}}$ with a different ordering.
+Now $\mathbb Z/p$ is a field so each element has it's additive inverse in the sum and there are no elements $a$ such that $a+a = 0$ with the exception of $0$ then we can use each element to cancel it's negative out and we get $$\sumfrom{n=1}{p-1}{(p-1)!\frac 1n} \equiv \eqclass 0$$ and otherwise stated $a \equiv 0\mod p$ so $p|a$ and we are done.
+
+\subsection{Section 3}
+\subsubsection{Question 3}
+
+Choose $a\in R$ then we get $1a=a=a1$ and therefore $\varphi(1a) = \varphi(a) = \varphi(a1)$ and we conclude with $\varphi(1)\varphi(a) =\varphi(a) = \varphi(a)\varphi(1)$ so $\varphi(1)$ is the unit of $R'$.
+
+\subsubsection{Question 4}
+If $x,y \in I+J$ then $x = a+c$ and $y=b+d$ for some $a,b\in I$ and $c,d \in J$ therefore $x+y = a+c+b+d = a+b+c+d \in I+J$ so we have closure under addition.
+If $x\in I+J$ then $x=i+j$ for some $i\in I$ and $j\in J$, therefore $-x = -(i+j) = -i+(-j) \in I+J$ so we have additive inverses.
+From this we already know that $I+J$ is an additive subgroup of $R$.
+Now consider $r \in R$ and $a \in I+J$.
+As $a\in I+J$ there is some $i\in I$ and $j\in J$ such that $a=I+J$.
+Now we have $ra = r(i+j) = ri + rj \in I+J$ and $ar = (i+j)r = ir+ij \in I+J$.
+From this we conclude that $I+J$ is an ideal of $R$.
+
+\subsubsection{Question 17}
+
+\question{(a)}In order to show that some set $A$ is a subring of some ring $B$ we need to show
+\begin{enumerate}
+	\item $A\subset B$
+	\item $a,b\in A \implies a+b\in A$
+	\item $a\in A \implies -a \in A$
+	\item $a,b\in A \implies ab \in A$
+\end{enumerate}
+
+$A+I \subset R$ is trivial.
+For any $x,y\in A+I$, $x = a+i$ and $y=b+j$ for some $a,b\in A$ and $i,j\in I$.
+From this we get $x+y = a+i+b+j = (a+b)+(i+j) \in A+I$ so we get item 2.
+We also have $xy = (a+i)(b+j) = ab+aj+ib+ij$ and we have $ab \in A$ and $aj,ib,ij\in I$ so $xy \in A+I$ which fulfills item 4.
+Now consider $a+i \in A+I$ and we get $-(a+i) = -a+(-i) \in A+I$, and therefore $A+I$ is a subring of $R$.
+Also note that $A+I\supset I$ as $0 \in A$.
+
+\question{(b)}
+First notice that if $x \in (A+I)/I$ then $x = a + i + I = a + I$ for some $a\in A$ and $i \in I$ and from this it follows that $(A+I)/I = \setbuilder{a+I}{a \in A}$.
+Now let us define $B = A\inter I$ and we can now try and define $\varphi:(A+I)/I \to A/B$ as $\varphi(a+I) = a + B$.
+
+$\varphi$ is a function as if $a,b\in A$ and $a+I = b+I$ then we get $a-b \in I$ and $a-b \in A$ due to closure so $a-b \in B$.
+From this we now conclude $b+B = b+a-b+B = a+B$, so $\varphi$ must be well defined.
+
+$\varphi$ is a homomorphism as if $a,b \in A$ then $$\varphi(a+I)+\varphi(b+I) = (a+B)+(b+B) = a + b + B = \varphi(a+b + I)$$ and $$\varphi(a+I)\varphi(b+I) = (a+B)(b+B) = ab+B = \varphi(ab+B) = \varphi((a+B)(b+B))$$
+
+$\varphi$ is 1-1 as if $\varphi(a+I) = \varphi(b+I)$ then $a+B = b+B$ so $b-a\in B$ and therefore $b-a \in I$ as $B = A\inter I$. From this we conclude $a+I=a+b-a+I = b+I$.
+
+Finally $\varphi$ is onto as if $x \in A/B$ then $x = a + B$ for some $a \in A$ and therefore $a + I\in (A+I)/I$ so $\varphi(a+I) = a+B = x$.
+
+Now we have constructed a isomorphism, $\varphi:(A+I)/I \to A/(A\inter I)$ so $(A+I)/I\simeq A/(A\inter I)$.
+
+\subsubsection{Question 20}
+Suppose $a,b \in R$. Now we get 
+\begin{align*}\varphi(a+b) &= \pair{a+b+I}{a+b+J}\\& = \pair{(a+I)+(b+I)}{(a+J)+(b+J)}\\& = \pair{a+I}{a+J}+\pair{b+I}{b+J} \\&= \varphi(a)+\varphi(b)\end{align*}
+and
+\begin{align*}
+\varphi(ab)&= \pair{ab+I}{ab+J}\\
+&= \pair{(a+I)(b+I)}{(a+J)(b+J)} \\
+&= \pair{a+I}{a+J}\pair{b+I}{b+J} \\
+&= \varphi(a)\varphi(b)
+\end{align*}
+so $\varphi$ is a homomorphism.
+
+Now consider $\varphi(0)$, we find that the 0 in $R_1\oplus R_2$ must be $\pair{0+I}{0+J} = \pair IJ$.
+So now we find $\ker(\varphi) = \setbuilder{x\in R}{\varphi(x) = \pair IJ}$.
+From this we can infer that $x\in \ker(\varphi)$ iff $x +I = I$ and $x + J = J$, so from this we get $x\in I$ and $x\in J$ so $x\in\ker(\varphi) \iff x \in I\inter J$ so $\ker(\varphi) = I\inter J$.
+
+\subsubsection{Question 24}
+
+Let $m$ and $n$ be relatively prime integers and consider the function $f:\mathbb Z_{mn}\to\mathbb Z_m\oplus\mathbb Z_n$ defined as $f(x) = \pair xx$.
+If we have $f(x) = f(y)$ then we have $x \equiv y\mod m$ and $x \equiv y \mod n$ so it follows that $x\equiv y\mod mn$.
+Now $\mathbb Z_{mn}$ has exactly $m\cdot n$ elements and $\mathbb Z_m\oplus \mathbb Z_n$ also has exactly $m\cdot n$ so if $f$ is 1-1 then $f$ is also onto.
+Finally we may then take any $a,b\in\mathbb Z$ and let $\inv f(\pair ab) = x$.
+We know this to be well defined as $f$ is onto so we then have $x \equiv a\mod m$ and $x\equiv b\mod n$.
+
+\subsubsection{Question 27}
+
+Let $P$ be the product of our $n$ primes and we get from our previous question that we may define $f:\mathbb Z_p \to \prodfrom{i=1}n{\mathbb Z_{p_i}}$ just as before with $f(x)=(x,x,\ldots,x)$ and again this function will be 1-1 as if $f(x) = f(y)$ then we get $x \equiv y \mod p_i$ for all $0<i\le n$, and therefore $x \equiv y \mod \prodfrom{i=1}{n}{p_i}$ otherwise stated as $x\equiv y\mod P$.
+Just like before this is a map from two spaces with the same finite cardinality of $P$ so $f$ being 1-1 also makes $f$ onto.
+Here we also will note that $f$ is a homomorphism as \[f(xy) = (xy,xy,\ldots,xy) = (x,x,\ldots,x)(y,y,\ldots,y)=f(x)f(y)\]  and \[f(x+y) = (x+y,x+y,\ldots,x+y)=(x,x,\ldots,x)+(y,y,\ldots,y) = f(x)+f(y)\]
+
+Now from this we get that in order for $x^2 \equiv x\mod P$ then $f(x) = f(x^2) = (f(x))^2$ and also that if $f(x^2) \not= f(x)$ then $x^2 \not= x$ as $f$ is an isomorphism, so we simply need to count the number of $(a_1,a_2,\ldots,a_n)\in \prodfrom{i=1}{n}{\mathbb Z_{p_i}}$ such that $(a_1,a_2,\ldots,a_n)^2 = (a_1,a_2,\ldots,a_n)$.
+From this we need ${a_i}^2 \equiv a_i\mod p_i$ and that happens exactly when $a_i \equiv 1\mod p_i$ or $a_i \equiv 0\mod p_1$.
+This gives us two options for each $a_i$ and as each option is independent we then have $2^n$ total ways to create $x\in Z_P$ such that $x^2 \equiv x\mod P$.
+
+\subsection{Section 4}
+\subsubsection{Question 1}
+Notice that $1^2 \equiv 1\mod 3$ and $2^2\equiv 1\mod3$ so if $a \not\equiv 0\mod 3$ and $b\not\equiv 0\mod 3$ then $a^2+b^2 \equiv 1+1\mod 3$ so $a^2+b^2\equiv 2\mod 3$.
+
+\subsubsection{Question 9}
+Assume that $a^2 \equiv b^2 \mod p$ with $a\not=0\not=b$.
+We then find that $a^2-b^2\equiv 0\mod p$ so $(a+b)(a-b)\equiv0\mod p$.
+We know that $\mathbb Z_p$ is a division ring when $p$ is prime so then either $a+b\equiv 0\mod p$ or $a-b\equiv 0\mod p$.
+From this we get that the only way for $a^2 \equiv b^2\mod p$ is if $a\equiv \pm b\mod p$.
+This means that every non-zero quadratic residue in a prime modulus has exactly two ways to be represented as for all $a\not\equiv0\mod p$, $a\not\equiv -a\mod p$ as then $a+a = 2a \equiv 0$ and we would then have $2\equiv 0\mod p$, which would be true if $p=2$, however we are assuming $p$ to be an odd prime.
+Now we finish the proof by saying each $a^2$ has two distinct representations and thus there are $\frac{p-1}2$ quadratic residues and $\frac{p-1}2$ quadratic nonresidues mod $p$.
+
+Consider $Q = \setbuilder{x^2}{x\not=0\in\mathbb Z_p}$ with $p$ prime.
+It follows then that for any $a^2,b^2 \in Q$ that $a^2b^2 = (ab)^2\in Q$ as multiplication is commutative in $\mathbb Z_p$.
+We also have for any $a^2 \in Q$, that $\inv a\in \mathbb Z_p$ and therefore $\left(\inv a\right)^2 = a^{-2} = \inv{\left(a^2\right)} \in Q$.
+From this we get that $Q$ is a group, and more specifically a subgroup of $\mathbb Z_p\setminus\set 0$ under multiplication.
+
+\subsubsection{Question 10}
+
+Choose $m \in \mathbb Z$ such that $m > 0$ and $\sqrt m \not\in Z$ and define $R = \setbuilder{a+b\sqrt m}{a,b\in \mathbb Z}$ and define addition and multiplication on $R$ in the standard way from the reals.
+It is obvious that $R\subset \mathbb R$ so in order to show that $R$ is a ring we simply need to show it to be a subring of $\mathbb R$, and to do this we only need show it is closed under addition and multiplication and that it has additive inverses.
+
+Choose $a+b\sqrt m \in R$, then we find $$-\left(a+b\sqrt m\right) = -a+-b\sqrt m \in R$$ so we have additive inverses.
+
+Choose $a_1+b_1\sqrt m \in R$ and $a_2+b_2\sqrt m \in R$. We then have $$\left(a_1+b_1\sqrt m\right)+\left(a_2+b_2\sqrt m\right) = (a_1+a_2)+(b_1+b_2)\sqrt m \in R$$ and \begin{align*}
+\left(a_1+b_1\sqrt m\right)\left(a_2+b_2\sqrt m\right) &= a_1a_2+a_1b_2\sqrt m + a_2b_1\sqrt m+b_1\sqrt mb_2\sqrt m \\
+&= (a_1a_2 + b_1b_2m) + (a_1b_2+a_2b_1)\sqrt m \in R
+\end{align*}
+so we have closures.
+
+Now we conclude that $R$ is a subring of $\mathbb R$.
+
+\subsubsection{Question 11}
+First let us show that $I_p$ is an additive subgroup of $R$.
+Let $a+b\sqrt m \in I_p$ and $c+d\sqrt m \in I_p$.
+Then $$a + b \sqrt m + c + d\sqrt m = (a+c)+(b+d)\sqrt m$$ and we know $p|a$ and $p|c$ so $p|(a+c)$ and the same is true for $b+d$, therefore $I_p$ is closed under addition.
+Also $$-\left(a+b\sqrt m\right) =-a+-b\sqrt m$$ and as $p|a$ then $p|-a$ and again the same argument goes for $-b$ so we now know that $I_p$ is an additive subgroup of $R$.
+
+Now consider $a+b\sqrt m \in I_p$ and $c+d\sqrt m \in R$.
+We only need show that this is an ideal from one side as multiplication is commutative in $\mathbb R$, which this is all contained within.
+So we find $$
+\left(a+b\sqrt m\right)\left(c+d\sqrt m\right)=ac+bdm + (ad+bc)\sqrt m $$ We know $p|a$ so $p|ac$.
+We also know that $p|b$ so we know that $p|bdm$ and therefore $p|(ac + bdm)$.
+Next we know that $p|a$ so $p|ad$ and we know $p|b$ so $p|ac$ and therefore $p|(ad+bc)$ so we conclude that $ac+bdm+(ad+bc)\sqrt m \in I_p$ and therefore $I_p$ is an ideal of $R$.
+
+\subsection{Section 5}
+\subsubsection{Question 2}
+
+For this problem I will assume that $x$ commutes with $R$ as otherwise I end up with $ax^nbx^m$ and can't be sure that this is really can be written as $cx^k$.
+I feel this is a a safe assumption, despite the book not stating this in the problem, as it does say that it is mostly dealing with commutative rings.
+To be more precise I'm really saying that for any $p(x) \in R[x]$, $p(x)$ is a function $p:A\to B$ and for any $x\in A$ and $r \in R$, we need to have $xr = rx$.
+
+\question{(a)} Consider $f(x), g(x) \in R[x]$ with $f(x)\not=0\not=g(x)$.
+Let $\deg f(x) = n$ and $\deg g(x) = m$ and we get that $f(x) = \sumfrom{i=0}{n}{f_ix^i}$ and $g(x) = \sumfrom{i=0}{m}{g_ix^i}$ for some $f_1,f_2,\ldots,f_n,g_1,g_2,\ldots,g_m \in R$.
+From this we get
+\def\LB{\left[}
+\def\RB{\right]}
+\begin{align*}
+f(x)g(x)&= \sumfrom{i=0}{n}{f_ix^i}\sumfrom{i=0}{m}{g_ix^i}\\
+&= \sumfrom{j=0}n{f_jx^j\sumfrom{i=0}m{g_ix^i}}\\
+&= \sumfrom{j=0}n{\sumfrom{i=0}m{f_jx^jg_ix^i}} \\
+&= \sumfrom{j=0}n{\sumfrom{i=0}m{f_jg_ix^{j+i}}}
+\end{align*}
+so we get that the largest power possible for $x$ to be $n+m$ and therefore $\deg(f(x)g(x)) \le m+n = \deg f(x)+\deg g(x)$.
+
+\question{(b)} Consider the ring $\mathbb Z_{ab}$, with $a,b > 1$. Then we can have $f(x) = ax$ and $g(x) = bx+1$ and so we find $f(x)g(x) = abx^2+ax = 0x^2+ax = ax$ as $ab \equiv 0\mod ab$.
+
+\subsubsection{Question 3}
+Using the Euclidean algorithm, I will not show the work as it's quite a lot to be typed up, however the algorithm takes in $a_0(x)$ and $b_0(x)$ and then finds $a_0 = q_0(x)b_0(x)+r_0(x)$ with $\deg r_0(x) < \deg b_0(x)$ as per the division algorithm.
+Then we let $a_1(x) = b_0(x)$ and $b_1(x) = r_1(x)$ and we repeat.
+This means we have $a_i = b_{i-1}$ and $b_i = r_{i-1}$ and $a_i =q_i(x)b_i(x)+r_i(x)$ with $\deg r_i(x) < \deg b_i(x)$.
+Eventually there is some $n$ such that $b_n(x) = 0$, and then $a_n(x) = \gcd(a_0(x),b_0(x))$.
+Some normalizing may be required to keep the polynomials monic, but this does not mess with the algorithm.
+Remember that if $a(x)|f(x)$ then any $ca(x)|f(x)$ as $a(x)b(x) = f(x)$ so $ca(x)c^{-1}b(x) | f(x)$ as $c^{-1}$ must exist due to us working in $F[x]$ with $F$ a field.
+With no further ado, the solutions:
+
+\question{(a)} $1$
+
+\question{(b)} $x-1$
+
+\question{(c)} $1$
+
+\question{(d)} $x^3-1$
+
+\subsubsection{Question 10}
+
+\question{(a)} $x^2+7$ over $\mathbb R$.
+If a polynomial is not irreducible then it can be written as the product of irreducible polynomials.
+For $x^2 + 7$ over $\mathbb R$ we would have to have some $g(x),f(x)\in\mathbb R[x]$ such that $g(x)$ is monic irreducible and $\deg f(x),\deg g(x) > 0$.
+This means that $\deg f(x) = 1 = \deg g(x)$ so $f(x) = ax+b$ and $g(x) = x+c$.
+From this we would have $f(x)g(x) = ax^2+(ac+b)x + bc = x^2+7$.
+From this we get $a= 1$, $ac+b = 0$ and $bc = 7$.
+We then have $c+b = 0$ so $b=-c$.
+That means that $bc = -b^2$ and all squares are positive in $\mathbb R$ so we can not have $-b^2 = 7$ so we have a contradiction.
+
+\question{(b)} $x^3-3x+3$ over $\mathbb Q$.
+If this is not irreducible then it is the product of some smaller monic polynomials and a constant so by it being degree 3 this must be a polynomial of order 1 and order 2.
+Therefore we let $f(x) = x^2+ax+b$ and $g(x) = x+c$ and finally $d\in \mathbb R$ such that $f(x)g(x)d = x^3-3x+3$.
+Immediately we get $d=1$ as $x^3-3x+3$ is monic, so we are left with $$x^3-3x+3=x^3+(a+1)x^2+(ac+b)x+bc$$ and from that $a + 1 = 0$ so $a=-1$, $ac+b = b-c = -3$ and $bc =3$.
+It follows that $c-b=3=bc$.
+From this the sign of $b$ and $c$ must be the same as $bc$ is positive, so that means $c > 3$ as otherwise we could not have $c-b=3$.
+Now we let $\frac nm = c$ and $\frac pq = b$, with $p,q,n,m \in\mathbb Z$ and $\gcd(n,m) =1 = \gcd(p,q)$.
+We know $a,b > 0$ so $p,q,n,m>0$.
+We know $c>3$ so $\frac nm > 3$ and thus $n>3m\ge 3$.
+And finally we know $\frac nm\frac pq = 3 = \frac nm-\frac pq$ which we rewrite as $\frac{np}{mq} = 3 = \frac{nq-mp}{mq}$ and then one step further we get $$np=3mq=nq-mp$$ Here we divide by $n$ and $p$ and we get two equalities: first $$n=\frac{3mq}p=\frac{nq}p-m$$ and therefore $p|3mq$ and $p|nq$, and as we know $\gcd(p,q)=1$ then $p|3m$ and $p|n$; and our second equation $$p=\frac{3mq}n=q+\frac{mp}n$$ and therefore $n|3mq$ and $n|mp$, however we know $\gcd(n,m) = 1$ so we have $n|3q$ and $n|p$.
+We now have shown $n|p$ and $p|n$ so $p=n$ and therefore we know that $n|3m$ as we had $p|3m$.
+We know $\gcd(n,m)=1$ so $n|3m\implies n|3$ and thus $n \le 3$ which contradicts $n > 3m \ge 3$ we already had, so thus there can not possibly be any polynomials $g(x),f(x)$ over $\mathbb Q$ such that $g(x)f(x) = x^3-3x+3$ with both being lower order than three, so $x^3-3x+3$ is irreducible.
+
+\question{(c)} $x^2+x+1$ over $\mathbb Z_2$.
+From our previous results we know that in order for this not to be irreducible we need $g(x),f(x)\in\mathbb Z_2[x]$, both with lower order and monic be such that $g(x)f(x) = x^2+x+1$.
+It follows that $g(x)=x+a$ and $f(x)= x+b$ and therefore $f(x)g(x) = x^2+(a+b)x+ab$.
+We know then that $ab=1$ and $a+b=1$.
+In order for $ab=1$ we need both $a,b = 1$ and therefore $a+b=0$ so we have a contradiction and thus $x^2+x+1$ is irreducible.
+
+\question{(d)} $x^2+1$ over $\mathbb Z_{19}$.
+Just like before let $g(x) = x+a$ and $f(x) = x+b$ and we get $a+b=0$ and $ab = 1$.
+From this we get that $a=-b$ so $ab=-bb=-b^2=1$ so $b^2 = -1$ which is not a square in $\mathbb Z_{19}$ which we can show simply by listing all the squares.
+I will not do that here, however here is python code that will verify the result.
+\begin{center}
+	\verb|[pow(x,2,19) for x in range(0,19)]|
+\end{center}
+
+\question{(e)} $x^3-9$ over $\mathbb Z_{13}$.
+Just like before let $f(x) + x^2+ax+b$ and $g(x) = x+c$ and we find $$f(x)g(x) = x^3+(a+c)x^2+(ac+b)x+bc$$ so $a+c = 0$, $ac+b=0$ and $bc=1$.
+From this we get $a=-c$ and therefore $ac+b = -c^2+b = 0$, so $b=c^2$ and thus finally $bc = c^3 = -9$.
+$\mathbb Z_{13}$ is a small space so we can just check to see if $-9$ is a cube, notice $-9=13-9=4$ and $4$ is not a cube.
+I verified this with the following python code.
+\begin{center}
+	\verb|[pow(x,3,13) for x in range(0,13)]|
+\end{center}
+
+\question{(f)} $x^4+2x^2+2$ over $\mathbb Q$. If this is reducible then either it is a degree 3 and a degree 1 or two degree 2 polynomials. Let us degree 3 and 1 and then two degree 2 polynomials.
+
+Let $f(x) = x^3+ax^2+bx+c$ and $g(x) = x+d$, then we have $$f(x)g(x) = x^4+(a+d)x^3+(ad+b)x^2+(bd+c)x + cd$$ so $a+d = 0$, $ad+b=2$, $bd+c = 0$, and $cd = 2$.
+We then have $a=-d$ and therefore $-a^2+b=2$ so $b=2+a^2$.
+Further $bd+c = (2+a^2)(-a)+c = 0$ so $c = a(2+a^3)$ and $cd = a(2+a^3)(-a) = 2$, so we have $-a^2(2+a^3) = 2$.
+Now $a^2 > 0$ so $2+a^3 < 0$ for the multiplication to work, this simply means $a^3 <-2$ and therefore $a < -\sqrt[3]{2}$.
+Now we also know that $a\in\mathbb Q$ and $a$ is negative so $a = -\frac pq$ with integers $p,q > 0$.
+From this we get
+\begin{align*}2 &= -\left(-\frac pq\right)^2\left(2+\left(-\frac pq\right)^3\right)\\
+&= -\frac{p^2}{q^2}\left(2-\frac{p^3}{q^3}\right)\\
+&= -2\frac{p^2}{q^2}+\frac{p^5}{q^5}\\
+2q^2 &= -2p^2+\frac{p^5}{q^3}\\
+2q^2+2p^2&=\frac{p^5}{q^3}\\
+2q^5+2p^2q^3 &= p^5\\
+\frac{2q^5}{p^2}+2q^3 &= p^3
+\end{align*}
+so we have $p^2|2q^5$, however as $\gcd(p,q) = 1$ then $p^2|2$ and therefore $p=1$.
+From this we get $\frac pq\le 1$ so $2-\left(\frac pq\right)^3 > 0$ and $-\left(\frac pq\right)^2 < 0$ so then $2=-\left(\frac pq\right)^2\left(2-\left(\frac pq\right)^3\right) < 0$ and we have a contradiction.
+
+Now let us try two order 2 polynomials, $f(x) = x^2+ax+b$ and $g(x) = x^2+cx+d$ and we find $$f(x)g(x) = x^4+(a+c)x^3+(b+ac+d)x^2+(ad+bc)x+bd$$ so $a+c = 0$, $b+ac+d = 2$, $ad+bc=0$ and $bd = 2$.
+From $a+c=0$ we get $a=-c$ and therefore our equality $ad=bc=0$ becomes $ad-ab=0$ so $ad=ab$ and therefore either $a=0$ or $b=d$.
+
+If $b=d$ then $bd=b^2=2$ and therefore $b=\sqrt 2$ which is known to be irrational, so this can not be.
+
+If $a=0$ then $b-ac+d=2$ becomes $b+d=2$ and we also have $bd=2$ so $a+b=2=bd$.
+$bd$ is positive and therefore $b$ and $d$ must share a sign, however $b+d$ is also positive so if they are to share a sign they both must be positive.
+Now let $b = \frac nm$ and $d=\frac pq$ with $p,q,n,m$ positive integers and $\gcd(p,q) = 1 = \gcd(n,m)$.
+Now we have $\frac nm + \frac pq = 2=\frac nm\cdot\frac pq$ so it follows that $\frac{nq+pm}{mq}=2=\frac{np}{mq}$ and therefore $$2mq=nq+pm=np$$ From this we can do some division and find $$\frac{2mq}n = q+\frac{pm}q=p$$ so $n|pm$ and $n|2mq$ and by $\gcd(n,m)=1$ we get $n|p$ and $n|2q$; and we find $$\frac{2mq}p=\frac{nq}p+m=n$$ so $p|2mq$ and $p|nq$ and by $\gcd(p,q) = 1$ we get $p|n$ and $p|2m$.
+From this we then have $p|n$ and $n|p$ so it follows that $n=p$ and therefore $n|2$ as $n=p|2m$ so either $n=1$ or $n=2$.
+If $n=1$ then $2=\frac{1}{mq}$ which is impossible, so $n\not=1$.
+If $n=2$ then $2mq = 2q+m=4$.
+From this we get $mq=q+m=2$, in order for $mq = 2$ we need one of $m,q$ to be 1 and the other to be 2, however that would give $q+m=3\not=2$ so we have a contradiction, and are now done.
+
+\subsubsection{Question 11}
+Suppose $p(x)\in F[x]$ is of order 3.
+If $p(x)$ is reducible then there must be some $f(x),g(x)\in F[x]$ and some $a_0\in F$ such that $p(x)=a_0f(x)g(x)$ and both $f(x)$ and $g(x)$ have lower order then $p(x)$ and are monic.
+This means one will have order 2 while the other has order 1.
+Suppose then without loss of generality $f(x)$ has order 2 and $f(x) = x+b$.
+Then we notice that $f(-b) = 0$ so $a_0f(-b)g(-b) = 0$ and thus $p(x)=0$ for at least some value in $F$.
+It follows then that if $p(x)\not0$ for all $x\in F$ then $p(x)$ is irreducible.
+
+\subsubsection{Question 12}
+
+By theorem 4.5.9 in the book we have if $f(x),g(x)$ are relatively prime then there is some $a(x),b(x)$ such that $a(x)f(x)+b(x)g(x) = 1$.
+This means that there is $a(x),f(x),b(x),g(x) \in F$ such that $a(x)f(x)+b(x)g(x) =1$, and as $F\subset K$ then $a(x)f(x)+b(x)g(x) = 1$ is also true in $K[x]$.
+Now by theorem 4.5.9 again we get that this means $f(x)$ and $g(x)$ are relatively prime.
+
+\subsubsection{Question 13}
+Let $p(x) = x^2 +1$.
+Now $\mathbb R[x]$ is an principal ideal domain, so for all $f(x) \in (p(x))$, $f(x) = a(x)p(x)$ for some $a(x)$.
+So the first thing we wish to show is that if $\deg f(x) \ge 2$ then there is some $g(x)$ of order less than 2 such that $(p(x))+f(x) = (p(x)) +g(x)$ or $f(x)\in (p(x))$.
+
+\begin{proof}
+	Suppose $\deg f(x) \ge 2$, then there exists $q(x),r(x)$ such that $f(x)=q(x)p(x)+r(x)$ and $\deg r(x) < \deg p(x)$ or $r(x) = 0$ by the division algorithm.
+From this we get $\deg r(x) < 2$ or $r(x) = 0$.
+If $r(x)=0$ then $f(x) = q(x)p(x)\in(p(x))$.
+If $\deg r(x) < 2$ then $f(x) \in (p(x))+r(x)$.
+\end{proof}
+
+Now further we wish to show that for any $a(x),b(x)$ with order less than 2, if $a(x)\not=b(x)$ then $(p(x))+a(x)\not=(p(x))+b(x)$. We include the 0 function as having order less than 2.
+
+\begin{proof}
+	Suppose $a(x) \not=b(x)$ and both have order less than 2, then assume for the sake of contradiction that $(p(x))+a(x)=(p(x))+b(x)$.
+From this we get $a(x)=c(x)p(x)+b(x)$ and we find $\deg(c(x)p(x)+b(x)) = \max(\deg c(x)+\deg p(x), \deg b(x)) = \deg c(x)+\deg p(x)$ as $\deg p(x) > \deg b(x)$ unless $c(x) = 0$.
+If $c(x) = 0$ then we get $a(x) = b(x)$ which we already said it is not, and otherwise we get $\deg a(x) = \deg c(x) + \deg p(x) \ge \deg p(x) = 2$ thus contradiction that $a(x)$ has order 2 or less, so we conclude that $(p(x))+a(x)\not=(p(x))+b(x)$
+\end{proof}
+
+So every element in $\mathbb R[x]/(p(x))$ has a unique representation by a polynomial with that is either 0, or has order less than 2.
+Notice finally that $f(x) = x$ has $f(x)^2=x^2$ and $(p(x))+x^2 = (p(x))-1$ by the division algorithm.
+So we can conclude that $\varphi:\mathbb C\to\mathbb R[x]/p(x)$ defined as $\varphi(a+bi)=(p(x)) + bx+a$ is a isomorphism.
+
+\subsubsection{Question 19}
+
+Consider $P(x) = x^2-a \in \mathbb Z_p[x]$ with $p$ an odd prime.
+If $P(x)$ is reducible then there is some $f(x)g(x) = P(x)$ with both having lower order and monic as $P(x)$ is monic.
+Let $f(x) = x+c$ and $g(x) = c+d$ so $$P(x)=x^2-a=f(x)g(x)=(x+c)(x+d) = x^2+(c+d)x+cd$$ and therefore $c+d = 0$ so $c=-d$ and we also have $cd=-a$ so $-c^2=-a$ and therefore $c^2=a$.
+So only if $a$ is a square in $\mathbb Z_p$ is $P(x)$ reducible, so let $a$ be a quadratic nonresidue mod $p$, and we know such an element exists from Question 9 in Section 4.
+
+Now consider $\mathbb Z_p[x]/P(x)$ and we know from the last problem that every element of this has a unique representation by a polynomial of order less than 2.\footnote{While we didn't actually prove it in the last problem the steps we went through would also work for this case, so I'm not going to go through the work again.} So now we already know this is a commutative ring, so we simply need to show the existence of a unit and inverses and we have a field.
+So as every element of this has a unique second degree polynomial representing it then any element takes the form $\eqclass{bx+c}$ and there are $p^2$ such polynomials.
+
+So for a unit we have $e(x) = 1$, as $e(x)(bx+c) = 1(bx+c) = bx+c$.
+Now consider $f(x) = bx+c$ and we find $$\eqclass{f(x)}^2 = \eqclass{b^2x^2+2bcx+c^2} = \eqclass{2bcx+b^2a+c^2}$$, thus in order for $\eqclass{f(x)}^2 = 0$ we need $2bc = 0$ so either $b=0$ or $c=0$ and either way then $b^2a+c^2=0$ would imply that the other (between $b$ and $c$) must be $0$.
+From this we get that no element multiplied by itself is 0, unless that element was the 0 element.
+So we can conclude that $\eqclass{f(x)}^{2^n} \not=\eqclass 0$.
+This in-fact means all powers of $f(x)$ are not zero as then there would some $2^n$ power greater then it which would be zero.
+Now from some results we had in finite groups we can be sure that $\eqclass{f(x)}$ has an inverse.
+Now we know that $\mathbb Z_p[x]/P(x)$ is a field with order $p^2$.
+
+\subsubsection{Question 26}
+%TODO this problem and next (sort of samey)
+
+\subsubsection{Question 28}
+
+\subsection{Section 6}
+\subsubsection{Question 3}
+Any $a$ such that $a=5k$ with $k\equiv 0\mod 5$ or $a=3k$ with $k\equiv 0\mod3$.
+\subsubsection{Question 4}
+
+Consider $g(x) = {a_0}^{n-1}f(x)$ and then let $y = a_0x$ and we find $h(y)$ such that $h(y) = g(x)$.
+Therefore we have $$h(y) = h(a_0x) = g(x)$$ The first term of $g(x)$ is ${a_0x}^n$ so then $h(y)$ must be monic, and we may use the Einstein criterion on this to test if $f(x)$ is reducible.
+
+\subsubsection{Question 7}
+For this we will define arbitrary polynomial $f(x) = \sumfrom{i=0}{\infty}{f_ix^i}$ with $f_i = 0$ for all $i > \deg f(x)$. This will make notation much smoother.
+
+\begin{itemize}
+	\item $\varphi$ is a homomorphism as: \begin{align*}
+	\varphi(f(x)) +\varphi(g(x)) &= f(x+1)+g(x+1) \\
+	&= \sumfrom{i=0}{\infty}{f_i\left(x+1\right)^i}+\sumfrom{i=0}{\infty}{g_i\left(x+1\right)^i} \\
+	&= \sumfrom{i=0}{\infty}{(f_i+g_i)(x+1)^i} \\
+	&= \varphi\left(\sumfrom{i=0}{\infty}{(f_i+g_i)x^i}\right)\\
+	%&=\varphi\left(\sumfrom{i=0}{\infty}{f_ix^i}+\sumfrom{i=0}{\infty}{g_ix^i}\right)\\
+	&=\varphi(f(x)+g(x))\\
+	\\
+	\varphi(f(x))\varphi(g(x)) &= f(x+1)g(x+1) \\
+	&= \sumfrom{i=0}{\infty}{\sumfrom{j=0}{i}{f_{i-j}g_j}(x+1)^i} \\
+	&= \varphi\left(\sumfrom{i=0}{\infty}{\sumfrom{j=0}{\infty}{f_{i-j}g_j}x^i}\right) \\
+	&= \varphi(f(x)g(x))
+	\end{align*}
+	\item $\varphi$ is 1-1 as if $\varphi(f(x)) = \varphi(g(x))$ then $f(x+1)=g(x+1)$ and we can define $p(x) = f(x+1)$ and $q(x) = g(x+1)$ so we have $p(x) = q(x)$ and it follows then that $p(x-1) = q(x-1)$ so $f(x)=g(x)$.
+
+	\item $\varphi$ is onto as $f(x) = g(x+1)$ with $g(x) = f(x-1)$, so $\varphi(g(x)) = f(x)$.
+\end{itemize}
+
+Further consider that for any $a\in F$, we can construct $f(x) = a$ and then $\varphi(f(x)) = a$, so $\varphi(a) = a$.
+
+\subsubsection{Question 11}
+
+We have $\varphi:F[x]\to F[x]$ is an automorphism and $\varphi(a) = a$ for all $a\in F$.
+Now we have $$\varphi(f(x)) = \varphi\left(\sumfrom{i=0}{n}{f_ix^i}\right)=\sumfrom{i=0}{n}{\varphi(f_i)\varphi(x)^i} = \sumfrom{i=0}{n}{f_i\varphi(x)^i}$$.
+Now as $x\in F[x]$ then so must $\varphi(x) \in F[x]$ as $\varphi$ is an automorphism.
+From this we get $\varphi(x) = p(x) \in F[x]$, so $\varphi(f(x)) = f(p(x))$.
+Now we have $\deg f(g(x)) = \deg f(x)\cdot\deg g(x)$, so $\deg p(x) = 1$ as if it were greater we could never map to a order 1 polynomial and if it were less everything would map to the zero function or a constant.
+So now $\sigma(f(x)) = f(p(x))$ and $\deg p(x) = 1$ so $p(x) = ax+b$ for some $a,b\in F$ with $a\not=0$.
+
+\subsection{Section 7}
+\subsubsection{Question 3}
+We have $[a,b][c,d] = [ac,bd]$. So \begin{align*}
+[a,b]\left([c,d][e,f]\right) &= [a,b][ce,df]\\
+&= [ace,bdf] \\
+&= [ac,bd][e,f]\\
+&=\left([a,b][c,d]\right)[e,f]\\\\
+[a,b][c,d] &= [ac,bd]\\
+&= [ca,db]\\
+&= [c,d][a,b]
+\end{align*}
+so we have associativity and commutativity for multiplication.
+
+\subsubsection{Question 4}
+Let $K$ be a field and $D$ an integral domain with $D\subset K$.
+Let $F$ be the quotient field generated by $D$.
+Now assume for the sake of contradiction there is some $\frac ab \in F$ such that $\frac ab \not\in K$.
+If $\frac 1b \in K$ then we get $\frac ab\in K$ as $a\in K$ and thus we would have $a\frac 1b \in K$.
+Now $\frac 1b = \inv b$ so therefore we have found some $b\not=0$ such that $b$ does not have an inverse in $K$, so $K$ is not a field.
+Therefore $\frac ab \in K$ so $F\subset K$.
+
+\section{Chapter 5}
+\subsection{Section 1}
+\subsubsection{Question 3}
+For notational reasons we will let polynomials be the sum of infinite terms, with only finitely many having non-zero coefficients.
+
+\question{(a)} Consider $f(x,y) \in S[y]$, then $$f(x,y) =\sumfrom{i=0}{\infty}{f_i(x)y^i} = \sumfrom{i=0}{\infty}{\sumfrom{j=0}{\infty}{f_{i,j}x^j}y^i}$$
+
+\question{(b)} If $f(x,y) = \sumfrom{i=0}{\infty}{\sumfrom{j=0}{\infty}{f_{i,j}x^j}y^i}$ and $g(x,y) = \sumfrom{i=0}{\infty}{\sumfrom{j=0}{\infty}{g_{i,j}x^j}y^i}$ then simply, we need $f_{i,j}=g_{i,j}$ for all $i,j$.
+
+\question{(c)} 
+\begin{align*}f(x,y) + g(x,y) &= \sumfrom{i=0}{\infty}{\sumfrom{j=0}{\infty}{f_{i,j}x^j}y^i} + \sumfrom{i=0}{\infty}{\sumfrom{j=0}{\infty}{g_{i,j}x^j}y^i}\\
+&=\sumfrom{i=0}{\infty}{\sumfrom{j=0}{\infty}{f_{i,j}x^j}y^i+\sumfrom{j=0}{\infty}{g_{i,j}x^j}y^i}\\
+&= \sumfrom{i=0}{\infty}{\left(\sumfrom{j=0}{\infty}{f_{i,j}x^j}+\sumfrom{j=0}{\infty}{g_{i,j}x^j}\right)y^i}\\
+&= \sumfrom{i=0}{\infty}{\sumfrom{j=0}{\infty}{f_{i,j}x^j+g{i,j}x^j}y^i}\\
+&= \sumfrom{i=0}{\infty}{\sumfrom{j=0}{\infty}{\left(f_{i,j}+g_{i,j}\right)x^j}y^i}
+\end{align*}
+
+\question{(d)}
+\begin{align*}
+f(x,y)g(x,y) &= \sumfrom{i=0}{\infty}{\sumfrom{j=0}{\infty}{f_{i,j}x^j}y^i} \sumfrom{i=0}{\infty}{\sumfrom{j=0}{\infty}{g_{i,j}x^j}y^i} \\
+&=\sumfrom{i=0}{\infty}{\sumfrom{j=0}{\infty}{f_{i,j}x^j}y^i\sumfrom{k=0}{\infty}{\sumfrom{j=0}{\infty}{g_{k,j}x^j}y^k}}\\
+&=\sumfrom{i=0}{\infty}{\sumfrom{j=0}{\infty}{\sumfrom{k=0}{\infty}{f_{i,k}x^k}y^i\sumfrom{k=0}{\infty}{g_{j,k}x^k}y^j}} \\
+\text{(If $R$ is commutative)}\quad&=\sumfrom{i=0}{\infty}{\sumfrom{j=0}{\infty}{\sumfrom{k=0}{\infty}{f_{i,k}x^k}\sumfrom{k=0}{\infty}{g_{j,k}x^k}y^iy^j}} \\
+&= \sumfrom{i=0}{\infty}{\sumfrom{j=0}{\infty}{\sumfrom{k=0}{\infty}{\sumfrom{l=0}{\infty}{f_{i,l}x^l}g_{j,k}x^k}y^{i+j}}}\\
+&= \sumfrom{i=0}{\infty}{\sumfrom{j=0}{\infty}{\sumfrom{k=0}{\infty}{\sumfrom{l=0}{\infty}{f_{i,l}x^lg_{j,k}x^k}}y^{i+j}}}\\
+&= \sumfrom{i=0}{\infty}{\sumfrom{j=0}{\infty}{\sumfrom{k=0}{\infty}{\sumfrom{l=0}{\infty}{f_{i,l}g_{j,k}x^{l+k}}}y^{i+j}}} \\
+&= \sumfrom{i=0}{\infty}{\sumfrom{j=0}{i}{\sumfrom{k=0}{\infty}{\sumfrom{l=0}{\infty}{f_{i-j,l}g_{j,k}x^{l+k}}}}y^{i}}\\
+&= \sumfrom{i=0}{\infty}{\sumfrom{j=0}{i}{\sumfrom{k=0}{\infty}{\sumfrom{l=0}{k}{f_{i-j,l}g_{j,k-l}}x^{k}}}y^{i}}\\
+&=\sumfrom{i=0}{\infty}{\sumfrom{k=0}{\infty}{\sumfrom{j=0}{i}{\sumfrom{l=0}{k}{f_{i-j,l}g_{j,k-l}}x^{k}}}y^{i}}\\
+&= \sumfrom{i=0}{\infty}{\sumfrom{k=0}{\infty}{\sumfrom{j=0}{i}{\sumfrom{l=0}{k}{f_{i-j,l}g_{j,k-l}}}x^{k}}y^{i}}
+\end{align*}
+
+\subsubsection{Question 8}
+\def\LB{}\def\RB{}
+
+Let us do this by induction on $n$ where $m = p^n$.
+If $n=0$ this is trivial and when $n = 1$ we get $(a+b)^p = \sumfrom{i=0}{p}{\binom pia^ib^{p-i}}$ and as $p|\binom pi$ for all $i$ such that $0 < i < p$ we then get $(a+b)^p = a^p+b^p$.
+Choose $n\in\mathbb N$ and suppose that for all $k < n$ that $$(a+b)^{p^k} = (a+b)^{p\cdot p^k} = \left((a+b)^p\right)^{p^{k-1}} = (a^p+b^p)^{p^{k-1}} = a^{p\cdot p^{k-1}}+b^{p\cdot p^{k-1}} = a^{p^n}+b^{p^n}$$
+
+\subsubsection{Question 9}
+\question{(a)}
+First $$\varphi(ab) = (ab)^p = a^pb^p = \varphi(a)\varphi(b)$$ Second, using the result from our previous problem $$\varphi(a+b) = (a+b)^p = a^p+b^p = \varphi(a) + \varphi(b)$$ Finally if $\varphi(a) = \varphi(b)$ then $a^p = b^p$, $b = a+c$ for some $c \in F$, so $a^p=(a+c)^p = a^p+c^p$ and therefore $c^p = 0$, and as $F$ is a field, $c^p = 0 \implies c = 0$.
+From this we have $b=a+0$ so $b=a$.
+
+If you do not believe that $c^p = 0 \implies c = 0$ then suppose $c\not=0$ let  $n$ be such that $c^n = 0$ and for all $0< m < n$, $c^m \not = 0$, that is $n$ is the lowest power $c$ that is zero.
+Now consider these statements $$c(c^{n-1}c^{1-n}) = c1 = c$$ $$(cc^{n-1})c^{1-n} = 0c^{1-n} = 0$$ and now we have a contradiction, so $c^n\not=0$ and thus all powers of non zero elements of fields are non zero.
+
+\question{(b)} Consider $\mathbb Z_p$ and we have a finite field.
+From this we can construct the field of quotients over $\mathbb Z_p[x]$, and let us call this field $K$.
+For any $\frac{f(x)}{g(x)} \in K$ we have $p\frac{f(x)}{g(x)} = 0$ as $pf(x) = p\sumfrom{i=0}{\infty}{f_ix^i} = \sumfrom{i=0}{\infty}{pf_ix^i} = 0$.
+Now there is so $\frac{f(x)}{g(x)}$ such that $\varphi\left(\frac{f(x)}{g(x)}\right)=x$ as $\varphi\left(\frac{f(x)}{g(x)} \right)=\frac{f(\varphi(x))}{g(\varphi(x))}=\frac{f(x^p)}{g(x^p)}$ so the numerator's order will be $p\cdot \deg f(x)$ and the denominator's will be $p\cdot \deg g(x)$.
+Only if $g(x^p)|f(x^p)$ then can we reduce this to a polynomial and in that case we will have something of order $p\cdot \deg f(x) - p\cdot \deg g(x) = p(\deg f(x) - \deg g(x))\not = 1$.
+
+\subsubsection{Question 10}
+If $f:A\to A$ is 1-1 and $A$ is finite then $f$ must be onto, therefore we have $F$ is finite and $\varphi:F\to F$ is 1-1 so $\varphi$ must be onto and thus a n automorphism as we already know it to be a monomorphism.
+
+\subsection{Section 2}
+\subsubsection{Question 2}
+Only the trivial solution exists. I proved this by brute force checking all 125 possible solutions, and only the trivial one worked.
+
+\subsubsection{Question 3}
+If $V$ has dimension $n$ over $\mathbb Z_p$ then choose a basis $a_1, a_2, \ldots, a_n\in V$.
+Then any element of $V$ has a unique representation as $\sumfrom{i=1}n{\alpha_ia_i}$ with every $\alpha_i\in\mathbb Z_p$.
+This gives us a bijection $f:V\to{\mathbb Z_p}^n$ as $f(\sumfrom{i=1}n{\alpha_ia_i}) = (a_1, a_2, \ldots, a_n)$ and this we know has $p^n$ possible distinct values.
+
+\subsubsection{Question 6}
+
+\question{(a)}
+Assume there is some set of linearly independent vectors in $W$, therefore this set is also linearly independent in $V$.
+So by theorem 5.2.7 if $W$ were to have dimension greater than $V$'s dimension, it would imply that it has a set $S$ of linearly independent vectors with $\card S > \dim_F(V)$.
+Now $S$ is also linearly independent in $V$ which gives us a contradiction by theorem 5.2.6.
+
+If $\dim_F(W) = \dim_F(V) = n$ then we can choose some basis for $W$ with $n$ elements.
+This is then linearly independent in $W$ and thus also linearly independent in $V$ and forms a basis by theorem 5.2.7.
+
+\subsubsection{Question 10}
+I assume a vector space homomorphism $\psi$ must follow $\psi(a+b) = \psi(a)+\psi(b)$ and $\alpha\psi(a) = \psi(\alpha a)$.
+If we view $V$ and $V'$ as groups under addition then by one of our homomorphism theorems from groups we already have $V'\simeq V/K$, So that means that there is a group isomorphism from $V'$ to $V/K$, let us call it $\phi$.
+All we need to do is show that $\alpha \phi(a) = \phi(\alpha a)$.
+Let $a \in V'$ and then consider $\setbuilder{v\in V}{\psi(v) = a} = \inv\psi(a) \in V/K$.
+Remember $\psi:V\to V'$ is a vector space homomorphism.
+Let us try and construct $\phi$ as $\phi = \inv\psi$.
+We should already have this to be a group isomorphism so let us simply consider scaler multiplication.
+\begin{align*}
+\alpha\phi(a) &= \alpha\inv\psi(a)\\
+& = \alpha\setbuilder{v \in V}{\psi(v) = a}\\ &= \setbuilder{\alpha v}{v\in V, \psi(v) = a}
+\end{align*} Then we would have $\psi(v) = a \implies \psi(\alpha v) = \alpha a$ so $\alpha\phi(a) = \setbuilder{v\in V}{\psi(v) = \alpha a} = \inv\psi(\alpha a)= \phi(\alpha a)$ and we have shown $\phi$ to be a vector space isomorphism.
+
+\subsubsection{Question 11}
+Let us proceed with a proof by contradiction.
+Suppose there is some finite dimensional vector space $V$ over $F$ with a linearly independent set of vectors $v_1,v_2,\ldots, v_n$ and $\dim_F(v) > n$ such that we can not add another vector $v_{n+1}$ without breaking linear independence.
+This is impossible as $v_1,v_2,\ldots,v_n$ is not a basis as $\dim_F(v)>n$ so we can find some $v$ such that $v \not\in<v_1,v_2,\ldots,v_n>$ and let $v_{n+1} = v$ and this must maintain linear independence.
+Now going back to our problem, we may simply keep adding $v_{m+i}$ in this manner until we have a basis for $V$ over $F$.
+
+\subsubsection{Question 14}
+Consider the candidate basis $\eqclass 1, \eqclass x, \eqclass{x^2}, \ldots, \eqclass{x^{\deg f(x) - 1}}$.
+There are quite obviously $\deg f(x)$ elements in this so all that remains is to show it is a basis.
+For any $g(x) \in F[x]$, we know $[g(x)] = [h(x)]$ for some $h(x)$ with $\deg h(x) < \deg f(x)$ by the division algorithm, so this supposed basis can generate all of $F[x]/J$.
+Now if one were to remove $\eqclass {x^i}$ then there would be no way ever get element of $\eqclass{x^i}$ (with the exception of 0) as they all have order $i$ and when we add together functions we simply take the max of their orders, and we aren't allowed multiplication so we can't ever get anything with order $x^i$ or even with a non-zero $i^{\text{th}}$ coefficient.
+
+\subsubsection{Question 17}
+\question{(a)} Because $\dim_F(K) = m$ then there is a basis $k_1,k_2,\ldots,k_m$ of $K$ over $F$ and thus any element of $K$ can be represented as $ \sumfrom{i=0}{m}{\alpha_ik_i}$ with $\alpha_i \in F$ for all $i$.
+Now if $V$ is a vector space over $K$ then there is some basis that may or may not be finite for $V$ over $K$, let us denote this basis as the set $S$.
+Now any element of $V$ may be represented as $\sumacross{v \in S}{h_vv}$ with $h_v \in K$ for all $v\in S$.
+as $h_v \in K$ we may then say $h_v = \sumfrom{i=0}{m}{\alpha_{v,i}k_i}$ and therefore $$\sumacross{v\in S}{h_vv} = \sumacross{v\in S}{\sumfrom{i=0}{m}{\alpha_{v,i}k_i}v}$$ and $k_iv \in V$ and $\alpha{v,i}\in F$ so then $V$ must be a vector space over $F$.
+
+\question{(b)} If $V$ is finite dimensional over $K$ then using the equation we have already laid out becomes a finite sum and thus $\dim_F(V)$ must be finite.
+
+\question{(c)} In-fact, going a step further, $\setbuilder{k_iv}{v \in S, 0< i\le m}$ is a basis for $V$.
+To show this all we need it show linear independence.
+We know all the $v$ are linearly independent over $K$ and all the $k_i$ are linearly independent over $F$.
+Assume they are not linearly independent, it follows then that there is some non-trivial solution to $$\sumacross{v\in S}{\sumfrom{i=0}{m}{\alpha_{v,i}k_i}v} = 0$$ so there is some set $\alpha{v,i}$ that are not 0.
+From this we then say that if $\alpha_{w,j}$ is not zero then we get $\sumfrom{i=0}{m}{\alpha_{w,i}k_i}\not = 0\in K$ by the $k_i$s forming a basis.
+From this we go another step and we realize that we have one $h_w \not = 0$ so again $\sumacross{v\in S}{h_vv}\not=0$.
+Now we have shown that if any coefficient is nonzero then so must the entire sum.
+
+From this if $S$ is finite then we have a basis of size $m\card S$ which is also $\dim_K(V)\dim_F(K) = \dim_F(V)$.
+
+\subsection{Section 3}
+\subsubsection{Question 1}
+\question{(a)} Let $a = \sqrt 2 + \sqrt 3$, then $a^2 = 5+2\sqrt{6}$ and $a^4 = 31+10\sqrt 6$. so $a^4-5a^2 = 6$ and therefore $a^4-5a^2-a = 0$.
+
+\question{(b)} Consider $\sqrt 7^2-7 = 0$ and $\sqrt[3]{12}^3-12 = 0$ so both $\sqrt 7$ and $\sqrt[3]{12}$ are algebraic, and we know algebraic numbers are a field in $\mathbb C$ so their sum must be algebraic.
+
+\question{(c)} $2$ is algebraic as $2^2-2\cdot2^1 = 0$ and $i$ is algebraic as $i^2+1 = 0$ and $\sqrt 3$ is algebraic as $\sqrt 3^2-3 = 0$ so again as the algebraic numbers are a field in $\mathbb C$ then $2+i\sqrt 3$ must be algebraic.
+
+\question{(d)} $\cos(2\pi/k)+i\sin(2\pi/k) = e^{i2\pi/k} = a$ is algebraic when $k$ is a positive integer as $\left(e^{i2\pi/k}\right)^k = e^{i2\pi} = 1$ so $a^k - 1 = 0$.
+
+\subsubsection{Question 4}
+First we have $\cos(2\pi/8)+i\sin(2\pi/8)=e^{i2\pi/8}=e^{i\pi/4}$, so now consider $\left(e^{i\pi/4}\right)^4 = e^{i\pi} = -1$ so if $f(x) = x^4+1$ then $f(e^{i\pi/4}) = 0$, so the degree can be no greater than 4.
+Now $f(x+1) = (x+1)^4 + 1 = x^4+4x^3+6x^2+4x+2$ therefore is irreducible by Einstein criterion.
+From this we get there are no $g(x)q(x) = f(x)$ with $\deg q(x) > 0$.
+Now let $g(x)\not=0$ such that $g(e^{i\pi/4}) = 0$ with $g(x)$ being a minimal nontrivial polynomial with $g(e^{i\pi/4}) = 0$, we then would find by the division algorithm that $g(x)q(x)+r(x) = f(x)$ for some $q(x), r(x)$ with $\deg r(x) < g(x)$.
+Well then we would have $g(e^{i\pi/4})q(e^{i\pi/4}) +r(e^{i\pi/4}) = f(e^{i\pi/4}) = 0$ and as we assumed $g(e^{i\pi/4}) = 0$ then we have $0q(e^{i\pi/4})+r(e^{i\pi/4}) = f(e^{i\pi/4}) = 0$ so $r(e^{i\pi/4}) = 0$ and we know $\deg r(x) <\deg g(x)$ and due to $g(x)$ being minimal then it must be that $r(x) = 0$.
+From this we find $g(x)q(x) = f(x)$ and as $f(x)$ is irreducible then $\deg g(x) =\deg f(x)$.
+Thus $e^{i\pi/4}$ is of degree 4.
+
+\subsubsection{Question 6}
+Let us start with $$e=\sumfrom{i=0}\infty{\frac 1{n!}}$$ and assume for the sake of contradiction that $e \in \mathbb Q$, so $e=\frac ab$ with $a,b\in\mathbb Z$ and $b\not=0$.
+Now suppose $$x = b!\left(e-\sumfrom{n=0}{b}{\frac 1{n!}}\right)$$ and we get two immediate results about $x$.
+First as $e=\frac ab$ we have $$x=b!\left(\frac ab-\sumfrom{n=0}{b}{\frac 1{n!}}\right) = a(b-1)!-\sumfrom{n=0}{b}{\frac{b!}{n!}}$$ and as $b>n$ for all $n$ in the sum then we get $x$ is an integer.
+Our second result is from $e = \sumfrom{n=0}\infty{\frac 1{n!}}$ where we get $$x=b!\left(\sumfrom{n=0}{\infty}{\frac{1}{n!}}-\sumfrom{n=0}b{\frac1{n!}}\right) = b!\sumfrom{n=b+1}\infty{\frac 1{n!}} > 0$$ so $x$ must be a positive integer.
+Now consider $n\ge b+1$ and we would find $$\frac{n!}{b!} = \prodfrom{k=b+1}nk \ge \prodfrom{k=b+1}n{b+1} = (b+1)^{n-b}$$ and therefore $$\frac{b!}{n!}\le \frac{1}{(b+1)^{n-b}}$$ for any $n \ge b+1$, and further note that if $n \ge b+2$ then $\frac{b!}{n!} < \frac{1}{(b+1)^{n-b}}$.
+From this we now look again at $x$ and we find $$x = b!\sumfrom{n=b+1}{\infty}{\frac 1{n!}} = \sumfrom{n=b+1}{\infty}{\frac{b!}{n!}} < \sumfrom{n=b+1}{\infty}{\frac{1}{(b+1)^{n-b}}} = \sumfrom{n=1}\infty{(b+1)^n} = \frac 1b \le 1$$ So we find our selves with $x\in Z$ and $0<x<1$ so we have ourselves a contradiction and thus $e\not\in\mathbb Q$.
+
+\subsubsection{Question 10}
+Consider first that $1^\circ = \frac{\pi}{180}$ and therefore $\cos(1^\circ)+i\sin(1^\circ) $ is algebraic due to Question 1 part (d) of this section.
+Now $\cos(1^\circ)+i\sin(1^\circ)\not=0$ so $\left(\cos(1^\circ)+i\sin(1^\circ)\right)^{-1}$ must be algebraic.
+We find by De Moivre's theorem that $\left(\cos(1^\circ)+i\sin(1^\circ)\right)^{-1} = \cos(-1^\circ)+i\sin(-1^\circ)$.
+Now from basic trigonometry we have $\cos(-x) = \cos(x)$ and $\sin(-x) = -\sin(x)$ so we therefore have $\cos(-1^\circ)+i\sin(-1^\circ) = \cos(1^\circ) -i\sin(1^\circ)$.
+Now we can take the sum of these two algebraic numbers and have $$\left(\cos(1^\circ)+i\sin(1^\circ)\right)+\left(\cos(1^\circ)-i\sin(1^\circ)\right) = 2\cos(1^\circ)$$ must be algebraic.
+Now from here we multiply by $\frac 12$ which is trivially algebraic and get $\cos(1^\circ)$ which must be algebraic.
+
+\subsubsection{Question 13}
+$K$ forms a vector space over $F$, with $\dim_F(K) = n$.
+This means there is a basis $b_1,b_2,\ldots,b_n$ for $K$ over $F$, and each element of $K$ has a unique representation as $\sumfrom{k=0}{n}{\alpha_k b_k}$ with each $\alpha_k \in F$.
+So then simply by specifying a sequence of $n$ elements of $F$ we get a unique representation of a value in $K$ so if $\card F = q$ is finite then $\card K = q^n$.
+
+\subsubsection{Question 14}
+
+If $F$ is a finite field then $F$ has a nonzero finite characteristic, $p$.
+We know then that $p$ is prime, so we can construct a subfield of $F$ isomorphic to $\mathbb Z_p$, by taking the 1 element and then including any number that is formed by simply adding 1 to itself repeatedly.
+We can call $1+1 = 2$ and $1+1+1 = 3$ and so on up till $p$ at which point we have $1+1+\ldots+1 = 0$ because $F$ has characteristic $p$.
+Now that we have this subfield we know that $F$ can be viewed of as a vector space over this subfield we generated and therefore by the problem above we know that $\card F = p^n$ for some $n$.
+
+\subsection{Section 4}
+\subsubsection{Question 1}
+Without much work one find $a^2 = 5-2\sqrt3\sqrt2$ and $a^4=49-\sqrt3\sqrt2$ so if $f(x) = x^4-x^2-44$ then $f(a) = 0$.
+
+\subsubsection{Question 3}
+Consider $K_0 = \mathbb Q(\sqrt 2)$ and we get that $[k_0:\mathbb Q] = 2$, then we can construct $K_1 = K_0(\sqrt 5)$ and $K_2 = K_1(\sqrt 7)$ and finally $K_3=K_2(\sqrt{11})$.
+It follows then that $[K_4:\mathbb Q] = [K_4:K_3][K_3:K_2][K_2:K_1][K_1:K_0][K_0:\mathbb Q]$ from the corollary to theorem 5.4.1 in the book.
+Each one of $[K_i:K_{i-1}]\le 2$ so $[K_4:\mathbb Q] \le 2^4$ now we go one step further and realize $p(x) \in K_4[x]$ so for any $a$ such that $p(a) = 0$ then $[K_4(a):K_4 \le \deg p(x) = 5$ and thus $[K_4(a):\mathbb Q] \le 2^4\cdot5=80$.
+This tells us $a$ is an algebraic number of degree no greater than 80.
+
+\subsubsection{Question 5}
+Well we know $[K:T]$ is some positive integer, lets call it $k$ and therefore if we let $h = [T:F]$ we have $h$ also being a positive integer such that $hk = 2^n$.
+From this it follows that both $h$ and $k$ are smaller powers of 2 then $2^n$.
+
+\subsubsection{Question 6}
+
+Consider $a = \sqrt[3]{2}$ and $b = 1+\sqrt3i$.
+Now $a$ is quite obviously of degree 3.
+For $b$ we have $b^2 = 1-3+2\sqrt3i  = -2+2\sqrt3i$, therefore $b^2-2b=-4$ and so we can see that $b$ is degree 2.
+When we multiply together we get $ab=\sqrt[3]2\left(1+\sqrt3i\right)$.
+Let us now consider $$(ab)^3 = 2\left(1+3\sqrt3i-9-3\sqrt3i\right) = -16$$ and therefore $ab$ is algebraic of degree no greater than 3.
+
+\subsection{Section 5}
+\subsubsection{Question 2}
+Consider $f(x) = x^3-3x-1$.
+Suppose that it is reducible, if that is so then it would reduce into $(x^2+ax+b)(x+c) = f(x)$ and therefore $$x^3+(c+a)x^2+(ac+b)x+bc=x^3-3x-1$$ so $c+a=0$, $ac+b=-3$, and $bc = -1$.
+It follows from this that $a=-c$ and $c=-\inv b$ so $-c^2-\inv c = -3$ or $c^2+\inv c = 3$ and we know $c\not=0$.
+Consider $c = \frac pq$ with $q > 0$ and $\gcd(p,q) = 1$, we then have $\frac{p^2}{q^2}+\frac qp = 3$, so we know $$p^3+q^3=3pq^2$$.
+Now if we divide by $q$ and rearrange a bit we get $\frac{p^3}q = 3pq-q^2$ so $q|p^3$ and therefore as $\gcd(p,q)=1$, we have $q=1$.
+We also can divide through by $p$ and rearrange and get $\frac{q^3}{p}=3q^2-p^2$ so $p|q^3$ and again as $\gcd(p,q) =  1$ we have $p=1$.
+Now we go back and see that $p^3+q^3=2\not=3=3pq^2$ so we have a contradiction.
+Therefore $f(x)$ is irreducible in $\mathbb Q$.
+
+\subsubsection{Question 3}
+Drawing diagrams is hard in \latex so I will assume one is looking at the diagram in the book that the question is referring to.
+Consider first $\angle AEB$, which is known to be a right angle.\footnote{I do not know what the theorem that states this is called but I didn't think it relevant to prove here.} Now we will use the Pythagorean theorem to come up with a few equivalences.
+Now by our construction $a$ is the length of $AD$ and $DB$ is our unit.
+Let $p$ be the length $AE$, let $q$ be the length of $EB$, and let $h$ be the length of $ED$.
+Now using the Pythagorean theorem we get
+\begin{align*}
+p^2 &= a^2 + h^2\\
+q^2 &= 1^2 + h^2 \\
+(a+1)^2&= p^2 + q^2
+\end{align*}
+and therefore we can do some substitution and find $$a^2+h^2+1^2+h^2=(a+1)^2=a^2+2a+1$$ and we can simplify to having $h^2=a$ so therefore $h=\sqrt a$.
+
+\subsubsection{Question 4}
+Every angle in the regular heptagon will be be $\frac 57\pi$, so for a regular heptagon to be constructible we would need $\frac 57\pi$ to be a constructible angle.
+If we could construct the angle $\frac 57\pi$ we would also be able to construct the angle $\pi-\frac57\pi=\frac27\pi$.
+If we can construct this angle then we can surely construct a right triangle with one angle $\frac27\pi$ and a hypotenuse of unit length.
+This gives us side lengths of $\cos\left(\frac27\pi\right)$ and $\sin\left(\frac27\pi\right)$ so both of these would need to be constructible numbers.
+From this we would then have $\left[\mathbb Q\left(\cos\left(\frac27\pi\right), \sin\left(\frac27\pi\right)\right):\mathbb Q\right] = 2^n$ for some $n$.
+Within $\mathbb Q\left(\cos\left(\frac27\pi\right), \sin\left(\frac27\pi\right)\right)$, $e^{i\frac27\pi} = \cos\left(\frac27\pi\right)+i\sin\left(\frac27\pi\right)$ would be of degree two so $\left[\mathbb Q\left(e^{i\frac27\pi}\right):\mathbb Q\left(\cos\left(\frac27\pi\right), \sin\left(\frac27\pi\right)\right)\right] = 2$ and therefore $\left[\mathbb Q\left(e^{i\frac27\pi}\right):\mathbb Q \right]=2^{n+1}$.
+However $e^{i\frac27\pi}$ is of degree 6 due to the polynomial $x^6+x^5+x^4+x^3+x^2+x^1+1$, which is irreducible and has $e^{i\frac27\pi}$ as a root.
+
+\subsection{Section 6}
+\subsubsection{Question 3}
+\def\LB{\left[}\def\RB{\right]}
+Notice that $p(x)(x-1) = x^5-1$.
+$x^5-1$ has as roots any number who's fifth power is 1 and therefore any number a integer multiple fifth of the way around the complex unit circle, so $e^{i\frac{2k}5\pi}$ for all $k\in\mathbb Z$ are roots of $p(x)$ with the exception of $1$ as that we get from the $x-1$.
+This leaves us with the other four possible values as the roots.
+These numbers are of degree 4 as $p(x)$ is irreducible and they are roots for it, so we then get $p(x) = \prodfrom{i=1}{4}{x-e^{i\frac{2i}5\pi}}$ so we have factorized it into 4 linear parts in $\mathbb Q\left(e^{i\frac{2k}5\pi}\right)$.
+
+\subsubsection{Question 4}
+
+Let us rewrite the coefficients of $q(x)$ so that $q(x) = a_0+a_1x+\cdots+a_{n-1}x^{n-1}+x^n$, this does not change the problem in any ways, simply changes the notation to be one that I prefer.
+To take things a step further let $a_n=1$ and then we have $$q(x)=\sumfrom{k=0}{n}{a_kx^k}$$ Now if this thing has a rational root, then it will take the form of $\frac st$ with $s,t$ relatively prime and $t>0$.
+So we then have $$q\left(\frac st\right)=\sumfrom{k=0}{n}{a_k\frac{s^k}{t^k}} = 0$$ We can multiply out and get $$t^nq\left(\frac st\right) = t^n\sumfrom{k=0}{n}{a_k\frac{s^k}{t^k}} = \sumfrom{k=0}{n}{a_ks^kt^{n-k}} = 0$$
+Now we isolate the first term and we have
+\begin{align*}
+\sumfrom{k=1}{n}{a_ks^kt^{n-K}}+a_0t^n &= 0\\
+\therefore s\sumfrom{k=1}{n}{a_ks^{k-1}t^{n-K}}& =-a_0t^n
+\end{align*}
+so $s|a_0t^n$ and as $\gcd(s,t) = 1$ hen $s|a_0$. We can also go the other direction when we isolate the last term of our sum and get
+\begin{align*}
+\sumfrom{k=0}{n-1}{a_ks^kt^{n-k}}+a_ns^n &= 0\\
+\therefore t\sumfrom{k=0}{n-1}{a_ks^kt^{n-1-k}}&=-a_ns^n
+\end{align*}
+so $t|a_ns^n$, however remember we said $a_n=1$ so then we have $t|s^n$ and as $\gcd(t,s) = 1$ then $t=1$.
+
+When we put this together we have $\frac st = s$ and $s|a_0$ which concludes the proof. Notice that I relabeled the coefficients so $a_0$ is the coefficient of $x^0$ in $q(x)$.
+
+\subsubsection{Question 7}
+
+See solution to Section 1, Question 8 of this chapter. The problems are identical.
+
+\subsubsection{Question 8}
+Notice that $x^m-x$ is of degree $m$ so it would be impossible for it to have more than $m$ roots in any field.
+Now we need to show that these roots form a field, under our specified conditions.
+They will be the subfield of a finite extension to $\mathbb Z_p$ so  $(a+b)^m = a^m+b^m$ for any $a,b$ in this field
+
+So first to show addition, assume $a,b$ are roots of our polynomial, then $$(a+b)^m -(a+b) = a^m+b^m-a-b=(a^m-a)+(b^m-b)=0+0=0$$
+$$(-a)^m-(-a) = -a^m+a=-(a^m-a) = -0=0$$ so we have the additive group.
+
+For the multiplicative rules we again assume $a,b$ are roots of our polynomial, then notice first that as $a$ and $b$ are roots that $a^m-a = 0$ so $a^m =a$ and the same for $b^m=b$, from this we get 
+$$(ab)^m-ab=a^mb^m-ab=ab-ab=0$$
+and if $a\not=0$ then $$\left(\inv a\right)^m-\inv a = a^{-m}-\inv a = \inv{\left(a^m\right)}-\inv a = \inv a -\inv a = 0$$ so we have multiplication done and thus a field.
+
+\subsubsection{Question 11}
+First we will denote $f(x) \in F[x]$ as $$f(x) = \sumfrom{n=0}{\infty}{f_nx^n}$$ with $a_n = 0$ for all $n > \deg f(x)$ and use this notation for any polynomial in $F[x]$.
+From this we also have $$\delta(f(x)) = \sumfrom{n=1}{\infty}{nf_nx^{n-1}} = \sumfrom{n=0}\infty{(n+1)f_{n+1}x^n}$$ and that $$f(x)g(x) = \sumfrom{n=0}{\infty}{\sumfrom{k=0}{n}{f_kg_{n-k}}x^n}$$
+
+\question{(a)} Here we have
+\begin{align*}
+\delta(f(x))+\delta(g(x))&=\sumfrom{n=1}{\infty}{nf_nx^{n-1}}+\sumfrom{n=1}{\infty}{ng_nx^{n-1}}\\
+	&= \sumfrom{n=1}{\infty}{n(f_n+g_n)x^{n-1}}\\
+	&=\delta(f(x)+g(x))
+\end{align*}
+
+\question{(b)} Now since we already have that $\delta(f(x))+\delta(g(x)) = \delta(f(x)+g(x))$ then it follows that we only need to show that this is true for functions in the form $ax^n$, as we can construct other polynomials as sums of these polynomials.
+Now if we let $f(x) = ax^n$ and $g(x)=bx^m$ then \begin{align*}
+\delta(f(x)g(x)) &= \delta(abx^{n+m})\\
+&= ab(n+m)x^{n+m-1}\\
+&= abnx^{n+m-1}+abmx^{n+m-1} \\
+&= nax^{n-1}bx^m + ax^nmbx^{m-1}\\
+&= \delta(f(x))g(x)+f(x)\delta(g(x))
+\end{align*}
+
+\subsubsection{Question 14}
+
+Assuming the result from problem 13 to be true, consider $\delta(x^m-x) = mx^{m-1}-1 = -1$, so $\delta(x^m-x)$ must be relatively prime to $x^m-x$ and therefore $x^m-x$ has no roots with multiplicity greater than 1.
+
+\def\LB{}\def \RB{}
+\subsubsection{Question 15}
+\question{(a)} Let $f(x)\in F[x]$ be irreducible and let $f(x)=\sumfrom{i=0}{n}{f_ix^i}$ with $n=\deg f(x)$.
+If $f(x)$ has a root with multiplicity then $f(x)$ and $\delta(f(x))$ share a divisor and as $\deg \delta(f(x)) < \deg f(x)$ and as $f(x)$ is irreducible then it must be that $\delta(f(x)) = 0$.
+We know that $f_n \not=0$ as otherwise $n\not=\deg f(x)$, and as $\delta(f(x)) = 0$ then $nf_n=0$.
+This means that $F$ must have multiplicity $p$, where $p$ is some prime divisor of $n$, as otherwise $nf_n\not=0$.
+
+\question{(b)} Now that we have established $\delta(f(x)) = 0$ and $F$ has characteristic $p$, we can show there is some $g(x)\in F[x]$ such that $f(x) = g(x^p)$.
+Now for any $\deg f(x)\ge k>0$, we have $kf_k = 0$ from $\delta(f(x)) = 0$ and therefore either $f_k = 0$ or $p|k$.
+This means we can rewrite $f(x)$ as $$f(x) = f_0+f_px^p+f_{2p}x^{2p}+\cdots+a_{kp}a^{kp}$$ with $kp = n$ and therefore if we let $g(x)=f_0+f_1x+f_2x^2+\cdots+f_{kp}a^k$ then we find $f(x) = g(x^p)$.
+
 \end{document}

### 2018-10-02 Topology/Paper/paper.tex
hi

@@
 The overview will mainly be focused on giving a thorough understanding of what topological graph theory is as well as to briefly cover the history of the field.
-In giving an overview of the field we will cover some of the basic concepts and definitions needed for the more rigorous part of the paper; as this may be confusing, all definitions will be provided in a glossary at the end.
+In giving an overview of the field we will cover some of the basic concepts and definitions needed for the more rigorous part of the paper.
 After the overview we will dive into Kuratowski's Theorem, We will go through and attempt to have an intuitive understanding of a Kuratowski's Theorem and it's proof.
@@
 
-\section{Planar Graphs}
+\section{Graph Theory Background}
+
+\subsection{Planer Graphs}
 
@@
   \node[main node] (1) {$A$};
-  \node[main node] (2) [below of=1] {$B$};
-  \node[main node] (3) [below right of=2] {$C$};
-  \node[main node] (4) [below right of=1] {$D$};
-
-  \path[every node/.style={font=\sffamily\small}]
-    (1) edge node {} (4)
-    	edge [bend right = 100]node {} (3)
-    (2) edge node {} (1)
-        edge node {} (4)
-    (3) edge node {} (2)
-    (4) edge node {} (3);
-\end{tikzpicture}
-\end{center}
-
-So if this \gls{graph} can be drawn without intersection, can any \gls{graph} be drawn without intersections? If some can and some can't how do we tell which can be drawn and which can not?
-
-\section{Kuratowski's Theorem}
-Kuratowski's theorem tell us exactly what \glspl{graph} can be drawn on a plane or sphere.
-We say either a plane or sphere as it turns out to be the same question.
-%TODO prove that drawing on plane and sphere is same question
-Now before we tackle the theorem let's lay down some terminology.
-
-\subsection{Terminology}
-
-\subsubsection{Terminology: face}
-
-Consider the following \gls{graph}.
-
-\begin{center}
-	\begin{tikzpicture}[auto, node distance=3cm, every loop/.style={},
-	thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries}]
-
-	  \node[main node] (1) {$A$};
-	  \node[main node] (2) [below left of=1] {$B$};
-	  \node[main node] (3) [below right of=1] {$C$};
-
-	  \path[every node/.style={font=\sffamily\small}]
-	  (1) edge node {} (2)
-		  edge node {} (3)
-	  (2) edge node {} (3);
-
-	\end{tikzpicture}
-\end{center}
-
-We say this \gls{graph} has two \glspl{face}.
-One \gls{face} is easy to see and contained within triangle $ABC$.
-The other \gls{face} is a bit harder to see, however it is all the space outside of the triangle $ABC$.
-We may call this second face the outer \gls{face} for this drawing of the \gls{graph}, however it is also possible to draw it such that the inner face may be the outer face.
-You can think of this as kind of turning the triangle inside out.
-
-A face only makes sense to talk about for a \gls{graph} that can be embedded in a certain space. For example the \gls{graph} $K_4$ may look like it has $5$ faces in the following drawing.
-
-\begin{center}
-	\begin{tikzpicture}[auto, node distance=3cm, every loop/.style={},
-	thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries}]
-
-	\node[main node] (1) {$A$};
-	\node[main node] (2) [below of=1] {$B$};
-	\node[main node] (3) [right of=2] {$C$};
+  \node[main node] (2) [above left of=1] {$B$};
+  \node[main node] (3) [below left of=1] {$C$};
   \node[main node] (4) [right of=1] {$D$};
@@
 \end{center}
-This would be wrong as a face assumes a drawing without \glspl{edge} intersecting. This can be rectified if the \gls{graph} can be drawn without intersection and thus we find this drawing.
+
+So if this \gls{graph} can be drawn without intersection, can any \gls{graph} be drawn without intersections?
+If some can and some can't how do we tell which can be drawn and which can not?
+The answer to this comes in Kuratowski's theorem, however before we can even state this theorem we need to build up a bit of terminology for graph theory.
+
+\subsection{Graph Drawing}
+A graph drawing is exactly what it sounds like.
+We've already seen drawings of graphs like the one for K\"oingsberg and two drawings of $k_4$, this means there may be multiple distinct drawings for the same graph.
+Now we don't need to be very worried about what defines a drawing, that won't be important to us.
+Simply think of it as the drawing.
+
+If a drawing has no edges intersecting it is said to be a plane drawing. If there exists such a drawing for a particular graph, then that graph is a planar graph.
+
+\subsection{Face}
+Faces are a bit of an odd property here as they fundamentally are actually properties only of plane drawings and not graphs themselves; however the number of faces, as we will see stays consistent between any plane drawing of a planar graph and as such the number of faces is a property that planar graphs have.
+
+A face is defined as a connected space that contains no edges or verticies and itself is bounded by edges and verticies.
+
+If you think back to high-school geometry and cubes you may recall that a each of the corners is a vertex, the lines connecting verticies are edges and the area between the edges are faces.
+In a graph we have verticies connected by edges and when we draw them there are empty areas enclosed by edges and verticies.
+For example the following would correspond with a cube
 \begin{center}
@@
 	\node[main node] (2) [below of=1] {$B$};
-	\node[main node] (3) [below right of=2] {$C$};
-	\node[main node] (4) [below right of=1] {$D$};
+	\node[main node] (3) [right of=1] {$C$};
+	\node[main node] (4) [right of=2] {$D$};
+	\node[main node] (5) [above left of=1] {$E$};
+	\node[main node] (6) [below left of=2] {$F$};
+	\node[main node] (7) [above right of=3] {$G$};
+	\node[main node] (8) [below right of=4] {$H$};
 
 	\path[every node/.style={font=\sffamily\small}]
-	(1) edge node {} (4)
-	edge [bend right = 100]node {} (3)
-	(2) edge node {} (1)
-	edge node {} (4)
-	(3) edge node {} (2)
-	(4) edge node {} (3);
+	(1) edge node {} (2)
+	edge node {} (3)
+	edge node {} (5)
+	(2) edge node {} (4)
+	edge node {} (6)
+	(3) edge node {} (4)
+	edge node {} (7)
+	(4) edge node {} (8)
+	(5) edge node {} (6)
+	edge node {} (7)
+	(6) edge node {} (8)
+	(7) edge node {} (8);
 	\end{tikzpicture}
 \end{center}
-This means there are actually $4$ \glspl{face} in $K_4$.
+Now we can imagine that if we look at the cube straight on maybe $ABDC$ would be the face we are looking at.
+So too we see the area enclosed in $ABDC$ is a face by the definition we gave.
+The same is true for $ABFE$, $ACGE$, $DBFH$, and $DCGH$, however that leaves us with only five faces on this cube.
+The last face must logically come from $EFHG$, however the area enclosed by that contains all the other edges and verticies, so it doesn't fit our definition.
+However we may notice that the infinite space outside $EFHG$ does not contain any verticies, and therefore we get a sixth face.
 
-\subsubsection{Terminology: contraction}
+Consider then the following very simple graph:
+\begin{center}
+	\begin{tikzpicture}[auto, node distance=3cm, every loop/.style={},
+	thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries}]
 
-Let us consider the following \gls{graph}.
+	\node[main node] (1) {$A$};
+	\node[main node] (2) [right of=1] {$B$};
+
+	\end{tikzpicture}
+\end{center}
+Now we still only have one face, however it doesn't have as nice a boundary as they did in the cube.
+However if we look at all of space excluding $A$ and $B$ then we still get a valid space by our definition.
+
+\subsection{Path}
+Now moving onto a more traditional graph property we have the concept of a path.
+A path is defined as a finite sequence of verticies with the property that each element of the sequence (excluding the last one) has an edge from it to the next element.
+For example consider the following graph.
+
+\begin{center}
+	\begin{tikzpicture}[auto, node distance=3cm, every loop/.style={},
+	thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries}]
+
+	\node[main node] (a) {$A$};
+	\node[main node] (b) [below left of=a] {$B$};
+	\node[main node] (c) [below right of=a] {$C$};
+	\node[main node] (d) [below of=b] {$D$};
+	\node[main node] (e) [below of=c] {$E$};
+	\node[main node] (f) [above of=a] {$F$};
+	\node[main node] (g) [above left of=b] {$G$};
+	\node[main node] (h) [above right of=c] {$H$};
+	\node[main node] (i) [below left of=d] {$I$};
+	\node[main node] (j) [below right of=e] {$J$};
+
+	\path[every node/.style={font=\sffamily\small}]
+	(a) edge node {} (b)
+	edge node {} (c)
+	edge node {} (f)
+	(b) edge node {} (d)
+	edge node {} (g)
+	(c) edge node {} (e)
+	edge node {} (h)
+	(d) edge node {} (i)
+	(e) edge node {} (j)
+	(f) edge node {} (g)
+	edge node {} (h)
+	(g) edge node {} (i)
+	(h) edge node {} (j)
+	(i) edge node {} (j);
+	\end{tikzpicture}
+\end{center}
+
+Now the sequence $BGF$ is a path as $B$ connects to $G$ and $G$ connects to $F$.
+The sequence $ABGFACEJHCABA$ is also a path, however $JEDI$ is not a path as $E$ has no edge to $D$.
+Notice that how we draw the graph has nothing to do with what is and is not a path.
+
+\subsection{Connected}
+A graph is said to be connected if for any pair of verticies, $\pair ab$ there is a path from $a$ to $b$. So if we consider the following graphs 
+\begin{center}
+	\begin{tikzpicture}[auto, node distance=3cm, every loop/.style={},
+	thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries}]
+
+	\node[main node] (1) {};
+	\node[main node] (2) [right of=1] {};
+	\node[main node] (3) [below of=1] {};
+	\node[main node] (4) [right of=3] {};
+
+	\path[every node/.style={font=\sffamily\small}]
+	(1)	edge node {} (3)
+	(4) edge node {} (1);
+	\end{tikzpicture}\quad\quad\quad
+	\begin{tikzpicture}[auto, node distance=3cm, every loop/.style={},
+	thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries}]
+
+	\node[main node] (1) {};
+	\node[main node] (2) [right of=1] {};
+	\node[main node] (3) [below of=1] {};
+	\node[main node] (4) [right of=3] {};
+
+	\path[every node/.style={font=\sffamily\small}]
+	(1)	edge node {} (3)
+	(2) edge node {} (3)
+	(4) edge node {} (1);
+	\end{tikzpicture}\quad\quad\quad
+	\begin{tikzpicture}[auto, node distance=3cm, every loop/.style={},
+	thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries}]
+
+	\node[main node] (1) {};
+	\node[main node] (2) [right of=1] {};
+	\node[main node] (3) [right of=2] {};
+	\node[main node] (4) [below of=1] {};
+	\node[main node] (5) [right of=4] {};
+	\node[main node] (6) [right of=5] {};
+
+	\path[every node/.style={font=\sffamily\small}]
+	(1)	edge node {} (5)
+	(2) edge node {} (4)
+	edge node {} (6)
+	(3) edge node {} (5);
+	\end{tikzpicture}
+\end{center}
+We find that only the graph in the middle is connected.
+For the graph on the right consider any vertex on the bottom, there is no path to the vertex above it.
+The graph on the left is has the upper right vertex isolated from the rest of the graph.
+
+Any graph, connected or not, can be broken into connected components.
+To do this we simply take a vertex and every other vertex connected to it and call that one component, and then repeat with a vertex not in that component.
+This sort of breaking apart is nice as often we will prove things about connected graphs that are true about all graphs.
+For example if all components of a graph are planar then the entire graph must be planar, this will be proven below and it allows us to only deal with connected graphs.
+
+\subsection{Contraction}
+This is not a property, but rather an operation or action that we preform on a graph. Let us consider the following \gls{graph}.
 
@@
 This operation is particularly important as we will prove that if a \gls{graph} is planar, then so is any \gls{graph} or \gls{multigraph} obtained by contracting an \gls{edge}.
-The proof for this will be provided.
-%TODO put refrence to proof for contraction of planar graph is planar
 
-\subsubsection{Terminology: subgraph}
-We can say that a \gls{graph} $A$ is a \gls{subgraph} of another \gls{graph} $B$, if all \glspl{vertex} in $A$ are also in $B$ and each \glspl{edge} in $A$ is also in $B$.
+\newpage
 
+\section{Kuratowski's Theorem}
+\begin{theorem}[Kuratowski's Theorem]
+	A graph $G$ is planar if and only if it does not contain any subgraph $H$ such that a some series of edge contractions on $H$ would produce $K_5$ or $K_{3,3}$.
+\end{theorem}
+
+Here $K_5$ refers to the complete graph on 5 verticies, and $K_{3,3}$ is the complete bipartite graph with three verticies in both partitions.
+Drawings of both theses graphs are below with ($K_5$ on left and $K_{3,3}$ on right).
+\begin{center}
+	\begin{tikzpicture}[auto, node distance=3cm, every loop/.style={},
+	thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries}]
+
+	\node[main node] (1) {};
+	\node[main node] (2) [below left of=1] {};
+	\node[main node] (3) [below right of=1] {};
+	\node[main node] (4) [below of=2] {};
+	\node[main node] (5) [below of=3] {};
+
+	\path[every node/.style={font=\sffamily\small}]
+	(1)	edge node {} (2)
+	edge node {} (3)
+	edge node {} (4)
+	edge node {} (5)
+	(2) edge node {} (3)
+	edge node {} (4)
+	edge node {} (5)
+	(3) edge node {} (4)
+	edge node {} (5)
+	(4) edge node {} (5);
+	\end{tikzpicture}
+	\begin{tikzpicture}[auto, node distance=3cm, every loop/.style={},
+	thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries}]
+
+	\node[main node] (1) {};
+	\node[main node] (2) [below of=1] {};
+	\node[main node] (3) [below of=2] {};
+	\node[main node] (4) [right of=1] {};
+	\node[main node] (5) [below of=4] {};
+	\node[main node] (6) [below of=5] {};
+
+	\path[every node/.style={font=\sffamily\small}]
+	(1)	edge node {} (4)
+	edge node {} (5)
+	edge node {} (6)
+	(2)	edge node {} (4)
+	edge node {} (5)
+	edge node {} (6)
+	(3)	edge node {} (4)
+	edge node {} (5)
+	edge node {} (6);
+	\end{tikzpicture}
+\end{center}
 \subsection{Groundwork}
-Here we would like to prove some lemmas that we would like to use while proving Kuratowski's theorem.
 
-Now for some extensions of Kuratowski's theorem
+Here we prove some lemmas that we will use while proving Kuratowski's theorem before getting into the meat of the theorem.
 
@@
 
-This is not needed for our proof of Kuratowski's theorem, however it does help to think about drawing graphs on planes sometimes as well as helping to think about extensions beyond Kuratowski's theorem.
+This means that we may freely interchange usage of a sphere with a plane; for our purposes they are the same.
+
+\begin{theorem}[Euler's equation for planar graphs]
+	Let the number of edges in the graph be $e$, the number of verticies by $v$ and the number of faces be $f$.
+\end{theorem}
 

### 2018-10-13 Topology/Paper/paper.tex
microcenter backup

@@
 \end{center}
-\subsection{Groundwork}
 
-Here we prove some lemmas that we will use while proving Kuratowski's theorem before getting into the meat of the theorem.
-
-\begin{theorem}[Spherical and Planar graphs are the same] \label{sphere=plane}
-	If and only if a \gls{graph} may be drawn on a plane with no \glspl{edge} intersection then it may be drawn on a sphere without self intersection.
-\end{theorem}
-
-Now this we won't actually prove as it's quite difficult to do so, however notice that the plane is homeomorphic to the punctured sphere.
-Now it seems intuitive that if you can draw a finite graph, or even multi-graph on a sphere then it would not have to cover every single point on the sphere.
-This means that we could puncture the sphere at one point and thus we have the plane.
-
-This means that we may freely interchange usage of a sphere with a plane; for our purposes they are the same.
-
-\begin{theorem}[Euler's equation for planar graphs]
-	Let the number of edges in the graph be $e$, the number of verticies by $v$ and the number of faces be $f$.
-\end{theorem}
+The basic sketch of the proof will be:
+\begin{enumerate}
+	\item Prove that $K_5$ and $K_3,3$ are not planar.
+	\item Prove that if if a graph $G$ is planar than any graph obtained through an edge contraction is also planar.
+	\item 
+\end{enumerate}
 

### 2019-04-10 Seminar/FinalPaper/Paper.tex

\documentclass{article}

\input{../../definitions}
\title{A Guided Tour to Turing Completeness}

\begin{document}
	\maketitle
	\begin{abstract}
		The common consensus within the mathematical and computational communities is that there are no models for computation that can do something a Turing machine can not. In this paper we look at different models of computation that are equally powerful to a Turing machine and ones that aren't as powerful in an attempt to find some of the fundamental building blocks that make something Turing complete.
	\end{abstract}

	\section{Introduction}
	In computer science we have an idea called Turing Completeness. In order to fully understand this we first need to examine what a Turing machine is. Our goal however isn't to just explain Turing Completeness, but rather to understand what the building blocks of a Turing complete system is, and in doing this we will want to explore multiple Turing Complete systems and some systems that are not quite Turing Complete in order explore their similarities and differences.

	\subsection{Terminology}
	Before we can get started we need to define the notion of a Language.

	Let $\Sigma$ be a finite set, we may call it our alphabet. We say $x$ is a character or $x$ is a symbol if $x \in \Sigma$.\footnote{symbol and character are used interchangeably in this paper and have the exact same meaning unless otherwise denoted.} A string on $\Sigma$ is defined as a finite sequence of symbols. Finally A language $L$ on $\Sigma$ is defined to be a set of strings.

	For notational reasons we write strings somewhat differently then we usually would a finite sequence. For example, let $\Sigma = \set{1,2,3}$, then $1123$ is the same as the finite sequence $(1,1,2,3)$. This can be confusing if for example $1123\in\Sigma$. To avoid this issue we will write $1123 = (1,1,2,3)$ and $\{1123\}$ is the string with just the single element $1123$. In this paper we will also never have a symbol that could lead to any ambiguity. It is also worth noting that the string with no elements exists. We will, unless otherwise stated, denote this with $\lambda$; this will also be called the empty string.

	Finally, if $s$ is a string we may refer to it's first character as $s_0$ and it's second as $s_1$ and so on. For the entirety of this paper all counting starts at $0$ as it is considered a natural number.\footnote{\url{https://www.cs.utexas.edu/users/EWD/transcriptions/EWD08xx/EWD831.html}}

	\section{Deterministic Finite Automata}
	The first machine we investigate is a Deterministic Finite Automata, or DFA for short. A DFA has a set of states, a set of instructions. One state must be a special start state and at least one state must be an acceptance state. Instructions have three parts: a symbol, a start state, and an end state. When the DFA is given a string it starts at it's start state, $q_0$. If there is an instruction that has $q_0$ as the start state and whatever the first character in the string is, then we go to the end state given in the instruction and start again with the first character of the string removed and starting in our new state. If there is no instruction then the DFA rejects the string.

	For example, if I am given the string $aab$ and my DFA has states $\set{q_0,q_1}$ with $q_0$ being the start state and $q_1$ being the only acceptance state. Additionally it has instructions:
	\begin{center}
		\begin{tabular}{c|c|c|c}
			\#&Start State & Character & End State\\
			\hline
			0&$q_0$ & $a$ & $q_0$ \\
			1&$q_0$ & $b$ & $q_1$ \\
			2&$q_1$ & $b$ & $q_1$ \\
		\end{tabular}
	\end{center}
	Then the DFA works as follows
	\begin{enumerate}
		\item Start at $q_0$ (the start state) with string $aab$. $a$ is the character so we use instruction 0 and go to state $q_0$.
		\item We now are at $q_0$ and we have the string $ab$ and we again go to $q_1$ by instruction 0.
		\item We now are at $q_0$ and we have the string $b$ and we now use instruction 1 to go to $q_1$.
		\item We now have an empty string, we are on state $q_1$ which is an acceptance state so this string is accepted.
	\end{enumerate}

	Every DFA defines a language. The language it defines is the set of strings that the DFA accepts. Any language that has a DFA is called a regular language. For example any finite language (a language with only finitely many strings) is regular as we may make a DFA that accepts every individual string in the language. The language $\set{\lambda, a, aa, aaa. \ldots}$ is regular as we will have only a single state $q_0$ that is both an acceptance state and the start state and the only instruction will be $q_0$ goes to $q_0$ when an $a$ is seen.

	There is a corresponding notation that actually makes all this quite easy, called regular expressions. There are two kinds of regular expression: there is the formal mathematical regular expression that we will explore momentarily, and the computer programming regular expression that is based of the former, however is far more complicated.

	We define a regular expression to be read as follows. You may have a single symbol $a$, this is a valid regular expression and represents the language containing only $a$. If $p$ and $q$ are regular expressions then $p$

	\begin{itemize}
	\item If $a$ is a symbol, then $a$ is a valid regular expression representing the language $\set{a}$. That is the language with only $a$ the string $a$.
	\item Recalling that $\lambda$ represents the empty string, $\lambda$ is a valid regular expression representing the language $\set{\lambda}$, that is the language with only the empty string.
	\item Let $p$ and $q$ be valid regular expressions with $p$ representing languages $P$ and $Q$ respectively. We say $(p)+(q)$ is a valid regular expression representing the language $P\union Q$.
	\item Let $p$ and $q$ be valid regular expressions with $p$ representing languages $P$ and $Q$ respectively. We say $(p)(q)$ is a valid regular expression. In order to define what it represents we will adopt the notation that for strings $a$ and $b$, $ab$ is a $a$ concatenated with $b$. Now the language defined by $(p)(q)$ will be $\setbuilder{ab}{a \in P \land b \in Q}$.
	\item Let $p$ be a valid regular expression representing language $P$. We say $(p)^*$ is a valid regular expression representing language $K$, which we define recursively as $K = \set{\lambda} \union \setbuilder{ab}{a\in K\land b\in P}$.
	\end{itemize}

	We now make it easier to write by taking out the necessity for all the parentheses by adding an order of operations.
	\begin{enumerate}
		\item The Kleene star: $a^*$
		\item Juxtaposition: $ab$
		\item Addition: $a+b$
	\end{enumerate}
	This means the DFA we gave as an example above, may also be represented as $a^*b^*$, why this is left to the reader as a fun exercise.

	\section{Push Down Automata}
	Now it's worth noting that many every day languages are regular. For example, telephone numbers or email addresses. However the language of all valid regular expressions is not itself regular. The reason for this is the matching of parentheses. Take a simpler example, the language $a^nb^n$. This would be the language $\set{\lambda, ab, aabb, aaabbb, \ldots}$. Now a regular expression has no idea of memory so this language must not be regular. Here we introduce a stack.

	A stack is an object that allows for two fundamental operations. Push and Pop. If we have a stack $S$ and we push $a$ onto $S$ then $a$ has been added to the top of $S$. When we Pop from $S$ whatever is on top of $S$ is removed and returned. This means to see what is at the bottom of a stack, or indeed how many items are in a stack, one must throw away all the items. This is a very limited form of memory, however with it we can now tackle problems like $a^nb^n$ or even the language of all valid regular expressions.

	We construct a Push Down Automata, or PDA for short, from a DFA. We add to our DFA a stack, and every instruction may be based on what is on top the stack and also may give us stack instructions. The stack instructions must be a finite list of pops or pushes. The stack starts out empty, and it may contains only symbols.

	This defines a new class of language, a Context Free Grammar. Now any Regular Language is a Context Free Grammar as the PDA could just ignore it's stack, however let us construct a PDA for $a^nb^n$ to show we can do something new. Let our state set be $\set{q_0, q_1,q_2,q_3}$ with $q_0$ and $q_3$ being acceptance states and $q_0$ the start state. We also allow $\lambda$ to represent what is read when the stack is empty, this will be important.
	\begin{center}
		\begin{tabular}{c|c|c|c|c|c}
			\#&Start State & Character & Top of Stack & End State &Stack Operations\\
			\hline
			0&$q_0$ & $a$ & $\lambda$ & $q_1$ & \\
			1&$q_1$ & $a$ & $\lambda$ & $q_1$ & $\textbf{Push}(a)$ \\  
			2&$q_1$ & $a$ & $a$ & $q_1$ & $\textbf{Push}(a)$ \\
			3&$q_1$ & $b$ & $\lambda$ & $q_3$ & \\
			4&$q_1$ & $b$ & $a$ & $q_2$ & $\textbf{Pop}$ \\
			5&$q_2$ & $b$ & $a$ & $q_2$ & $\textbf{Pop}$ \\
			6&$q_2$&$b$&$\lambda$&$q_3$&
		\end{tabular}
	\end{center}
	In order to test this let try out this machine on the string $aabb$.
	\begin{enumerate}
		\item We start with the string $aabb$ and at state $q_0$, and our stack is empty. As such we use instruction 0, and we simply go to state $q_1$.
		\item We are at state $q_1$ with an empty stack and string $abb$. We then follow instruction 1, staying at state $q_1$ and pushing an $a$ onto the stack.
		\item We now have the string $bb$, while at state $q_1$ and having stack $a$. Due to this we follow instruction 4, go to state $q_2$ and pop off the top of the stack.
		\item We now have the string $b$, with empty stack and at state $q_2$. We must now follow instruction 6 and go to state $q_3$. We have now gone through the string and have ended on an acceptance state.
	\end{enumerate}

	Now, Push Down Automata are much more powerful then a regular language. There is a lot that can be done with just a stack. For example, given a specific alphabet $\Sigma$, the language of all regular expressions on that alphabet has a push down automaton:
	\begin{center}
		\begin{tabular}{c|c|c|c|c|c}
			\#&Start State & Character & Top of Stack & End State &Stack Operations\\
			\hline
			0&$q_0$ & \verb|(| & $\lambda$ & $q_0$ & $\textbf{Push}(\verb|(|)$ \\

			1&$q_0$ & $\sigma \in \Sigma$ & $\lambda$ & $q_1$&\\ 
			2&$q_0$ & \verb|(| & \verb|(| & $q_0$&$\textbf{Push}(\verb|)|)$\\
			3&$q_0$ & $\sigma \in \Sigma$ & \verb|(| & $q_2$&\\
			4&$q_0$ & \verb|(| & \verb|)| & $q_0$ & $\textbf{Push}(\verb|)|)$ \\
			5&$q_0$ & $\sigma\in\Sigma$ & \verb|)| & $q_0$ & \\
			6&$q_1$ & + & $\lambda$ & $q_0$ & \\
			7&$q_1$ & $^*$ & $\lambda$ & $q_1$&\\
			8&$q_1$ & $\sigma \in \Sigma$ & $\lambda$ & $q_1$&\\
			9&$q_1$ & \verb|(| & $\lambda$ &$q_2$& $\textbf{Push}(\verb|(|)$ \\
			10&$q_2$ & + & \verb|(| & $q_0$& \\
			11&$q_2$ & $^*$ & \verb|(| & $q_2$&\\
			12&$q_2$ & $\sigma \in \Sigma$ & \verb|(| & $q_2$&\\
			13&$q_2$ & \verb|(| & \verb|(| &$q_2$& $\textbf{Push}(\verb|)|)$\\
			14&$q_2$ & \verb|)| & \verb|(| &$q_1$&$\textbf{Pop}$\\
			15&$q_2$ & + & \verb|)| & $q_0$& \\
			16&$q_2$ & $^*$ & \verb|)| & $q_2$&\\
			17&$q_2$ & $\sigma \in \Sigma$ & \verb|)| & $q_2$&\\
			18&$q_2$ & \verb|(| & \verb|)| &$q_2$& $\textbf{Push}(\verb|)|)$\\
			19&$q_2$ & \verb|)| & \verb|)| &$q_2$&$\textbf{Pop}$\\
			20&$q_0$ & $\lambda$ & $\lambda$ & $q_1$ &\\
			21&$q_0$ & $\lambda$ & \verb|(| & $q_2$&\\
			22&$q_0$ & $\lambda$ & \verb|)| & $q_2$&\\
			23&$q_1$&$\lambda$&$\lambda$&$q_1$&\\
			24&$q_2$&$\lambda$&\verb|(|&$q_2$&\\
			25&$q_2$&$\lambda$&\verb|)|&$q_2$&
		\end{tabular}
	\end{center}\footnote{Here where we expect the character lambda (instructions 20-25), we actually mean to use lambda as a symbol as it is needed in regular expressions, however when we say top of stack has a lambda, that is the stack is empty.}
	Where $q_0$ is the start state and $q_1$ is the only acceptance state.

	Now one might logically ask, what happens if we add another stack to this machine, or change it from a stack to a queue\footnote{A queue is like a stack, but symbols are added at the bottom instead of at the top.}. In either case we actually end up with something that is equivalent to a Turing machine.

	\section{Turing Machine}
	A Turing machine has a `tape' that is infinitely long in both directions. Each spot on the tape can either be empty, or may contain a symbol. We start out with the tape empty, except that the string that we operate on is written onto the tape. For example if we were operating on $abc$ then the tape would be $(\ldots,\lambda,\lambda,a,b,c,\lambda,\lambda,\ldots)$. The Turing machine has a head (much like a typewriter or 3D printer) which can move along the tape. The head starts at the beginning of the input string (in our example it would start at the spot with $a$). Now each machine has a set of states, much like before. The only difference with our states is that we do not have acceptance states, rather this a a single Halt state that ends the machine. To test for acceptance we print a response onto the tape and leave the head at the beginning of the response. Our instructions will be similar to before, with the components being: Start State, Character at Head, End State, Character to Write, Direction to Move. The start and end state are just like before, with the special condition that end state may be the special Halt. The character to read and write may be any character or an empty ($\lambda$). The direction to move may either be left, right, or stay; this will tell the head where to move on the tape. If at any point in the execution of the program, there is no instruction that is valid, halt immediately.

	Turing machines aren't simple and even their smaller examples can still be quite large. The special about a Turing machine is that it can validate nearly any language you can think of. The set of languages it can validate are called computable. Additionally the Turing Machine can do much more then that. It can give outputs that aren't just true or false. Simply by writing something the tape it can give any output at all. You can construct arithmetic on anything you have a way to represent within the Tape using a Turing Machine. This is most rigorously put in the Church Turing Theses

	\comment{
	\begin{center}
		\begin{tabular}{c|c|c|c|c|c}
			\#&Start State & Character at Head & End State & Character to Write & Direction to Move\\
			\hline
			0&$q_0$ & $\lambda$ & Halt & $a$ & Stay \\
			1&$q_0$ & $a$ & $q_1$ & $a$ & Right \\
			2&$q_1$ & $a$ & $q_1$ & $a$ & Right \\
			3&$q_1$ & $b$ & $q_2$ & $b$ & Right \\
			4&$q_2$ & $a$ & Halt & $\lambda$ & Stay \\
			5&$q_2$ & $b$ & $q_2$ & $b$ & Right \\
			6&$q_2$ & $c$ & $q_3$ & $c$ & Right \\
			7&$q_3$ & $a$ & Halt & $\lambda$ & Stay \\
			8&$q_3$ & $c$ & $q_3$ & $c$ & Right\\
			9&$q_3$ & $\lambda$ & $q_4$ & $a$ & Left \\
			10&$q_4$ & $a$ & $q_4$ & $a$ & Left \\
			11&$q_4$ & $b$ & $q_4$ & $b$ & Left \\
			12&$q_4$ & $c$ & $q_4$ & $c$ & Left \\
			13&$q_4$ & $\lambda$ & $q_5$ & $a$ & Left\\
			14&$q_5$ & $\lambda$ & $q_6$ & $c$ & Right\\
			15&$q_6$ & $a$ & $q_7$ & $a$ & Right \\
			16&$q_7$ & $a$ & $q_8$ & $\lambda$ & Right\\
			17&$q_8$ & $a$ & $q_9$ & $a$ & Right\\
			18&$q_9$ & $\lambda$ & $q_9$ &$\lambda$&Right\\
			19&$q_9$ & $b$ & $q_{10}$ & $\lambda$ & Right\\
			20&$q_9$ & $a$ & Halt & $\lambda$ & Stay\\
			21&$q_{10}$ & $a$ & Halt & $\lambda$& Stay\\
			22&$q_{10}$ & $b$ & $q_{10}$ & $b$& Right\\
			23&$q_{10}$ & $c$ & $q_{11}$ & $\lambda$& Left\\
			24&$q_{11}$ & $a$ & $q_{12}$ & $a$ & Left\\
			25&$q_{11}$ & $b$ & $q_{13}$ & $b$ & Left\\
			26&$q_{11}$ & $\lambda$ & $q_{11}$ & $\lambda$ & Left \\
			27&$q_{12}$ & $a$ & Halt & $\lambda$ & Stay \\
			28&$q_{12}$ & $\lambda$ & Halt & $\lambda$ & Stay \\
			29&$q_{12}$ & $c$ & $q_{15}$ & $\lambda$ & Right \\
			30&$q_{13}$ & $b$ & $q_{13}$ & $b$ & Left \\
			31&$q_{13}$ & $a$ & $q_{14}$ & $a$ & Left \\
			32&$q_{13}$ & $\lambda$ & $q_{13}$ & $\lambda$ & Left \\
		\end{tabular}
	\end{center}
}
	\begin{quote}
		``A function on the natural numbers is computable by a human being following an algorithm, ignoring resource limitations, if and only if it is computable by a Turing machine.'' \\
		----- Wikipedia
	\end{quote}

	This is saying that any algorithm you can do can be done by a Turing Machine. Now whats remarkable about this statement is that despite a lack of proof, it has been accepted nearly universally by academia. So far there has been no reason to doubt this. Here is where the term Turing Complete comes in.

	\begin{definition}
		A system is Turing Complete if it can simulate any Turing Machine.
	\end{definition}

	For example, the system called Turing Machine is Turing Complete (trivially so), however a specific Turing Machine may not be, as it can only do one task. There are however Universal Turing Machines that take in another Turing Machine (formated as a string in some way), followed by some input, and can simulate the Turing Machine on that input. These Universal Turing Machines are themselves also Turing Complete.

	\section{Other Turing Complete Systems}
	Turing Completeness is the highest level of computable power that a system can have, despite this Turing Complete systems pop up in games and other places by accident all the time. For example Magic the Gathering, a popular card game, can implement any Turing Machine with up to a certain number of states on a alphabet with a fairly small number of characters. There is a Universal Turing machine that fits within these requirements and as such Magic the Gathering is Turing Complete. We won't be looking at Magic's Turing Machine as it's convoluted and uninteresting, it simply is an example of how even in unexpected places Turing Completeness pops up. Another good example of this is C++, a programming language. C++ was by all means meant to be Turing Complete, and it is, however within C++ there is a system called Templates. This template system is not so much part of the executing code and is rather just things that are done as the code is turned from C++ into Computer readable binaries. This system is to help with some concepts like abstraction in C++, however it was found that Templates, completely by accident, were also Turing Complete. Rather than looking at these complicated examples, lets look at some simple systems that are Turing Complete.

	\subsection{Procedural Languages}
	Procedural (or Imperative) programming Languages are the most standard type of programming language. They tend to achieve Turing Completeness by the use of a few simple components

	\begin{itemize}
		\item \textbf{Steps} - A program's most basic feature is stepping through. First line 1 happens, then line 2, and so on. This is very similar how states work in a Turing Machine.
		\item \textbf{Variables} - Variables are a way of holding data that can be changed, this is like the tape in a Turing Machine. Notice it is different then the stack from a Push Down Automata as it can access any information without throwing out data.
		\item \textbf{Loops and Conditionals} - A loop allows one to keep doing the same steps over and over again. This way a program doesn't just run through each step and then end. A loop also must have some way to end on some condition. In it's most basic form these work by having a conditional `jump' statement. It's allows you to go to any line of code on some condition. If the steps in a program are like the Turing Machines' states, then these are like the instructions allowing us to go where we want based on what is in the tape (or variables in this case).
	\end{itemize}

	Common languages of this type are: Java, C++, C, JavaScript, Python, R, Assembly Languages, Fortran, Basic.

	\subsection{Functional Languages}
	Where procedural languages work by stepping through a program, functional languages are completely different. They simply use Recursion to recreate all the things that a Procedural language can do. The basic idea here is that we can get looping by using recursion, and we can also use recursion to create new data, so we don't need loops or variables. Each function call creates new constant values when it is called. We still have conditionals as we will need to have end conditions in our recursion. This is actually how the Templates in C++ get their Turing Completeness.

	Common languages of this type are: LISP (and it's descendent's), Haskell, F\#, and Mathematica.

	In reality many procedural languages support functional programming and vice versa. For example C++, JavaScript, Python and R can all be functional.

	\subsection{Other}

	There are other weirder and less common ways to achieve Turing Completeness that are actually used in programming languages. I would rather focus on simple systems that are Turing complete, however not programming languages. The simplest system that one can formalize and find to be Turing Complete are Cellular Automata. John Conway's Game of Life is the most famous and with only a few simple rules on an infinite 2-D board, the Game of Life is Turing Complete. Even more surprising is the Automata Rule 110. This Automata is much like Conway's Game of Life but on a 1-D board, and with even simpler rules.

	\section{Conclusion}
	Now we've seen some ways to create Turing Completeness and some methods that don't quite make it, it's hard to say what exactly is needed to get Turing Completeness, but there does seem to be some common themes. The ability to store data and act on any part of that data without having to throw out information seems to be the key. For example in a Push Down Automata with a Queue instead of a Stack, one can simply cycle through the stack as much as they need and find any of the data.\footnote{In the two stack system you can either simulate a queue or go straight to simulating a Turing Machine by treating one stack as the tape to the left of the head and the other stack as what the head is pointing to and everything to the right of that.} It's hard to say if this by itself is enough, and as far as I can tell, there is no formal way to tell if something is Turing Complete other than just implementing a Universal Turing machine in it, but this does seem like a good litmus test. It would be nice to look at more systems that are weaker than a Turing Machine in order to get more contrast.

\end{document}

### 2019-04-10 SchoolCode/Combinatorics/mapColoring.tex
added schollcode

\documentclass{article}

% stuff from the percent sign to end of line is a comment, ignored by LaTeX

\usepackage{amsmath,amssymb,graphicx,algpseudocode,algorithm} %load extra symbols and environments
\usepackage[margin=1in]{geometry} %set margins
\usepackage{mathrsfs}

\title{Map Coloring}
\author{Benji Altman}
\let\union\cup
\let\intersection\cap
\let\inter\intersection
\let\emptyset\varnothing
\def\Return{\State\textbf{return} }
\newcommand{\setcomp}[1]{{#1}^{\mathsf{c}}}
\newcommand{\biginter}[2]{\bigcap\limits_{#1} \left( {#2} \right)}
\reversemarginpar

\begin{document}
\maketitle

\section{Question}
Given a map consisting of $n$ circles, what is an upper bound for the number of colors needed to color in the map such that every space has it's own color and each adjacent space has a different color from it. Spaces touching at a finite number of points do not count, they must share an edge (thus infinite points). More specifically find a better upper bound then $n^2$.

\section{Ideas}
The solution to this that we are going to try and show that the upper bound is $2$. One may get an intuitive sense as to why this is true by letting the outside space be color $A$ and notice that only spaces which may be written in the form $\biginter{i\in(0,n]-\{k\}}{\setcomp{S_i}} \inter S_k$ so that it is the intersection of $1$ circle with the compliment of all the others. Then those will only be touching areas that are the intersection of all the copmliments and areas that are the interesction of $2$ circles and all the other copliments. This extends out no mater how the cirlces ae laid out. Though as I do not see how to prove this it is more of an intuitive idea then anything concrete.

Now let $\mathscr U$ is the set of all circles, then let $\mathcal I \subseteq \mathscr U$ and let $\mathcal O = \mathscr U \setminus \mathcal I$. Now if we are able to show that for any valid $\mathcal I$ we can have the space defined as $\left[\biginter{A \in \mathcal I}{A}\right] \inter \left[\biginter{A \in \mathcal O}{\setcomp A}\right]$ thus

\subsection{construction}
One can construct an algorithim to color any map of $n$ circles with only $2$ colors. This was found by Proffesor Guetter, although I will lay it out here. Start with a map only having $0$ circles, and color the entire universe with color $A$. Now start to add circles, each time you do invert\footnote{if the color is $A$ then make it $B$ and if the color is $B$ then make it $A$} the colors wherever that circle is. Continue adding circles like this until you have all $n$. This will result in 2 working colors, again a proof is beyond me.

\end{document}

### 2019-04-10 SchoolCode/Foundations/2.4.tex
added schollcode

\documentclass{article}

% stuff from the percent sign to end of line is a comment, ignored by LaTeX

\usepackage{amsmath,amssymb,graphicx,algpseudocode,algorithm} %load extra symbols and environments
\usepackage[margin=1in]{geometry} %set margins
\usepackage{mathrsfs}

\title{Foundations of Mathematics \\ Section 2.3}
\author{Benji Altman}
\let\union\cup
\let\inter\cap
\let\emptyset\varnothing
\let\bigunion\bigcup
\let\biginter\bigcap
\def\Return{\State\textbf{return} }
\newcommand{\setcomp}[1]{{#1}^{\mathsf{c}}}
\newcommand{\interacross}[2]{\biginter\limits_{#1} \left( {#2} \right)}
\newcommand{\unionacross}[2]{\bigunion\limits_{#1} \left( {#2} \right)}
\newcommand{\unionfrom}[3]{\bigunion\limits_{#1}^{#2} \left( {#3 } \right)}
\newcommand{\interfrom}[3]{\biginter\limits_{#1}^{#2} \left( {#3 } \right)}
\newcommand{\set}[1]{\left\{ {#1} \right\}}
\reversemarginpar

\begin{document}
\maketitle

Let\marginpar{\flushright3(a)} $\mathscr A$ be a family of sets and $B \in \mathscr A$, and $x \in \unionacross{A \in \mathscr A}{A}$ then $x \in A$ for at least one $A \in \mathscr A$. As $B \in \mathscr A$ then $\left(\forall x \in B\right) x\in\unionacross{A \in \mathscr A}{A}$, thus by definition of subset $B \subseteq \unionacross{A \in \mathscr A}A$.
\medskip

Let\marginpar{\flushright(b)} $A \subseteq B$ for all $A \in \mathscr A$ where $\mathscr A$ is a family of sets. Then we know that for any $x \in A \in \mathscr A$ that $x \in B$ thus by the definition of subset the set $S = \set{x : (\exists A \in \mathscr A) x \in A} \subseteq B$ and by definition $S = \unionacross{A \in \mathscr A}{A}$, thus $\unionacross{A \in \mathscr A}{A} \subseteq B$.
\bigskip

The largest set $X$ such that $X\subseteq A$ for all $A\in\mathscr A$ is $\interacross{B\in\mathscr A}B$\marginpar{\flushright11(a)}. This is shown by proving that both $\interacross{B\in\mathscr A}B \subseteq A$ for all $A\in \mathscr A$ and that if $V \subseteq A$ for all $A \in \mathscr A$ then $V \subseteq \interacross{B\in\mathscr A}B$.
\begin{enumerate}
\item By theorem 2.3.1(a) we know that $\interacross{B\in\mathscr A}B \subseteq A$ for all $A\in \mathscr A$.
\item By theorem 2.3.2(a) we know that  if $V \subseteq A$ for all $A \in \mathscr A$ then $V \subseteq \interacross{B\in\mathscr A}B$.
\end{enumerate}
Thus we have shown that $\interacross{A\in\mathscr A}A$ is the largest set for which it is a subset of all $A \in \mathscr A$.
\medskip

The smallest\marginpar{\flushright(b)} set $Y$ such that $A \subseteq Y$ for all $A \in \mathscr A$ is $\unionacross{B\in\mathscr A}B$. This is shown by proving that both $A \subseteq \unionacross{B\in\mathscr A}B$ for all $A \in \mathscr A$ and that if $A \subseteq W$ for all $A \in \mathscr A$ then $\unionacross{B\in\mathscr A}B \subseteq W$.
\begin{enumerate}
\item By theorem 2.3.1(b) we know that $A \subseteq \unionacross{B\in\mathscr A}B$ for all $A \in \mathscr A$.
\item By theorem 2.3.2(b) we know that  if $A \subseteq W$ for all $A \in \mathscr A$ then $\unionacross{B\in\mathscr A}B \subseteq W$.
\end{enumerate}
Thus we have shwon that $\unionacross{B\in\mathscr A}B$ is the smallest set for which it is a superset of all $A \in \mathscr A$.
\bigskip

Let \marginpar{\flushright12(a)}$\mathscr A = \set{ \set{1, 2, \ldots, 10 }, \set{11, 12, \ldots, 20, 1}}$
\medskip

Let \marginpar{\flushright(b)}$\mathscr B = \set{ \set{1, 2, \ldots, 17}, \set{18}, \set{19}, set{20} }$
\medskip

Let \marginpar{\flushright(c)}$\mathscr C = \set{ \set1, \set2, \ldots, \set{20} }$
\bigskip

First we know \marginpar{\flushright17(a)}that if $Q \subseteq W$, then $Q \inter W = Q$, and using this we will show by induction that for any $k \in \mathbb N$ that $\interfrom{i=1}k{A_i}=A_k$ given that for any pair $i\in\mathbb N$, $j\in\mathbb N$ where $i\le j$ then $A_j \subseteq A_i$.

For our base case we let $k=1$, and it is trivial to show that $\interfrom{i=1}1{A_i}=A_1$.

For our inductive case we assume that $\interfrom{i=1}{k}{A_i}=A_{k}$ and we intend to show that $\interfrom{i=1}{k+1}{A_i}=A_{k+1}$.
\begin{align*}
\interfrom{i=1}{k+1}{A_i} &= \interfrom{i=1}{k}{A_i} \inter A_{k+1} \\
&= A_k \inter A_{k+1} \\
&= A_{k+1}
\end{align*}
The last step,  $A_k \inter A_{k+1} = A_{k+1}$ is true due to our knowledge that $A_{k+1} \subseteq A_k$.

Thus by PMI we know that for any $k \in \mathbb N$ that $\interfrom{i=1}k{A_i}=A_k$ given that for any pair $i\in\mathbb N$, $j\in\mathbb N$ where $i\le j$ then $A_j \subseteq A_i$.
\medskip

We\marginpar{\flushright(b)} again will let $A_j \subseteq A_i$ for any pair $i\in\mathbb N$, and $j\in\mathbb N$ where $i\le j$, and again we will use mathematical induction, this time to show that $\unionfrom{i=1}\infty{A_i}=A_1$.

For our base case we show that $\unionfrom{i=1}1{A_i}=A_1$, which is trivial.

For our inductive case we assume $\unionfrom{i=1}k{A_i}=A_1$ and show that it holds for $\unionfrom{i=1}{k+1}{A_i}=A_1$.
\begin{align*}
\unionfrom{i=1}{k+1}{A_i} &= \unionfrom{i=1}k{A_i} \union A_{k+1} \\
&= A_1 \union A_{k+1}
\end{align*}
We know that $ A_1 \union A_{k+1}=A_1$ because $\forall (n \in \mathbb N) A_n \subseteq A_1$, thus $A_{k+1}\subseteq A_1$, and because $A_{k+1}$ is a subset of $A_1$ the union of the two is $A_1$ (there are no elements in $A_{k+1}$, not in $A_1$).

Thus by PMI we know that for any $k\in\mathbb N$, $\unionfrom{i=1}k{A_i}=A_1$, although this isn't what we were actually trying to prove. The question states the union up to $\infty$, although $A_i$ is only defined for when $i \in \mathbb N$, thus it doesn't make sense to include infinity in this range.
\end{document}

### 2019-04-10 SchoolCode/Foundations/3.1.tex
added schollcode

\documentclass{article}

% stuff from the percent sign to end of line is a comment, ignored by LaTeX

\usepackage{amsmath,amssymb,graphicx,algpseudocode,algorithm} %load extra symbols and environments
\usepackage[margin=1in]{geometry} %set margins
\usepackage{mathrsfs}

\title{Foundations of Mathematics \\ Section 3.1}
\author{Benji Altman}

\newcommand{\sectionheading}[1]{\noindent\textbf{#1}

}
\let\union\cup
\let\inter\cap
\let\emptyset\varnothing
\let\bigunion\bigcup
\let\biginter\bigcap
\let\composed\circ
\let\cross\times
\def\And{\textit{ and }}
\def\Or{\textit{ or }}
\def\Return{\State\textbf{return}\par}
\newcommand{\setcomp}[1]{{#1}^{\mathsf{c}}}
\newcommand{\prodfrom}[3]{\prod\limits_{#1}^{#2}\left( #3 \right)}
\newcommand{\sumfrom}[3]{\sum\limits_{#1}^{#2} \left( {#3} \right)}
\newcommand{\unionfrom}[3]{\bigunion\limits_{#1}^{#2} \left( {#3} \right)}
\newcommand{\interfrom}[3]{\biginter\limits_{#1}^{#2} \left( {#3} \right)}
\newcommand{\interacross}[2]{\interfrom{#1}{}{#2}}
\newcommand{\unionacross}[2]{\unionfrom{#1}{}{#2}}
\newcommand{\sumacross}[2]{\sumfrom{#1}{}{#2}}
\newcommand{\prodacross}[2]{\prodfrom{#1}{}{#2}}
\newcommand{\set}[1]{\left\{ {#1} \right\}}
\newcommand{\setbuilder}[2]{\set{#1 : #2}}
\newcommand{\derivative}[2]{\frac{d}{d{#2}}\left( {#1} \right)}
\newcommand{\Exists}[2]{\exists_{#1}\left( {#2} \right)}
\newcommand{\All}[2]{\forall_{#1}\left( #2 \right)}
\newcommand{\abs}[1]{\left|{#1}\right|}
\newcommand{\cardinality}[1]{\overline{\overline{#1}}}
\newcommand{\range}[1]{\textit{\textbf{Rng}}\left( #1 \right)}
\newcommand{\domain}[1]{\textit{\textbf{Dom}}\left( #1 \right)}
\newcommand{\pset}[1]{\mathscr P\left( #1 \right)}
\newcommand{\pair}[2]{\left( #1 , #2 \right)}

\begin{document}

\maketitle

\sectionheading{7}
Let $R=\set{\pair15,\pair22,(3,4),(5,2)}$, $S=\set{(2,4),(3,4),(3,1),(5,5)}$, and $T={(1,4),(3,5),(4,1)}$. Find

\smallskip
\sectionheading{(a)}
$R\composed S$
\[R\composed S = \set{(3,5),(5,2)}\]

\medskip
\sectionheading{(b)}
$R \composed T$
\[R\composed T = \set{(3,2),(4,5)}\]

\medskip
\sectionheading{(f)}
$T \composed T$
\[T\composed T = \set{(1,1)}\]

\medskip
\sectionheading{(g)}
$R \composed (S \composed T)$
\begin{align*}
S \composed T &= \set{(3,5)} \\
R\composed (S \composed T) &= \set{(3,2)}
\end{align*}

\bigskip
\sectionheading{11}
Let $R$ be a relation from $A$ to $B$ and $S$ be a relation from $B$ to $C$.

\smallskip
\sectionheading{(a)}
Prove that $\range{R^{-1}}=\domain{R}$

\begin{align*}
R^{-1} &= \setbuilder{(y,x)}{(x,y) \in R} \\
\range{R^{-1}} &= \setbuilder{x}{\Exists{y}{(y,x) \in R^{-1}}} \\
\domain{R} &= \setbuilder{x}{\Exists{y}{(x,y) \in R}}
\end{align*}

Let $v\in\range{R^{-1}}$, thus there exists some $y$ such that $(y,v) \in R^{-1}$, now let $w$ be one possible value for $y$. Now we know that $(w,v) \in R^{-1}$ so we also know that $(v,w) \in R$. We now can say $v \in \domain R$, and as that would be true for any $v\in\range{R^{-1}}$, we then know $\range{R^{-1}} \subseteq \domain R$.

Now let $v\in\domain R$, there must now be some $y$ such that $(v,y) \in R$ and we will now let $w$ represent one such value of $y$. Now we can say $(v,w) \in R$ which also means that $(w,v) \in R^{-1}$ and that $v \in \range{R^{-1}}$, and because this is true for any $v\in\domain R$, then $\domain R \subseteq \range{R^{-1}}$

Now we can finally say $\domain R = \range{R^{-1}}$.

\medskip
\sectionheading{(b)}
Prove that $\domain{S \composed R} \subseteq \domain R$.

\begin{align*}
S \composed R &= \setbuilder{(a,c)}{\Exists{b}{(a,b) \in R \And (b,c) \in S}} \\
\domain{S \composed R} &= \setbuilder{a}{\Exists{c}{(a,c) \in S \composed R}} \\
\domain{R} &= \setbuilder{a}{\Exists{b}{(a,b) \in R}}
\end{align*}

First let $x \in \domain{S \composed R}$, that means that there is some $c$ such that $(a,c) \in S \composed R$, we will let $y$ be one such value of $c$. Now that we know $(x,y) \in S \composed R$ we can say there is some $b$ such that $(x,b)\in R$, we will let $z$ be one such value of $b$. Now we notice that $(x,z) \in R$, which means that $x\in\domain{R}$, and because that could be any $x\in\domain{S\composed R}$ we know that $\domain{S\composed R} \subseteq \domain{R}$.

\medskip
\sectionheading{(c)}
Show by example that $\domain{S \circ R} = \domain{R}$ may be false.

\begin{align*}
R &= \set {(0,0)} \\
S &= \emptyset \\
S \composed R &= \emptyset \\
\domain R &= \set 0 \\
\domain{S \composed R} &= \emptyset \\
\domain{S\composed R} = \emptyset &\not= \set 0 = \domain R
\end{align*}

\bigskip
\sectionheading{12}
Complete the proof of Theorem 3.1.2 by proving that if $R$ is a relation from $A$ to $B$ and $S$ is a relation from $B$ to $C$, then

\smallskip
\sectionheading{(c)}
$(S \composed R)^{-1}=R^{-1} \composed S^{-1}$.

\begin{align*}
S \composed R &= \setbuilder{(a,c)}{\Exists{b}{(a,b) \in R \And (b,c) \in S}} \\
(S\composed R)^{-1} &= \setbuilder{(c,a)}{(a,c)\in S\composed R} \\
R^{-1} &= \setbuilder{(b,a)}{(a,b)\in R} \\
S^{-1} &= \setbuilder{(c,b)}{(b,c)\in S} \\
R^{-1} \composed S^{-1} &= \setbuilder{(c,a)}{\Exists{b}{(c,b)\in S^{-1} \And (b,a) \in R^{-1}}}
\end{align*}

First we will start by showing $(S\composed R)^{-1} \subseteq R^{-1}\composed S^{-1}$ and then we will show $(S\composed R)^{-1} \supseteq R^{-1}\composed S^{-1}$.

For our first step we let $(x,y) \in (S \composed R)^{-1}$, which means that $(y,x)\in S\composed R$. Now we can say there is some $b$ such that $(y,b) \in R$ and $(b,x) \in S$, we will let $z$ be a possible value for $b$, which means $(y,z) \in R$ and $(z,x) \in S$. Now we can say that $(z,y) \in R^{-1}$ and that $(x,z) \in S^{-1}$. Now we can show that $(x,y)\in R^{-1}\composed S^{-1}$, which means that $(S\composed R)^{-1} \subseteq R^{-1}\composed S^{-1}$

For our second step we will start by letting $(x,y) \in R^{-1}\composed S^{-1}$, using this we can say that there exists a $b$ such that $(x,b)\in S^{-1}$ and $(b,y)\in R^{-1}$, we will let $z$ be one such possible value of $b$. Now we have $(x,z)\in S^{-1}$ and $(z,x) \in R^{-1}$

\bigskip
\sectionheading{14}
Prove that if $A$ has $m$ elements and $B$ has $n$ elements, then there are $2^{mn}$ different relations from $A$ to $B$.

\smallskip

First let us notice that the maximal relation, one with every possible pair from $A$ to $B$ is $A \cross B$. Now we want to find how many possible subsets of $A\cross B$ there are, as any subset is a unique relation from $A$ to $B$, there may be no other possible relations that are not subsets of $A\cross B$ as $A\cross B$ has all ordered pairs $(a,b)$ where $a\in A$ and $b \in B$, and thus all relations must be subsets of $A\cross B$. Now to count how many subsets there are we simply must realize that any element may either be in a subset or not in a subset, then we are looking at two possibilities for each element in $A\cross B$. This translates to $2^{\cardinality{A\cross B}}$ different relations (this could also be looked at as $\cardinality{\pset{A\cross B}}$.) We now simply need to find how many elements there are in $A\cross B$ and here we use the multiplication rule and find $\cardinality{A\cross B} = \cardinality{A}\times\cardinality{B}$ which we know is $m\cdot n$. Thus the total number of possible relations from $A$ to $B$ is $2^{mn}$.

\bigskip
\sectionheading{15(a)}
Let $R$ be a relation from $A$ to $B$. For $a \in A$, define the \textbf{vertical section of $R$ at $a$} to be $V_a=\setbuilder{y\in B}{(a,y)\in R}$. Prove that $\unionacross{a\in A}{V_a}=\range{R}$.

Let \[y\in \unionacross{a\in A}{V_a}\]
then we can say
\begin{align*}
\Exists{x}{y\in V_x} &\implies \Exists{x}{(x,y)\in R}\\
&\implies y \in \range{R}\\
&\implies \unionacross{a\in A}{V_a} \subseteq \range{R}
\end{align*}
Now let \[y \in \range{R}\]
then we can say
\begin{align*}
\Exists{x}{(x,y)} \in R &\implies \Exists{x}{y\in V_x} \\
&\implies y\in\unionacross{a\in A}{V_a}\\
&\implies \range{R} \subseteq \unionacross{a\in A}{V_a}
\end{align*}
Now we have shown
\[\range{R} = \unionacross{a\in A}{V_a}\]

\medskip
\sectionheading{(b)}
Let $R$ be a relation from $A$ to $B$. For $b \in B$, define the \textbf{horizontal section of $R$ at $b$} to be $H_b=\setbuilder{x\in A}{(x,b)\in R}$. Prove that $\unionacross{b\in B}{H_b}=\domain{R}$.

\end{document}

### 2019-04-10 SchoolCode/Topology/MidTerm.tex
added schollcode

--- 2018-01-28 Topology/Midterm/Midterm.tex
@@
 \documentclass{article}
-\input{../../definitions.tex}
-\input{../topology.tex}
+
+\usepackage{amsmath,amssymb,graphicx,algpseudocode,algorithm}
+\usepackage[margin=1in]{geometry}
+\usepackage{mathrsfs}
+\let\mathcrl\mathscr
+\usepackage[mathscr]{euscript}
 
 \title{Topology Midterm}
+\author{Benji Altman}
+
+\reversemarginpar
+\newcommand{\question}[1]{\marginpar{\flushright {#1}}}
+\let\union\cup
+\let\inter\cap
+\let\emptyset\varnothing
+\let\bigunion\bigcup
+\let\biginter\bigcap
+\let\composed\circ
+\let\cross\times
+\def\And{\textit{ and }}
+\def\Or{\textit{ or }}
+\def\Return{\State\textbf{return}\par}
+\newcommand{\setcomp}[1]{{#1}^{\mathsf{c}}}
+\newcommand{\prodfrom}[3]{\prod\limits_{#1}^{#2}\left( #3 \right)}
+\newcommand{\sumfrom}[3]{\sum\limits_{#1}^{#2} \left( {#3} \right)}
+\newcommand{\unionfrom}[3]{\bigunion\limits_{#1}^{#2} \left( {#3} \right)}
+\newcommand{\interfrom}[3]{\biginter\limits_{#1}^{#2} \left( {#3} \right)}
+\newcommand{\interacross}[2]{\interfrom{#1}{}{#2}}
+\newcommand{\unionacross}[2]{\unionfrom{#1}{}{#2}}
+\newcommand{\sumacross}[2]{\sumfrom{#1}{}{#2}}
+\newcommand{\prodacross}[2]{\prodfrom{#1}{}{#2}}
+\newcommand{\set}[1]{\left\{ {#1} \right\}}
+\newcommand{\setbuilder}[2]{\set{#1 | #2}}
+\newcommand{\derivative}[2]{\frac{d}{d{#2}}\left( {#1} \right)}
+\newcommand{\Exists}[2]{\exists_{#1}\left( {#2} \right)}
+\newcommand{\All}[2]{\forall_{#1}\left( #2 \right)}
+\newcommand{\abs}[1]{\left|{#1}\right|}
+\newcommand{\cardinality}[1]{\overline{\overline{#1}}}
+\newcommand{\range}[1]{\textit{\textbf{Rng}}\left( #1 \right)}
+\newcommand{\domain}[1]{\textit{\textbf{Dom}}\left( #1 \right)}
+\newcommand{\pset}[1]{\mathscr P\left( #1 \right)}
+\newcommand{\pair}[2]{\left( #1 , #2 \right)}
+\newcommand{\closure}[1]{\overline{#1}}
+\newcommand{\limpts}[1]{#1 '}
+\newcommand{\ooint}[2]{\left( #1 , #2 \right)}
+\newcommand{\ocint}[2]{\left( #1 , #2 \right]}
+\newcommand{\coint}[2]{\left[ #1 , #2 \right)}
+\newcommand{\ccint}[2]{\left[ #1 , #2 \right]}
+\newcommand{\eqclass}[1]{\overline{#1}}
+\newcommand{\ceil}[1]{\left\lceil #1 \right\rceil}
+\newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
 
@@
 and thus, iff $a$ and $b$ are limit points for the interval $\ooint ab$, then our equality ($\ccint ab = \closure{\ooint ab}$) holds.
-
 \bigskip
 
-\question{17.17}Consider the lower limit topology on $\mathbb R$, and the topology given by the basis $\mathscr C$ of Exercise 8 \S 13.
+Consider\question{17.17} the lower limit topology on $\mathbb R$, and the topology given by the basis $\mathscr C$ of Exercise 8 \S 13.
 Determine the closures of the intervals $A = \ooint0{\sqrt{2}}$ and $B=\ooint{\sqrt2}3$ in these two topologies.
@@
 By definition we know that $\closure C $ is the intersection of all closed sets that contain $C$.
-We know that $\ooint{-\infty}a\union\coint b\infty \in \mathbb R_\ell$ and thus $\coint ab$ is closed in $\mathbb R_\ell$, thus $\closure C \subset \left[a,b\right)$.
+We know that $\coint ab \in \mathbb R_\ell$ and that $\left[a,b\right) \supset A$, thus $\closure C \subset \left[a,b\right)$.
 
@@
 Now to find $\closure{\ooint{0}{\sqrt2}}$ we simply must determine if $0$ is a limit point of $\ooint 0{\sqrt2}$ and if $\sqrt2$ is a limit point of $\ooint 0{\sqrt2}$.
+If an open set contains $0$ then it must contain an interval $\coint\alpha\beta$, where $\alpha\le 0$ and is rational, and $\beta>0$ and is rational.
+Because $\beta > 0$ then there must be some number between $0$ and $\beta$ that is in $\ooint 0{\sqrt2}$, thus $0$ is a limit point of $\ooint 0{\sqrt2}$.
+If an open set contains $\sqrt2$ then it must contain an interval $\coint\alpha\beta$, where $\alpha\le\sqrt2$ and is rational, and $\beta>\sqrt2$ and is rational.
+Because $\alpha$ is rational $\alpha\not=\sqrt2$, thus there must be a number between $\alpha$ and $\sqrt2$ that is in $\ooint0{\sqrt2}$, thus $\sqrt2$ is a limit point of $\ooint 0{\sqrt2}$.
+Thus we may now say that $\closure{\ooint0{\sqrt2}} = \ccint{0}{\sqrt2}$.
 
-Any open interval around $0$ must have an upper bound greater then $0$, and thus $0$ is a limit point for $\ooint 0{\sqrt2}$.
-
-Any open interval around $\sqrt2$ must have a lower bound that is a rational number, $\sqrt2$ is not rational, thus there must be a rational number less then $\sqrt2$ in the interval, and thus $\sqrt2$ is a limit point for $\ooint 0{\sqrt2}$.
-
-Thus we have shown \[\ccint{0}{\sqrt2} = \closure{\ooint{0}{\sqrt2}}\]
-
-Next we will find $\closure{\ooint{\sqrt2}3}$. We first will check if $\sqrt2$ and $3$ are limit points of $\ooint{\sqrt2}3$.
-
-For an open interval in $\mathcrl C$ to include $\sqrt2$ there must a rational number greater then $\sqrt2$ as the upper bound, thus there is some value between $\sqrt2$ and that upper bound that is in $\ooint{\sqrt2}3$.
-Thus $\closure{\ooint{\sqrt2}3} \supset \coint{\sqrt2}3$.
-
-The interval $\coint34$ includes $3$ and is in $\mathscr C$, thus it is a nood\footnote{nood = neighborhood} of $3$ which contains no values in $\ooint{\sqrt2}3$.
-Thus we know $3 \not\in \closure{\ooint{\sqrt2}3}$.
-
-Now we wish to show that $\coint{\sqrt2}3$ is closed, if we can do that then we know that $\coint{\sqrt2}3 \subset \closure{\ooint{\sqrt2}3} \subset \coint{\sqrt2}3$ or $\coint{\sqrt2}3 = \closure{\ooint{\sqrt2}3}$.
+Now let us attempt to find $\closure{\ooint{\sqrt2}3}$. We will consider the set $\coint{\sqrt2}3$, and attempt to show that it is closed by showing it's compliment is open.
 \begin{align*}
 \setcomp{\coint{\sqrt2}3} &= \ooint{-\infty}{\sqrt2} \union \coint3\infty \\
-&= \left( \unionacross{a<b<\sqrt2 \And a,b\in\mathbb Q}{\coint ab} \union \unionacross{3 \le a < b \And a,b \in \mathbb Q}{\coint ab} \right) \in \mathcrl C
+&=\left(\unionacross{a<b<\sqrt2\And a,b\in\mathbb Q}{\coint ab} \union \unionacross{3 \le a < b \And a,b\in\mathbb Q}{\coint ab}\right) \in \mathcrl C
 \end{align*}
-Thus we have shown $\coint{\sqrt2}3$ is closed, and thus have shown
-\[\coint{\sqrt2}3 = \closure{\ooint{\sqrt2}3}\]
+Thus $\coint{\sqrt2}3$ is closed, and thust $\closure{\ooint{\sqrt2}3} \subset \coint{\sqrt2}3 = \ooint{\sqrt2}3\union\set{\sqrt2}$.
+To to find $\closure{\ooint{\sqrt2}3}$ we must simply determine if $\sqrt2$ is a limit point of $\ooint{\sqrt2}3$.
+If an open set contains $\sqrt2$ then it must contain an interval $\coint\alpha\beta$, where $\alpha\le\sqrt2$ and is rational, and $\beta>\sqrt2$ and is rational.
+Because $\beta > \sqrt2$ then there must be a number between $\sqrt2$ and $\beta$ that is in $\ooint{\sqrt2}3$, thus $\sqrt2$ is a limit point of $\ooint{\sqrt2}3$.
+Thus we may now say that $\closure{\ooint{\sqrt2}3}=\coint{\sqrt2}3$.
 
 \bigskip
-Consider \question{18.5}the linear function $f:\mathbb R \to \mathbb R$ defined as $f(x) = \frac{x-a}{b-a}$. We know all linear functions are continuous, we have the homeomorphisms
+Consider \question{18.5}the linear function $f:\mathbb R \to \mathbb R$ defined as $f(x) = \frac{x-a}{b-a}$. We know all linear functions are continious, we have the homeomorphisms
 \begin{align*}
@@
 \end{align*}
-thus we have shown homeomorphism between $\ooint ab$ and $\ooint01$, and between $\ccint ab$ and $\ccint01$ for any $a<b\in\mathbb R$.
+thus we have shown homeomophism between $\ooint ab$ and $\ooint01$, and between $\ccint ab$ and $\ccint01$.
 
 \bigskip
-\question{18.8(a)} Consider first $\setcomp{\setbuilder{x\in X}{f(x)\le g(x)}} = \setbuilder{x\in X}{f(x)>g(g)} = S$. Let us now choose $x\in S$.
-
-By theorem 17.11 we know that $Y$ is Hausdorff, thus there exists disjoint open sets $\mathfrak A$ and $\mathfrak B$ such that $f(x)\in\mathfrak A$ and $g(x)\in\mathfrak B$.
-Let $A \subset\mathfrak A$ be a basis element in $Y$'s order topology such that $f(x)\in A$ and let $B\subset\mathfrak B$ be a basis element in $Y$'s order topology such that $g(x)\in B$.
-Now we have $\All{a\in A}{\All{b\in B}{[a>b]}}$ due to the definition of the order topology.
-
-Next we notice that $\inv{g}(B)$ is open by continuity of $g$ and $\inv{f}(A)$ is open by continuity of $f$.
-Finite intersections are open so $\inv g(B) \inter \inv f(A)$ must be open.
-Now for any $\hat x\in \inv g(B) \inter \inv f(A)$ we have $g(\hat x) \in B$ and $f(\hat x) \in A$ thus $g(\hat x) < f(\hat x)$.
-We now have shown that for every $x \in S$ there exists a nood of $x$ that is completely contained in $S$.
-We may now take the union of a nood for each $x$ and we get that $S$ is the union of open sets, thus $S$ is open.
-We now conclude that $\setbuilder{x\in X}{f(x)\le g(x)}$ is closed.
-
+\question{18.8(a)}
 \medskip
 \question{(b)}
-Let $A = \setbuilder{x\in X}{f(x) \le g(x)}$ and $B = \setbuilder{x\in X}{g(x) \le f(x)}$, thus $\All{a \in A}{f(a) = h(a)}$ and $\All{b \in B}{g(b) = h(b)}$; additionally $X = A \union B$.
-Notice that if $x\in A\inter B$ then $f(x) \le g(x)$ and $g(x) \le f(x)$, thus $g(x) = f(x)$.
-Now the final thing we must show is that $A$ and $B$ are both closed, however we just showed that in part a of this problem, so we may use the pasting lemma and we know that $h(x)$ is continuous.
-
 \bigskip
 \question{19.7}
-\textbf{Box topology:} Let $x\in \mathbb R^\omega\setminus\mathbb R^\infty$, therefore $x = (x_\alpha)_{\alpha\in J}$ where $x_a\not=0$ for infinitely many $\alpha\in J$.
-For each $\alpha\in J$ such that $x_\alpha\not=0$ let $A_\alpha$ be a nood of $x_\alpha$ that does not include $0$, for all other $\alpha\in J$ let $A_\alpha$ be a nood of $0$.
-We find that $\prodacross{\alpha\in J}{A_\alpha}$ is open in $\mathbb R^\omega$ as it is a basis element.
-We have now shown that for any $x \in\mathbb R^\omega\setminus\mathbb R^\infty$ there is an open set $A(x)$ such that $x \in A(x) \subset\mathbb R^\omega\setminus\mathbb R^\infty$, thus we may take the union and find $\unionacross{x\in\mathbb R^\omega\setminus\mathbb R^\infty}{A(x)} =\mathbb R^\omega\setminus\mathbb R^\infty$, thus $\mathbb R^\omega\setminus\mathbb R^\infty$ is open, and thus $\mathbb R^\infty$ is closed so $\mathbb R^\infty = \closure{\mathbb R^\infty}$.
+\bigskip
+\question{20.4}
 
-\textbf{Product topology:} Let $x \in\mathbb R^\omega$ and let $N$ be a nood of $x$, thus there exists some basis element of $\mathbb R^\omega$, $A$ such that $x \in A \subset N$.
-There must then exists $(x_\alpha)_{\alpha\in J} = x$ and $\prodacross{\alpha \in J}{A_\alpha} = A$ with $x_\alpha \in \mathbb R$ for all $\alpha \in J$ and $A_\alpha$ open in $\mathbb R$ for all $\alpha \in J$.
-We also know that for only finitely many $\alpha\in J$, $A_\alpha \not= \mathbb R$.
-We will now let $y_\alpha = 0$ for all $\alpha \in J$ where $A_\alpha=\mathbb R$, and let $y_\alpha = x_\alpha$ for all $\alpha\in J$ where $A_\alpha\not= \mathbb R$, thus $y = (y_\alpha)_{\alpha\in J} \in A$.
-We also notice that there are at most finitely many $\alpha \in J$ such that $y_\alpha\not=0$ thus $y \in \mathbb R^\infty$.
-This means that for any $x\in\mathbb R^\omega$ and any nood of $x$, there is some point $y\in\mathbb R^\infty$ such that $y$ is in the chosen nood of $x$, thus all points in $\mathbb R^\omega$ are limit points of $\mathbb R^\infty$.
-Finally we conclude that $\closure{\mathbb R^\infty} = \mathbb R^\omega$.
-
-\bigskip
-
-\question{20.4} 
-\begin{center}
-	\begin{tabular}{r|c c c}
-		&box topology&uniform topology &product topology\\
-		\hline\question{(a)}
-		$f$&not continuous&not continuous&continuous \\
-		$g$&not continuous&continuous&continuous\\
-		$h$&not continuous&continuous&continuous\\
-		\hline\question{(b)}
-		$\mathbf w$&does not converge&does not converge&converges\\
-		$\mathbf x$&does not converge&converges&converges\\
-		$\mathbf y$&does not converge&converges&converges\\
-		$\mathbf z$&converges&converges&converges
-	\end{tabular}
-\end{center}
 \end{document}

### 2019-04-10 SchoolCode/Compilers/Kata/src/kata/Kata.java

@@ -1,0 +1,21 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+package kata;
+
+/**
+ *
+ * @author Benji
+ */
+public class Kata {
+
+	/**
+	 * @param args the command line arguments
+	 */
+	public static void main(String[] args) {
+		// TODO code application logic here
+	}
+
+}

### 2019-04-10 SchoolCode/Compilers/SampleScaner/src/samplescaner/SimpleScanner.java

@@ -1,0 +1,135 @@
+package samplescaner;
+
+import java.util.HashMap;
+
+/**
+ *
+ * @author steinmee
+ */
+public class SimpleScanner {
+
+	// CONSTANTS
+	private static final int START = 0;
+	private static final int IN_ID = 1;
+	private static final int IN_NUM = 2;
+	// Completion states
+	private static final int ERROR = 10;
+	private static final int ID_COMPLETE = 11;
+	private static final int NUM_COMPLETE = 12;
+	private static final int SYMBOL_COMPLETE = 13;
+
+	// Instance variables
+	private String theSource = "";
+	private int currentIndex = 0;
+	private HashMap<String, TokenType> lookupTable = new HashMap<String, TokenType>();
+
+	// Constructor
+	public SimpleScanner(String toScan) {
+		this.theSource = toScan;
+
+		// put stuff in the lookup table
+		lookupTable.put("+", TokenType.PLUS);
+		lookupTable.put("-", TokenType.MINUS);
+		lookupTable.put(";", TokenType.SEMI);
+		lookupTable.put("=", TokenType.ASSIGN);
+		lookupTable.put("while", TokenType.WHILE);
+		lookupTable.put("program", TokenType.PROGRAM);
+	}
+
+	// Instance functions
+	public Token nextToken() {
+		Token answer = null;
+		// if there is no more string to consume, return null
+		if (currentIndex >= theSource.length()) {
+			return null;
+		}
+
+		String lexeme = "";
+
+		// Start in start state
+		int currentState = SimpleScanner.START;
+		while (currentState < SimpleScanner.ERROR) {
+			//System.out.println("While index is " + currentIndex + " and state is " + currentState);
+			// By default the char is whitespace
+			char currentChar = ' ';
+			if (currentIndex >= theSource.length() && currentState != 0) {
+				currentChar = ' ';
+			} else if (currentIndex < theSource.length()) {
+				currentChar = theSource.charAt(currentIndex);
+			} else {
+				break;
+			}
+
+			switch (currentState) {
+				case SimpleScanner.START:
+					if (Character.isLetter(currentChar)) {
+						lexeme = lexeme + currentChar;
+						currentState = SimpleScanner.IN_ID;
+						currentIndex++;
+					} else if (Character.isDigit(currentChar)) {
+						lexeme = lexeme + currentChar;
[…]

### 2019-04-10 SchoolCode/Compilers/SampleScaner/src/samplescaner/Token.java

@@ -1,0 +1,21 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+package samplescaner;
+
+/**
+ *
+ * @author steinmee
+ */
+public class Token {
+
+	public String lexeme;
+	public TokenType type;
+
+	public Token(String l, TokenType t) {
+		this.lexeme = l;
+		this.type = t;
+	}
+}

### 2019-04-10 SchoolCode/Compilers/Scanner/run.sh

@@ -1,0 +1,2 @@
+java -jar jflex-1.6.1.jar Scanner.jflex
+mv Scanner.java ../Compiler/src/scanner/

### 2019-04-10 SchoolCode/Cryptogorphy/Testing/src/Main/Testing.java

@@ -1,0 +1,27 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+package Main;
+
+import java.math.BigInteger;
+import java.util.Random;
+
+/**
+ *
+ * @author Benji
+ */
+public class Testing {
+
+	/**
+	 * @param args the command line arguments
+	 */
+	public static void main(String[] args) {
+		BigInteger bi = new BigInteger(1024, new Random());
+		// TODO code application logic here
+		System.out.println(bi);
+		System.out.println(bi.bitLength());
+	}
+
+}

### 2019-04-14 Topology/Paper/paper.tex
Hi
updates

@@
 \subsection{History}
-%TODO add more to section
+%TODO Make how short this is less obvious
 The seven bridges of K\"onigsberg problem was solved by Euler %TODO Citation (wikipedia for seven bridges of konigsberg)
@@
 
+\subsection{Subdivision}
+%TODO rename unsubdivide
+\def\unsubdivide{vertex replacement}
+\def\unsubdividepl{vertex replacements}
+
+To define this we first describe, we first have to describe an operation where we take a vertex $v$ that has degree 2, and replace with an edge as follows.
+
+\begin{center}
+	$
+	\begin{array}{l}
+		\begin{tikzpicture}[auto, node distance=3cm, every loop/.style={},
+		thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries}]
+
+		\node[main node] (1) {$v$};
+		\node[main node] (2) [left of=1] {$A$};
+		\node[main node] (3) [right of=1] {$B$};
+
+		\path[every node/.style={font=\sffamily\small}]
+		(1)	edge node {} (2)
+		edge node {} (3);
+		\end{tikzpicture}
+	\end{array}
+	$
+	\scalebox{2}{$\to$}
+	$
+	\begin{array}{l}
+		\begin{tikzpicture}[auto, node distance=3cm, every loop/.style={},
+		thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries}]
+
+		\node[main node] (1) {$A$};
+		\node[main node] (2) [right of=1] {$B$};
+
+		\path[every node/.style={font=\sffamily\small}]
+		(1)	edge node {} (2);
+		\end{tikzpicture}
+	\end{array}
+	$
+
+	or
+
+	$
+	\begin{array}{l}
+		\begin{tikzpicture}[auto, node distance=3cm, every loop/.style={},
+		thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries}]
+
+		\node[main node] (1) {$v$};
+		\node[main node] (2) [left of=1] {$A$};
+		\node[main node] (3) [right of=1] {$B$};
+
+		\path[every node/.style={font=\sffamily\small}]
+		(1)	edge node {} (2)
+		edge node {} (3)
+		(2) edge [bend left] node {} (3);
+		\end{tikzpicture}
+	\end{array}
+	$
+	\scalebox{2}{$\to$}
+	$
+	\begin{array}{l}
+		\begin{tikzpicture}[auto, node distance=3cm, every loop/.style={},
+		thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries}]
+
+		\node[main node] (1) {$A$};
+		\node[main node] (2) [right of=1] {$B$};
+
+		\path[every node/.style={font=\sffamily\small}]
+		(1)	edge node {} (2);
+		\end{tikzpicture}
+	\end{array}
+	$
+
+	\scalebox{.9}{Here $A$ and $B$ may be connected in any way to a larger graph, however only this subgraph will change.}
+\end{center}
+
+Now we are going to call this operation \unsubdivide, and using it we define a graph subdivision as follows.
+
+\begin{definition}[graph subdivision]
+	A graph $G$ is a subdivision of $H$ if $H$ may be produced by some series of \unsubdividepl\ on $G$.
+\end{definition}
+
 \newpage
@@
 \begin{theorem}[Kuratowski's Theorem]
-	A graph $G$ is planar if and only if it does not contain any subgraph $H$ such that a some series of edge contractions on $H$ would produce $K_5$ or $K_{3,3}$.
+	A graph $G$ is nonplanar if and only if it contains a subgraph that is a subdivision of $K_{3,3}$ or $K_5$
 \end{theorem}
 
-Here $K_5$ refers to the complete graph on 5 verticies, and $K_{3,3}$ is the complete bipartite graph with three verticies in both partitions.
+%TODO Maybe explanation of what $K_5$ and $K_{3,3}$ are should be earlier?
+Here $K_5$ refers to the complete graph on 5 vertices, and $K_{3,3}$ is the complete bipartite graph with three vertices in both partitions.
 Drawings of both theses graphs are below with ($K_5$ on left and $K_{3,3}$ on right).
@@
 
-The basic sketch of the proof will be:
-\begin{enumerate}
-	\item Prove that $K_5$ and $K_3,3$ are not planar.
-	\item Prove that if if a graph $G$ is planar than any graph obtained through an edge contraction is also planar.
-	\item 
-\end{enumerate}
+\subsection{$K_{3,3}$ and $K_5$}
+Our first step is proving that $K_{3,3}$ and $K_5$ are nonplanar. To do this we are going to use the following theorem.
+
+\begin{theorem}[Euler's formula on planar graphs]
+	For any plane drawing of a graph, we have $$v-e+f=2$$, where $v$ is the number of vertices in the graph, $e$ is the number of edges in the graph, and $f$ is the number of faces in the plane drawing of the graph.
+\end{theorem}
+%TODO credit this to https://www.ics.uci.edu/~eppstein/junkyard/euler/interdig.html
+Before we can prove this we need to define the dual of a planar graph.
+\begin{definition}[graph dual]
+	For any plane drawing $G$ of a graph, we may construct it's dual $G*$ by putting a single vertex in each face, and putting an edge between any two adjacent faces (faces that share an edge).
+Note that this dual is not necessarily a graph, but will fit our definition of a multigraph.
+\end{definition}
+For example consider the following graph drawing
+\input{Duals_graphs.tex}
+
+\begin{proof}
+
+\end{proof}
 

### 2019-04-14 SchoolCode/Combinatorics/MaximalFrequentSetsPsudocode.tex

\documentclass{article}

\title{Maximal Frequent Set Algorithm}
\author{Benji Altman}

\usepackage{amsmath,amssymb,graphicx,algpseudocode,algorithm} %load extra symbols and environments
\usepackage[margin=1in]{geometry} %set margins
\usepackage{mathrsfs}

\let\union\cup
\let\inter\cap
\let\cross\times
\let\emptyset\varnothing
\let\bigunion\bigcup
\let\true\top
\let\false\bot
\let\biginter\bigcap

\let\setminus-
\let\bigcross\bigtimes
\def\Return{\State\textbf{return} }
\newcommand{\setcompliment}[1]{{#1}^{\mathsf{c}}}
\newcommand{\unionfrom}[3]{\bigunion\limits_{#1}^{#2} \left( {#3} \right)}
\newcommand{\interfrom}[3]{\biginter\limits_{#1}^{#2} \left( {#3} \right)}
\newcommand{\crossfrom}[3]{\bigcross\limits_{#1}^{#2} \left( #3 \right)}
\newcommand{\productfrom}[3]{\prod\limits_{#1}^{#2} \left( #3 \right)}
\newcommand{\sumfrom}[3]{\sum\limits_{#1}^{#2} \left( {#3} \right)}
\newcommand{\set}[1]{\left\{ {#1} \right\}}
\newcommand{\setbuilder}[2]{\set{#1 | #2}}
\newcommand{\derivative}[2]{\frac{d}{d{#2}}\left( {#1} \right)}
\newcommand{\Exists}[2]{\exists_{#1}\left( {#2} \right)}
\newcommand{\abs}[1]{\left|{#1}\right|}
\newcommand{\cardinality}[1]{\overline{\overline{#1}}}
\newcommand{\interacross}[2]{\interfrom{#1}{}{#2}}
\newcommand{\unionacross}[2]{\unionfrom{#1}{}{#2}}
\let\times\cdot

\newcommand{\CommentLine}[0]{\State\textbackslash\textbackslash}
\begin{document}
\maketitle
\section{Pseudocode}
Let $P(S)$ be read as the statement ``$S$ is a special set'', and let $\mathcal U$ be any finite superset of $\left\{x: P\left(\{x\}\right)\right\}$.

\begin{algorithm}
	\caption{depth-first searth}\label{dfs}
	\begin{algorithmic}[1]
		\Function{FindMaximalSpecialSet}{\null}
			\Return \Call{GetSpecialSuperset}{$\mathcal U,\emptyset,\emptyset$}
		\EndFunction
		\\
		\Function{GetSpecialSuperset}{$A,B,\mathcal O$}
			\CommentLine Step 1: thin out array
			\ForAll{$x \in A$}
				\If{$\neg$ \Call {$P$}{$B \union \set x$}}
					\State $A \gets A \setminus \set x$
				\EndIf
			\EndFor
			\\
			\CommentLine Step 2: add to output, or call recursive
			\If{$A=\emptyset$}
				\\
				\CommentLine If $B$ is not a subset of any set in $\mathcal O$ add it to $\mathcal O$ and return.
				\ForAll{$O \in \mathcal O$}
					\If{$B \subseteq O$}
						\Return $\mathcal O$ \Comment{Ends the function if the return statement is hit.}
					\EndIf
				\EndFor
				\Return $\mathcal O \union \set B$
			\Else
				\\
				\CommentLine Make recursive calls, moving elements from $A$ into $B$.
				\ForAll{$a \in A$}
					\State $A \gets A \setminus \set a$
					\State $\mathcal O \gets $ \Call{GetSpecialSuperset}{$A,B\union\set a,\mathcal O$} \Comment{$\mathcal O \subseteq$ \Call{GetSpecialSuperset}{$A,B,\mathcal O$}}
				\EndFor
				\Return $\mathcal O$
			\EndIf
		\EndFunction
	\end{algorithmic}
\end{algorithm}

\section{Explanation}

\subsection{details}
We are going to tackle this problem with recursion, so we are going to try and show that our function ``GetSpecialSuperset'' will return the set of maximal special supersets of $B$, if $B$ is a special set and $A$ is a finite superset of the set of all elements which are special with $B$.\footnote{$x$ is special with $S$ iff $S \union \set x$ is special and $x\not\in S$.}

We start by limiting $A$ to only being the set of elemetns with are special with $B$. If there are none, then $A$ will become the empty set, and we would know that $B$ is the only maximal special superset of $B$, and thus return the set $\set B$.

If $A$ is not the empty set (there are elements that are special with $B$), then for each element $x\in A$ we get the set, $\mathcal R$, of maximal special supersets of $B \union \set x$. $\mathcal R$ is found by applying this function again with the new $A$ set as our current $A$, just without $x$, and the new $B$ set as $B \union \set x$. We can see this is true as if some $k$ is speical with $B \union \set x$ then it must also be special with $B$, $A$ is the set of all things special with $B$ and $A \setminus \set x$ is the set of all things special with $B$ except $x$, which we know is in $B \union \set x$, thus $A\supseteq \setbuilder{k}{k \text{ is special with } B \union \set x}$, which is our requirement for what we need $A$ to be. We also know that our new $B$ is special by defintion of $x$ being special with $B$. To take things one step further, we can remove $x$ from our current $A$ as if we have all maximal supersets $B \union \set x$ then we never need to check $B$ with $x$ again as it would have already been found.\footnote{This justifies line 18.} Once we have found $\mathcal R$ we add all sets in $\mathcal R$ to $\text{Output}$.

Once we have iterated through all $x\in A$ we return $\text{Output}$ as it now contains all supersets of $B$ which are special.

\subsection{example}

Let $\mathcal U=\set{0,1,2,3}$ and our set of maximal special sets, the expected output we will call $\mathcal T$ and we will let $\mathcal T = \set{\set{0,2},\set{1}}$, thus $P(S)=\Exists{E\in\mathcal T}{S\subseteq E}$.

\def\ind{\phantom{$\rightarrow$}\hspace{1em}}
\def\nnd{$\rightarrow$\hspace{1em}}
\vspace{4ex}
\noindent
$A: \set{0,1,2,3}$\\
$B: \set{}$\\
$\mathcal O: \set{}$\\
$x:0$\\
$P(B\union\set x)$\\
$x:1$\\
$P(B\union\set x)$\\
$x:2$\\
$P(B\union\set x)$\\
$x:3$\\
$\neg P(B\union\set x)$\\
$A:\set{0,1,2}$\\
$A\not=\emptyset$\\
$a:0$\\
$A:\set{1,2}$\\
\nnd$A:\set{1,2}$\\
\ind$B:\set0$\\
\ind$\mathcal O:\set{}$\\
\ind$x:1$\\
\ind$\neg P(B\union\set x)$\\
\ind$A:\set{2}$\\
\ind$x:2$\\
\ind$P\set{0,2}$\\
\ind$A\not=\emptyset$\\
\ind$a:2$\\
\ind$A:\set{}$\\
\ind\nnd$A:\set{}$\\
\ind\ind$B:\set{0,2}$\\
\ind\ind$\mathcal O:\set{}$\\
\ind\ind$A=\emptyset$\\
\ind$\mathcal O:\set{\set{0,2}}$\\
$\mathcal O:\set{\set{0,2}}$\\
$a:1$\\
$A:\set2$\\
\nnd$A:\set{2}$\\
\ind$B:\set{1}$\\
\ind$\mathcal O:\set{\set{0,2}}$\\
\ind$x:2$\\
\ind$\neg P(B\union\set x)$\\
\ind$A:\set{}$\\
\ind$A=\emptyset$\\
\ind$O:\set{0,2}$\\
\ind$B\not\subseteq O$\\
$\mathcal O: \set{\set{0,2},\set1}$\\
$a:2$\\
$A:\set{}$\\
\nnd$A:\set{}$\\
\ind$B:\set{2}$\\
\ind$\mathcal O:\set{\set{0,2},\set1}$\\
\ind$A=\emptyset$\\
\ind$O:\set{0,2}$\\
\ind$B\subseteq O$\\
$\mathcal O: \set{\set{0,2},\set1}$\\

\end{document}

### 2019-04-14 SchoolCode/Combinatorics/chapter1.tex

\documentclass{article}

% stuff from the percent sign to end of line is a comment, ignored by LaTeX

\usepackage{amsmath,amssymb,graphicx} %load extra symbols and environments
\usepackage[margin=1in]{geometry} %set margins
\usepackage{mathrsfs}

\title{Combinatorics Homework Chapter 1}
\author{Benji Altman}

\reversemarginpar

\begin{document}
\maketitle

We\marginpar{\flushright Prob 1.2} can refer to each square on any chess board uniquely with notation $(x,y)$ where $x$ is the number of squares to the right, and $y$ is the number of squares to the left.\footnote{Thus $(0,0)$ would be the upper right hand corner, $(0,1)$ would be one square down from that, and $(1,0)$ would be one square left of the upper right hand corner.} The problem states that the upper right hand corner or $(0,0)$ is white, thus we know that the white squares can be defined as ``The set of all squares $(x,y)$ where $x+y$ is even.''\footnote{This can be proved by defining black and white squares as the following
\begin{enumerate}
\item A black square is any square adjacent to a white square.
\item A white square is any square, either adjacent to a black square, or is $(0,0)$.
\item A square, $(a_x,a_y)$, is adjacent to another square, $(b_x,b_y)$, iff $(b_x = a_x \pm 1 \land b_y = a_y) \lor (b_x = a_x \land b_y = a_y \pm 1)$
\end{enumerate}

Let us also define a function $f(s)=s_x+s_y$, where $s=(s_x,s_y)$. Notice that for any square $q$, where $f(q) = n$, for any adjacent square to it, $r$, $f(r) = n \pm 1$. That means that for any $q$ where $f(q)$ is odd, all $f(r)$ is even, where $r$ is any adjacent square, and if $f(q)$ is even, then all $f(r)$ would have been odd.

Now to prove that $\forall_{x \in \left\{\text{white squares}\right\}}\left(f(x) \text{ is even}\right)$ and $\forall_{x \in \left\{\text{black squares}\right\}}\left(f(x) \text{ is odd}\right)$ we start by showing
\begin{equation}
f((0,0)) = 0 \in \left\{\text{Evens}\right\}
\end{equation}
and we know that (0,0) is a white square by definition. Now let $f((a,b))=k$, where $a$ and $b$ are natural numbers (ie: in the set $\{0,1,2,\ldots \}$), thus
\begin{equation}
\begin{aligned}
f((a+1,b))=a+1+b=k+1 \\
f((a-1,b))=a-1+b=k-1 \\
f((a,b+1))=a+b+1=k+1 \\
f((a,b-1))=a+b-1=k-1
\end{aligned}
\end{equation}
so for adjacent square to $(a,b)$, $(a,b)'$, $f\left((a,b)'\right)$ can be written as $a+b\pm1$ or $f((a,b))\pm1$. Any even number $\pm 1$ is an odd number, and any odd number $\pm 1$ is an even number. Now we can say that for any square $X$, any adjacent square to it $X'$, is odd iff $X$ is even, and is even iff $X$ is odd. We also know by definitions 1 and 2 that $X'$ is black if $X$ is white and $X'$ is white if $X$ is black. We can now show by induction that if $f(X)$ is even, then $X$ is a white square, and if $f(X)$ is odd, then $X$ is a black square.} Thus if $X$ is on an odd row
\end{document}

### 2019-04-14 SchoolCode/Combinatorics/sectoio2.tex

\documentclass{article}

\usepackage{amsmath,amssymb,graphicx,esint} %load extra symbols and environments
\usepackage[margin=1in]{geometry} %set margins
\usepackage{mathrsfs}

\title{Foundations of Mathematics\\Section 1.5 Problems}
\author{Benji Altman}

\reversemarginpar

\begin{document}
\maketitle
$$
\mathbb{R}
$$
We\marginpar{\flushright3(c)} are trying to prove $4\not|x^2\implies x\in\{\text{Odds}\}$, where $x\in\mathbb{Z}$. By contrapositive, $4\not|x^2\implies x\in\{\text{Odds}\}$ is equivalent to trying to prove $4|x^2\impliedby x\in2\mathbb Z$.

Let $x$ be an even number. Thus it can be written as $2k$, where $k\in\mathbb Z$. Now
\[x^2=4k^2\]
and $4k^2$ is divisible by $4$ by definition of divisibility. Thus $4\not|x^2\implies x\in\{\text{Odds}\}$.
\vspace{2\baselineskip}

Let\marginpar{\flushright5} $\mathfrak C$ be a circle with center at $(2,4)$ and radius length of $r$, this will be referred to throughout problem 5.
\medskip

The\marginpar{\flushright(a)} point $(-1,5)$ is distance $d_1$ from the center of $\mathfrak C$, and the point $(5,1)$ is distance $d_2$ from the center of $\mathfrak C$.
\begin{align*}
d_1
&= \sqrt{(2-(-1))^2+(4-5)^2} \\
&= \sqrt{3^2+(-1)^2} \\
&= \sqrt{9+1} \\
&= \sqrt{10}
\\ \\
d_2
&= \sqrt{(5-2)^2+(1-4)^2} \\
&= \sqrt{3^2+(-3)^2} \\
&= \sqrt{9+9} \\
&= \sqrt{18} \\
&= 3\sqrt{2}
\end{align*}
\begin{equation*}
\sqrt{10} = d_1 \not= d_2 = 3\sqrt2
\end{equation*}
By the definition of circle, two points of of different distance from the centerpoint may not both lie upon it's edge.
\bigskip

T\marginpar{\flushright(b)}he distance from the line $y=x-6$, which will herein be referred to as $\mathfrak L$, to the center point of $\mathfrak C$ at $x$ is given by the function:
\begin{align*}
\mathfrak D(x)&=\sqrt{(2-x)^2+(4-(x-6))^2}\\
&=\sqrt{(2-x)^2+(10-x)^2} \\
&=\left((2-x)^2+(10-x)^2\right)^\frac12
\end{align*}
We can find $\mathfrak D(x)$'s minima by using calculus.
\begin{align*}
\mathfrak D'(x) &= \frac12\cdot\left((2-x)^2+(10-x)^2\right)^{-\frac12} \cdot \left(2\cdot(2-x)\cdot(-1)+2\cdot(10-x)\cdot(-1)\right) \\
&= \frac{2(x-6)}{\sqrt{(2-x)^2+(10-x)^2}}
\end{align*}
$\mathfrak D'(x)=0$ when $(2(x-6)=0)\land\left(\sqrt{(2-x)^2+(10-x)^2}\not=0\right)$
\begin{align*}
2(x-6)&=0 \\
x-6&=0 \\
x&=6
\end{align*}
\begin{align*}
\sqrt{(2-6)^2+(10-6)^2}&=\sqrt{(-4)^2+4^2} \\
&=4\sqrt{2} \\
&\not=0
\end{align*}
Thus $\mathfrak D$'s only critical point is when $x=6$. We can tell $x=6$ is a minima for $\mathfrak D(x)$ if $\mathfrak D''(6)>0$.
\begin{align*}
\mathfrak D'(x)&=2(x-6)\left((2-x)^2+(10-x)^2\right)^{-1/2} \\
\mathfrak D''(x)&=2\left((2-x)^2+(10-x)^2\right)^{-1/2}-(x-6)\left((2-x)^2+(10-x)^2\right)^{-3/2}\cdot2\left(x-12\right) \\
\mathfrak D''(6)&=2\left((2-6)^2+(10-6)^2\right)^{-1/2}-(6-6)\left((2-6)^2+(10-6)^2\right)^{-3/2}\cdot2\left(6-12\right) \\
&=2\left((-4)^2+(4)^2\right)^{-1/2}-(0)\left((-4)^2+4^2\right)^{-3/2}\cdot2\left(-6\right) \\
&= \frac{\sqrt{2}}4 > 0
\end{align*}
Thus the distance between $\mathfrak C$'s center point and $\mathfrak L$ is $\mathfrak D(6)$, which is equal to
\begin{align*}
\mathfrak D(6) &= \sqrt{(2-6)^2+(4-(6-6))^2} \\
&= \sqrt{(-4)^2+4^2} \\
&= \sqrt{16\cdot2} \\
&= 4\sqrt2
\end{align*}
If $4\sqrt2>r$ then $\mathfrak L$ does not cross over $\mathfrak C$ because $\mathfrak L$ will never have a point as close or closer then $r$ to $\mathfrak C$'s center point.

We can say that $\sqrt2>\frac43$ because $\sqrt2^2=2>\frac43^2=\frac{16}9$, thus $4\sqrt2>4\cdot\frac43=\frac{16}3>\frac{15}3=5$. Thus $4\sqrt2>5$ so if $r=5$, $\mathfrak L$ will not intersect $\mathfrak C$.
\bigskip

Claim\marginpar{\flushright(c)}: $(0,3)$ is not inside $\mathfrak C\implies(3,1)$ is not inside $\mathfrak C$. We proove this by contrapostive, so we are going to show that if $(3,1)$ is inside $\mathfrak C\implies(0,3)$ is inside $\mathfrak C$.

Proof: The point $(0,3)$ is of distance $\sqrt{(2-0)^2+(4-3)^2}$ from the center of $\mathfrak C$.
\begin{align*}
\sqrt{(2-0)^2+(4-3)^2} &= \sqrt{2^2+1^2} \\
&= \sqrt{4+1} \\
&= \sqrt5
\end{align*}
The point $(3,1)$ is of distance $\sqrt{(3-2)^2+(1-4)^2}$ from the center of $\mathfrak C$.
\begin{align*}
\sqrt{(3-2)^2+(1-4)^2}&=\sqrt{1^2+(-3)^2} \\
&=\sqrt{1+9} \\
&=\sqrt{10}
\end{align*}
For the point $(3,1)$ to be in $\mathfrak C$, $r>\sqrt{10}$, thus $(0,3)$ will always be contained within that circle as it is only $\sqrt5$ from the center of $\mathfrak C$.
\vspace{2\baselineskip}

Prove \marginpar{\flushright10}that $\sqrt5\not\in\mathbb Q$. This will be shown by contradiction so we start by assuming $\sqrt5\in \mathbb Q$, which by definition of $\mathbb Q$ means that it can be written as $\frac ab$, where $a\in\mathbb Z$ and $b\in\mathbb Z_+$ and there are no common factors between $a$ and $b$. \footnote{$\mathbb Z_+$ is the set of positive integers, ie: $\{1, 2, 3, \ldots\}$.} We also know, by definition of square root, that $\sqrt5^2=5$, thus $\frac ab^2=5$ and $a^2=5b^2$.

We also will show that for any integer $x$, if it is not divisible by some prime number $d$, then $x^2$ is also not divisible by $d$. We show this by saying that any value $x$ can be written as $(-1)^b p_1^{e_1} p_2^{e_2} p_3^{e_3} \ldots p_v^{e_v}$, where $b\in\{0,1\}, \forall_{p_k, k\in\mathbb N}(p_k\in\mathbb P) $

\marginpar{\flushright11}

\end{document}

### 2019-04-14 SchoolCode/Foundations/3.3.tex

\documentclass{article}

\input{definitions}
\title{Foundations of Mathematics \\ Section 3.3}

\begin{document}

\maketitle

\question{3.3.4}

\question{a)}

Here our partition $\mathscr P$ on $\mathbb R$ may be defined as the following
\begin{enumerate}
\item $\All{x\in\coint01}{x \in P_x \in \mathscr P}$
\item $\All{P \in \mathscr P}{x \in P \implies \left( x + 1 \in P \And x - 1 \in P \right)}$
\end{enumerate}

\question{c)}
Here our partition $\mathscr P$ on $\mathbb R$ may be defined as the following
\begin{enumerate}
\item $\All{x \in \ccint{-\frac\pi2}{\frac\pi2}}{x \in P_x \in \mathscr P}$
\item $\All{x \in \ooint{-\frac\pi2}{\frac\pi2}}{\pi-x \in P_x}$
\item $\All{P \in \mathscr P}{x \in P \implies \left( x + 2\pi \in P \And x - 2\pi \in P \right)}$
\end{enumerate}

\question{d)}

Here our partition $\mathscr P$ on $\mathbb R$ may be defined as the following
\[
\All{x\in\coint0\infty}{\set{-x,x}\in\mathscr P}
\]

\question{e)}

Here our partition $\mathscr P$ on $\mathbb R^2$ may be defined as the following
\begin{enumerate}
\item $\mathscr P = \set{P_-, P_0, P_+}$
\item $P_- = \setbuilder{\pair xy \in \mathbb R^2}{xy < 0}$
\item $P_0 = \setbuilder{\pair xy \in \mathbb R^2}{xy = 0}$
\item $P_+ = \setbuilder{\pair xy \in \mathbb R^2}{xy > 0}$
\end{enumerate}

\question{3.2.5}

Here we define our partition $\mathscr P$ on $\set{1,i,-1,-i}$ as
\[\mathscr P = \set{\set{1,-1},\set{i,-i}}\]

\question{3.2.6}

Here we define our partition $\mathscr P$ on $S^2$ where $S = \set{1,i,-1,-i}$ as
\[\mathscr P = \setbuilder{\setbuilder{\pair xy\in S^2}{xy = s}}{s\in S}\]
This may more clearly be defined as the following, the two are equivalent.
\[\All{s\in S}{\setbuilder{\pair xy\in S^2}{xy = s} \in \mathscr P}\]

\end{document}

### 2019-04-14 SchoolCode/Topology/HW1.tex

\documentclass{article}

\input{definitions.tex}
\def\useLim{}

\title{Topology Homework 1}

\begin{document}
\maketitle

\question{1.2(b)}
\[A\subset B \Or A \subset C \iff A \subset (B \union C)\]

First we show $A\subset B \Or A \subset C \implies A \subset (B \union C)$. We note that if $A \subset B$ then $A \subset (B \union X)$ for any set $X$. The same is true for $A \subset C$. Thus we know that if $A$ is a subset of $B$ or $C$ then it must also be a subset of $B \union C$. Thus we have shown $A\subset B \Or A \subset C \implies A \subset (B \union C)$.

Next we try and show that $A\subset B \Or A \subset C \impliedby A \subset (B \union C)$. This we can disprove by example. Let $A$ be the set of all prime numbers, let $B$ be the set of all even numbers, and let $C$ be the set of all odd numbers.

\question{(e)}
\[A\setminus(A\setminus B) = B\]

First we will do some manipulation
\begin{align*}
A \setminus (A \setminus B) &= A \inter \setcomp{(A \setminus B)} \\
&= A \inter \setcomp{\left(A \inter \setcomp B \right)} \\
&= A \inter \left(\setcomp A \union \setcomp{\setcomp B}\right) \\
&= A \inter \left(\setcomp A \union B\right) \\
&= \left(A \inter \setcomp A\right) \union \left( A \inter B \right) \\
&= \emptyset \union (A \inter B) \\
&= A \inter B
\end{align*}
Now we only need to see if $A \inter B = B$. This is obviously not true, but it is safe to say that $A \inter B \subset B$.

\question{(o)}
\[A \cross (B \setminus C) = (A \cross B) \setminus (A \cross C)\]

\begin{align*}
A \cross (B \setminus C) &= \setbuilder{x}{x \in A \cross (B \setminus C)} \\
&= \setbuilder{\pair ab}{a \in A \land b \in B \setminus C} \\
&= \setbuilder{\pair ab}{a \in A \land (b \in B \land b \not\in C)}
\end{align*}
\begin{align*}
(A \cross B) \setminus (A \cross C) &= \setbuilder{x}{x \in (A \cross B)\setminus(A \cross C)} \\
&= \setbuilder{x}{x \in A \cross B \land x \not\in A \cross C}\\
&= \setbuilder{\pair ab}{(a \in A \land b \in B)\land \lnot(a \in A \land b \in C)}
\end{align*}

At this point one may notice that these two are equivalent as can be shown by truth table. The truth table will not be presented as it's really really hard to make them in \latex and I'm kinda lazy.

\question{(q)}

\[(A\cross B) \setminus (C \cross D) = (A \setminus C) \cross (B \setminus D)\]

\begin{align*}
(A \cross B) \setminus (C \cross D) &= \setbuilder{x}{x \in A\cross B \land x \not\in C\cross D} \\
&= \setbuilder{\pair ab}{(a \in A \land b \in B) \land \lnot(a \in C \land b \in D)}
\end{align*}
\begin{align*}
(A \setminus C) \cross (B \setminus D) &= \setbuilder{\pair ab}{(a \in A \setminus C) \land (b \in B \setminus D)} \\
&= \setbuilder{\pair ab}{(a \in A \land a \not\in C) \land (b \in B \land  b\not\in D)}
\end{align*}

At this point one may make truth tables, and this time I'll actually do that...
\[
\begin{array}{c|c|c|c|c|c}
a \in A & b \in B & a \in C & b \in D & (a \in A \land b \in B) \land \lnot(a \in C \land b \in D) & (a \in A \land a \not\in C) \land (b \in B \land b \not\in D) \\
\hline
\false & \false & \false & \false & \false & \false \\
\false & \false & \false & \true & \false & \false \\
\false & \false & \true & \false & \false & \false \\
\false & \false & \true & \true & \false & \false \\
\false & \true & \false & \false & \false & \false \\
\false & \true & \false & \true & \false & \false \\
\false & \true & \true & \false & \false & \false \\
\false & \true & \true & \true & \false & \false \\
\true & \false & \false & \false & \false & \false \\
\true & \false & \false & \true & \false & \false \\
\true & \false & \true & \false & \false & \false \\
\true & \false & \true & \true & \false  & \false \\
\true & \true & \false & \false & \true & \true \\
\true & \true & \false & \true & \true & \false \\
\true & \true & \true & \false & \true & \false \\
\true & \true & \true & \true & \false & \false
\end{array}
\]
... and we notice that cases for $(A \cross B) \setminus (C \cross D)$ is a superset of the cases for $(A \setminus C) \cross (B \setminus D)$, thus \[(A\cross B) \setminus(C\cross D) \supset (A\setminus C) \cross (B\setminus D)\]

\question{4(a)} For at least one $a \in A$, it is true that $a^2 \not\in B$.

\question{(b)} For every $a \in A$, it is true that $a^2 \not\in B$.

\question{(c)} For at least one $a \in A$, it is true that $a^2 \in B$.

\question{(d)} For every $a \not\in A$, it is true that $a^2 \not\in B$.

\question{5 and 6}

\begin{center}
\begin{tabular}{c|c|c|c}
part & statement & converse & problem 6 \\
\hline
(a) & $\true$ & $\true$ & $x\not\in \unionacross{A \in \mathcal A}{A} \impliedby x \not\in A \text{ for every } A \in \mathcal A$\\
(b) & $\false$ & $\true$ & $x \not\in \unionacross{A \in\mathcal A}A \impliedby x \not\in A \text{ for at least one } A \in \mathcal A$\\
(c) & $\true$ & $\false$ & $x\not\in\interacross{A \in \mathcal A}A \impliedby x \not\in A \text{ for every } A \in\mathcal A$\\
(d) & $\true$ & $\true$ & $x \not\in\interacross{A \in\mathcal A}A \impliedby x \not\in A \text{ for at least one } A \in\mathcal A$
\end{tabular}
\end{center}

\question{10(a)} Yes, $\mathbb Z \cross \mathbb R$.

\question{(b)} Yes, $\mathbb R \cross \ocint01$.

\question{(c)} No.

\question{(d)} Yes, $(\mathbb R \setminus \mathbb Z) \cross \mathbb Z$.

\question{(e)} No.

\question{2.2(b)}
\begin{align*}
x\in f^{-1}\left(B_0 \union B_1\right) &\iff f(x) \in B_0 \union B_1 \\
&\iff f(x) \in B_0 \Or f(x) \in B_1 \\
&\iff x \in f^{-1}\left(B_0\right) \Or x \in f^{-1}\left(B_1\right) \\
&\iff x \in f^{-1}\left(B_0\right) \union f^{-1}\left(B_1\right)
\end{align*}

\question{(g)} We have to be careful about notation here, when we have an inverse function we will say that it maps to sets. For example if $f:\mathbb R \to \mathbb R$ defined as $f(x)=x$ then $f^{-1}(x)=\set x$. This is to deal with functions where $f^{-1}$ maps to multiple points like if $f(x)=x^2$ then $f^{-1}(x) = \set{\sqrt x, -\sqrt x}$.

First we notice that for all $y \in \func f{A_0 \inter A_1}$ there exists at least one $x \in A_0 \inter A_1$ su. $f(x) = y$. Next we notice $x \in A_0 \inter A_1 \iff x \in A_0 \And x \in A_1$. Now we can say \[\All{x\in A_0 \inter A_1}{\func fx \in \func f{A_0} \And \func fx \in \func f{A_1}}\] which also means that \[\All{y\in\func f{A_0\inter A_1}}{y \in \func f{A_0} \And y \in \func f{A_1}}\] thus \[\func{f}{A_0\inter A_1} \subset \func f{A_0} \inter \func f{A_1}\]

Now we have shown $f\left(A_0\inter A_1\right) \subset f\left(A_0\right) \inter f\left(A_1\right)$, for any function $f:A\to B$. Now we will show that if $f$ is injective then $f\left(A_0 \inter A_1\right) \supset f\left( A_0 \right) \inter f\left(A_1\right)$.

Our definition of injective is as follows: $f:A\to B$ is injective iff $f(a) = f(a') \implies a = a'$.

In order to prove this we will first show that for any injective function, $g:X\to Y$, then for any $\bar X \subset X$, if $y \in\func f{\bar X}$ then $\func{g^{-1}}y \subset \bar X$.

To show this we will let $\bar X$ be any subset of $X$. Now let $y \in \func g{\bar X}$ and $x\in\bar X$ su. $\func gx = y$. Then for all $k \in\func{g^{-1}}y$, $k=x$, by $g$ being injective. Thus $\func{g^{-1}}y\subset\bar X$.

\begin{align*}
y \in \func f{A_0} \inter \func f{A_1} &\implies y \in \func f{A_0} \And y \in \func f{A_1} \\
&\implies \func{f^{-1}}y \subset A_0 \And \func{f^{-1}}y \subset A_1 \\
&\implies \func{f^{-1}}y \subset A_0 \inter A_1 \\
&\implies y \in \func f{A_0 \inter A_1}
\end{align*}

\question{3(b)} First we show $\func{f^{-1}}{\bigunion B_i} \subset \bigunion\func{f^{-1}}{B_i}$.
\begin{align*}
x \in \func{f^{-1}}{\bigunion B_i} &\implies \func fx \in \bigunion B_i \\
&\implies \Exists{i}{\func fx \in B_i} \\
&\implies \Exists{i}{x \in \func{f^{-1}}{B_i}} \\
&\implies x \in \bigunion\func{f^{-1}}{B_i}
\end{align*}
and now we show $\bigunion\func{f^{-1}}{B_i}\subset\func{f^{-1}}{\bigunion B_i}$.
\begin{align*}
x\in\bigunion\func{f^{-1}}{B_i} &\implies \Exists i{x\in\func{f^{-1}}{B_i}} \\
&\implies \Exists i{\func fx\in B_i} \\
&\implies \func fx \in \bigunion B_i \\
&\implies x \in \func{f^{-1}}{\bigunion B_i}
\end{align*}
Thus we have shown $\func{f^{-1}}{\bigunion B_i} = \bigunion\func{f^{-1}}{B_i}$.

\question{(g)} First we will show $\func f{\biginter A_i}\subset\biginter\func f{A_i}$. We start by noting that $\All{b\in\func f{\biginter A_i}}{\Exists{a \in \biginter A_i}{\func fa = b}}$, thus in the following proof we will let $b\in\func{f}{\biginter A_i}$ and let $a$ be such that $a \in \biginter A_i$ and $f(a) = b$.
\begin{align*}
a \in \biginter A_i &\implies \All i{a\in A_i} \\
&\implies \All i{\func fa \in \func f{A_i}} \\
&\implies \func fa \in\biginter\func f{A_i} \\
&\implies b \in \biginter\func f{A_i}
\end{align*}

Next we will let $f:A\to B$ be injective and show that then $\func f{\biginter A_i} \supset \biginter \func f{A_i}$.
\begin{align*}
b\in\biginter\func f{A_i} &\implies \All i{b\in\func f{A_i}} \\
&\implies \All i{\Exists{a\in\func{f^{-1}}b}{a\in A_i}} \\
&\implies \All i{f^{-1}b}\subset A_i \\
&\implies \func{f^{-1}}b \subset \biginter A_i \\
&\implies b \in \func f{\biginter A_i}
\end{align*}

\question{4(a)}
\begin{align*}
\func{f^{-1}}{\func{g^{-1}}{C_0}} &= \setbuilder a{\func fa\in\func{g^{-1}}{C_0}} \\
&= \setbuilder a{\func fa \in\setbuilder b{\func gb \in C_0}} \\
&= \setbuilder a{\Exists{b\in B}{\func fa=b \And \func gb\in C_0}} \\
&= \setbuilder a{\func{g\composed f}a \in C_0} \\
&= \func{(g\composed f)^{-1}}{C_0}
\end{align*}

\question{(b)} The definition of injective is $\func fa=\func f{a'} \implies a = a'$, thus by contra-position we know can also say that some function $f$ is injective iff
\begin{equation}\label{contra injective}
a \not= a' \implies \func fa \not= \func f{a'}
\end{equation}
So if we can show that \eqref{contra injective} is true for when the function is $g\composed f$, where $f$ and $g$ are injective. We also will make use of the fact that $\func{g\composed f}x= \func g{\func fx}$.

First let $a \in A$ and $a' \in A$ su. $a\not=a'$, then $\func ga \not= \func g{a'}$ as $g$ is injective. Now we can say that $\func f{\func ga} \not= \func f{\func g{a'}}$ by the same logic. Thus we can say $f\composed g$ is injective.

\question{(c)} $f$ is injective, and we don't know weather or not $g$ is injective. We will prove that $f$ is injective if $g\composed f$ is injective by contradiction.

First, let it be a given that $g \composed f$ is injective, and let us assume that $f$ is not injective. That would mean \[\Exists{x\not=x'}{\func fx = \func f{x'}}\] then we would know that \[\Exists{x\not=x'}{\func{g\composed f}x = \func{g\composed f}{x'}}\], thus $g \composed f$ would not be injective, thus by contradiction we know $f$ is injective.

\question{5(a)} An identity function must be injective, thus by the proof from above we know that if $g\composed f = i_A$ then $f$ is injective.

An identity function must be surjective, thus by the proof given below we know that if $f \composed h = i_A$ then $f$ is surjective.

Let $f\composed h: A \to C$ be a surjective function, and let $f: B\to C$, and $h:A\to B$. Assume $f$ is not surjective, then \[\Exists{c\in C}{\All{b\in B}{\func fb \not= c}}\] This would then mean \[\Exists{c \in C}{\All{a \in A}{\func {f \composed h}b \not= c}}\] thus $f \composed h$ would not be surjective, thus there is a contra diction and $f$ must be a surjective.

\question{(b)} The function $f:\mathbb R \to \mathbb R_+$ defined by $\func fx = e^x$.

\question{3.13} Prove: If an ordered set $A$ has the least upper bound property, then it has the greatest lower bound property.

Let $A$ be a least upper bound property. Let $B \subset A$ such that $B$ has a lower bound. Let $L$ be the set of all lower bounds for $B$.
\[L = \setbuilder{a}{\All{b\in B}{a\le b}}\]
now let $b\in B$, thus $\All{\ell \in L}{b \ge \ell}$, thus $L$ has an upper bound. Thus $L$ has a least upper bound, which we will refer to as $x$.
\[\All{\ell\in L}{\ell\in x}\]
thus $x$ is the greatest lower bound for $B$. Thus $B$ has a greatest lower bound, and thus $A$ has a greatest lower bound property.
\end{document}

### 2019-04-14 SchoolCode/Topology/HW2.tex

\documentclass{article}

\input{definitions.tex}
\def\useLim{}

\title{Topology Homework 2}

\begin{document}
\maketitle

\question{13.1.} Given that $A \subset X$ and $X$ has topology $\mathscr T$ and $\All{x\in A}{\Exists{U\in\mathscr T}{x \in U \And U \subset A}}$, show that $A \in \mathscr T$.

Let $U_x$ be an open subset of $A$ su. $x \in U$, we know this exists as it is given.
\begin{enumerate}
\item $\unionacross{x\in A}{U_x}$ is open as it is the union of open sets.
\item $\unionacross{x\in A}{U_x} \subset A$ as all $U_x \subset A$.
\item $\unionacross{x\in A}{U_x} \supset A$ as for any $x'\in A$ is in at least one $U_x$ namely $U_{x'}$.
\end{enumerate}
Thus $\unionacross{x\in A}{U_x} = A$ and is open, thus $A$ must be open.

\question{13.2.} We will make a table here comparing each pair of two topologies on $X$. It will be read as: $<$ means that the row's value is finer then the column's value, $>$ means that the row's value is coarser then the column's value, $=$ means the row and column are the same, and $/$ means they are not compareable. First let us list all nine topologies though.

\begin{enumerate}
\item $\set{\emptyset, X}$
\item $\set{\emptyset, \set a, \set{a,b}, X}$
\item $\set{\emptyset, \set{a,b}, \set b, \set{b,c}, X}$
\item $\set{\emptyset, \set b, X}$
\item $\set{\emptyset, \set a, \set{b,c}, X}$
\item $\set{\emptyset, \set{a,b}, \set b, \set{b,c},\set c, X}$
\item $\set{\emptyset, \set{a,b}, X}$
\item $\set{\emptyset, \set a, \set{a,b}, \set b, X}$
\item $\func{P}{X}$, where $\func PS$ is the powerset of $S$.
\end{enumerate}

\[
\begin{array}{c|c|c|c|c|c|c|c|c|c}
&1&2&3&4&5&6&7&8&9\\\hline 1
&=&<&<&<&<&<&<&<&<\\\hline 2
&>&=&/&/&/&/&>&/&<\\\hline 3
&>&/&=&>&/&<&>&/&<\\\hline 4
&>&/&<&=&/&<&/&<&<\\\hline 5
&>&/&/&/&=&/&/&/&<\\\hline 6
&>&/&>&>&/&=&>&/&<\\\hline 7
&>&<&<&/&/&<&=&<&<\\\hline 8
&>&/&/&>&/&/&>&=&<\\\hline 9
&>&>&>&>&>&>&>&>&=
\end{array}
\]

\question{3.} Let $X$ be a set; show that $\mathscr T_c = \setbuilder{U\subset X}{X-U \text{ is countable } \Or X - U = X}$ is a topology on $X$.
\begin{align*}
\mathscr T_c &= \setbuilder{U\subset X}{X-U \text{ is countable } \Or X - U = X} \\
&= \setbuilder{U\subset X}{\setcomp U \text{ is countable } \Or \setcomp U = X} \\
&= \setbuilder{U\subset X}{\setcomp U \text{ is countable } \Or U = \emptyset}
\end{align*}

First note that $\emptyset = \emptyset \implies \emptyset \in \mathscr T_c$ and $\setcomp X = \emptyset$ is countable $\implies X \in \mathscr T_c$, thus the first condition is satisfied.

Now to show the second condition, let $\mathscr A \subset \mathscr T_c$. We will show $\unionacross{A\in\mathscr A}A \in \mathscr T_c$ by contradiction, so we will assume $\unionacross{A\in\mathscr A}A \not\in \mathscr T_c$, thus we know \[\setcomp{\left(\unionacross{A\in\mathscr A}A\right)}\text{ is not countable}\And\unionacross{A\in\mathscr A}A \not= \emptyset\] thus \[\unionacross{A\in\mathscr A}A\not=\emptyset\implies\Exists{A\in\mathscr A}{A\not=\emptyset}\implies\Exists{A\in\mathscr A}{\setcomp A\text{ is countable}}\] and \[\setcomp{\left(\unionacross{A\in\mathscr A}A\right)}\text{ is not countable }\implies\interacross{A\in\mathscr A}{\setcomp A}\text{ is not countable }\implies\All{A\in\mathscr A}{\setcomp{A}\text{ is not countable}}\] thus there is a contradiction, thus our second condition is met.

Now to show the third condition, we will try to show that for any finite $\mathscr A \subset \mathscr T_c$\[\interacross{A\in\mathscr A}{A}\in\mathscr T_c\] If $A$ is finite, that means that $\cardinality A \in \mathbb N$.\footnote{$\mathbb N = \set{0, 1, 2, \ldots}$} Thus if show that the statement holds when $\cardinality{\mathscr A} = 0$, and then show that the statement holding when $\cardinality{\mathscr A}=n$ implies that the statement will hold when $\cardinality{\mathscr A}=n+1$, where $n \in \mathbb N$, then we will have shown that our statement is true in all cases.

If $\cardinality{\mathscr A} = 0$ then $\mathscr A = \emptyset$, thus $\interacross{A\in\mathscr A}{A} = X \in \mathscr T_c$, thus our base case is fulfiled.

Now let us assume that for any $\mathscr A \subset \mathscr T_c$ with cardinality $n$, $\interacross{A\in\mathscr A}{A}\in\mathscr T_c$. Now let $\mathscr A \subset \mathscr T_c$ such that $\cardinality{\mathscr A} = n+1$. Let $B$ and $C$ form a partition on $\mathscr A$ such that $\cardinality C = 1$, thus we know that $\cardinality B = n$. Since $\cardinality B = n$ and $B \subset \mathscr A \subset \mathscr T_c$ we know, via our assumption that $\interacross{A\in B}A\in\mathscr T_c$. We also know that $C \subset \mathscr A \subset \mathscr T_c$. Because $B$ and $C$ form a partition on $\mathscr A$ we can say that \[\interacross{A\in\mathscr A}A = \interacross{A\in B}A \inter \interacross{A\in C}A\] Now there are two cases either one of the intersection across a partition, is the empty set, in which case it's tirvial that the entire intersection is in the topology, or they both compliments of countable sets. In the case where both are countable sets we will let \begin{align*}\interacross{A\in B}A &= \mathcal B\\\interacross{A\in C}A&=\mathcal C\end{align*} thus, $\setcomp{\mathcal B}$ and $\setcomp{\mathcal C}$ are countable.\[\setcomp{\mathcal B} \inter \setcomp{\mathcal C} = \setcomp{\left(\mathcal B \union \mathcal C\right)}\] Because the union of countable sets is countable, then $\setcomp{\left(\mathcal B \union \mathcal C\right)}$ is the compliment of two countable sets and thus is in the topology $\mathscr T_c$.

The set defined by $\mathscr T_\infty$ is not a topology for all sets $X$, a counter example is consider $\mathscr T_\infty$ on $\mathbb R$ then then any singleton set is in $\mathscr T_\infty$, then if we take the union of all singletons except $\set0$, then we have a set not in $\mathscr T_\infty$.

\question{4.}

\question{7.}

\question{8.}

\end{document}

### 2019-04-16 Topology/Paper/paper.tex
Hi
read section 4

@@
 
-\newpage
-
 \section{Kuratowski's Theorem}
@@
 
-\subsection{$K_{3,3}$ and $K_5$}
+\subsection{$K_5$ and $K_{3,3}$}
 Our first step is proving that $K_{3,3}$ and $K_5$ are nonplanar. To do this we are going to use the following theorem.
 
-\begin{theorem}[Euler's formula on planar graphs]
-	For any plane drawing of a graph, we have $$v-e+f=2$$, where $v$ is the number of vertices in the graph, $e$ is the number of edges in the graph, and $f$ is the number of faces in the plane drawing of the graph.
+\begin{theorem}[Euler's formula on planar multigraphs]
+	For any plane drawing of a multigraph (with the exception of a multigraph with no vertices), we have $$v-e+f=2$$, where $v$ is the number of vertices in the multigraph, $e$ is the number of edges in the multigraph, and $f$ is the number of faces in the plane drawing of the multigraph.
 \end{theorem}
-%TODO credit this to https://www.ics.uci.edu/~eppstein/junkyard/euler/interdig.html
-Before we can prove this we need to define the dual of a planar graph.
-\begin{definition}[graph dual]
-	For any plane drawing $G$ of a graph, we may construct it's dual $G*$ by putting a single vertex in each face, and putting an edge between any two adjacent faces (faces that share an edge).
-Note that this dual is not necessarily a graph, but will fit our definition of a multigraph.
-\end{definition}
-For example consider the following graph drawing
-\input{Duals_graphs.tex}
+
+%TODO cite https://www.ics.uci.edu/~eppstein/junkyard/euler/iedge.html
 
 \begin{proof}
+	First consider a connected multigraph with no edges, as this is connected we may only have a single vertex.
+This produces a single and no edges so we find $$v-e+f=1-0+1=2$$.
+Now that we no that for 0 edges this rule fits, then either the rule ($v-e+f-2$) is true no mater the number of edges, or there is some number at which point this rule breaks, and $v-e+f\not=2$.
+If there is a number that breaks this rule, then there must be a lowest number (lets call it $k$) that breaks this rule.
+For any multigraph with $k$ edges, choose any edge $e$ in the graph.
+	\begin{itemize}
+		\item If $e$ connects a vertex to itself it is a loop and it's removal will result in the loss of one edge and one face (each loop creates a face\footnote{Jordan curve theorem}).
+The resulting multigraph has less than $k$ edges and thus we know that for it \begin{align*}2&=v-e+f \\&= v-(e+1)+(f+1)\end{align*} and as the original graph had one more edge and one more face it too would fit this rule.
+		\item If $e$ is not a loop we may preform an edge contraction on it and this will reduce both the number of edges and the number of vertices by one.
+Again this gives us a multigraph with less than $k$ edges so we know that for it \begin{align*}2&=v-e+f\\&=(v+1)-(e+1)+f\end{align*} and as the original graph had one more edge and one more vertex it to would fit this rule.
+	\end{itemize}
 
+	From this we know that there can not possibly be some $k$, and thus all multigraphs, regardless of the number of edges must fit this rule.
+\end{proof}
+This leads to a nice corollary, that will be helpful when talking about graphs.
+\begin{corallary}
+	Any plane drawing of any multigraph has the same number of faces.
+\end{corallary}
+\begin{proof}
+	Any planar multigraph can be broken into connected components.
+Each component of a planar multigraph is a connected planar multigraph and thus any planar drawing of it fits the rule $v-e+f=2$.
+Now any plane drawing we make of a planar multigraph will be made of parts that already have a constant number of faces.\footnote{This is not a complete proof, to complete it you simply make an induction on the number of components drawn and realize each time you add a component you add exactly $f_{i}-1$ new faces (if $f_i$ is the number of faces in the $i^{\text{th}}$ component drawn).}
+
+	%Each drawing of every component has the same number of edges and vertices, and therefore by our equation the number of faces must also be the same in each component's drawing.
+Now we make a plane drawing of each component one by one to create a plane drawing of the full multigraph.
+Choose a component to draw first and when we draw it we know it will have some number $f_1$ of faces regardless of it's drawing.
+Now if we have already drawn in $k$ components we can add the $k+1^{\text{th}}$ component.
+To do this we must draw it completely within one of the faces that already exists as it is a plane drawing.
+This adds exactly $f_{k+1}-1$ faces by drawing this component as it simply splits one already existing face into $f_{k+1}$ new faces.
+This means that no mater what order we add faces in
+\end{proof}
+
+This means that given any planar multigraph $G$, we can talk about the number of faces $G$ has without referring to any drawing of $G$, as all plane drawings will have the same number of faces.
+
+Now using this we can prove that $K_{3,3}$ and $K_5$ are nonplanar.
+
+\begin{theorem}
+	$K_5$ is nonplanar.
+\end{theorem}
+\begin{center}
+	\scalebox{.6}{
+		\begin{tikzpicture}[auto, node distance=3cm, every loop/.style={},
+		thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries}]
+
+			\node[main node] (1) {};
+			\node[main node] (2) [below left of=1] {};
+			\node[main node] (3) [below right of=1] {};
+			\node[main node] (4) [below of=2] {};
+			\node[main node] (5) [below of=3] {};
+
+			\path[every node/.style={font=\sffamily\small}]
+			(1)	edge node {} (2)
+			edge node {} (3)
+			edge node {} (4)
+			edge node {} (5)
+			(2) edge node {} (3)
+			edge node {} (4)
+			edge node {} (5)
+			(3) edge node {} (4)
+			edge node {} (5)
+			(4) edge node {} (5);
+		\end{tikzpicture}
+	}
+
+	\scalebox{.9}{$K_5$}
+\end{center}
+\begin{proof}
+	$K_5$ is a graph\footnote{Recall that all graphs are multigraphs, but not all multigraphs are graphs.}, and as such an edge can not be a loop and two vertices can share at most one edge.
+This means that in any plane drawing of a graph, there must be at least 3 edges bordering every face.
+	\begin{itemize}
+		\item To only have one edge bordering a face would require that the edge be a loop (which we can't have in a graph).
+		\item To only have only two edges bordering a face would require that some pair of vertices share more than one edge (which we can't have in a graph).
+	\end{itemize}
+	Additionally every edge boarders no more than two faces, so from this we know that in any graph $2e \ge 3f$ or $\frac23e\ge f$.
+Now $K_5$ has 10 edges and 5 vertices, so we know that $$\frac2310=\frac{20}3=6.\bar6\ge f$$ We know that $K_5$ is a connected graph (and thus also a connected multigraph) so if $K_5$ were planar then we would have $$2=v-e+f=5-10+f\le5-10+6.\bar6 = 1.\bar6$$ which is clearly false as $$2\not\le1.\bar6$$ Therefore $K_5$ must not be planar.
+\end{proof}
+
+\begin{theorem}
+	$K_{3,3}$ is nonplanar.
+\end{theorem}
+\begin{center}
+	\scalebox{.6}{
+		\begin{tikzpicture}[auto, node distance=3cm, every loop/.style={},
+		thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries}]
+
+			\node[main node] (1) {};
+			\node[main node] (2) [below of=1] {};
+			\node[main node] (3) [below of=2] {};
+			\node[main node] (4) [right of=1] {};
+			\node[main node] (5) [below of=4] {};
+			\node[main node] (6) [below of=5] {};
+
+			\path[every node/.style={font=\sffamily\small}]
+			(1)	edge node {} (4)
+			edge node {} (5)
+			edge node {} (6)
+			(2)	edge node {} (4)
+			edge node {} (5)
+			edge node {} (6)
+			(3)	edge node {} (4)
+			edge node {} (5)
+			edge node {} (6);
+		\end{tikzpicture}
+	}
+
+	\scalebox{.9}{$K_{3,3}$}
+\end{center}
+\begin{proof}
+	$K_{3,3}$ is a bipartite graph, meaning that there is some way to break the graph into two collections of vertices, where there are no edges that stay within one of these collections.
+If we look at the drawing of $K_{3,3}$ above we see that the right and left works as these collections for us.
+There is no edge that goes between two vertices on the right or two vertices on the left.
+This means that if we can make a plane drawing of $K_{3,3}$ each face must have at east four edges on it's boundary.
+We know from our proof of $K_5$'s nonplanarity that each face in a graph must have at least three edges on it's boundary.
+If any face were to have three edges then the cycle bounding the face would have exactly three vertices as well.
+Each pair of vertices within these three vertices would share an edge and therefore there is no way to split them up into two groups such that neither group has an edge within it.
+Additionally every edge boarders no more than two faces, so from this we know that in any bipartite graph $2e \ge 4f$ or $e\ge 2f$.
+
+	Now $K_{3,3}$ has 6 vertices and 9 edges.
+$K_{3,3}$ is bipartite so the number of faces, $f \le \frac e2 = \frac92 = 4.5$.
+$K_{3,3}$ is connected, so if it were planar we would have Euler's formula giving us $$2=v-e+f=6-9+f\le6-9+4.5=1.5$$ and this is false as $$2\not\le1.5$$ Therefore $K_{3,3}$ is nonplanar.
 \end{proof}

### 2019-04-16 Topology/Paper/paper.tex
no to know

@@
 \begin{theorem}[Euler's formula on planar multigraphs]
-	For any plane drawing of a multigraph (with the exception of a multigraph with no vertices), we have $$v-e+f=2$$, where $v$ is the number of vertices in the multigraph, $e$ is the number of edges in the multigraph, and $f$ is the number of faces in the plane drawing of the multigraph.
+	For any plane drawing of a multigraph (with the exception of a multigraph with no vertices), we have $$v-e+f=2$$, where $v$ is the number of vertices in the multigraph, $e$ is the number of edges in the multigraph, and $f$ is the number of faces in a plane drawing of the multigraph.
 \end{theorem}
@@
 This produces a single and no edges so we find $$v-e+f=1-0+1=2$$.
-Now that we no that for 0 edges this rule fits, then either the rule ($v-e+f-2$) is true no mater the number of edges, or there is some number at which point this rule breaks, and $v-e+f\not=2$.
+Now that we know that for 0 edges this rule fits, then either the rule ($v-e+f-2$) is true no mater the number of edges, or there is some number at which point this rule breaks, and $v-e+f\not=2$.
 If there is a number that breaks this rule, then there must be a lowest number (lets call it $k$) that breaks this rule.

### 2019-04-16 Topology/Paper/paper.tex
reload again

@@
 	First consider a connected multigraph with no edges, as this is connected we may only have a single vertex.
-This produces a single and no edges so we find $$v-e+f=1-0+1=2$$.
-Now that we know that for 0 edges this rule fits, then either the rule ($v-e+f-2$) is true no mater the number of edges, or there is some number at which point this rule breaks, and $v-e+f\not=2$.
+This produces a single and no edges so we find $$v-e+f=1-0+1=2$$ Now that we know that for 0 edges this rule fits, then either the rule ($v-e+f-2$) is true no mater the number of edges, or there is some number at which point this rule breaks, and $v-e+f\not=2$.
 If there is a number that breaks this rule, then there must be a lowest number (lets call it $k$) that breaks this rule.

### 2019-04-16 Topology/Paper/paper.tex
evidenently Let's has an appostrophy
Julia revisions

@@
 In giving an overview of the field we will cover some of the basic concepts and definitions needed for the more rigorous part of the paper.
-After the overview we will dive into Kuratowski's Theorem, We will go through and attempt to have an intuitive understanding of a Kuratowski's Theorem and it's proof.
+After the overview we will dive into Kuratowski's Theorem, We will go through and attempt to have an intuitive understanding of a Kuratowski's Theorem and its proof.
 After proving Kuratowski's Theorem, we will continue onto talking about generalizations of the theorem and map colorings, however their coverage will be rather shallow and lacking proofs.
@@
 
-\subsection{K\"onigsberg, and it's seven bridges}
+\subsection{K\"onigsberg, and its seven bridges}
 
@@
 This produces a single and no edges so we find $$v-e+f=1-0+1=2$$ Now that we know that for 0 edges this rule fits, then either the rule ($v-e+f-2$) is true no mater the number of edges, or there is some number at which point this rule breaks, and $v-e+f\not=2$.
-If there is a number that breaks this rule, then there must be a lowest number (lets call it $k$) that breaks this rule.
+If there is a number that breaks this rule, then there must be a lowest number (let's call it $k$) that breaks this rule.
 For any multigraph with $k$ edges, choose any edge $e$ in the graph.
 	\begin{itemize}
-		\item If $e$ connects a vertex to itself it is a loop and it's removal will result in the loss of one edge and one face (each loop creates a face\footnote{Jordan curve theorem}).
+		\item If $e$ connects a vertex to itself it is a loop and its removal will result in the loss of one edge and one face (each loop creates a face\footnote{Jordan curve theorem}).
 The resulting multigraph has less than $k$ edges and thus we know that for it \begin{align*}2&=v-e+f \\&= v-(e+1)+(f+1)\end{align*} and as the original graph had one more edge and one more face it too would fit this rule.
-		\item If $e$ is not a loop we may preform an edge contraction on it and this will reduce both the number of edges and the number of vertices by one.
+		\item If $e$ is not a loop we may perform an edge contraction on it and this will reduce both the number of edges and the number of vertices by one.
 Again this gives us a multigraph with less than $k$ edges so we know that for it \begin{align*}2&=v-e+f\\&=(v+1)-(e+1)+f\end{align*} and as the original graph had one more edge and one more vertex it to would fit this rule.
@@
 Now we make a plane drawing of each component one by one to create a plane drawing of the full multigraph.
-Choose a component to draw first and when we draw it we know it will have some number $f_1$ of faces regardless of it's drawing.
+Choose a component to draw first and when we draw it we know it will have some number $f_1$ of faces regardless of its drawing.
 Now if we have already drawn in $k$ components we can add the $k+1^{\text{th}}$ component.
@@
 There is no edge that goes between two vertices on the right or two vertices on the left.
-This means that if we can make a plane drawing of $K_{3,3}$ each face must have at east four edges on it's boundary.
-We know from our proof of $K_5$'s nonplanarity that each face in a graph must have at least three edges on it's boundary.
+This means that if we can make a plane drawing of $K_{3,3}$ each face must have at least four edges on its boundary.
+We know from our proof of $K_5$'s nonplanarity that each face in a graph must have at least three edges on its boundary.
 If any face were to have three edges then the cycle bounding the face would have exactly three vertices as well.

### 2019-04-20 Topology/Paper/paper.tex
Nearly there

@@
 \begin{theorem}[Euler's formula on planar multigraphs]
-	For any plane drawing of a multigraph (with the exception of a multigraph with no vertices), we have $$v-e+f=2$$, where $v$ is the number of vertices in the multigraph, $e$ is the number of edges in the multigraph, and $f$ is the number of faces in a plane drawing of the multigraph.
+	For any plane drawing of a multigraph (with the exception of a multigraph with no vertices), we have $$v-e+f=2$$, where $v$ is the number of vertices in the multigraph, $e$ is the number of edges in the multigraph, and $f$ is the number of faces in the plane drawing of the multigraph.
 \end{theorem}
@@
 
+\subsection{Some basic lemmas}
+This is the point in the paper where it is no longer written to be understood by everyone. %TODO make this better
+
+\begin{lemma}
+	If a graph $G$ has a nonplanar subgraph, then $G$ is nonplanar.
+\end{lemma}
+
+%TODO prove
+
+\begin{lemma}
+	If a graph $G$ is a subdivision of a nonplanar graph, then $G$ is nonplanar.
+\end{lemma}
+
+%TODO prove
+
+\begin{definition}[minimal nonplanar graph]
+	A nonplanar graph $G$ is said to be a minimal nonplanar graph if for all edges $e\in G$ the removal of $e$ would yield a  graph.
+\end{definition}
+
+\begin{lemma}
+	For any nonplanar graph $G$ there exists a minimal nonplanar subgraph.
+\end{lemma}
+\begin{proof}
+	Let $G$ be a nonplanar graph with $n$ edges.
+The removal of all edges from $G$ would yield a graph with only vertices which is trivially planar.
+This means there is some least number $k$ such that there exists a nonplanar subgraph of $G$ with $k$ edges.
+Any such nonplanar subgraph of $G$, must be a minimal nonplanar graph as the removal of any edge from it would yield a subgraph of $G$ with less than $k$ edges.
+\end{proof}
+
+\begin{lemma}
+	Every minimal nonplanar graph contains a connected minimal nonplanar subgraph.
+\end{lemma}
+\begin{proof}
+	%TODO redo proof
+	Let $G$ be a minimal nonplanar graph.
+If $G$ is connected then $G$ contains itself as a minimal nonplanar subgraph.
+If $G$ is not connected then it is composed of connected components.
+When embedding $G$ within the plane, if every component was planar we could embed them into any space homeomorphic to $\mathbb R^2$.
+For example each component could be embedded in an open disk with radius $1/2$ about a separate point in $\mathbb Z^2$, and this would then be a plane drawing.
+This means that at least one component in $G$ must be nonplanar.
+Now every other component in this graph may not have any edges as their removal would still yield a nonplanar graph (which breaks the definition of minimal nonplanar).
+This means that there is only one nonplanar component, and further if any edge from this component is to be removed then $G$ would be planar.
+Now by .
+From this we get that this component is itself a connected minimal nonplanar subgraph of $G$.
+\end{proof}
+
 \printnoidxglossary

### 2019-05-04 Topology/Paper/paper.tex
SO much progress

@@
 \input{../topology}
-\input{glossary}
 \title{Topological Graph Theory}
@@
 \subsection{Graphs}
-Before we talk about topological graph theory with any level of understanding we must first understand what a \gls{graph} is.
+Before we talk about topological graph theory with any level of understanding we must first understand what a graph is.
 
-A \gls{graph} is generally defined as a \gls{set} of \glspl{vertex} combined with a \gls{set} of \glspl{edge} between \glspl{vertex}, however here it may be more useful to think about them visually with a simple representation.
+A graph is generally defined as a set of vertices combined with a set of edges between vertices, however here it may be more useful to think about them visually with a simple representation.
 
-Consider first a \gls{set} of points, this may be thought of as just drawing dots on a sheet of paper.
-Each of these points will be called a \gls{vertex}.
-Now we may start drawing lines between \glspl{vertex}.
+Consider first a set of points, this may be thought of as just drawing dots on a sheet of paper.
+Each of these points will be called a vertex.
+Now we may start drawing lines between vertices.
 Lines may cross over each other and need not be straight.
-There is no requirement that all \glspl{vertex} have a line going to it.
-Each of these lines are called an \gls{edge}.
-We will simply insist that no \gls{edge} connects two \glspl{vertex} and that we do not have multiple \glspl{edge} between the same pair of \glspl{vertex}.
+There is no requirement that all vertices have a line going to it.
+Each of these lines are called an edge.
+We will simply insist that no edge connects two vertices and that we do not have multiple edges between the same pair of vertices.
 
-Once we have drawn this we have a representation of a \gls{graph}.
-If we were to move the \glspl{vertex} around on the paper but leave them having the same \glspl{edge} (the same \glspl{vertex} are connected to the point as they were before).
-we would be left with the same \gls{graph}.
-That is to say, it doesn't mater where we put a \gls{vertex} on our sheet, the \gls{graph} exists independently of the representation we draw.
+Once we have drawn this we have a representation of a graph.
+If we were to move the vertices around on the paper but leave them having the same edges (the same vertices are connected to the point as they were before).
+we would be left with the same graph.
+That is to say, it doesn't mater where we put a vertex on our sheet, the graph exists independently of the representation we draw.
 
@@
 While undoubtedly an interesting problem, it is quite misleading to try and think of this as a geometry problem.
-Instead we will try and reduce it to a \gls{graph} problem.
+Instead we will try and reduce it to a graph problem.
 
-Let us start by thinking of every island as a \gls{vertex} and every bridge as an \gls{edge}. We find the following \gls{graph}.
+Let us start by thinking of every island as a vertex and every bridge as an edge. We find the following graph.
 
@@
 It is worth noting two things about the above diagram.
-First that the labels on the \glspl{vertex} and \glspl{edge} are unrelated to the problem, but have been added simply to make referring to parts of the \gls{graph} much easier.
-Second that whatever the above image depicts, does not fit our definition of a \gls{graph}.
+First that the labels on the vertices and edges are unrelated to the problem, but have been added simply to make referring to parts of the graph much easier.
+Second that whatever the above image depicts, does not fit our definition of a graph.
 
-Notice that \gls{edge} $2$ and \gls{edge} $3$ both connect \gls{vertex} $A$ to $B$, as well \glspl{edge} $5$ and $6$ do for $B$ and $C$.
-This is a strict violation of our definition for a \gls{graph}.
-The issue of course then comes to what would one call such a beast as this where, presumably, one is able to have as many connections between any pair of \glspl{vertex} and could even have connections from a \gls{vertex} to itself.
+Notice that edge $2$ and edge $3$ both connect vertex $A$ to $B$, as well edges $5$ and $6$ do for $B$ and $C$.
+This is a strict violation of our definition for a graph.
+The issue of course then comes to what would one call such a beast as this where, presumably, one is able to have as many connections between any pair of vertices and could even have connections from a vertices to itself.
 
-I am particularly glad that you're paying enough attention to notice that the diagram does not depict a \gls{graph}.
-This is what we will refer to as a \gls{multigraph}.
-It is worth noting that \glspl{graph} are a type of \gls{multigraph}, so anything we show to be true for all \glspl{multigraph}, is also true for all \glspl{graph}.
+I am particularly glad that you're paying enough attention to notice that the diagram does not depict a graph.
+This is what we will refer to as a multigraph.
+It is worth noting that graphs are a type of multigraph, so anything we show to be true for all multigraphs, is also true for all graphs.
 
@@
 This means, that with the exception of the island we start on and end on, each island must have an even number of bridges connected to it.
-On the \gls{multigraph} we would say that we need all \glspl{vertex} but a start and end \gls{vertex} to have an even number of edges.
-If we look at the \gls{multigraph} above, we have four \glspl{vertex} that have an odd number of \glspl{edge} connected to them.
+On the multigraph we would say that we need all vertices but a start and end vertex to have an even number of edges.
+If we look at the multigraph above, we have four vertices that have an odd number of edges connected to them.
 
@@
 
-Consider the following \gls{graph}.
+Consider the following graph.
 
@@
 
-This \gls{graph} is called a \gls{complete} as every \gls{vertex} is connected to every other \gls{vertex} by an \gls{edge}; in fact this \gls{graph} in particular is called $K_4$ as it is the complete four vertex \gls{graph}.
-We would like to find out if we can draw this above \gls{graph} without having any lines crossing.
-We can in fact draw this \gls{graph} without any intersections and for any skeptics who may being reading this, the below is $K_4$ without any \glspl{edge} intersecting.
+This graph is called a complete as every vertex is connected to every other vertex by an edge; in fact this graph in particular is called $K_4$ as it is the complete four vertex graph.
+We would like to find out if we can draw this above graph without having any lines crossing.
+We can in fact draw this graph without any intersections and for any skeptics who may being reading this, the below is $K_4$ without any edges intersecting.
 
@@
 
-So if this \gls{graph} can be drawn without intersection, can any \gls{graph} be drawn without intersections?
+So if this graph can be drawn without intersection, can any graph be drawn without intersections?
 If some can and some can't how do we tell which can be drawn and which can not?
@@
 
-A face is defined as a connected space that contains no edges or verticies and itself is bounded by edges and verticies.
+A face is defined as a connected space that contains no edges or vertices and itself is bounded by edges and vertices.
 
-If you think back to high-school geometry and cubes you may recall that a each of the corners is a vertex, the lines connecting verticies are edges and the area between the edges are faces.
-In a graph we have verticies connected by edges and when we draw them there are empty areas enclosed by edges and verticies.
+If you think back to high-school geometry and cubes you may recall that a each of the corners is a vertex, the lines connecting vertices are edges and the area between the edges are faces.
+In a graph we have vertices connected by edges and when we draw them there are empty areas enclosed by edges and vertices.
 For example the following would correspond with a cube
@@
 The same is true for $ABFE$, $ACGE$, $DBFH$, and $DCGH$, however that leaves us with only five faces on this cube.
-The last face must logically come from $EFHG$, however the area enclosed by that contains all the other edges and verticies, so it doesn't fit our definition.
-However we may notice that the infinite space outside $EFHG$ does not contain any verticies, and therefore we get a sixth face.
+The last face must logically come from $EFHG$, however the area enclosed by that contains all the other edges and vertices, so it doesn't fit our definition.
+However we may notice that the infinite space outside $EFHG$ does not contain any vertices, and therefore we get a sixth face.
 
@@
 
-\subsection{Path}
-Now moving onto a more traditional graph property we have the concept of a path.
-A path is defined as a finite sequence of verticies with the property that each element of the sequence (excluding the last one) has an edge from it to the next element.
+\subsection{Walks}
+Now moving onto a more traditional graph property we have the concept of a walk.
+A walk can be thought of as if you were standing on some vertex $v_0$ and just kept following edges to neighboring vertices some number of times.
+We define it as follows.
+
+\begin{definition}[walk]
+	A walk is a finite sequence of vertices and edges with the following properties.
+	\begin{itemize}
+		\item Every odd element in the sequence is a vertex.
+		\item Every even element in the sequence is an edge that connects the vertex before and after it.
+		\item A walk always begins and ends with a vertex.
+	\end{itemize}
+\end{definition}
+
 For example consider the following graph.
@@
 	\path[every node/.style={font=\sffamily\small}]
-	(a) edge node {} (b)
-	edge node {} (c)
-	edge node {} (f)
-	(b) edge node {} (d)
-	edge node {} (g)
-	(c) edge node {} (e)
-	edge node {} (h)
-	(d) edge node {} (i)
-	(e) edge node {} (j)
-	(f) edge node {} (g)
-	edge node {} (h)
-	(g) edge node {} (i)
-	(h) edge node {} (j)
-	(i) edge node {} (j);
+	(a) edge node {$a$} (b)
+	edge node {$b$} (c)
+	edge node {$c$} (f)
+	edge node {$o$} (e)
+	(b) edge node {$d$} (d)
+	edge node {$e$} (g)
+	(c) edge node {$f$} (e)
+	edge node {$g$} (h)
+	(d) edge node {$h$} (i)
+	(e) edge node {$i$} (j)
+	(f) edge node {$j$} (g)
+	edge node {$k$} (h)
+	(g) edge node {$l$} (i)
+	(h) edge node {$m$} (j)
+	(i) edge node {$n$} (j);
 	\end{tikzpicture}
@@
 
-Now the sequence $BGF$ is a path as $B$ connects to $G$ and $G$ connects to $F$.
-The sequence $ABGFACEJHCABA$ is also a path, however $JEDI$ is not a path as $E$ has no edge to $D$.
-Notice that how we draw the graph has nothing to do with what is and is not a path.
+Now the sequence $BeGjF$ is a walk as we can think of starting at vertex $B$, walking down $e$ to $G$, then down $j$ to $F$ and  finishing.
+The sequence $AaBaA$ is also a walk as we could start at $A$, go down edge $a$ to $B$, then back up $a$ to $A$ again.
+The sequence $CfEi$ however isn't a walk as it doesn't end with a vertex.
+
+\subsubsection{Path}
+\begin{definition}[path]
+	A path is a walk where a vertex and edge can not appear twice in the sequence.
+\end{definition}
+
+You could think of a path as you start at some vertex and start building a path as you talk your walk. You aren't allows to have your path intersect with itself, so you always
+
+So for example with the above graph $BeGjF$ is not only a walk, but also a path. The sequence $AaBaA$, while it is a walk, it however is not a path as both edge $a$ and vertex $A$ are used twice.
+
+\subsubsection{Cycle}
+\begin{definition}[cycle]
+	A cycle is a walk, of length greater than one, where a vertex and edge can not appear twice in the sequence with the exception of the first and last vertex which must be the same.
+\end{definition}
+
+The definition for cycle is quite similar to that of a path, it effectively is a path that loops back to where it started at the end.
+The stipulation that a cycle must be "of length greater than one" simply means that the walk $A$ (just the vertex $A$ and nothing else) is not a cycle.
+Examples of a cycle would include $AbCgHkFcA$, $AbCfEoA$, and $FkHmJnIlGjF$.
+It is important to note that something like $FcAcF$ is not a cycle as it includes the edge $c$ twice.
 
 \subsection{Connected}
-A graph is said to be connected if for any pair of verticies, $\pair ab$ there is a path from $a$ to $b$. So if we consider the following graphs 
+A graph is said to be connected if for any pair of vertices, $\pair ab$ there is a walk from $a$ to $b$. So if we consider the following graphs 
 \begin{center}
@@
 
+%\subsection{Neighborhood}
+%Given some graph $G$ with vertex $v$.
+The neighborhood of $v$ within $G$ is the set of all vertices that share an edge with $v$, not including $v$.\footnote{If $G$ is a multigraph the definition stays the same, however $v$ maybe it's own neighbor if it has an edge with itself or a loop} Given a subgraph $H$ of $G$, the neighborhood of $H$ within $G$ is a new subgraph of $G$ that includes $H$ as well as any vertex in $G$ that is adjacent to a vertex in $H$ and the edge that they share.
+%
+%Lets look at some examples
+%\begin{center}
+%	\begin{tikzpicture}[auto, node distance=3cm, every loop/.style={},
+%	thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries}]
+%	
+%		\node[main node] (0) {\textcolor{blue}{$a$}};
+%		\node[main node] (1) [above right of=0] {\textcolor{red}{$b$}};
+%		\node[main node] (2) [right of=1] {$c$};
+%		\node[main node] (3) [below right of=2] {$d$};
+%		\node[main node] (4) [below of=3] {\textcolor{red}{$e$}};
+%		\node[main node] (5) [below left of=4] {$f$};
+%		\node[main node] (6) [left of=5] {$g$};
+%		\node[main node] (7) [above left of=6] {$h$};
+%		
+%		\path[every node/.style={font=\sffamily\small}]
+%		(0)
+%		edge node {} (2)
+%		edge node {} (3)
+%		edge node {} (4)
+%		(1)
+%		edge node {} (3)
+%		edge node {} (4)
+%		edge node {} (5)
+%		(2)
+%		edge node {} (4)
+%		edge node {} (5)
+%		(3)
+%		edge node {} (7)
+%		(4)
+%		edge node {} (6)
+%		edge node {} (7)
+%		(5)
+%		edge node {} (6)
+%		edge node {} (7)
+%		(6)
+%		edge node {} (7);
+%	\end{tikzpicture}
+%\end{center}
+%
+%First let us consider the neighborhood of just the vertex \textcolor{blue}{$a$}, this would then be all the vertices that it is adjacent to so we get $$\set{c, d, \textcolor{red}{e}}$$ We could also let $A$ be a subgraph containing only the vertex $\textcolor{blue}{a}$ and so it's neighborhood within $G$ will be the graph below.
+%\begin{center}
+%	\begin{tikzpicture}[auto, node distance=3cm, every loop/.style={},
+%	thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries}]
+%	
+%		\node[main node] (0) {\textcolor{blue}{$a$}};
+%		\node[main node] (2) [above right of=0] {$c$};
+%		\node[main node] (3) [below right of=2] {$d$};
+%		\node[main node] (4) [below of=3] {\textcolor{red}{$e$}};
+%		
+%		\path[every node/.style={font=\sffamily\small}]
+%		(0)
+%		edge node {} (2)
+%		edge node {} (3)
+%		edge node {} (4)
+%		(2)
+%		edge node {} (4);
+%	\end{tikzpicture}
+%\end{center}
+%The difference is that this is actually a subgraph of $G$, whereas the previous is just vertices.
+%
+%For another example let $H$ be the subgraph with only the \textcolor{red}{$b$}, \textcolor{red}{$e$} and the edge they share.
+The neighborhood of $H$ within $G$ within $G$ would then be all of $G$ as every vertex is either a neighbor of $b$ or $e$.
+%
 \subsection{Contraction}
-This is not a property, but rather an operation or action that we preform on a graph. Let us consider the following \gls{graph}.
+This is not a property, but rather an operation or action that we preform on a graph. Let us consider the following graph.
 
@@
 
-We wish to preform a \gls{contraction} on \gls{edge} $R$.
-To be clear all graph \glspl{contraction} are on \glspl{edge}.
-So we will make a new \gls{vertex}, $r\cdot s$ which has all the \glspl{edge} of $r$ and all the \glspl{edge} of $s$ except the \gls{edge} we are contracting across.
-In this case the \gls{edge} we are contracting across is $R$ and thus we get the following \gls{multigraph}.
+We wish to preform a contraction on edge $R$.
+To be clear all graph contractions are on edges.
+So we will make a new vertex, $r\cdot s$ which has all the edges of $r$ and all the edges of $s$ except the edge we are contracting across.
+In this case the edge we are contracting across is $R$ and thus we get the following multigraph.
 
@@
 
-This can then be reduced into a \gls{graph} again by simply treating $b_r$ and $b_s$ as the same edge.
-This operation is particularly important as we will prove that if a \gls{graph} is planar, then so is any \gls{graph} or \gls{multigraph} obtained by contracting an \gls{edge}.
+This can then be reduced into a graph again by simply treating $b_r$ and $b_s$ as the same edge.
+This operation is particularly important as we will prove that if a graph is planar, then so is any graph or multigraph obtained by contracting an edge.
 
 \subsection{Subdivision}
-%TODO rename unsubdivide
-\def\unsubdivide{vertex replacement}
-\def\unsubdividepl{vertex replacements}
+There are two types of subdivision, an edge subdivision and graph subdivision.
+Edge subdivisions can best be though of as an operation, much like a contraction.
+We then can define a graph subdivision in terms of the edge version.
 
-To define this we first describe, we first have to describe an operation where we take a vertex $v$ that has degree 2, and replace with an edge as follows.
-
+\subsubsection{Edge Subdivision}
+An edge subdivision is where we take an an edge and add a vertex into the middle of it.
+If we have an edge $e$ that goes between vertex $a$ and $b$ then to subdivide it we add a vertex $c$, remove edge $e$ and then add an edge between $a$ and $c$ and between $b$ and $c$.
+This is demonstrated in the diagram below.
 \begin{center}
@@
 
-		\node[main node] (1) {$v$};
-		\node[main node] (2) [left of=1] {$A$};
-		\node[main node] (3) [right of=1] {$B$};
+			\node[main node] (1) {$a$};
+			\node[main node] (2) [right of=1] {$b$};
 
 			\path[every node/.style={font=\sffamily\small}]
-		(1)	edge node {} (2)
-		edge node {} (3);
+			(1)	edge node {$e$} (2);
 		\end{tikzpicture}
@@
 
-		\node[main node] (1) {$A$};
-		\node[main node] (2) [right of=1] {$B$};
+		\node[main node] (1) {$a$};
+		\node[main node] (3) [right of=1] {$c$};
+		\node[main node] (2) [right of=3] {$b$};
 
 		\path[every node/.style={font=\sffamily\small}]
-		(1)	edge node {} (2);
+		(1)	edge node {} (3)
+		(2) edge node {} (3);
 		\end{tikzpicture}
@@
 	$
-
-	or
-
-	$
-	\begin{array}{l}
-		\begin{tikzpicture}[auto, node distance=3cm, every loop/.style={},
-		thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries}]
-
-		\node[main node] (1) {$v$};
-		\node[main node] (2) [left of=1] {$A$};
-		\node[main node] (3) [right of=1] {$B$};
-
-		\path[every node/.style={font=\sffamily\small}]
-		(1)	edge node {} (2)
-		edge node {} (3)
-		(2) edge [bend left] node {} (3);
-		\end{tikzpicture}
-	\end{array}
-	$
-	\scalebox{2}{$\to$}
-	$
-	\begin{array}{l}
-		\begin{tikzpicture}[auto, node distance=3cm, every loop/.style={},
-		thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries}]
-
-		\node[main node] (1) {$A$};
-		\node[main node] (2) [right of=1] {$B$};
-
-		\path[every node/.style={font=\sffamily\small}]
-		(1)	edge node {} (2);
-		\end{tikzpicture}
-	\end{array}
-	$
-
-	\scalebox{.9}{Here $A$ and $B$ may be connected in any way to a larger graph, however only this subgraph will change.}
 \end{center}
 
-Now we are going to call this operation \unsubdivide, and using it we define a graph subdivision as follows.
+This can be thought of as a sort of inverse to contractions. To see this simply preform a contraction on either edge of the output graph above and you will return the the original graph.
 
-\begin{definition}[graph subdivision]
-	A graph $G$ is a subdivision of $H$ if $H$ may be produced by some series of \unsubdividepl\ on $G$.
-\end{definition}
+\subsubsection{Graph Subdivision}
+A graph $G$ is said to be a subdivision of $H$ if $G$ can be obtained from $H$ via some series of edge subdivisions. For example consider the two following graphs.
+This can be thought of as just adding vertices along an edge.
+Intuitively this shouldn't actually change the shape of a graph.
+This not changing the shape of a graph is something that will be touched on later in lemma \ref{subdivision}.
 
 \section{Kuratowski's Theorem}
-\begin{theorem}[Kuratowski's Theorem]
+\begin{theorem}[Kuratowski's Theorem]\label{THEBIGONE}
 	A graph $G$ is nonplanar if and only if it contains a subgraph that is a subdivision of $K_{3,3}$ or $K_5$
@@
 	\begin{itemize}
-		\item If $e$ connects a vertex to itself it is a loop and its removal will result in the loss of one edge and one face (each loop creates a face\footnote{Jordan curve theorem}).
+		\item If $e$ connects a vertex to itself it is a loop and its removal will result in the loss of one edge and one face (each loop creates a face\footnote{this is due to the Jordan curve theorem}).
 The resulting multigraph has less than $k$ edges and thus we know that for it \begin{align*}2&=v-e+f \\&= v-(e+1)+(f+1)\end{align*} and as the original graph had one more edge and one more face it too would fit this rule.
@@
 \subsection{Some basic lemmas}
-This is the point in the paper where it is no longer written to be understood by everyone. %TODO make this better
+Up to this point the paper has been writing such that anyone with a basic mathematical competency and interest could understand and work through the content.
+From this point on the paper moves a bit faster and assumes knowledge of basic mathematical notation and more experience with math.
 
-\begin{lemma}
+The purpose of the next couple sections is to build up the mathematical machinery that we need for our proof of Kuratowski's theorem (theorem \ref{THEBIGONE})
+
+\begin{lemma} \label{subgraph}
 	If a graph $G$ has a nonplanar subgraph, then $G$ is nonplanar.
@@
 
-%TODO prove
+\begin{proof}
+	If we have a graph $G$ with a nonplanar subgraph $H$ then when drawing $G$ there is a part of the drawing that is $H$.
+This part of the drawing can not be planar and therefore the drawing of $G$ can not be a plane drawing.
+\end{proof}
 
-\begin{lemma}
+\begin{lemma} \label{subdivision}
 	If a graph $G$ is a subdivision of a nonplanar graph, then $G$ is nonplanar.
@@
 
-%TODO prove
+\begin{proof}
+
+\end{proof}
+
+\begin{lemma} \label{component}
+	If a graph $G$ is nonplanar than at least one of it's connected components is nonplanar.
+\end{lemma}
 
@@
 \begin{lemma}
-	Every minimal nonplanar graph contains a connected minimal nonplanar subgraph.
+	Every minimal nonplanar graph contains a connected minimal nonplanar subgraph
+\end{lemma}
+
+\begin{proof}
+	Let $G$ be a minimal nonplanar graph.
+We know by lemma \ref{component} that $G$ contains at least one nonplanar component, $C_1$.
+Additionally for a graph to be nonplanar it must have edges (as it is trivial to embed a graph of finite vertices with no edges in the plane), so $C_1$ has edges.
+Now assume for the sake of contradiction that there is another connected component in $G$, $C_2\not=C_1$, and that $C_2$ has at least one edge in it.
+We know that $C_1$ is nonplanar so if in $G$ we remove an edge from $C_2$ then $G$ would still be planar as it contains $C_1$ (by lemma \ref{subgraph}).
+Therefore by contradiction $G$ contains only one connected component, $C_1$, with any edges.
+
+	Now to finish the proof assume for the sake of contradiction that $C_1$ is not minimally nonplanar.
+This means there is some edge in $C_1$, $e$, for which $C_1\setminus\set e$ is nonplanar.
+Therefore if we remove the same edge $e$ in $G$, $G$ still contains a nonplanar graph $C_1\setminus\set e$, and therefore is nonplanar by lemma \ref{subgraph}.
+Therefore we have a contradiction as we know $G$ to be minimally nonplanar and thus $C_1$ must also be minimally nonplanar.
+\end{proof}
+
+\begin{definition}[cut set]
+	In a graph $G$, any set of vertices, whose removal would yield a disconnected graph is called a cut set.
+\end{definition}
+
+\begin{definition}[$k$ connected]
+	A graph $G$, is said to be $k$ connected if it's minimal cut set is of size $k$.
+\end{definition}
+
+\subsection{Some larger theorems}
+
+\begin{theorem}[Menger's theorem] %TODO make sure mutally distinct path is well defined and make sure $n$ connected is well defined
+	A graph is $n$ connected if and only if there are at least $n$ mutually distinct paths between any two vertices.
+\end{theorem}
+
+%TODO prove
+
+\begin{theorem}
+	Any connected minimal nonplanar graph is at least 3 connected.
+\end{theorem}
+
+%TODO prove
+
+\subsection{Bridges}
+First consider a planar graph $G$ with cycle $C$.
+When we make a plane drawing of $G$ we find that $C$ in this drawing is a loop that separates the plane into an interior and exterior.
+The proof for this comes from the Jordan curve theorem, however we won't be getting into the Jordan curve theorem in this paper.
+Even so, just to make this complete we must state the Jordan curve theorem, define a Jordan curve and show that $C$ is a Jordan curve.
+\subsubsection{The Jordan Curve Theorem}
+\begin{theorem}[Jordan curve theorem] %TODO cite wikipedia https://en.wikipedia.org/wiki/Jordan_curve_theorem#Definitions_and_the_statement_of_the_Jordan_theorem
+	Let $C$ be a Jordan curve in the plane $\mathbb R^2$.
+Then its complement, $\mathbb R^2 \setminus C$, consists of exactly two connected components.
+One of these components is bounded (the interior) and the other is unbounded (the exterior), and the curve C is the boundary of each component.
+\end{theorem}
+
+\begin{definition}[Jordan curve]
+	A Jordan curve is a curve, $f:\ccint01\to \mathbb R^2$, with the following properties:
+	\begin{itemize}
+		\item $f$ is continuous
+		\item $f$ is injective on the interval $\coint 01$
+		\item $f(0) = f(1)$
+	\end{itemize}
+\end{definition}
+\begin{lemma}
+	For any plane drawing of a graph, $G$, containing cycle $C$, $C$ is a Jordan curve in the drawing.
 \end{lemma}
 \begin{proof}
-	%TODO redo proof
-	Let $G$ be a minimal nonplanar graph.
-If $G$ is connected then $G$ contains itself as a minimal nonplanar subgraph.
-If $G$ is not connected then it is composed of connected components.
-When embedding $G$ within the plane, if every component was planar we could embed them into any space homeomorphic to $\mathbb R^2$.
-For example each component could be embedded in an open disk with radius $1/2$ about a separate point in $\mathbb Z^2$, and this would then be a plane drawing.
-This means that at least one component in $G$ must be nonplanar.
-Now every other component in this graph may not have any edges as their removal would still yield a nonplanar graph (which breaks the definition of minimal nonplanar).
-This means that there is only one nonplanar component, and further if any edge from this component is to be removed then $G$ would be planar.
-Now by .
-From this we get that this component is itself a connected minimal nonplanar subgraph of $G$.
+	In order to fully rigorously prove this we have to go back and formalize what a plane drawing is. So let us do this now.
+
+	A drawing is a subset, $D$, of some topological space $S$. For plane drawings this space will be $\mathbb R^2$ with it's standard topology.
+
+	Given a graph $G$, with vertex set $V$ and edge set $E$, a drawing $D$ is said to be a drawing of $G$ if and only if the following criteria are met:
+	\begin{itemize}
+		\item There exists an injective function $v:V\to D$.
+		\item If there is an edge $e\in E$ between vertices $a$ and $b$ then there is a continuous injective function $\hat e:\ccint01\to S$ with $\hat e(0) = v(a)$ and $\hat e(1) = v(b)$ and the image of $e$ is contained within $D$.
+		\item For any vertex $a\in V$ and edge $e\in E$ and any real number $x\in\ooint 01$, $\hat e(x)\not=v(a)$.
+		\item For any two edges $e\not=f$, $\hat e(x) \not= \hat f(y)$ for all $x,y \in\ooint01$.
+		\item for all $d\in D$ there exists either a vertex $a\in V$ such that $v(a) = d$ or there exists an edge $e\in E$ such that $d$ is in the image of $\hat e$.
+	\end{itemize}
+
+%TODO ask Shaw what he thinks
+	Now consider a plane drawing of a graph $G$ with cycle $C$.
+We may write out $C$ as $v_1e_1v_2e_2\ldots v_ke_kv_1$.
+We know that each of these $e_i$s have a corresponding curve $\hat e_i$ that starts at the end of the previous ($\hat e_{i-1}$) curve and ends at the beginning of the next ($\hat e_{i+1}$) curve.
+This means we can construct a new continuous curve simply by stringing each of these together and then resize the domain.
+What we end with will then be a curve $f:\ccint 01\to\mathbb R^2$ that is continuous.
+We will also have $f(0) = f(1)$ as $v_1$ as $e_1$ starts at $v_1$ and $e_k$ ends at $v_1$.
+We will also have $f$ injective on $\coint{0}{1}$ as we know that edges do not overlap each other (this is formalized in the fourth bullet point of our definition for a drawing).
+This then means that our cycle creates a Jordan curve.
 \end{proof}
 
-\printnoidxglossary
+\subsubsection{Bridges}
+
+Let $G$ be a connected graph with cycle $C$. Let $G'$ be the graph of $G$ when all edges of $C$ are removed. 
+\begin{definition}[partial bridge]
+	A partial bridge, $B$, of $C$ in $G$ is any connected subgraph of $G'$ that contains at lest one edge and for any two edges $a$ and $b$ in $B$, there is a walk in $B$ that contains both $a$ and $b$ and does not pass through any vertex of $C$ (it may begin or end on with a vertex of $C$, but no internal vertex may be in $C$).
+\end{definition}
+\begin{definition}[bridge]
+	A partial bridge, $B$, is a bridge of $C$ in $G$ if there does not exist a partial bridge $B'\not=B$ of $C$ in $G$ such that $B\subset B'$.
+
+	Alternatively a bridge is a maximal partial bridge.
+\end{definition}
+
+Bridges are the final tool we use to prove Kuratowski's theorem.
+We will now build up some lemmas, that we will need and might help us to build up a conception of a bridge.
+For these let $G$ be a connected graph with cycle $C$ and let $G'$ be the subgraph.
+All bridges and partial bridges will be in reference to $C$.
+
+\begin{lemma}\label{walktopartialbridge}
+	Let $W$ be a walk in $G'$ that does not pass through $C$ (it may start and end in $C$) and has at least one edge. Then the graph, $H$, composed of the vertices and edges in $W$ is a partial bridge.
+\end{lemma}
+\begin{proof}
+	First $H$ is a subgraph of $G'$ as $W$ is a walk in $G'$.
+Second $H$ contains at least one edge as $W$ contains at least one edge.
+Third $H$ is connected trivially.
+Finally $W$ is a walk containing all edges of $H$ and not passing through $C$, so $H$ must be a partial bridge.
+\end{proof}
+
+\begin{lemma}\label{partialbridgeunion}
+	Let $A$ and $B$ be partial bridges sharing a vertex, $v\not\in C$, then $A\union B$ is a partial bridge.
+\end{lemma}
+\begin{proof}
+	First $A\union B$ is trivially a subgraph of $G'$ and contains at least one edge as both $A$ and $B$ contain at least one edge.
+Additionally $A\union B$ is connected as for any pair of vertices $a,b \in A\union B$ we have the following possibilities:
+	\begin{itemize}
+		\item If both $a$ and $b$ are in $A$ or both $a$ and $b$ are in $B$, then there is a walk from $a$ to $b$ within $A$ or $B$ respectively as both $A$ and $B$ are connected.
+		\item Otherwise one of the vertices is in $A$ and the other is in $B$.
+Without loss of generality let $a\in A$ and $b\in B$, then we can construct a walk from $a$ to $v$ within $A$ as both are in $A$ and a walk from $v$ to $b$ as within $B$ both are in $B$.
+We then combine these two walks and have a walk from $a$ to $b$ that stays within $A\union B$.
+	\end{itemize}
+	Therefore $A\union B$ is connected.
+Finally we can make a similar argument that for any edges in $a,b\in A\union B$ there is a walk within $A\union B$ that doesn't pass through $C$ that contains both $a$ and $b$.
+	\begin{itemize}
+		\item If both $a$ and $b$ are in $A$ or both $a$ and $b$ are in $B$ then there is such a walk as $A$ and $B$ are both partial bridges.
+		\item If $a$ and $b$ are not both in $A$ or both in $B$ then without loss of generality we can let $a\in A$ and $b \in B$.
+First as $A$ and $B$ are both connected and contain at least one edge, then $v$ must have at least one edge in each $A$ and $B$.
+Now we know there exists a walk in $A$ containing both $a$ and an edge of $v$ and there is a walk in $B$ containing both $b$ and an edge of $v$, and both these walks do not pass through $C$.
+Any walk passing though an edge of $v$ must also contain $v$, so both these paths must contain $v$.
+Without loss of generality we will assume the walk in $A$ contains $v$ after $a$ and the walk in $B$ contains $b$ after $v$.
+We now construct a walk that starts as the first walk up until has passed through $a$ and continued on to $v$, then we start following the walk in $B$ as it does after $v$ until reaching $b$.
+This walk's internal vertices are composed only of internal vertices from the walk in $A$, the walk in $B$ and of $v$.
+All of these are known not to be in $C$.
+	\end{itemize}
+	Now we have shown that $A\union B$ is a partial bridge.
+\end{proof}
+
+\begin{corallary}
+	No two bridges of the same cycle will share any edges and may only share a vertex if the vertex is in the cycle. 
+\end{corallary}
+\begin{proof}
+	Let $A$ and $B$ be bridges of $C$.
+If they share a vertex that is not in $C$, then by lemma \ref{partialbridgeunion} we know that $A\union B$ is a partial bridge, and it would contain both $A$ and $B$, so then $A = A\union B = B$.
+If $A$ and $B$ share an edge, $e$, then they must also share the vertices of $e$.
+If either one of $e$'s vertices are not in $C$ then we already know that $A=B$.
+If both of $e$'s vertices are in $C$ then $e$ is the only edge in both $A$ and $B$ as for any other edge $e'$ a walk that contains both $e$ and $e'$ must through one of $e$'s vertices to get between $e$ and $e'$.
+Additionally neither $A$ nor $B$ can contain any other vertices than $e$'s vertices as they are connected.
+Therefore $A=B$ again.
+\end{proof}
+
+%Let $G$ be a connected graph with cycle $C$.
+We can define an equivalence relation $\sim$ on the set of all edges and vertices not in $C$ as $a\sim b$ if there is a walk, $v_1e_1v_2e_2\ldots v_{k-1}e_{k-1}v_k$, with the following properties.
+%\begin{itemize}
+%	\item All vertices $v_i$ with $1 < i < k$ are not on $C$. ($v_1$ and $v_k$ may be on $C$ but this is not a requirement.)
+%	\item All edges in the walk must not be in $C$.
+%	\item Both $a$ and $b$ must be in the walk, they may be either an edge or vertex.
+%\end{itemize}
+%We should check that this is a equivalence relation.
+%\begin{itemize}
+%	\item (\textit{symmetry}) - trivial from how we construct $\sim$.
+%	\item (\textit{reflexivity}) - For a vertex $v$ we can define a walk with just $v$ and therefore $v\sim v$ as this walk fits our requirements.
+For an edge $e$, $e$ must have two vertices it is attached two, $a$ and $b$.
+We then construct a walk $aeb$, and therefore $e\sim e$.
+%	\item (\textit{transitivity)} - If $a\sim b$ and $c$ then there is a walk that goes through both $a$ and $b$ and a walk that goes through both $b$ and $c$.
+None of $a$, $b$, or $c$ are on $C$ as $\sim$ is not defined on $C$.
+Any walk $W$ we can reverse the direction of and it will still fit our rules above.
+This means that we can say there is a walk that goes through $a$ and then through $b$ as well as a walk that goes through $b$ and then through $c$.
+These walks will then take the the form $\alpha_1\alpha_2\ldots\alpha_{k}$ and $\beta_1\beta_2\ldots\beta_n$ with $a = \alpha_i$, $b = \alpha_j = \beta_m$, and $c = \beta_o$ for some $1\le i \le j \le k$ and $1\le m \le o \le n$.
+Now if $b$ is a vertex we can construct a walk as follows:
+%	$$\alpha_1\ldots\alpha_{i-1}a\alpha_{i+1}\ldots\alpha_{j-1}b\beta_{m+1}\ldots\beta_{o-1}c\beta_{o+1}\ldots\beta_n$$
+%	giving us a valid walk containing both $a$ and $c$.
+If $b$ is an edge then $\alpha_{i-1}$ is a vertex adjacent to $b$ and thus it must appear either before or after $b$ in any walk including $b$ as an edge.
+Additionally we know $\alpha{i-1}$ is not part of $C$ as it is in the interior of our walk containing $a$ and $b$.
+Therefore we can construct a walk just like we did last time that starts at $\alpha_1$ then goes through $a$ and then up to $\alpha_{i-1}$ at which point it switches to the equivalent vertex in the other walk be it $\beta{m-1}$ or $\beta{m+1}$ and simply follows that walk through $c$ until it reaches $b_n$.
+This walk will contain both $a$ and $b$ and therefore we know $a\sim b$ in all cases.
+%\end{itemize}
+%Now we may consider the partition created by $\sim$ on the set of all vertices and edges not in $C$.
+For any partition $P$ then we may construct $\bar P$ as $P$ with any vertices in $C$ that an edge $P$ connects to.
+This $\bar P$ is then what we call a bridge.
+Lets take a bit to get an intrinsic understanding of what a bridge is.
+%
+%Conceptually a bridge is a sort of bit of the graph
+
+\begin{lemma}
+	Every bridge $B$ of cycle $C$ contains at least one vertex in $C$.
+\end{lemma}
+\begin{proof}
+	Let $B$ be a partial bridge that does not contain any vertex in $C$.
+We know $C$ and $B$ are contained within a larger graph $G$ that is connected, so there must be a walk from any vertex in $B$ to any vertex in $C$.
+Consider then a walk $W$ that starts at vertex $b\in B$ and ends at vertex $c\in C$.
+There must be some first vertex in $W$ that is in $C$, so let us call $W'$ the subwalk of $W$ from $b$ to that first vertex in $C$.
+Now we know that $W'$'s first vertex in $C$ is also it's last vertex, so it does not pass through $C$.
+Therefore by lemma \ref{walktopartialbridge} the graph $H$ composed of $W'$'s vertices and edges is a partial bridge.
+We know also that $B\union H$ is a partial bridge by lemma \ref{partialbridgeunion}.
+Finally $B\not=B\union H$ as $B\union H$ contains a vertex in $C$ and $B$ does not.
+Now we have a partial bridge, $B\union H$ that contains $B$, so we know $B$ is not a bridge.
+\end{proof}
+
+\begin{lemma}
+	In a plane drawing of a graph $G$, given some cycle $C$, every bridge, $B$, of $C$ will either entirely be in the interior or exterior of $C$ with the exception of the vertices of $B$ that are in $C$.
+\end{lemma}
+\begin{proof}
+	We know that $C$ splits the plane into the interior and exterior.
+We know every vertex and edge that are not in $C$, must be entirely in the interior or exterior.
+As $B$ is a subgraph $G'$ which contains no edges of $C$ then every edge in $B$ is entirely in the interior or exterior.
+
+	Now assume for the sake of contradiction there is an edge, $e\in B$ that is in the exterior and an edge $i\in B$ that is in the interior.
+Then any walk containing both $e$ and $i$ must pass over $C$ which can only be done at vertices of $C$.
+This then means that every walk contain $e$ and $i$ passes through $C$ and thus we have a contradiction.
+
+	Now for any vertex $v\in B$ there is some edge $e\in B$ that connects to $v$.
+If $v$ is in the interior of $C$ then $e$ must also be entirely in the interior, and if $v$ is in the exterior then $e$ must be entirely in the exterior.
+This means that if any part of $B$ is in the interior, then $B$ must have at least one edge in the interior and if any part of $B$ is in the exterior then $B$ must have at least one edge in the exterior.
+We then can conclude that all of $B$ must be solely in the interior of $C$ or the exterior of $C$.
+\end{proof}
+
+\subsection{The home stretch}
+We can finally provide the proof for Kuratowski's theorem.
+
+\begin{theorem}[Kuratowski's Theorem]
+	A graph $G$ is nonplanar if and only if it contains a subgraph that is a subdivision of $K_{3,3}$ or $K_5$
+\end{theorem}
 

### 2019-05-09 Topology/Paper/paper.tex
Just second half of Mengers theorem and wrap up

@@
 \input{../topology}
+\usepackage{thmtools}
+\usepackage{thm-restate}
 \title{Topological Graph Theory}
@@
 \section{Kuratowski's Theorem}
-\begin{theorem}[Kuratowski's Theorem]\label{THEBIGONE}
+\begin{restatable}[Kuratowski]{theorem}{THEBIGONE}\label{THEBIGONE}
 	A graph $G$ is nonplanar if and only if it contains a subgraph that is a subdivision of $K_{3,3}$ or $K_5$
-\end{theorem}
+\end{restatable}
 
@@
 
-\subsection{Some basic lemmas}
+\subsection{Drawings}
 Up to this point the paper has been writing such that anyone with a basic mathematical competency and interest could understand and work through the content.
@@
 
-The purpose of the next couple sections is to build up the mathematical machinery that we need for our proof of Kuratowski's theorem (theorem \ref{THEBIGONE})
+The purpose of the next couple sections is to build up the mathematical machinery that we need for our proof of Kuratowski's theorem (theorem \ref{THEBIGONE}).
+In this section we will be proving a slew of lemmas and theorems, as well as provide a couple definitions, all of which will be needed in our final proof.
+
+We start by going back and formalizing our idea of a graph drawing. All this is meant to do is use mathematical language to define what we have already been thinking of as a graph drawing.
+
+\begin{definition}[Drawing]
+	A drawing is a subset, $D$, of some topological space $S$. For plane drawings this space will be $\mathbb R^2$ with it's standard topology.
+\end{definition}
+
+\begin{definition}[Graph Drawing]
+Given a graph $G$, with vertex set $V$ and edge set $E$, a drawing $D$ is said to be a drawing of $G$ if and only if the following criteria are met:
+\begin{itemize}
+	\item There exists an injective function $v:V\to D$.
+	\item If there is an edge $e\in E$ between vertices $a$ and $b$ then there is a continuous injective function $\hat e:\ccint01\to S$ with $\hat e(0) = v(a)$ and $\hat e(1) = v(b)$ and the image of $e$ is contained within $D$.\footnote{In a multigraph drawing we may have $a=b$ and thus $\hat e(0) = \hat e(1)$ making $\hat e$ not injective, however it must still be injective in $\coint 01$.}
+	\item For any vertex $a\in V$ and edge $e\in E$ and any real number $x\in\ooint 01$, $\hat e(x)\not=v(a)$.
+	\item For any two edges $e\not=f$, $\hat e(x) \not= \hat f(y)$ for all $x,y \in\ooint01$.
+	\item for all $d\in D$ there exists either a vertex $a\in V$ such that $v(a) = d$ or there exists an edge $e\in E$ such that $d$ is in the image of $\hat e$.
+\end{itemize}
+\end{definition}
+
+\subsection{Subgraph lemmas}
 
@@
 \begin{proof}
-
+	Let $H$ be a nonplanar graph with edge, $e$, between vertices $a$ and $b$.
+Let $H'$ be the graph produced by preforming an edge subdivision on edge $e$.
+Let us call the new call the new vertex $v$ and the new edges $e_a$ and $e_b$ ($e_a$ is an edge from $a$ to $v$ and $e_b$ is an edge from $b$ to $v$).
+
+	Suppose there exists a plane drawing, $D$, of $H'$.
+Then there are continuous injective functions $\hat e_a,\hat e_b\ccint01\to\mathbb R^2$ with $\hat e_a(1) = \hat e_b(0)$ whose range is contained in $D$.
+Additionally we know that $\hat e_a(x) \not= \hat e_b(y)$ for any $x,y\in\ooint 01$.
+Further we know that $a\not=b$ as otherwise $H$ would be a multigraph with $e$ being a loop in it.
+This means that $v(a) = \hat e_a(0) \not= \hat e_b(x)$ and $v(b) = \hat e_b(1)\not=\hat e_a(x)$ for all $x\in\ccint 01$.
+With all this we can construct an continuous injective function $\hat e:\ccint01\to \mathbb R^2$ such that $\hat e(0) = a$ and $\hat e(1) = b$ with
+	$$\hat e(x) = \begin{cases}
+	\hat e_a(x*2) & x \le \frac12\\
+	\hat e_b(x*2-1) & x > \frac 12
+	\end{cases}$$
+	As both $\hat e_a$ and $\hat e_b$ map into $D$, then so must $\hat e$ map into $D$. This contradicts our original statement that $H$ is nonplanar, and therefore $H'$ must not have a plane drawing.
+
+	It follows by induction that if a graph is a subdivision of a nonplanar graph, that graph must be nonplanar.
 \end{proof}
@@
 
-\begin{definition}[minimal nonplanar graph]
-	A nonplanar graph $G$ is said to be a minimal nonplanar graph if for all edges $e\in G$ the removal of $e$ would yield a  graph.
-\end{definition}
-
-\begin{lemma}
-	For any nonplanar graph $G$ there exists a minimal nonplanar subgraph.
-\end{lemma}
-\begin{proof}
-	Let $G$ be a nonplanar graph with $n$ edges.
+\begin{proof}
+	Suppose there exists a nonplanar graph $G$ for which all of it's components are planar.
+If each component is planar we may also make a drawing of it in any space homeomorphic to $\mathbb R^2$.
+Simply embed each component in a separate open epsilon ball about an integer point, with $\varepsilon \le \frac12$, and we find a contradiction with a planar embedding of $G$.
+\end{proof}
+
+\begin{lemma} \label{subdivisionCarryOn}
+	If a graph $G$ has a subdivision of $H$ as a subgraph, then any subdivision of $G$ contains a subdivision of $H$ as a subgraph.
+\end{lemma}
+\begin{proof}
+	Let $H$ be a graph.
+Let $H'$ be a subdivision of $H$.
+Let $G$ be a graph that contains $H'$ as a subgraph.
+Let $G'$ be a subdivision of $G$.
+There is some sequence of edge subdivisions $h_1,h_2,\ldots,h_\ell$ that produce $H'$ from $H$ as is there some sequence of edge subdivisions $g_1,g_2,\ldots,g_m$ that produce $G'$ from $G$.
+Let $g_{i_1},g_{i_2},\ldots,g_{i_n}$ be the subsequence of all the edge subdivisions that happen within $H'$.
+We then can produce $H''$ by taking $H$ and doing the sequence of edge subdivisions $h_1,h_2,\ldots,h_\ell,g_{i_1},g_{i_2},\ldots,g_{i_n}$ so $H''$ is a subdivision of $H$.
+\end{proof}
+
+%\begin{lemma}
+%	For any nonplanar graph $G$ there exists a minimal nonplanar subgraph.
+%\end{lemma}
+%\begin{proof}
+%	Let $G$ be a nonplanar graph with $n$ edges.
 The removal of all edges from $G$ would yield a graph with only vertices which is trivially planar.
@@
 Any such nonplanar subgraph of $G$, must be a minimal nonplanar graph as the removal of any edge from it would yield a subgraph of $G$ with less than $k$ edges.
-\end{proof}
-
-\begin{lemma}
-	Every minimal nonplanar graph contains a connected minimal nonplanar subgraph
-\end{lemma}
-
-\begin{proof}
-	Let $G$ be a minimal nonplanar graph.
-We know by lemma \ref{component} that $G$ contains at least one nonplanar component, $C_1$.
-Additionally for a graph to be nonplanar it must have edges (as it is trivial to embed a graph of finite vertices with no edges in the plane), so $C_1$ has edges.
-Now assume for the sake of contradiction that there is another connected component in $G$, $C_2\not=C_1$, and that $C_2$ has at least one edge in it.
-We know that $C_1$ is nonplanar so if in $G$ we remove an edge from $C_2$ then $G$ would still be planar as it contains $C_1$ (by lemma \ref{subgraph}).
-Therefore by contradiction $G$ contains only one connected component, $C_1$, with any edges.
-
-	Now to finish the proof assume for the sake of contradiction that $C_1$ is not minimally nonplanar.
-This means there is some edge in $C_1$, $e$, for which $C_1\setminus\set e$ is nonplanar.
-Therefore if we remove the same edge $e$ in $G$, $G$ still contains a nonplanar graph $C_1\setminus\set e$, and therefore is nonplanar by lemma \ref{subgraph}.
-Therefore we have a contradiction as we know $G$ to be minimally nonplanar and thus $C_1$ must also be minimally nonplanar.
-\end{proof}
-
-\begin{definition}[cut set]
-	In a graph $G$, any set of vertices, whose removal would yield a disconnected graph is called a cut set.
-\end{definition}
-
-\begin{definition}[$k$ connected]
-	A graph $G$, is said to be $k$ connected if it's minimal cut set is of size $k$.
-\end{definition}
-
-\subsection{Some larger theorems}
-
-\begin{theorem}[Menger's theorem] %TODO make sure mutally distinct path is well defined and make sure $n$ connected is well defined
-	A graph is $n$ connected if and only if there are at least $n$ mutually distinct paths between any two vertices.
-\end{theorem}
-
-%TODO prove
-
-\begin{theorem}
-	Any connected minimal nonplanar graph is at least 3 connected.
-\end{theorem}
-
-%TODO prove
-
-\subsection{Bridges}
-First consider a planar graph $G$ with cycle $C$.
-When we make a plane drawing of $G$ we find that $C$ in this drawing is a loop that separates the plane into an interior and exterior.
-The proof for this comes from the Jordan curve theorem, however we won't be getting into the Jordan curve theorem in this paper.
-Even so, just to make this complete we must state the Jordan curve theorem, define a Jordan curve and show that $C$ is a Jordan curve.
-\subsubsection{The Jordan Curve Theorem}
+%\end{proof}
+
+\subsection{The Jordan Curve Theorem}
 \begin{theorem}[Jordan curve theorem] %TODO cite wikipedia https://en.wikipedia.org/wiki/Jordan_curve_theorem#Definitions_and_the_statement_of_the_Jordan_theorem
@@
 \begin{proof}
-	In order to fully rigorously prove this we have to go back and formalize what a plane drawing is. So let us do this now.
-
-	A drawing is a subset, $D$, of some topological space $S$. For plane drawings this space will be $\mathbb R^2$ with it's standard topology.
-
-	Given a graph $G$, with vertex set $V$ and edge set $E$, a drawing $D$ is said to be a drawing of $G$ if and only if the following criteria are met:
-	\begin{itemize}
-		\item There exists an injective function $v:V\to D$.
-		\item If there is an edge $e\in E$ between vertices $a$ and $b$ then there is a continuous injective function $\hat e:\ccint01\to S$ with $\hat e(0) = v(a)$ and $\hat e(1) = v(b)$ and the image of $e$ is contained within $D$.
-		\item For any vertex $a\in V$ and edge $e\in E$ and any real number $x\in\ooint 01$, $\hat e(x)\not=v(a)$.
-		\item For any two edges $e\not=f$, $\hat e(x) \not= \hat f(y)$ for all $x,y \in\ooint01$.
-		\item for all $d\in D$ there exists either a vertex $a\in V$ such that $v(a) = d$ or there exists an edge $e\in E$ such that $d$ is in the image of $\hat e$.
-	\end{itemize}
-
 %TODO ask Shaw what he thinks
-	Now consider a plane drawing of a graph $G$ with cycle $C$.
+	Consider a plane drawing of a graph $G$ with cycle $C$.
 We may write out $C$ as $v_1e_1v_2e_2\ldots v_ke_kv_1$.
@@
 
-\subsubsection{Bridges}
+\subsection{Connectivity lemmas}
+
+\begin{lemma} \label{outside}
+	For any face, $F$, in a plane drawing, $D$, of a graph $G$, there is a corresponding drawing plane drawing of $G$, $D'$, where all edges and vertices that boarder $F$ in $D$, now boarder the outer face.
+\end{lemma}
+\begin{proof}
+	Let $G$ be a graph with face $F$ in plane drawing $D$.
+Now let $\inv f$ be a stereographic projection from the punctured sphere onto the plane.
+Therefore $f(D)$ is a drawing of $G$ on the punctured sphere.
+If $f(D)$ is a drawing of $G$ on the punctured sphere then it must also be a drawing of $G$ on the sphere.
+Now we pick a point on the interior of $F$ and puncture the sphere there rather than where our original puncture was.\footnote{There is a problem in this proof.
+How do we know that $F$ has an interior?
+Simply put if we have a finite number of vertices and never use any space filling curves for edges we will never fill space.
+We know that we are never forced to use a space filling curve as for any space filling curve $c$ we may create a new curve $c'$ that connects the same end points, stays within $c$'s image, and is not space filling.
+%TODO ask Shaw if maybe turn into lemma and prove
+	} We may now use a sterographic projection, $g$ to map $f(D)$ from the new punctured sphere back to $\mathbb R^2$ creating $D' = g(f(D))$.
+We know that in $D'$ the face that corresponds to $F$ is the outer face as it contained the punctured point in $\inv g(D')$.
+%TODO Ask shaw if I should prove that the puctured point in the sphere corresponds to a limit point
+\end{proof}
+
+\begin{definition}[cut set]
+	In a graph $G$, any set of vertices, whose removal would yield a disconnected graph is called a cut set.
+\end{definition}
+
+\begin{definition}[$k$ connected]
+	A graph, $G$, is $k$ connected if it's minimal cut set is of size $k$. The complete graph on $n$ vertices is defined to be $n-1$ connected.
+\end{definition}
+
+\begin{lemma}
+	For all non-empty graphs, $G$, there exists exactly one number $k\in\mathbb N$ such that $G$ is $k$ connected.
+\end{lemma}
+\begin{proof}
+	If a graph is a complete graph then two no vertices $a$ and $b$ can ever be separated by a cut set as they will always share an edge. Therefore there are no cut sets in a complete graph.
+
+	If a graph is not a complete graph, then there exists some vertex pair $a,b$ such that there is no edge between $a$ and $b$.
+Let $S$ be the set of all vertices in our graph except $a$ and $b$.
+It is clear that $S$ must be a cut set of $G$.
+Therefore $G$ must also have a minimal cut set.
+\end{proof}
+
+\begin{definition}[neighborhood]
+	The neighborhood of a vertex $v$ in a graph $G$ is the set of vertices that are adjaacent to $v$.
+This is denoted by $N(v)$.
+In a graph (not multigraph) we will never have $v \in N(v)$ as $v$ can not have an edge to itself.
+\end{definition}
+
+\begin{definition}[mutually disjoint paths]
+	A set of paths, $S$, is mutually disjoint if no two paths share a vertex. A path $p\in S$ is said to be mutually disjoint from the the other paths in $S$ if $S$ is mutually disjoint.
+\end{definition}
+
+\begin{definition}[mutually internally disjoint paths]
+	A set of paths, $S$, is mutually internally disjoint if no to paths share an internal vertex.
+That is no two paths, $p_1\not=p_2\in S$ share a vertex other than their first or last vertex.
+A path $p\in S$ is said to be mutually internally disjoint from the other paths in $S$ if $S$ is mutually internally disjoint.
+\end{definition}
+
+\begin{theorem}[Menger's theorem]
+	A non-empty graph is $n$ connected if and only if among all pairs of vertices $a\not=b$ in $G$ the least number of mutually internally disjoint paths from $a$ to $b$ is $n$.
+\end{theorem}
+%TODO cite Wikipeida menger's theorem
+\begin{proof}
+	This is trivially true on complete graphs, so for the rest of this proof we will only be considering graphs that are not complete.
+
+	Let $A$ and $B$ be vertex sets in a finite graph $G$.
+Define an $AB$ path as any path that starts in $A$ and has no other vertices in $A$, and ends in $B$ and has no other vertices in $B$.
+Notice that if $v\in A\inter B$ then the path $v$ is an $AB$ path.
+Define an $AB$ separator as any vertex set, $S$, for which all $AB$ paths contain at least one member of $S$.
+Define an $AB$ connector a set of mutually disjoint $AB$ paths.
+
+	Now by induction we will show that for any pair of vertex sets $A,B$ in a graph $G$, the maximum size of an $AB$ connector is also the minimum size of an $AB$ separator.
+
+	Base case: Suppose $G$ has no edges, therefore all paths in $G$ are single vertex paths.
+For all $v \in A \inter B$ the path $v$ is an $AB$ path, and any other path will either not start in $A$ or not end in $B$.
+This means that any $AB$ separator contains $A\inter B$ and that our maximal $AB$ connector is composed of single vertex paths for each vertex in $A\inter B$.
+Therefore our statement must be true when $G$ has no edges.
+
+	Inductive case: Suppose $H$ is a graph with $k>0$ edges, and that our statement is true for any graph with less than $k$ edges. Now choose an edge $e\in H$%TODO
+
+	Now let $G$ be a graph with vertices $a\not=b$. Further let $A = N(a)$ and $B = N(b)$.
+
+	$$(\implies)$$
+
+	First let us suppose $G$ is $n$ connected, meaning the smallest cut set in $G$ is $n$.
+If $a$ is not adjacent to $b$ then any $AB$ separator serves as a cut set in $G$, separating $a$ from $b$.
+It follows that the size of the smallest $AB$ separator is at least $n$, therefore there is an $AB$ connector with at least $n$ paths.
+Therefore there are at least $n$ mutually internally disjoint paths from $a$ to $b$.
+
+	Now let us suppose $a$ is adjacent to $b$ and further let us suppose that there can be an $AB$ separator of size $k < n$.
+First off we know that $\card A \ge n$ and $\card B \ge n$ as otherwise we would have one of the following:
+	\begin{enumerate}
+		\item $A$ or $B$ would serve as a cut set of size less than $n$ separating $a$ or $b$ from the rest of $G$. This clearly is a contradiction.
+		\item $A$ and $B$ both contain all vertices except $a$ and $b$ respectively. If $G$ has $m$ vertices then $G$ can be at most $m-1$ connected and therefore we still have $\card A = m-1 = \card B$.
+	\end{enumerate}
+	If $S$ is a minimal $AB$ separator of size $k < n$ then there are no $AB$ paths that do not contain a vertex in $S$.
+Let $\bar a\in A$ and $\bar b \in B$ and let $p$ be a path from $\bar a$ to $\bar b$.
+$p$ must contain a final vertex, $p_i$, that is within $A$.
+$p$ must contain an earliest vertex, $p_j$, that is within $B$ and after $p_i$.
+If we consider the subpath of $p$ simply going from $p_i$ to $p_j$ we have an $AB$ path.
+This means that any path from $\bar a$ to $\bar b$ must pass through $S$, this means that if $\bar a$ is not adjacent to $\bar b$ and $\bar a\not=\bar b$ $S$ is a cut set separating $\bar a$ from $\bar b$.
+Therefore as $\card S = k < n$ we know that all for all $\bar a \in A$ and all $\bar b\in B$, either $\bar a= \bar b$ or $\bar a$ is adjacent to $\bar b$.
+Without loss of generality we can suppose that $\card A \le \card B$.
+Now every vertex in $A\setminus B$ has an $AB$ path to every vertex in $B \setminus A$ as they are adjacent.
+Now for every vertex $a'\in A$ we have a mutually distinct $AB$ path from $a'$ to some vertex in $B$.
+This is because either $a'\in A\inter B$ and it is already an $AB$ path or $a'$ is adjacent to all $b' \in B$ and simply select one that isn't used by any other $AB$ path.
+We know that $\card A \ge n$, so we have a contradiction and the minimal $AB$ separator must still be at least size $n$.
+We then have at least one $AB$ connector of at least size $n$, and therefore there are at least $n$ mutually internally disjoint paths from $a$ to $b$.
+
+	Further we know there is a cut set of size $n$ in $G$.
+Therefore there must be some vertex pair $\alpha, \beta$ that are separated by such a cut set of size $n$.
+This means that there is a minimal $N(\alpha)N(\beta)$ separator of size $n$.
+Therefore the maximal $N(\alpha)N(\beta)$ connector is size $n$.
+Therefore if $G$ is $n$ connected, then among all pairs of vertices $a\not=b$ in $G$ the least number of mutually internally disjoint paths from $a$ to $b$ is $n$.
+
+	$$(\impliedby)$$
+
+	Now let us suppose $G$ is not $n$ connected, then the graph must be $k\not= n$ connected.
+By what we have shown above we know that among all the vertex pairs $a\not= b$ in $G$ the least number of mutually internally disjoint paths from $a$ to $b$ is $k\not=n$.
+\end{proof}
+
+\begin{definition}[minimal nonplanar graph]
+	A nonplanar graph $G$ is said to be a minimal nonplanar graph if every proper subgraph of $G$ is planar.
+\end{definition}
+
+\begin{lemma}\label{2connect}
+	Any connected minimal nonplanar graph is at least 2 connected.
+\end{lemma}
+
+\begin{proof}
+	First consider the complete graph.
+We know that $K_4$ is planar (see below), therefore by the contrapositive of lemma \ref{subgraph} all subsets of $K_4$, are planar.
+Any complete graph $K_i$ with $i < 4$ is a subgraph of $K_4$ (simply remove any $4-i$ vertices from $K_4$) so a nonplanar complete graph must be at least 4 connected.
+
+	\begin{center}
+		\scalebox{.5}{
+			\begin{tikzpicture}[auto, node distance=3cm, every loop/.style={},
+			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries}]
+
+			\node[main node] (1) {};
+			\node[main node] (2) [above left of=1] {};
+			\node[main node] (3) [below left of=1] {};
+			\node[main node] (4) [right of=1] {};
+
+			\path[every node/.style={font=\sffamily\small}]
+			(1) edge node {} (4)
+			edge node {} (3)
+			(2) edge node {} (1)
+			edge node {} (4)
+			(3) edge node {} (2)
+			(4) edge node {} (3);
+			\end{tikzpicture}
+		}
+	\end{center}
+
+	Now let $G$ be a minimal nonplanar graph that is not a complete graph.
+By lemma \ref{component} $G$ contains connected component, $G'$, that is nonplanar.
+We know $G'\subset G$ and that all proper subsets of $G$ are planar, therefore $G'=G$.
+This means that $G'$ is the only component in $G$ so $G$ must be at least 1 connected.
+
+	If $G$ is 1 connected then there exists some vertex $v$ for which $G\setminus\set v$ into at least two components.
+Let $H$ be one such component and $H'$ be the graph produced by adding $v$ back into $H$ ($H'$ is $v$ with all of $H$ and all edges between $H$ and $v$).
+Now $H'$ is a proper subgraph of $G$ so it must be planar.
+We also know that $G\setminus H$ is a proper subgraph of $G$ and therefore must also be planar.
+By lemma $\ref{outside}$ we may draw both $G\setminus H$ and $H'$ such that $v$ boarders the outer face.
+We may split $\mathbb R^2$ into two disjoint subsets
+	\begin{align*}
+	R^- &= \setbuilder{\pair xy\in\mathbb R^2}{x < 0}\\
+	R^+&=\setbuilder{\pair xy\in\mathbb R^2}{x > 0}
+	\end{align*}	
+	then draw $H'$ in $R^-$ with the exception of putting $v$ at $\pair 00$ and then draw $G\setminus H$ in $R^+$ with the exception of putting $v$ at $\pair 00$.
+This then yields a plane drawing of $G$, so $G$ must be at least 2 connected.
+\end{proof}
+
+%TODO 3 connected stuff
+\begin{definition}[lobe]
+	Let $G$ be a graph with cut set $S$.
+Further let $C_1, C_2, \ldots C_n$ be the connected components of $G\setminus S$.
+A lobe $L_i$ of $S$ is then what we would get if we took the subset of $G$ containing all of $C_i$ and $S$.
+This can more formally be written as
+	$$
+	L_i = G\setminus \left(\unionacross{j\not=i}{C_j}\right)
+	$$
+\end{definition}
+
+\begin{lemma}\label{lobes}
+	Let $G$ be a nonplanar 2 connected graph with minimal cut set $S=\set{x,y}$.
+Further if $L$ is a lobe of $S$ let $L^+$ be the graph of $L$ with an edge added between $x$ and $y$.
+There exists some lobe $L$ of $S$ for which $L^+$ is nonplanar.
+\end{lemma}
+%TODO cite http://www.cs.rpi.edu/~goldberg/14-GT/19-kurat.pdf
+\begin{proof}
+	Let $G$ be a graph with lobes $L_1, L_2, \ldots, L_n$ of separating set $S=\set{x,y}$.
+Suppose that for all $i$, $L_i^+$ is planar.
+We may then draw $L_1^+$ on the plane.
+If we have a planar drawing of $\unionfrom{j = 1}{i-1}{L_j^+}$ we can then embed a drawing of $L_i^+$ where the edge between $x$ and $y$ boarders the outer edge into a face that is bordered by the edge between $x$ and $y$ in our planar drawing of $\unionfrom{j = 1}{i-1}{L_j^+}$.
+We then can redraw this embedding such that $x$ and $y$ in $L_i^+$ are at the same points as $x$ and $y$ in $\unionfrom{j = 1}{i-1}{L_j^+}$ yielding a planar drawing of $\unionfrom{j=1}{i}{L_j^+}$.
+By induction then $\unionfrom{i=1}{n}{L_i^+}$ is planar.
+Clearly $G \subset \unionfrom{i=1}{n}{L_i^+}$ so by lemma \ref{subgraph} we know $G$ must be planar.
+\end{proof}
+
+\begin{lemma}
+	If $G$ is a graph with the properties listed below, then $G$ is at least 3-connected.
+	\begin{enumerate}
+		\item $G$ does not contain any subdivision of $K_{3,3}$ or $K_5$ as a subgraph.
+		\item $G$ is nonplanar.
+		\item Of all graphs satisfying properties (1) and (2), $G$ has the least number of edges.
+		\item Of all graphs satisfying properties (1), (2) and (3), $G$ has the least number of vertices.
+	\end{enumerate}
+\end{lemma}
+%TODO cite http://www.cs.rpi.edu/~goldberg/14-GT/19-kurat.pdf
+
+\begin{proof}
+	Let $G$ be a graph fitting the above properties.
+Any proper subgraph, $H$, of $G$ will be missing at least one vertex or one edge from $G$.
+If $H$ is missing a vertex from $G$, then $H$ must break one of the first 3 properties.
+$H$ can not contain a subdivision of $K_{3,3}$ or $K_5$ as then $G$ would also contain it and $H$ can not have more vertices than $G$.
+This leaves only that $H$ must be planar.
+If $H$ is missing an edge from $G$, then $H$ must break one of the first 2 properties.
+Again $H$ can not contain a subdivision of $K_{3,3}$ or $k_5$ as then $G$ would also contain it.
+This again leaves only that $H$ must be planar.
+This means that all proper subgraphs $H$ of $G$ are planar so $G$ is minimally nonplanar.
+Additionally we know that $G$ is not a complete graph as all complete graphs either contain $K_5$ or are planar.
+
+	By lemma \ref{2connect} we know that $G$ is at least 2 connected.
+Suppose that $G$ is 2 connected.
+Let $\set xy = S$ be a cut set in $G$.
+We know by lemma \ref{lobes} that there is a lobe $L$ for which adding an edge between $x$ and $y$ would yield a nonplanar graph $L^+$.
+Clearly $L^+$ has less edges then $G$, so $L^+$ must contain $K_{3,3}$ or $K_{5}$ as a subdivision.
+Consider another lobe $M$ of $S$.
+There must be a path, $p$, from $x$ to $y$ in $M$ as otherwise $G$ would not be either 0 or 1 connected.
+Clearly $L\union p$ is a subgraph of $G$ and $L\union p$ is a subdivision of $L^+$.
+By lemma \ref{subdivisionCarryOn} we then know that $L\union p$ contains a subdivision of $K_{3,3}$ or $K_5$.
+This gives us a contradiction so $G$ can not be 2-connected and therefore must be at least 3 connected.
+\end{proof}
+
+\subsection{Bridges}
 
@@
 
-\begin{theorem}[Kuratowski's Theorem]
-	A graph $G$ is nonplanar if and only if it contains a subgraph that is a subdivision of $K_{3,3}$ or $K_5$
-\end{theorem}
-
-\bibliographystyle{unsrt}
-\bibliography{bibliography}
+\THEBIGONE*
+
+\begin{proof}
+%TODO prove
+\end{proof}
 

### 2019-05-10 Topology/Paper/paper.tex
LETS DO THIS!

@@
 %Given some graph $G$ with vertex $v$.
-The neighborhood of $v$ within $G$ is the set of all vertices that share an edge with $v$, not including $v$.\footnote{If $G$ is a multigraph the definition stays the same, however $v$ maybe it's own neighbor if it has an edge with itself or a loop} Given a subgraph $H$ of $G$, the neighborhood of $H$ within $G$ is a new subgraph of $G$ that includes $H$ as well as any vertex in $G$ that is adjacent to a vertex in $H$ and the edge that they share.
+The neighborhood of $v$ within $G$ is the set of all vertices that share an edge with $v$, not including $v$.\footnote{If $G$ is a multigraph the definition stays the same, however $v$ maybe its own neighbor if it has an edge with itself or a loop} Given a subgraph $H$ of $G$, the neighborhood of $H$ within $G$ is a new subgraph of $G$ that includes $H$ as well as any vertex in $G$ that is adjacent to a vertex in $H$ and the edge that they share.
 %
@@
 %
-%First let us consider the neighborhood of just the vertex \textcolor{blue}{$a$}, this would then be all the vertices that it is adjacent to so we get $$\set{c, d, \textcolor{red}{e}}$$ We could also let $A$ be a subgraph containing only the vertex $\textcolor{blue}{a}$ and so it's neighborhood within $G$ will be the graph below.
+%First let us consider the neighborhood of just the vertex \textcolor{blue}{$a$}, this would then be all the vertices that it is adjacent to so we get $$\set{c, d, \textcolor{red}{e}}$$ We could also let $A$ be a subgraph containing only the vertex $\textcolor{blue}{a}$ and so its neighborhood within $G$ will be the graph below.
 %\begin{center}
@@
 \subsection{Contraction}
-This is not a property, but rather an operation or action that we preform on a graph. Let us consider the following graph.
+
+\subsubsection{Edge contraction}
+This is not a property, but rather an operation or action that we perform on a graph. Let us consider the following graph.
 
@@
 
-We wish to preform a contraction on edge $R$.
+We wish to perform a contraction on edge $R$.
 To be clear all graph contractions are on edges.
@@
 
-This can then be reduced into a graph again by simply treating $b_r$ and $b_s$ as the same edge.
-This operation is particularly important as we will prove that if a graph is planar, then so is any graph or multigraph obtained by contracting an edge.
-
-\subsection{Subdivision}
-There are two types of subdivision, an edge subdivision and graph subdivision.
+Often we may prefer to have the end result be a graph rather than a multigraph, which brings us to our next kind of contraction
+
+\subsubsection{Simple edge contraction}
+
+We can take any multigraph produced by an edge contraction and for any edge pairs that go between the same vertices, simply replace it with a single edge.
+This will reduce the multigraph back to a graph, and from the previous example the result of a simple edge contraction on $R$ will give the below graph.
+
+\begin{center}
+	\begin{tikzpicture}[auto, node distance=3cm, every loop/.style={},
+	thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries}]
+
+	\node[main node] (1) {$r\cdot s$};
+	\node[main node] (2) [right of=1] {$B$};
+	\node[main node] (3) [above left of=1] {$A$};
+	\node[main node] (4) [below left of=1] {$C$};
+
+	\path[every node/.style={font=\sffamily\small}]
+	(1)	edge node {$a$} (3)
+	(2) edge node {$b$} (1)
+	(4) edge node {$c$} (1);
+	\end{tikzpicture}
+\end{center}
+
+%\subsection{Subdivision}
+%There are two types of subdivision, an edge subdivision and graph subdivision.
 Edge subdivisions can best be though of as an operation, much like a contraction.
@@
 
-\subsubsection{Edge Subdivision}
-An edge subdivision is where we take an an edge and add a vertex into the middle of it.
+%\subsubsection{Edge Subdivision}
+%An edge subdivision is where we take an an edge and add a vertex into the middle of it.
 If we have an edge $e$ that goes between vertex $a$ and $b$ then to subdivide it we add a vertex $c$, remove edge $e$ and then add an edge between $a$ and $c$ and between $b$ and $c$.
 This is demonstrated in the diagram below.
-\begin{center}
-	$
-	\begin{array}{l}
-		\begin{tikzpicture}[auto, node distance=3cm, every loop/.style={},
-		thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries}]
-
-			\node[main node] (1) {$a$};
-			\node[main node] (2) [right of=1] {$b$};
-
-			\path[every node/.style={font=\sffamily\small}]
-			(1)	edge node {$e$} (2);
-		\end{tikzpicture}
-	\end{array}
-	$
-	\scalebox{2}{$\to$}
-	$
-	\begin{array}{l}
-		\begin{tikzpicture}[auto, node distance=3cm, every loop/.style={},
-thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries}]
-
-		\node[main node] (1) {$a$};
-		\node[main node] (3) [right of=1] {$c$};
-		\node[main node] (2) [right of=3] {$b$};
-
-		\path[every node/.style={font=\sffamily\small}]
-		(1)	edge node {} (3)
-		(2) edge node {} (3);
-		\end{tikzpicture}
-	\end{array}
-	$
-\end{center}
-
-This can be thought of as a sort of inverse to contractions. To see this simply preform a contraction on either edge of the output graph above and you will return the the original graph.
-
-\subsubsection{Graph Subdivision}
-A graph $G$ is said to be a subdivision of $H$ if $G$ can be obtained from $H$ via some series of edge subdivisions. For example consider the two following graphs.
-This can be thought of as just adding vertices along an edge.
+%\begin{center}
+%	$
+%	\begin{array}{l}
+%		\begin{tikzpicture}[auto, node distance=3cm, every loop/.style={},
+%		thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries}]
+%		
+%			\node[main node] (1) {$a$};
+%			\node[main node] (2) [right of=1] {$b$};
+%			
+%			\path[every node/.style={font=\sffamily\small}]
+%			(1)	edge node {$e$} (2);
+%		\end{tikzpicture}
+%	\end{array}
+%	$
+%	\scalebox{2}{$\to$}
+%	$
+%	\begin{array}{l}
+%		\begin{tikzpicture}[auto, node distance=3cm, every loop/.style={},
+%thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries}]
+%
+%		\node[main node] (1) {$a$};
+%		\node[main node] (3) [right of=1] {$c$};
+%		\node[main node] (2) [right of=3] {$b$};
+%		
+%		\path[every node/.style={font=\sffamily\small}]
+%		(1)	edge node {} (3)
+%		(2) edge node {} (3);
+%		\end{tikzpicture}
+%	\end{array}
+%	$
+%\end{center}
+%
+%This can be thought of as a sort of inverse to contractions. To see this simply perform a contraction on either edge of the output graph above and you will return the the original graph.
+%
+%
+%\subsubsection{Graph Subdivision}
+%A graph $G$ is said to be a subdivision of $H$ if $G$ can be obtained from $H$ via some series of edge subdivisions. For example consider the two following graphs.
+%This can be thought of as just adding vertices along an edge.
 Intuitively this shouldn't actually change the shape of a graph.
@@
 	\end{itemize}
-	Additionally every edge boarders no more than two faces, so from this we know that in any graph $2e \ge 3f$ or $\frac23e\ge f$.
+	Additionally every edge borders no more than two faces, so from this we know that in any graph $2e \ge 3f$ or $\frac23e\ge f$.
 Now $K_5$ has 10 edges and 5 vertices, so we know that $$\frac2310=\frac{20}3=6.\bar6\ge f$$ We know that $K_5$ is a connected graph (and thus also a connected multigraph) so if $K_5$ were planar then we would have $$2=v-e+f=5-10+f\le5-10+6.\bar6 = 1.\bar6$$ which is clearly false as $$2\not\le1.\bar6$$ Therefore $K_5$ must not be planar.
@@
 Each pair of vertices within these three vertices would share an edge and therefore there is no way to split them up into two groups such that neither group has an edge within it.
-Additionally every edge boarders no more than two faces, so from this we know that in any bipartite graph $2e \ge 4f$ or $e\ge 2f$.
+Additionally every edge borders no more than two faces, so from this we know that in any bipartite graph $2e \ge 4f$ or $e\ge 2f$.
 
@@
 \begin{definition}[Drawing]
-	A drawing is a subset, $D$, of some topological space $S$. For plane drawings this space will be $\mathbb R^2$ with it's standard topology.
+	A drawing is a subset, $D$, of some topological space $S$. For plane drawings this space will be $\mathbb R^2$ with its standard topology.
 \end{definition}
@@
 
-\begin{lemma} \label{subdivision}
-	If a graph $G$ is a subdivision of a nonplanar graph, then $G$ is nonplanar.
+\begin{definition}[contactable]
+	A graph $G$ is said to be contactable to a graph $H$ if there is some series of simple edge contractions that when performed on $G$ produce $H$.
+\end{definition}
+
+\begin{lemma}
+	If a graph $G$ with edge $e$ is planar then so is the graph produced by performing a simple edge contraction on $e$.
 \end{lemma}
@@
 \begin{proof}
-	Let $H$ be a nonplanar graph with edge, $e$, between vertices $a$ and $b$.
-Let $H'$ be the graph produced by preforming an edge subdivision on edge $e$.
+	Let $G$ be a planar graph with edge $e$ between $x$ and $y$. et $G'$ be the graph produced by an edge contraction on $e$. We are going to prove this using induction on the number of edges of $y$.
+
+	Statement: $G'$ is planar and there is a plane drawing of $G'$ where all vertices, $v$, that border a face that $y$ borders in $G$ also a face that $x\cdot y$ borders in $G'$ ($x\cdot y$ is the vertex produced by contracting across $e$).
+
+	Base case: Suppose $y$ only has edge $e$.
+Clearly $G'\subset G$ so by lemma \ref{subgraph} $G'$ must be planar.
+Additionally as $y$ has only one edge it can not possibly lie upon any cycles in $G$, this means that $y$ can only border at most 1 face, and as it has an edge to $x$ it must share this face with $x$.
+We may draw $G'$ simply be removing $e$ and $y$ from any drawing of $G$ and relabeling $x$ as $x\cdot y$.
+Clearly then the statement above must be true when $y$ has only one edge.
+
+	Inductive step: Let $z\not=x$ be a vertex sharing edge $\bar e$ with $y$.
+Assume that the statement is true in $G\setminus\set{\bar e}$.
+Now perform a contraction on $e$ in $G\setminus\set{\bar e}$ to produce $H$.
+$x\cdot y$ in $H$ must border a face $\bar f$ that $z$ borders so we may add in edge $\bar e$ to $H$ in face $\bar f$ and produce a plane drawing of $G'$.
+Further let $v$ be a vertex bordering a face $f$ in $G$ that $y$ also borders.
+We then know that there is a face $f'$ in $H$ that borders both $v$ and $x \cdot y$.
+If $f'\not=\bar f$ then clearly $x\cdot y$ and $v$ both boarder $f'$ in $G'$ as well as $H$.
+If $f'=\bar f$ then $f'$ is split into two parts by $\bar e$ in $G'$, both of which are bordered by $x\cdot y$.
+Therefore our statement must be true for $G$.
+
+	Now by induction we have proven the statement is true on all graphs and therefore our lemma is proved.
+\end{proof}
+
+\begin{corallary} \label{contractible}
+	If a graph $G$ is planar, and if $G$ is contactable to a graph $H$, then $H$ must also be planar.
+\end{corallary}
+
+\begin{proof}
+	Let $c_1,c_2,\ldots, c_n$ be the sequence of contractions on $G$ that produce $H$.
+Let $H_i$ be the graph produced after the first $i$ contractions on $G$, so $H_i = G$ and $H_n = H$.
+If $G$ is planar then clearly $H_0$ is planar.
+If $H_i$ is planar, then by the above lemma clearly $H_{i+1}$ is planar.
+Now by induction, if $G$ is planar $H$ must be planar.
+\end{proof}
+
+\begin{lemma} \label{contractibleCarryOn}
+	If a graph $G$ has a subgraph that is contactable to $H$ as a subgraph, then graph $G'$ that is contactable to $G$ also contains a subgraph that is contactable to $H$.
+\end{lemma}
+
+\begin{proof}
+		Let $H$ be a graph.
+Let $H'$ be contactable to $H$.
+Let $G$ be a graph that contains $H'$ as a subgraph.
+Let $G'$ be a graph that is contactable to $G$.
+There is some sequence of simple edge contractions $h_1,h_2,\ldots,h_\ell$ that produce $H$ from $H'$ as is there some sequence of simple edge contractions $g_1,g_2,\ldots,g_m$ that produce $G$ from $G'$.
+		If we reverse these sequences we get sequences of inverse simple edge contractions that take produce $H'$ from $H$ and $G'$ from $G$.
+Each inverse simple edge contraction will be done on a single vertex (and turn it into two vertices that share an edge).
+Let $f_i = h_{\ell-i+1}$ and $e_i = g_{i-m+1}$ so that they are the reversed sequences of $g$ and $h$.
+Take the subsequence, $e_{i_1},e_{i_2},\ldots,e_{i_n}$ that consists of all the inverse simple edge contractions that act on a vertex within the subgraph $H'$ of $G$.
+Now we can produce $H''$ as the graph produced by performing the following inverse simple edge contractions on $H$
+		$$ f_1,f_2,\ldots,f_\ell,e_{i_1},e_{i_2},\ldots,e_{i_n} $$
+		Clearly now $H''$ is contactable to $H$ and $H''$ must be a subgraph of $G'$.
+\end{proof}
+
+%%TODO remove?
+%\begin{lemma} \label{subdivision}
+%	If a graph $G$ is a subdivision of a nonplanar graph, then $G$ is nonplanar.
+%\end{lemma}
+%
+%\begin{proof}
+%	Let $H$ be a nonplanar graph with edge, $e$, between vertices $a$ and $b$.
+Let $H'$ be the graph produced by performing an edge subdivision on edge $e$.
 Let us call the new call the new vertex $v$ and the new edges $e_a$ and $e_b$ ($e_a$ is an edge from $a$ to $v$ and $e_b$ is an edge from $b$ to $v$).
-
-	Suppose there exists a plane drawing, $D$, of $H'$.
+%	
+%	Suppose there exists a plane drawing, $D$, of $H'$.
 Then there are continuous injective functions $\hat e_a,\hat e_b\ccint01\to\mathbb R^2$ with $\hat e_a(1) = \hat e_b(0)$ whose range is contained in $D$.
@@
 With all this we can construct an continuous injective function $\hat e:\ccint01\to \mathbb R^2$ such that $\hat e(0) = a$ and $\hat e(1) = b$ with
-	$$\hat e(x) = \begin{cases}
-	\hat e_a(x*2) & x \le \frac12\\
-	\hat e_b(x*2-1) & x > \frac 12
-	\end{cases}$$
-	As both $\hat e_a$ and $\hat e_b$ map into $D$, then so must $\hat e$ map into $D$. This contradicts our original statement that $H$ is nonplanar, and therefore $H'$ must not have a plane drawing.
-
-	It follows by induction that if a graph is a subdivision of a nonplanar graph, that graph must be nonplanar.
-\end{proof}
+%	$$\hat e(x) = \begin{cases}
+%	\hat e_a(x*2) & x \le \frac12\\
+%	\hat e_b(x*2-1) & x > \frac 12
+%	\end{cases}$$
+%	As both $\hat e_a$ and $\hat e_b$ map into $D$, then so must $\hat e$ map into $D$. This contradicts our original statement that $H$ is nonplanar, and therefore $H'$ must not have a plane drawing.
+%	
+%	It follows by induction that if a graph is a subdivision of a nonplanar graph, that graph must be nonplanar.
+%\end{proof}
 
 \begin{lemma} \label{component}
-	If a graph $G$ is nonplanar than at least one of it's connected components is nonplanar.
+	If a graph $G$ is nonplanar than at least one of its connected components is nonplanar.
 \end{lemma}
@@
 \begin{proof}
-	Suppose there exists a nonplanar graph $G$ for which all of it's components are planar.
+	Suppose there exists a nonplanar graph $G$ for which all of its components are planar.
 If each component is planar we may also make a drawing of it in any space homeomorphic to $\mathbb R^2$.
@@
 
-\begin{lemma} \label{subdivisionCarryOn}
-	If a graph $G$ has a subdivision of $H$ as a subgraph, then any subdivision of $G$ contains a subdivision of $H$ as a subgraph.
-\end{lemma}
-\begin{proof}
-	Let $H$ be a graph.
+%%TODO remove?
+%\begin{lemma} \label{subdivisionCarryOn}
+%	If a graph $G$ has a subdivision of $H$ as a subgraph, then any subdivision of $G$ contains a subdivision of $H$ as a subgraph.
+%\end{lemma}
+%\begin{proof}
+%	Let $H$ be a graph.
 Let $H'$ be a subdivision of $H$.
@@
 We then can produce $H''$ by taking $H$ and doing the sequence of edge subdivisions $h_1,h_2,\ldots,h_\ell,g_{i_1},g_{i_2},\ldots,g_{i_n}$ so $H''$ is a subdivision of $H$.
-\end{proof}
+%\end{proof}
 
@@
 \end{definition}
-\begin{lemma}
+\begin{lemma}\label{JordansLemma}
 	For any plane drawing of a graph, $G$, containing cycle $C$, $C$ is a Jordan curve in the drawing.
@@
 \begin{lemma} \label{outside}
-	For any face, $F$, in a plane drawing, $D$, of a graph $G$, there is a corresponding drawing plane drawing of $G$, $D'$, where all edges and vertices that boarder $F$ in $D$, now boarder the outer face.
+	For any face, $F$, in a plane drawing, $D$, of a graph $G$, there is a corresponding drawing plane drawing of $G$, $D'$, where all edges and vertices that border $F$ in $D$, now border the outer face.
 \end{lemma}
@@
 \begin{definition}[$k$ connected]
-	A graph, $G$, is $k$ connected if it's minimal cut set is of size $k$. The complete graph on $n$ vertices is defined to be $n-1$ connected.
+	A graph, $G$, is $k$ connected if its minimal cut set is of size $k$. The complete graph on $n$ vertices is defined to be $n-1$ connected.
 \end{definition}
@@
 
-\begin{definition}[mutually disjoint paths]
-	A set of paths, $S$, is mutually disjoint if no two paths share a vertex. A path $p\in S$ is said to be mutually disjoint from the the other paths in $S$ if $S$ is mutually disjoint.
-\end{definition}
-
-\begin{definition}[mutually internally disjoint paths]
-	A set of paths, $S$, is mutually internally disjoint if no to paths share an internal vertex.
+\begin{definition}[disjoint paths]
+	A set of paths, $S$, is disjoint if no two paths share a vertex. A path $p\in S$ is said to be disjoint from the the other paths in $S$ if $S$ is disjoint.
+\end{definition}
+
+\begin{definition}[internally disjoint paths]
+	A set of paths, $S$, is internally disjoint if no to paths share an internal vertex.
 That is no two paths, $p_1\not=p_2\in S$ share a vertex other than their first or last vertex.
-A path $p\in S$ is said to be mutually internally disjoint from the other paths in $S$ if $S$ is mutually internally disjoint.
-\end{definition}
-
-\begin{theorem}[Menger's theorem]
-	A non-empty graph is $n$ connected if and only if among all pairs of vertices $a\not=b$ in $G$ the least number of mutually internally disjoint paths from $a$ to $b$ is $n$.
+A path $p\in S$ is said to be internally disjoint from the other paths in $S$ if $S$ is internally disjoint.
+\end{definition}
+
+\begin{theorem}[Menger's theorem]\label{menger}
+	A non-empty graph is $n$ connected if and only if among all pairs of vertices $a\not=b$ in $G$ the least number of internally disjoint paths from $a$ to $b$ is $n$.
 \end{theorem}
@@
 Define an $AB$ separator as any vertex set, $S$, for which all $AB$ paths contain at least one member of $S$.
-Define an $AB$ connector a set of mutually disjoint $AB$ paths.
-
-	Now by induction we will show that for any pair of vertex sets $A,B$ in a graph $G$, the maximum size of an $AB$ connector is also the minimum size of an $AB$ separator.
+Define an $AB$ connector a set of disjoint $AB$ paths.
+
+	We will show by induction that for any pair of vertex sets $A,B$ in a graph $G$, the maximum size of an $AB$ connector is also the minimum size of an $AB$ separator.
+First however note that the size of the minimum $AB$ separator always forms an upper bound for the size of an $AB$ connector, as every path in an $AB$ connector must pass through one element of every $AB$ separator.
+Likewise the maximum size of an $AB$ connector forms a lower bound for the size of an $AB$ separator.
 
@@
 
-	Inductive case: Suppose $H$ is a graph with $k>0$ edges, and that our statement is true for any graph with less than $k$ edges. Now choose an edge $e\in H$%TODO
+	Inductive case: Suppose $H$ is a graph with $k>1$ edges.
+Further suppose that for any sets pair of vertex sets $A,B$ in a graph with $k-1$ edges, the size of the maximum $AB$ connector is also the size of the minimum $AB$ separator.
+Choose vertex sets $A$ and $B$ within $H$ and suppose the minimum size of an $AB$ separator is $n$.
+Choose an edge $e \in H$ and consider $H\setminus\set e$.
+Any $AB$ separator in $H$ is also an $AB$ separator in $H\setminus\set e$, so the size of the minimum $AB$ separator in $H\setminus\set e$ is at most $n$.
+
+	If $H\setminus\set e$ has a minimum $AB$ separator of size $n$ then $H\setminus\set e$ must have a maximum $AB$ connector of size $n$.
+This $AB$ connector is also a $AB$ connector of size $n$ in $H$.
+Therefore $H$ has a maximum $AB$ connector of size $n$.
+
+	If $H\setminus\set e$ has a minimum $AB$ separator of size less than $n$, then let $S$ be such an $AB$ separator.
+Any $AB$ path in $H$ must contain a vertex in $S$ or the edge $e$.
+Now we know that $\card S = n-1$ as $S$ combined with either vertex of $e$ is an $AB$ separator in $H$.
+We know there exists some $AB$ path in $H$ that contains edge $e$ and no vertices in $S$ as otherwise $S$ would be an $AB$ separator in $H$.
+Along this path let us call the earlier vertex of $e$, $e_a$ and the later vertex $e_b$.
+In $(H\setminus\set e)\setminus S$ we have a path from $A$ to $e_a$ and a path from $e_b$ to $B$.
+This also means there is no path from $e_a$ to $B$ or from $A$ to $e_b$ in $(H\setminus \set e)\setminus S$ as otherwise $S$ would not be an $AB$ separator in $H\setminus\set e$.
+Now we let $S_a = S\union\set{e_a}$ and $S_b = S\union\set{e_b}$.
+$S_a$ and $S_b$ are both vertex sets within $H\setminus\set e$ so the minimal $AS_a$ separators is the same size as the maximal $AS_a$ connector and the minimal $S_bB$ separator is the same size as the maximal $S_bB$ connector by our inductive hypothesis.
+Now let $T_a$ be a minimal $AS_a$ separator in $H\setminus\set e$ and $T_b$ be a minimal $S_bB$ separator in $H\setminus\set e$.
+We know that $T_a$ is a minimal $AS_a$ separator in $H$ as any path through $e$ from $A$ must have already passed through $S_a$.
+Likewise we know that $T_b$ is a minimal $S_bB$ separator in $H$ for the same reason.
+As $T_a$ is a $AS_a$ separator in $H$ and $S_a$ is a $AB$ separator in $H$ then any $AB$ path must contain an element of $S_1$ and also contains an element of $T_a$.
+Likewise as $T_b$ is a $S_bB$ separator in $H$ and $S_b$ is a $AB$ separator in $H$ then any $AB$ contains an element of $S_2$ and therefore also contains an element of $T_b$.
+From this we know that both $T_a$ and $T_b$ must be at least size $n$.
+This then means that the minimal $AS_a$ connector in $H\setminus\set e$ is at least size $n$, so it must be exactly $n$ as there are only $n$ elements in $S_a$.
+Likewise the maximal $S_bB$ connector must be of size $n$.
+Finally we can construct an $AB$ connector in $H$ of size $n$ by taking an $AS_a$ path starting at $A$ going to $S_a$, if we are at $e_a$ then take edge $e$ to $e_b$ then we are in $S_b$ and we can continue down a $S_bB$ path.
+There can not be a larger $AB$ connector as we have an $AB$ separator of size $n$ and this forms an upper bound like before.
+
+	Now by induction we know that for any graph $G$, and any pair of vertex sets $A,B$ within $G$, the maximal $AB$ connector is the same size as the minimal $AB$ separator.
 
@@
 It follows that the size of the smallest $AB$ separator is at least $n$, therefore there is an $AB$ connector with at least $n$ paths.
-Therefore there are at least $n$ mutually internally disjoint paths from $a$ to $b$.
+Therefore there are at least $n$ internally disjoint paths from $a$ to $b$.
 
@@
 We know that $\card A \ge n$, so we have a contradiction and the minimal $AB$ separator must still be at least size $n$.
-We then have at least one $AB$ connector of at least size $n$, and therefore there are at least $n$ mutually internally disjoint paths from $a$ to $b$.
+We then have at least one $AB$ connector of at least size $n$, and therefore there are at least $n$ internally disjoint paths from $a$ to $b$.
 
@@
 Therefore the maximal $N(\alpha)N(\beta)$ connector is size $n$.
-Therefore if $G$ is $n$ connected, then among all pairs of vertices $a\not=b$ in $G$ the least number of mutually internally disjoint paths from $a$ to $b$ is $n$.
+Therefore if $G$ is $n$ connected, then among all pairs of vertices $a\not=b$ in $G$ the least number of internally disjoint paths from $a$ to $b$ is $n$.
 
@@
 	Now let us suppose $G$ is not $n$ connected, then the graph must be $k\not= n$ connected.
-By what we have shown above we know that among all the vertex pairs $a\not= b$ in $G$ the least number of mutually internally disjoint paths from $a$ to $b$ is $k\not=n$.
+By what we have shown above we know that among all the vertex pairs $a\not= b$ in $G$ the least number of internally disjoint paths from $a$ to $b$ is $k\not=n$.
 \end{proof}
@@
 We also know that $G\setminus H$ is a proper subgraph of $G$ and therefore must also be planar.
-By lemma $\ref{outside}$ we may draw both $G\setminus H$ and $H'$ such that $v$ boarders the outer face.
+By lemma $\ref{outside}$ we may draw both $G\setminus H$ and $H'$ such that $v$ borders the outer face.
 We may split $\mathbb R^2$ into two disjoint subsets
@@
 
-%TODO 3 connected stuff
 \begin{definition}[lobe]
@@
 We may then draw $L_1^+$ on the plane.
-If we have a planar drawing of $\unionfrom{j = 1}{i-1}{L_j^+}$ we can then embed a drawing of $L_i^+$ where the edge between $x$ and $y$ boarders the outer edge into a face that is bordered by the edge between $x$ and $y$ in our planar drawing of $\unionfrom{j = 1}{i-1}{L_j^+}$.
+If we have a planar drawing of $\unionfrom{j = 1}{i-1}{L_j^+}$ we can then embed a drawing of $L_i^+$ where the edge between $x$ and $y$ borders the outer edge into a face that is bordered by the edge between $x$ and $y$ in our planar drawing of $\unionfrom{j = 1}{i-1}{L_j^+}$.
 We then can redraw this embedding such that $x$ and $y$ in $L_i^+$ are at the same points as $x$ and $y$ in $\unionfrom{j = 1}{i-1}{L_j^+}$ yielding a planar drawing of $\unionfrom{j=1}{i}{L_j^+}$.
@@
 
-\begin{lemma}
+\begin{lemma}\label{3connect}
 	If $G$ is a graph with the properties listed below, then $G$ is at least 3-connected.
 	\begin{enumerate}
-		\item $G$ does not contain any subdivision of $K_{3,3}$ or $K_5$ as a subgraph.
+		\item $G$ does not contain any subgraph that is contactable to of $K_{3,3}$ or $K_5$.
 		\item $G$ is nonplanar.
@@
 If $H$ is missing a vertex from $G$, then $H$ must break one of the first 3 properties.
-$H$ can not contain a subdivision of $K_{3,3}$ or $K_5$ as then $G$ would also contain it and $H$ can not have more vertices than $G$.
+$H$ can not contain a subgraph that is contactable to $K_{3,3}$ or $K_5$ as then $G$ would also contain it and $H$ can not have more vertices than $G$.
 This leaves only that $H$ must be planar.
 If $H$ is missing an edge from $G$, then $H$ must break one of the first 2 properties.
-Again $H$ can not contain a subdivision of $K_{3,3}$ or $k_5$ as then $G$ would also contain it.
+Again $H$ can not contain a subgraph that is contactable to $K_{3,3}$ or $k_5$ as then $G$ would also contain it.
 This again leaves only that $H$ must be planar.
@@
 We know by lemma \ref{lobes} that there is a lobe $L$ for which adding an edge between $x$ and $y$ would yield a nonplanar graph $L^+$.
-Clearly $L^+$ has less edges then $G$, so $L^+$ must contain $K_{3,3}$ or $K_{5}$ as a subdivision.
+Clearly $L^+$ has less edges then $G$, so $L^+$ must contain a subgraph that is contractible to $K_{3,3}$ or $K_{5}$.
 Consider another lobe $M$ of $S$.
 There must be a path, $p$, from $x$ to $y$ in $M$ as otherwise $G$ would not be either 0 or 1 connected.
-Clearly $L\union p$ is a subgraph of $G$ and $L\union p$ is a subdivision of $L^+$.
-By lemma \ref{subdivisionCarryOn} we then know that $L\union p$ contains a subdivision of $K_{3,3}$ or $K_5$.
+Clearly $L\union p$ is a subgraph of $G$ and $L\union p$ is contractible to $L^+$.
+By lemma \ref{contractibleCarryOn} we then know that $L\union p$ contains a subgraph that is contractible to $K_{3,3}$ or $K_5$.
 This gives us a contradiction so $G$ can not be 2-connected and therefore must be at least 3 connected.
@@
 \end{proof}
+
+\subsubsection{Some more useful definitions about bridges}
+\begin{definition}[vertex of attachment]
+	If $B$ is a bridge of cycle $C$, then any vertex in both $B$ and $C$ is a vertex of attachment
+\end{definition}
+
+\begin{definition}[degree]
+	The degree of a bridge is the number of vertices of attachment it has.
+\end{definition}
 
@@
 There must be some first vertex in $W$ that is in $C$, so let us call $W'$ the subwalk of $W$ from $b$ to that first vertex in $C$.
-Now we know that $W'$'s first vertex in $C$ is also it's last vertex, so it does not pass through $C$.
+Now we know that $W'$'s first vertex in $C$ is also its last vertex, so it does not pass through $C$.
 Therefore by lemma \ref{walktopartialbridge} the graph $H$ composed of $W'$'s vertices and edges is a partial bridge.
@@
 \begin{proof}
-%TODO prove
+	Suppose that $G$ is a graph with the following properties.
+	\begin{enumerate}
+		\item $G$ does not contain any subgraph that is contactable to of $K_{3,3}$ or $K_5$.
+		\item $G$ is nonplanar.
+		\item Of all graphs satisfying properties (1) and (2), $G$ has the least number of edges.
+		\item Of all graphs satisfying properties (1), (2) and (3), $G$ has the least number of vertices.
+	\end{enumerate}
+	We will try and show that $G$ does not exist.
+
+	First off we have lemma \ref{3connect} which says that $G$ must be at least 3 connected.
+Additionally we know that $G$ must be minimally nonplanar.\footnote{This was proved in the beginning of the proof for lemma \ref{3connect}.} Now choose an edge $e \in G$ between $x$ and $y$ and let $G' = G\setminus\set e$.
+Clearly $G'$ is planar.
+Because $G$ is 3 connected, by Menger's theorem (theorem \ref{menger}) we know that between any two vertices $a\not=b$ there are at least 3 internally disjoint paths in $G$.
+From this we can see that in $G'$ there must be at least 2 internally disjoint paths between $a$ and $b$.
+This means that every pair of paths in $G'$ lie upon a cycle, start at $a$ go down one path to $b$, then follow the other internally distinct path back to $a$.
+Let $\mathcal C$ be the set of all cycles that $x$ and $y$ lie on in $G'$.
+Let $\mathcal D$ be the set of all plane drawings of $G'$.
+By lemma \ref{JordansLemma} we know that every drawing $D\in\mathcal D$ we know that all cycles $C\in\mathcal C$ form a Jordan curve.
+Now choose a pair $\pair CD \in \mathcal C\cross\mathcal D$ such the curve created by $C$ in $D$ has the maximum possible number of edges in its interior.
+Now lets take a look at the bridges of $C$ in $D$.
+
+	$C$ has no bridges of degree 1 as their vertex of attachment would be a single vertex cut set and we know $G'$ is at least 2 connected.
+Now we can break $C$ into two parts.
+If we start at $x$ and travel along $C$ to $y$ we get a path we are calling $p$.
+If we continue along $C$ from $y$ back to $x$ we get another path $q$.
+
+	Claim: There are no external bridges of $C$ that have more than one vertex of attachment in either $p$ or $q$.
+
+	Proof: Assume there is an external bridge $B$ of $C$ with vertices of attachment $b_1$, $b_2$ with either both in $p$ or both in $q$.
+Let $r$ be the path (either $p$ or $q$) that contains $b_1$ and $b_2$.
+Further assume without loss of generality that $b_1$ comes before $b_2$ in $r$.
+As $B$ is connected, there must be a path $s$ in $B$ from $b_1$ to $b_2$.
+Now construct a path $r'$ that starts where $r$ starts, goes down $r$ to $b_1$ then follows $s$ to $b_2$ where it continues down $r$ until $r$'s end.
+If $b_2 = r_j$ this would look like
+	$$
+	r' = r_1r_2\ldots b_1s_1s_2\ldots b_2r_{j+1}r_{j+2}\ldots r_{\card r}
+	$$
+	Now we can construct $C'$ to be $C$ but replace $r$ with $r'$.
+$C'$ clearly contains both $x$ and $y$, and it also will have more edges on it's interior than $C$ did.
+This is a contradiction as $C$ is the cycle containing $x$ and $y$ with the most edges on the interior.
+
+	Now by the pigeonhole principle there can not be any external bridges of $C$ with degree greater than 2.
+Further no external bridge may have $x$ or $y$ as a vertex of attachment as $x$ and $y$ are in both $p$ and $q$.
+This means that all external bridges of $C$ are degree two with one vertex of attachment in $p$ and one vertex of attachment in $q$ and neither in $\set{x,y}$.
+We also know there is at least one external bridge of $C$ as otherwise $x$ and $y$ would both be bordering the outer face so the edge $e$ can be drawn within the outer face yielding $G$ to be a planar graph.
+By similar logic there must be some internal bridge $I$ that has one vertex of attachment in $p\setminus\set{x,y}$ and one vertex of attachment in $q\setminus\set{x,y}$ (This is because if there was no such bridge $x$ and $y$ would share a face and we could draw in $e$ making $G$ planar).
 \end{proof}

### 2019-05-11 Topology/Paper/paper.tex
Possible mistake

@@
 \end{proof}
-
-\subsubsection{Some more useful definitions about bridges}
-\begin{definition}[vertex of attachment]
-	If $B$ is a bridge of cycle $C$, then any vertex in both $B$ and $C$ is a vertex of attachment
-\end{definition}
-
-\begin{definition}[degree]
-	The degree of a bridge is the number of vertices of attachment it has.
-\end{definition}
 
@@
 
+\subsubsection{Some more useful definitions about bridges}
+\begin{definition}[vertex of attachment]
+	If $B$ is a bridge of cycle $C$, then any vertex in both $B$ and $C$ is a vertex of attachment
+\end{definition}
+
+\begin{definition}[degree]
+	The degree of a bridge is the number of vertices of attachment it has.
+\end{definition}
+
+\begin{definition}[Skew]
+	Let $A$ and $B$ be bridges of cycle $C$.
+$A$ and $B$ are skew one another if there exists vertices of attachment $a_1, a_2 \in A$ and $b_1,b_2\in B$ with ordering $a_1,b_1,a_2,b_2$ in $C$ and $\set{a_1,a_2}\inter\set{b_1,b_2}=\emptyset$.
+\end{definition}
+
+\begin{lemma}\label{skew}
+	If $A$ and $B$ are bridges of cycle $C$ in a planar graph $G$, and $A$ and $B$ are skew one another then $A$ and $B$ can not both be drawn in interior or both in the exterior of $C$.
+\end{lemma}
+
+\begin{proof}
+	In $C$ the vertices $a_1$ and $a_2$ separate $C$ into two parts.
+One part contains $b_1$ and the other contains $b_2$.
+If $A$ is drawn on the interior of $C$ then there must be a path from $a_1$ to $a_2$ already drawn on the interior of $C$.
+This means that any path drawn from $b_1$ to $b_2$ on the interior of $C$, must pass over this path.
+The same argument works for the exterior of $C$.
+\end{proof}
+
 \subsection{The home stretch}
@@
 We also know there is at least one external bridge of $C$ as otherwise $x$ and $y$ would both be bordering the outer face so the edge $e$ can be drawn within the outer face yielding $G$ to be a planar graph.
-By similar logic there must be some internal bridge $I$ that has one vertex of attachment in $p\setminus\set{x,y}$ and one vertex of attachment in $q\setminus\set{x,y}$ (This is because if there was no such bridge $x$ and $y$ would share a face and we could draw in $e$ making $G$ planar).
+By similar logic there must be some internal bridge $I$ that has at least one vertex of attachment in $p\setminus\set{x,y}$ and at least one vertex of attachment in $q\setminus\set{x,y}$ (This is because if there was no such bridge $x$ and $y$ would share a face and we could draw in $e$ making $G$ planar).
+
+	Let $E$ be an external bridge of $C$ with vertices of attachment $e_p$ and $e_q$ with $e_p$ in $p\setminus\set{x,y}$ and $e_q\setminus\set{x,y}$ in $q$.
+If we consider $C\setminus\set{e_p,e_q}$ we get two connected components.
+One of these components will have $x$ and the other will have $y$.
+Let us define $X(E)$ to be the component containing $x$ and $Y(E)$ to be the component containing $y$.
+Additionally there must be some internal bridge of $C$ with a vertex of attachment in both $X(E)$ and $Y(E)$ as otherwise $E$ could be redrawn on the inside of $C$.
+
+	Claim: There must exist some external bridge $E$ of $C$ with a vertex of attachment in both $p\setminus\set{x,y}$ and $q\setminus\set{x,y}$ for which there is an internal bridge $B$ of $C$ with at least one vertex of attachment in all of the following:
+	\begin{enumerate}
+		\item $X(E)$
+		\item $Y(E)$
+		\item $p\setminus\set{x,y}$
+		\item $q\setminus\set{x,y}$.
+	\end{enumerate}
+
+	Proof: Assume there is no such bridge external bridge $E$.
+We know there must still be be an external bridge with a vertex of attachment in $p\setminus\set{x,y}$ and a vertex of attachment in $q\setminus\set{x,y}$, and let $A$ be one such bridge.
+We will show that we can add $e$ back into the interior of $C$ yielding a planar $G$.
+
+	Start by letting $B$ be a bridge with no vertex of attachment in $p\setminus\set{x,y}$.
+This bridge clearly does not prevent us from drawing the edge $e$ into the interior of $C$.
+The same is true for a bridge $B$ with no vertex of attachment in $q\setminus\set{x,y}$.
+
+	%Some more work needed on bridges that are skew one another
+	Now let $B$ be a bridge with a vertex of attachment in all of the above except $X(A)$.
+If there is no bridge that is skew with $B$ then $B$ can be redrawn on the exterior of $C$.
+If there is a bridge, $B'$, that is skew with $B$ then it's vertices of attachment must all be within $Y(A)\union\set{e_p,e_q}$ as otherwise it would be skew $A$ (see lemma \ref{skew}).
+We also know that all of $B'$'s vertices of attachment must be in either $e_q$ or in $e_p$ as otherwise if we let $E = B'$ we would find a contradiction to our initial assumption.
+This means we can redraw $B$ and $B'$ by switching which one is on the interior and exterior.
+Clearly $B'$ does not prevent us from redrawing $e$ on the interior of $C$.
+
+	The only remaining type of bridge that could prevent us from redrawing $e$ on the interior of $C$ is a bridge with a vertex of attachment in all the above except $Y(A)$.
+The same exact argument as above will work for any such bridge.
+
+	This means that any bridge on the interior does not prevent $e$ from being drawn, so we may 
 \end{proof}

### 2019-05-11 Topology/Paper/paper.tex
starting revisions

@@
 Topological graph theory is an entire field within topology and as such this paper is by no means meant to cover all of topological graph theory in any depth.
-This paper instead will first cover a rather shallow overview of the field, followed by a more in depth study of graphs and their genus.
+This paper instead will first cover a rather shallow overview of the field (section 2), followed by a more in depth study of graphs theory (section 3).
 The overview will mainly be focused on giving a thorough understanding of what topological graph theory is as well as to briefly cover the history of the field.
-In giving an overview of the field we will cover some of the basic concepts and definitions needed for the more rigorous part of the paper.
-After the overview we will dive into Kuratowski's Theorem, We will go through and attempt to have an intuitive understanding of a Kuratowski's Theorem and its proof.
-After proving Kuratowski's Theorem, we will continue onto talking about generalizations of the theorem and map colorings, however their coverage will be rather shallow and lacking proofs.
+After the overview we will spend section 3 building up definitions from graph theory that we will need for the later more rigorous parts of the paper.
+After this we will dive into Kuratowski's Theorem.
+We will start by defining $K_5$ and $K_{3,3}$ and showing that they are both nonplanar.
+Up until this point the paper is written to be accessible by anyone, no mater their level of math background.
+After we show the nonplanarity of $K_5$ and $K_{3,3}$ we continue onto thoroughly prove Kuratowkski's theorem.
+The audience for this part is expected to have at least an undergraduate understanding of topology and some exposure to graph theory.
+After Kuratowski's theorem we finish with a brief discussion of what lies beyond Kuratowski's theorem.
 
@@
 \subsection{Graphs}
-Before we talk about topological graph theory with any level of understanding we must first understand what a graph is.
+Before we talk about topological graph theory we must first understand what a graph is.
 
@@
 
-\begin{theorem}
+\begin{theorem} \label{k5}
 	$K_5$ is nonplanar.
@@
 
-\begin{theorem}
+\begin{theorem} \label{k3,3}
 	$K_{3,3}$ is nonplanar.
@@
 	\item For any two edges $e\not=f$, $\hat e(x) \not= \hat f(y)$ for all $x,y \in\ooint01$.
-	\item for all $d\in D$ there exists either a vertex $a\in V$ such that $v(a) = d$ or there exists an edge $e\in E$ such that $d$ is in the image of $\hat e$.
+	\item For all $d\in D$ there exists either a vertex $a\in V$ such that $v(a) = d$ or there exists an edge $e\in E$ such that $d$ is in the image of $\hat e$.
 \end{itemize}
@@
 \begin{lemma} \label{subgraph}
-	If a graph $G$ has a nonplanar subgraph, then $G$ is nonplanar.
+	If a graph $G$ can be drawn in a space, $S$, then so can any subgraph of $G$.
 \end{lemma}
@@
 \begin{proof}
-	If we have a graph $G$ with a nonplanar subgraph $H$ then when drawing $G$ there is a part of the drawing that is $H$.
-This part of the drawing can not be planar and therefore the drawing of $G$ can not be a plane drawing.
+	Let $D$ be a graph drawing of $G$ in $S$. Simply remove all edges and vertices from $D$ that $H$ does not have and we have a new drawing $D'\subset D$ that is a graph drawing of $H$ in $S$.
 \end{proof}
@@
 Simply put if we have a finite number of vertices and never use any space filling curves for edges we will never fill space.
-We know that we are never forced to use a space filling curve as for any space filling curve $c$ we may create a new curve $c'$ that connects the same end points, stays within $c$'s image, and is not space filling.
-%TODO ask Shaw if maybe turn into lemma and prove
-	} We may now use a sterographic projection, $g$ to map $f(D)$ from the new punctured sphere back to $\mathbb R^2$ creating $D' = g(f(D))$.
+We know that we are never forced to use a space filling curve as for any space filling curve $c$ we may create a new curve $c'$ that connects the same end points, stays within $c$'s image, and is not space filling.} We may now use a sterographic projection, $g$ to map $f(D)$ from the new punctured sphere back to $\mathbb R^2$ creating $D' = g(f(D))$.
 We know that in $D'$ the face that corresponds to $F$ is the outer face as it contained the punctured point in $\inv g(D')$.
@@
 From this we can see that in $G'$ there must be at least 2 internally disjoint paths between $a$ and $b$.
-This means that every pair of paths in $G'$ lie upon a cycle, start at $a$ go down one path to $b$, then follow the other internally distinct path back to $a$.
+By Menger's theorem (theorem \ref{menger}) we know that $G'$ is 2 connected.
+This also means that every pair of paths in $G'$ lie upon a cycle, start at $a$ go down one path to $b$, then follow the other internally distinct path back to $a$.
 Let $\mathcal C$ be the set of all cycles that $x$ and $y$ lie on in $G'$.
@@
 
-	Claim: There must exist some external bridge $E$ of $C$ with a vertex of attachment in both $p\setminus\set{x,y}$ and $q\setminus\set{x,y}$ for which there is an internal bridge $B$ of $C$ with at least one vertex of attachment in all of the following:
+	Claim: There must exist some external bridge $E$ of $C$ for which there is an internal bridge $B$ of $C$ with at least one vertex of attachment in all of the following:
 	\begin{enumerate}
@@
 
-	Proof: Assume there is no such bridge external bridge $E$.
-We know there must still be be an external bridge with a vertex of attachment in $p\setminus\set{x,y}$ and a vertex of attachment in $q\setminus\set{x,y}$, and let $A$ be one such bridge.
-We will show that we can add $e$ back into the interior of $C$ yielding a planar $G$.
-
-	Start by letting $B$ be a bridge with no vertex of attachment in $p\setminus\set{x,y}$.
-This bridge clearly does not prevent us from drawing the edge $e$ into the interior of $C$.
-The same is true for a bridge $B$ with no vertex of attachment in $q\setminus\set{x,y}$.
-
-	%Some more work needed on bridges that are skew one another
-	Now let $B$ be a bridge with a vertex of attachment in all of the above except $X(A)$.
-If there is no bridge that is skew with $B$ then $B$ can be redrawn on the exterior of $C$.
-If there is a bridge, $B'$, that is skew with $B$ then it's vertices of attachment must all be within $Y(A)\union\set{e_p,e_q}$ as otherwise it would be skew $A$ (see lemma \ref{skew}).
-We also know that all of $B'$'s vertices of attachment must be in either $e_q$ or in $e_p$ as otherwise if we let $E = B'$ we would find a contradiction to our initial assumption.
-This means we can redraw $B$ and $B'$ by switching which one is on the interior and exterior.
-Clearly $B'$ does not prevent us from redrawing $e$ on the interior of $C$.
-
-	The only remaining type of bridge that could prevent us from redrawing $e$ on the interior of $C$ is a bridge with a vertex of attachment in all the above except $Y(A)$.
-The same exact argument as above will work for any such bridge.
-
-	This means that any bridge on the interior does not prevent $e$ from being drawn, so we may 
-\end{proof}
+	Proof: Assume there is no such bridge external bridge $E$. We will show a contradiction as we will be able to redraw $G'$ such that we can add $e$ in the interior of $C$.
+
+	For any bridge $B$ on the interior of $C$ that does not have a vertex of attachment in $p\setminus\set {x,y}$, $B$ does not prevent the edge $e$ from being added in the interior of $C$.
+The same is true for any bridge on the interior of $C$ with no vertex of attachment in $p\setminus\set{x,y}$ this means that if we can redraw $G'$ such that all bridges on the interior of $C$ have no vertices of attachment in $p\setminus\set{x,y}$ or no vertices of attachment in $q\setminus\set{x,y}$ then we will have shown a contradiction.
+
+	Let $B$ be a bridge on the interior of $C$ that has a vertex of attachment in both $q\setminus\set{x,y}$ and in $p\setminus\set{x,y}$.
+If there is any bridge, $E$, that is skew with $B$ then $E$ must be on the exterior and it's existence would contradict our initial assumption.
+As there may not be any bridges that are skew with $B$ we may simply redraw $B$ on the exterior of $C$.
+This then yields a contradiction, so the claim as been proved.
+
+	Now that we know there is some external bridge $E$ of $C$ for which there is an internal bridge $B$ of $C$ with at least one vertex of attachment in each of $X(E), Y(E), q\setminus\set{x,y},p\setminus\set{x,y}$.
+This means that the set $B\inter C$ (the set of all vertices of attachment of $B$) must intersect each of the following sets $X(E),Y(E),q\setminus\set{x,y},p\setminus\set{x,y}$.
+Choose $A\subset B\inter C$ such that $A$ intersects with each of $X(E),Y(E),q\setminus\set{x,y},p\setminus\set{x,y}$ and there is no $A'\subset B\inter C$ for which $\card{A'} < A$ and $A'$ intersects with each of $X(E),Y(E),q\setminus\set{x,y},p\setminus\set{x,y}$.
+
+	We know that $\card A\not=0$ as then it cant intersect anything.
+We know that $\card A\not= 1$ as then there exists only one $a\in A$ and we can not have both $a\in X(E)$ and $a\in Y(E)$ as $X(E)\inter Y(E) = \emptyset$.
+We know that $\card A < 5$ by the pigeonhole principle.
+This means that we only have three possibilities left: $\card A = 2$, $\card A = 3$, or $\card A = 4$.
+Lets go through them.
+
+	\begin{enumerate}
+		\item If $\card A = 2$ then we may let $A = \set{u,v}$ with $u\in X(E)$ and $v\in Y(E)$.
+Now either $u\in q\setminus\set{x,y}$ and $v\in p\setminus\set{x,y}$, or $v\in q\setminus\set{x,y}$ and $u\in p\setminus\set{x,y}$.
+Either way this will result in $G$ containing a subgraph that contracts to $K_{3,3}$.
+
+		\item If $\card A = 3$.
+There must be some $a\in A$ for which $a\in\set{x,y,e_p,e_q}$ as otherwise $A$ would contain a subset that fit our previous case.
+Whatever $a$'s value, it will be in exactly one of the four sets $X(E),Y(E),q\setminus\set{x,y},p\setminus\set{x,y}$.
+This means no other element can also be in whichever of these sets $a$ is in as then we could simply remove $a$ from $A$.
+
+		Suppose there is another element $b\in A$ with $b \in\set{x,y,e_p,e_q}$.
+We know that $\set{a,b}\not=\set{x,y}$ and $\set{a,b}\not=\set{e_p,e_q}$ as then we would have only one vertex left that would need to be in two disjoint sets.
+This means that we can say without loss of generality let $a \in\set{x,y}$ and $b\in\set{e_p,e_q}$.
+This leaves one last element $c\in A$ with $c$ along the path in $C$ between the element of $\set{x,y}\setminus\set a$ and the element of $\set{e_p,e_q}\setminus\set b$.
+By simply removing the path between $a$ and $b$ in $C$ we would get a graph that looks very similar to what we got when $\card A = 2$.
+This will result again in $G$ containing a subgraph that contracts to $K_{3,3}$.
+
+		Suppose there is no other element in $A$ that is also in $\set{x,y,e_p,e_q}$.
+We know then that if $a\in\set{x,y}$ then the other two elements are on the paths in $C$ between the element in $\set{x,y}\setminus\set x$ and $e_p$ or $e_q$ respectively.
+Let $b\in A$ be on the path in $C$ between $e_p$ and the element of $\set{x,y}\setminus\set x$.
+Simply contract all the edges on $C$ between $e_p$ and $b$ and we have contracted to a graph that would be in our previous case.
+Then by lemma \ref{contractibleCarryOn} we know that $G$ must contain a subgraph that is a subdivision of $K_{3,3}$.
+If $a\in\set{e_p,e_q}$ then we can make the same argument that both the other elements of $A$ will be on paths between the element of $\set{e_p,e_q}\setminus a$ and $x$ or $y$ respectively.
+Then we may let $b\in A$ be on the path in $C$ between $x$ and the element of $\set{e_p,e_q}\setminus a$, and then contract all the edges on the path along $C$ between $b$ and $x$.
+This again leaves us at the previous case so $G$ will have a subgraph that contracts to $K_{3,3}$.
+
+		\item If $\card A = 4$ then $A = \set{x,y,e_q,e_p}$ as otherwise one of the previous cases would be a subset of $A$.
+In this, when we add back in edge $e$ we find that $G$ contains a subgraph that is contactable to $K_5$.
+	\end{enumerate}
+
+	Now we have shown a contradiction with our original statement, so there is no graph $G$ that is nonplanar does not contain a subgraph that is contactable to $K_5$ or $K_{3,3}$.
+Further suppose $G$ is a graph that contains a subgraph $H$ that is contactable to either $K_5$ or $K_{3,3}$.
+We know that $K_5$ is nonplanar by theorem \ref{k5} and that $K_3$ is nonplanar by theorem \ref{k3,3}.
+It follows then from lemma \ref{contractible} that $H$ is nonplanar.
+Finally $G$ must also be nonplanar by lemma \ref{subgraph}.
+\end{proof}
+
+\section{Beyond Kuratowski's theorem}
+Kuratowski's theorem is an unexpectedly elegant statement that says there are only two base case nonplanar graphs, and that all other nonplanar graphs derive their nonplanarity from at least one of these two graphs.
+A logical next step might be to ask about different surfaces.
+We've found which graphs can be drawn on a plane, but what about a sphere or a torus?
+It turns out that the set of graphs that can be drawn on a sphere is the same set of graphs that can be drawn on the plane,\footnote{We actually showed most of what is needed to prove this in our proof for lemma \ref{outside}.} however this is not true for a torus and certainly not true in general.
+For example $K_{3,3}$ can be drawn on both a torus and a M\"obius strip.
+So the question naturally arises, do all surfaces have a set of base forbidden graphs like $\set{K_{3,3},K_5}$ is for the plane.
+
+The graph minor theorem answers this question, at least in part.
+It states that any countable set $\mathcal G$ of finite graphs, contains a finite subset $\mathcal H\subset\mathcal G$ such that for all $G\in\mathcal G$ there is some $H\in\mathcal H$ such that $G$ contains a subset that is contactable to $H$.
+%TODO cite https://arxiv.org/pdf/1608.04066.pdf
+This means that if a surface $S$ has the following property
+\begin{itemize}
+	\item For any graph $G$ that can be drawn in $S$, any graph produced by preforming an edge contraction on $G$ is able to be drawn in $S$.
+\end{itemize}
+then $S$ has a finite set of forbidden graphs.
+
+Another reasonable question is, now that we've talked so much about what can be drawn in $\mathbb R^2$, what about in $\mathbb R^k$.
+This turns out to be a rather disappointing line of inquiry.
+When $k=1$ we can only draw line graphs and unions thereof.\footnote{A line graph is any graph $G$ such that there is some path $p$ in $G$ that contains every vertex and every edge in $G$.} When $k\ge 3$ we can draw any graph whatsoever pretty easily.
+Simply make a drawing that allows for edges to cross in $\mathbb R^2$ and wherever there is a crossing simply lift ``up" one edge.\footnote{Up here refers to any direction perpendicular to the plane we initially drew the graph in.}
+
+\subsection{Genus of a graph}
+
+We can also flip the question we are asking and rather ask which surfaces can a given graph can be drawn on.
+The genus of a graph is one such way to characterize this.
+If we let $S_0$ be the sphere and $S_n$ be the sphere with $n$ handles attached to it.
+This would mean $S_1$ is a torus and $S_n$ is an $n$ holed torus.
+Now every graph $G$ can be drawn on some space $S_n$.
+To see this simply draw $G$ on a sphere and allow crossings.
+Now wherever there is a cross simply add a handle and draw one of the edges over the handle and the other going through the handle.
+Armed with this knowledge we can define the genus of a graph, $G$, to be the least possible $n$ such that $G$ can be drawn on $G_n$.
+There is also a nonorientable analog of this using a sequence of nonorientable spaces.
+
+\section{Conclusion}
+We have built up a basic understanding of graphs and graph theory.
+We've thoroughly proven Kuratowski's theorem, and hopefully in a way that is approachable.
+We then spent a bit of time talking about possible next steps.
+The graph minor theorem for example is a spectacular theorem that deserves far more attention then we are giving it.
+This however is where we end the paper.
+Thank you for reading.
+%TODO Make better?
+
+\section{Acknowledgments}
+I would like to thank Professor Shaw for his extreme patients while I wrote this paper.
+I would like to thank my family (especially my mother) who pushed me to continue writing the paper.
+Finally I would like to thank anyone who took time to help revise the paper.
+Thank you.
 

### 2019-05-12 Topology/Paper/paper.tex
Topology: paper is being revised publicly, using double spaced

@@
 \usepackage{thm-restate}
+\usepackage{setspace}
+\doublespacing
 \title{Topological Graph Theory}
@@
 Topological graph theory is an entire field within topology and as such this paper is by no means meant to cover all of topological graph theory in any depth.
-This paper instead will first cover a rather shallow overview of the field (section 2), followed by a more in depth study of graphs theory (section 3).
+This paper instead will first cover a rather shallow overview of the field (section \ref{SoftOverview}), followed by a more in depth study of graphs theory (section \ref{SoftBackground}).
 The overview will mainly be focused on giving a thorough understanding of what topological graph theory is as well as to briefly cover the history of the field.
-After the overview we will spend section 3 building up definitions from graph theory that we will need for the later more rigorous parts of the paper.
+After the overview we will spend section \ref{SoftBackground} building up definitions from graph theory that we will need for the later more rigorous parts of the paper.
 After this we will dive into Kuratowski's Theorem.
@@
 
-\section{Overview}
+\section{Overview} \label{SoftOverview}
 \subsection{Graphs}
@@
 Each of these lines are called an edge.
-We will simply insist that no edge connects two vertices and that we do not have multiple edges between the same pair of vertices.
+We will simply insist that no edge connects a vertex to itself and that we do not have multiple edges between the same pair of vertices.
 
@@
 This is a strict violation of our definition for a graph.
-The issue of course then comes to what would one call such a beast as this where, presumably, one is able to have as many connections between any pair of vertices and could even have connections from a vertices to itself.
-
-I am particularly glad that you're paying enough attention to notice that the diagram does not depict a graph.
-This is what we will refer to as a multigraph.
+The issue of course then comes to what would one call this graph like object one is able to have as many connections between any pair of vertices and could even have connections from a vertices to itself.
+
+This is what we will call a multigraph.
+A multigraph is like a graph, but can have an edge that connects a vertex to itself and have two vertices share an edge.
 It is worth noting that graphs are a type of multigraph, so anything we show to be true for all multigraphs, is also true for all graphs.
@@
 If we look at the multigraph above, we have four vertices that have an odd number of edges connected to them.
-
-\subsection{History}
-%TODO Make how short this is less obvious
-The seven bridges of K\"onigsberg problem was solved by Euler %TODO Citation (wikipedia for seven bridges of konigsberg)
-in 1736. In mathematics this problem is of great historical significance as it is considered to be the beginning of graph theory as well as a sort of precursor to topology. %TODO Citation
-
-\section{Graph Theory Background}
+This means no mater where you start this is no way to take a stroll across every bridge without crossing any bridge twice.
+
+The seven bridges of K\"onigsberg problem was solved by Euler in 1736.\footnote{\url{https://en.wikipedia.org/wiki/Seven_Bridges_of_K\%C3\%B6nigsberg}} In the history of mathematics this problem is of some significance as it is considered to be the beginning of graph theory as well as a sort of precursor to topology.\footnote{\url{https://en.wikipedia.org/wiki/Seven_Bridges_of_K\%C3\%B6nigsberg}}
+
+\subsection{What is topological graph theory?}
+
+Topology the area of math where we deal with different spaces and fundamental concepts like continuity on these spaces.
+Much of topological graph theory has to do with the relationship between a graph and topological spaces.
+Once we have a bit more of an overview of graph theory we will dive into Kuratowski's theorem.
+We use Kuratowski's theorem as a sort of introduction to topological graph theory in this paper as it is a prime example of the relation between a graph and topological spaces.
+
+\section{Graph Theory Background} \label{SoftBackground}
 
@@
 If some can and some can't how do we tell which can be drawn and which can not?
-The answer to this comes in Kuratowski's theorem, however before we can even state this theorem we need to build up a bit of terminology for graph theory.
+This is the question at the center of Kuratowski's theorem.
+The rest of this section will serve two purposes.
+This sections will serve to build up some familiarity with graph theory for those without any previous exposure.
+The second purpose of this section is to familiarize the reader with definitions and terms from graph theory that will be needed later in our proof of Kuratowski's theorem.
 
@@
 We've already seen drawings of graphs like the one for K\"oingsberg and two drawings of $k_4$, this means there may be multiple distinct drawings for the same graph.
-Now we don't need to be very worried about what defines a drawing, that won't be important to us.
-Simply think of it as the drawing.
+Simply thinking of a drawing as a drawing on a sheet of paper good enough for the vast majority of this paper.
+We will return to formally define a drawing later in section \ref{Draw} when we need to.
 
@@
 \subsection{Face}
-Faces are a bit of an odd property here as they fundamentally are actually properties only of plane drawings and not graphs themselves; however the number of faces, as we will see stays consistent between any plane drawing of a planar graph and as such the number of faces is a property that planar graphs have.
-
+Faces are a bit of an odd property here.
+Fundamentally faces are a property of plane drawings of a graph, not of the graph itself.
 A face is defined as a connected space that contains no edges or vertices and itself is bounded by edges and vertices.
@@
 This sort of breaking apart is nice as often we will prove things about connected graphs that are true about all graphs.
-For example if all components of a graph are planar then the entire graph must be planar, this will be proven below and it allows us to only deal with connected graphs.
+For example if all components of a graph are planar then the entire graph must be planar, this will be proven in section \ref{SubGraphSec} and it allows us to only deal with connected graphs.
 
@@
 
-\section{Kuratowski's Theorem}
+\section{Kuratowski's Theorem}\label{TheTheorem}
 \begin{restatable}[Kuratowski]{theorem}{THEBIGONE}\label{THEBIGONE}
@@
 
-\subsection{$K_5$ and $K_{3,3}$}
+\subsection{$K_5$ and $K_{3,3}$}\label{k5k33}
 Our first step is proving that $K_{3,3}$ and $K_5$ are nonplanar. To do this we are going to use the following theorem.
@@
 
-%TODO cite https://www.ics.uci.edu/~eppstein/junkyard/euler/iedge.html
-
-\begin{proof}
+\begin{proof}\footnote{This proof comes from: \url{https://www.ics.uci.edu/~eppstein/junkyard/euler/iedge.html}.}
 	First consider a connected multigraph with no edges, as this is connected we may only have a single vertex.
@@
 \begin{corallary}
-	Any plane drawing of any multigraph has the same number of faces.
+	Any plane drawing of a specific multigraph $G$ has the same number of faces.
 \end{corallary}
@@
 \end{center}
-\begin{proof}
+\begin{proof}\footnote{This proof comes from \url{http://www.math.cmu.edu/~mradclif/teaching/228F16/Kuratowski.pdf}.}
 	$K_5$ is a graph\footnote{Recall that all graphs are multigraphs, but not all multigraphs are graphs.}, and as such an edge can not be a loop and two vertices can share at most one edge.
@@
 \end{center}
-\begin{proof}
+\begin{proof}\footnote{This proof comes from \url{http://www.math.cmu.edu/~mradclif/teaching/228F16/Kuratowski.pdf}.}
 	$K_{3,3}$ is a bipartite graph, meaning that there is some way to break the graph into two collections of vertices, where there are no edges that stay within one of these collections.
@@
 
-\subsection{Drawings}
+\subsection{Drawings} \label{Draw}
 Up to this point the paper has been writing such that anyone with a basic mathematical competency and interest could understand and work through the content.
@@
 
-\subsection{Subgraph lemmas}
+\subsection{Subgraph lemmas} \label{SubGraphSec}
 
@@
 \subsection{The Jordan Curve Theorem}
-\begin{theorem}[Jordan curve theorem] %TODO cite wikipedia https://en.wikipedia.org/wiki/Jordan_curve_theorem#Definitions_and_the_statement_of_the_Jordan_theorem
+\begin{theorem}[Jordan curve theorem]
 	Let $C$ be a Jordan curve in the plane $\mathbb R^2$.
 Then its complement, $\mathbb R^2 \setminus C$, consists of exactly two connected components.
-One of these components is bounded (the interior) and the other is unbounded (the exterior), and the curve C is the boundary of each component.
+One of these components is bounded (the interior) and the other is unbounded (the exterior), and the curve C is the boundary of each component.\footnote{This statement of the Jordan curve theorem comes from \url{https://en.wikipedia.org/wiki/Jordan_curve_theorem\#Definitions_and_the_statement_of_the_Jordan_theorem}.}
 \end{theorem}
@@
 \begin{proof}
-%TODO ask Shaw what he thinks
 	Consider a plane drawing of a graph $G$ with cycle $C$.
@@
 We know that in $D'$ the face that corresponds to $F$ is the outer face as it contained the punctured point in $\inv g(D')$.
-%TODO Ask shaw if I should prove that the puctured point in the sphere corresponds to a limit point
 \end{proof}
@@
 \end{theorem}
-%TODO cite Wikipeida menger's theorem
-\begin{proof}
+\begin{proof}
+	\footnote{This proof comes from \url{https://en.wikipedia.org/wiki/Menger\%27s_theorem\#Other_proofs}.}
 	This is trivially true on complete graphs, so for the rest of this proof we will only be considering graphs that are not complete.
@@
 
-\begin{proof}
+\begin{proof}\footnote{This proof comes from \url{http://math.uchicago.edu/~may/REU2017/REUPapers/Xu,Yifan.pdf}}
 	First consider the complete graph.
-We know that $K_4$ is planar (see below), therefore by the contrapositive of lemma \ref{subgraph} all subsets of $K_4$, are planar.
+We know that $K_4$ is planar (see below), therefore by lemma \ref{subgraph} all subsets of $K_4$, are planar.
 Any complete graph $K_i$ with $i < 4$ is a subgraph of $K_4$ (simply remove any $4-i$ vertices from $K_4$) so a nonplanar complete graph must be at least 4 connected.
@@
 \end{lemma}
-%TODO cite http://www.cs.rpi.edu/~goldberg/14-GT/19-kurat.pdf
-\begin{proof}
+
+\begin{proof} \footnote{This proof comes from \url{http://www.cs.rpi.edu/~goldberg/14-GT/19-kurat.pdf}.}
 	Let $G$ be a graph with lobes $L_1, L_2, \ldots, L_n$ of separating set $S=\set{x,y}$.
@@
 \end{lemma}
-%TODO cite http://www.cs.rpi.edu/~goldberg/14-GT/19-kurat.pdf
-
-\begin{proof}
+
+\begin{proof}\footnote{This proof comes from \url{http://www.cs.rpi.edu/~goldberg/14-GT/19-kurat.pdf}.}
 	Let $G$ be a graph fitting the above properties.
@@
 
-\begin{proof}
+\begin{proof}\footnote{This proof comes from \url{http://math.uchicago.edu/~may/REU2017/REUPapers/Xu,Yifan.pdf}.
+This paper also is where most of the structure of everything that has been written from the beginning of this section up to this point comes from.}
 	Suppose that $G$ is a graph with the following properties.
@@
 
-\section{Beyond Kuratowski's theorem}
+\section{Beyond Kuratowski's theorem} \label{Extension}
 Kuratowski's theorem is an unexpectedly elegant statement that says there are only two base case nonplanar graphs, and that all other nonplanar graphs derive their nonplanarity from at least one of these two graphs.
@@
 The graph minor theorem answers this question, at least in part.
-It states that any countable set $\mathcal G$ of finite graphs, contains a finite subset $\mathcal H\subset\mathcal G$ such that for all $G\in\mathcal G$ there is some $H\in\mathcal H$ such that $G$ contains a subset that is contactable to $H$.
-%TODO cite https://arxiv.org/pdf/1608.04066.pdf
+It states that any countable set $\mathcal G$ of finite graphs, contains a finite subset $\mathcal H\subset\mathcal G$ such that for all $G\in\mathcal G$ there is some $H\in\mathcal H$ such that $G$ contains a subset that is contactable to $H$.\footnote{This comes from \url{https://arxiv.org/pdf/1608.04066.pdf}.}
 This means that if a surface $S$ has the following property

### 2019-05-12 Topology/Paper/paper.tex
Louis revisions for Section 1

@@
 \usepackage{thm-restate}
-\usepackage{setspace}
-\doublespacing
+%\usepackage{setspace}
+%\doublespacing
 \title{Topological Graph Theory}
@@
 \section{Introduction}
-Topological graph theory is an entire field within topology and as such this paper is by no means meant to cover all of topological graph theory in any depth.
-This paper instead will first cover a rather shallow overview of the field (section \ref{SoftOverview}), followed by a more in depth study of graphs theory (section \ref{SoftBackground}).
-The overview will mainly be focused on giving a thorough understanding of what topological graph theory is as well as to briefly cover the history of the field.
-After the overview we will spend section \ref{SoftBackground} building up definitions from graph theory that we will need for the later more rigorous parts of the paper.
-After this we will dive into Kuratowski's Theorem.
-We will start by defining $K_5$ and $K_{3,3}$ and showing that they are both nonplanar.
-Up until this point the paper is written to be accessible by anyone, no mater their level of math background.
-After we show the nonplanarity of $K_5$ and $K_{3,3}$ we continue onto thoroughly prove Kuratowkski's theorem.
-The audience for this part is expected to have at least an undergraduate understanding of topology and some exposure to graph theory.
-After Kuratowski's theorem we finish with a brief discussion of what lies beyond Kuratowski's theorem.
+Topological graph theory is a field within topology, and therefore this paper is by no means meant to cover all of topological graph theory in any depth.
+This paper instead will first be concerned with a rather shallow overview of the field (section \ref{SoftOverview}), followed by a more in-depth study of graph theory (section \ref{SoftBackground}).
+The overview will mainly be focused on conveying a thorough understanding of what topological graph theory is, as well as briefly covering the history of the field.
+After the overview, section \ref{SoftBackground} of this paper will build up definitions from graph theory that will needed for the later, more rigorous parts of this paper.
+After that this paper will dive into Kuratowski's Theorem.
+It will start by defining $K_5$ and $K_{3,3}$ and showing that they are both nonplanar.
+Up to this point the paper is written to be accessible by anyone, no matter their level of math background.
+After discussing the nonplanarity of $K_5$ and $K_{3,3}$ this paper continues by thoroughly proving Kuratowski's theorem.
+The audience for this part is expected to have at least an undergraduate understanding of topology, and some exposure to graph theory.
+After Kuratowski's theorem, this paper finishes with a brief discussion of what lies beyond Kuratowski's theorem.
 
@@
 we would be left with the same graph.
-That is to say, it doesn't mater where we put a vertex on our sheet, the graph exists independently of the representation we draw.
+That is to say, it doesn't matter where we put a vertex on our sheet, the graph exists independently of the representation we draw.
 
@@
 If we look at the multigraph above, we have four vertices that have an odd number of edges connected to them.
-This means no mater where you start this is no way to take a stroll across every bridge without crossing any bridge twice.
+This means no matter where you start this is no way to take a stroll across every bridge without crossing any bridge twice.
 
@@
 
-\subsection{Planer Graphs}
+\subsection{Planar Graphs}
 
@@
 	First consider a connected multigraph with no edges, as this is connected we may only have a single vertex.
-This produces a single and no edges so we find $$v-e+f=1-0+1=2$$ Now that we know that for 0 edges this rule fits, then either the rule ($v-e+f-2$) is true no mater the number of edges, or there is some number at which point this rule breaks, and $v-e+f\not=2$.
+This produces a single and no edges so we find $$v-e+f=1-0+1=2$$ Now that we know that for 0 edges this rule fits, then either the rule ($v-e+f-2$) is true no matter the number of edges, or there is some number at which point this rule breaks, and $v-e+f\not=2$.
 If there is a number that breaks this rule, then there must be a lowest number (let's call it $k$) that breaks this rule.
@@
 This adds exactly $f_{k+1}-1$ faces by drawing this component as it simply splits one already existing face into $f_{k+1}$ new faces.
-This means that no mater what order we add faces in
+This means that no matter what order we add faces in
 \end{proof}

### 2019-05-12 Topology/Paper/paper.tex
day one

@@
 \usepackage{thm-restate}
-%\usepackage{setspace}
-%\doublespacing
+\usepackage{setspace}
+\doublespacing
 \title{Topological Graph Theory}
@@
 \subsection{Graphs}
-Before we talk about topological graph theory we must first understand what a graph is.
-
-A graph is generally defined as a set of vertices combined with a set of edges between vertices, however here it may be more useful to think about them visually with a simple representation.
-
-Consider first a set of points, this may be thought of as just drawing dots on a sheet of paper.
+Before we talk about topological graph theory one must first understand what a graph is.
+A graph is generally defined as a set of vertices combined with a set of edges between vertices. However, here it may be more useful to think about of a graph visually with a simple representation.
+Consider first a set of points.
+This may be thought of as just dots on a sheet of paper.
 Each of these points will be called a vertex.
-Now we may start drawing lines between vertices.
-Lines may cross over each other and need not be straight.
-There is no requirement that all vertices have a line going to it.
-Each of these lines are called an edge.
-We will simply insist that no edge connects a vertex to itself and that we do not have multiple edges between the same pair of vertices.
-
-Once we have drawn this we have a representation of a graph.
-If we were to move the vertices around on the paper but leave them having the same edges (the same vertices are connected to the point as they were before).
-we would be left with the same graph.
-That is to say, it doesn't matter where we put a vertex on our sheet, the graph exists independently of the representation we draw.
+Then we may start drawing lines between vertices.
+Lines may cross over each other, and need not be straight.
+There is no requirement that all vertices have a line going to them.
+These lines will be called edges.
+We will simply insist that no edge connect a vertex to itself and that we do not have multiple edges between the same pair of vertices.
+
+Once we have drawn this, we have a representation of a graph.
+If we were to move the vertices around on the paper but leave them with the same edges, we would be left with the same graph.
+That is to say, it doesn't matter where we put a vertex, the graph exists independently of the representation.
 
@@
 
-Consider the following photo-realistic drawing of the city of K\"onigsberg.
+Consider the following drawing of the city of K\"onigsberg.
 
@@
 
-I first came across this question in the 8\textsuperscript{th} grade, and it was presented to us during geometry class.
-While undoubtedly an interesting problem, it is quite misleading to try and think of this as a geometry problem.
-Instead we will try and reduce it to a graph problem.
-
-Let us start by thinking of every island as a vertex and every bridge as an edge. We find the following graph.
-
+I first came across this question in an 8\textsuperscript{th} grade geometry class.
+While undoubtedly an interesting problem, it is quite misleading to think of this as a geometry problem.
+Instead we will reduce it to a graph problem.
+
+Let us start by thinking of every island as a vertex and every bridge as an edge. We find the following graph:
 \begin{center}
@@
 \end{center}
-
+%?
 It is worth noting two things about the above diagram.
-First that the labels on the vertices and edges are unrelated to the problem, but have been added simply to make referring to parts of the graph much easier.
-Second that whatever the above image depicts, does not fit our definition of a graph.
-
-Notice that edge $2$ and edge $3$ both connect vertex $A$ to $B$, as well edges $5$ and $6$ do for $B$ and $C$.
+First, that the labels on the vertices and edges are unrelated to the problem, but have been added simply to make referring to parts of the graph much easier.
+Second, that whatever the above image depicts, does not fit our definition of a graph.
+
+Notice that edge $2$ and edge $3$ both connect vertex $A$ to $B$, just as $5$ and $6$ do for vertices $B$ and $C$.
 This is a strict violation of our definition for a graph.
-The issue of course then comes to what would one call this graph like object one is able to have as many connections between any pair of vertices and could even have connections from a vertices to itself.
+The issue, of course, then comes to what would one call this graph-like object where one is able to have any number of connections between any pair of vertices.
 
 This is what we will call a multigraph.
-A multigraph is like a graph, but can have an edge that connects a vertex to itself and have two vertices share an edge.
-It is worth noting that graphs are a type of multigraph, so anything we show to be true for all multigraphs, is also true for all graphs.
-
-Now to solve this problem we need to make one simple observation about how we walk.
-If we are to go to island (or vertex) we must also leave that island, unless it is the last island we arrive on.
+A multigraph is like a graph, but can have an edge that connects a vertex to itself and can have two vertices that share multiple edges.
+It is worth noting that any graph is a multigraph, so anything shown to be true for all multigraphs must be true for all graphs.
+
+Now to solve the K\"onigsberg problem we need to make one simple observation about how we walk.
+If we are to go to an island (or vertex) we must also leave that island unless it is the last island we go to.
 This means, that with the exception of the island we start on and end on, each island must have an even number of bridges connected to it.
-On the multigraph we would say that we need all vertices but a start and end vertex to have an even number of edges.
+
+We now translate the K\"onigsberg problem into the language of multigraphs.
+The question becomes ``If we pick the right vertex and start going across edges to other vertices, is it possible to cross every edge exactly once?" We can translate what we've discovered about islands needing an even number of bridges to say that we can only make this sort of journey if all but two vertices (a start and end vertex) have an even number of edges.
+Looking at our multigraph representation of the city of K\"onigsberg we find that all four of the vertices have four edges.
+This means it is impossible to take a single walk and cross every bridge exactly once.
+
+%On the multigraph we would say that we need all vertices with the exception of a start and end vertex to have an even number of edges.
 If we look at the multigraph above, we have four vertices that have an odd number of edges connected to them.
@@
 
-Topology the area of math where we deal with different spaces and fundamental concepts like continuity on these spaces.
-Much of topological graph theory has to do with the relationship between a graph and topological spaces.
-Once we have a bit more of an overview of graph theory we will dive into Kuratowski's theorem.
-We use Kuratowski's theorem as a sort of introduction to topological graph theory in this paper as it is a prime example of the relation between a graph and topological spaces.
+Topology is the area of math in which we deal with different spaces and their fundamental properties.
+Much of topological graph theory has to do with the relationship between graphs and spaces.
+For example this paper focuses on Kuratowski's theorem, which deals with which graphs are able to be drawn in a plane.
+This paper uses Kuratowski's theorem as an introduction to topological graph theory.
 
@@
 Consider the following graph.
-
 \begin{center}
@@
 \end{center}
-
-This graph is called a complete as every vertex is connected to every other vertex by an edge; in fact this graph in particular is called $K_4$ as it is the complete four vertex graph.
-We would like to find out if we can draw this above graph without having any lines crossing.
-We can in fact draw this graph without any intersections and for any skeptics who may being reading this, the below is $K_4$ without any edges intersecting.
+This graph is called a complete graph as every vertex is connected to every other vertex by an edge.
+In fact this graph in particular is called $K_4$ as it is the complete graph on four vertices.
+We would like to find out if we can draw this graph without having any lines crossing.
+This is in fact possible, and for any skeptics who may be reading this the below is $K_4$ without any edges intersecting.
 
@@
 
-So if this graph can be drawn without intersection, can any graph be drawn without intersections?
-If some can and some can't how do we tell which can be drawn and which can not?
+So if this graph can be drawn without any intersection, can any graph be drawn without intersections?
+If some can and some can't, how do we tell which can be drawn and which can not?
 This is the question at the center of Kuratowski's theorem.
 The rest of this section will serve two purposes.
-This sections will serve to build up some familiarity with graph theory for those without any previous exposure.
+The first purpose of this section is to build up familiarity with graph theory for those without any previous exposure.
 The second purpose of this section is to familiarize the reader with definitions and terms from graph theory that will be needed later in our proof of Kuratowski's theorem.
@@
 A graph drawing is exactly what it sounds like.
-We've already seen drawings of graphs like the one for K\"oingsberg and two drawings of $k_4$, this means there may be multiple distinct drawings for the same graph.
-Simply thinking of a drawing as a drawing on a sheet of paper good enough for the vast majority of this paper.
-We will return to formally define a drawing later in section \ref{Draw} when we need to.
-
-If a drawing has no edges intersecting it is said to be a plane drawing. If there exists such a drawing for a particular graph, then that graph is a planar graph.
+We've already seen drawings of graphs like the one for K\"onigsberg and two drawings of $K_4$.
+The fact that there can be two distinct drawings of $K_4$ shows that there can be multiple distinct drawings for the same graph.
+Simply thinking of a drawing as a drawing on a sheet of paper will be good enough until section \ref{Draw} where we formally define a graph drawing.
+
+If a drawing has no edges intersecting, it is said to be a plane drawing. If there exists such a drawing for a particular graph, then that graph is a planar graph.
 
@@
 
-If you think back to high-school geometry and cubes you may recall that a each of the corners is a vertex, the lines connecting vertices are edges and the area between the edges are faces.
-In a graph we have vertices connected by edges and when we draw them there are empty areas enclosed by edges and vertices.
-For example the following would correspond with a cube
+If you think back to high-school geometry and cubes you may recall that a each of the corners is a vertex, the lines connecting vertices are edges, and the area between the edges are faces.
+In a graph we have vertices connected by edges, and when we draw them there are empty areas enclosed by edges and vertices.
+For example the following would correspond with a cube:
 \begin{center}
@@
 \end{center}
-Now we can imagine that if we look at the cube straight on maybe $ABDC$ would be the face we are looking at.
-So too we see the area enclosed in $ABDC$ is a face by the definition we gave.
-The same is true for $ABFE$, $ACGE$, $DBFH$, and $DCGH$, however that leaves us with only five faces on this cube.
-The last face must logically come from $EFHG$, however the area enclosed by that contains all the other edges and vertices, so it doesn't fit our definition.
-However we may notice that the infinite space outside $EFHG$ does not contain any vertices, and therefore we get a sixth face.
-
-Consider then the following very simple graph:
-\begin{center}
-	\begin{tikzpicture}[auto, node distance=3cm, every loop/.style={},
-	thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries}]
-
-	\node[main node] (1) {$A$};
-	\node[main node] (2) [right of=1] {$B$};
-
-	\end{tikzpicture}
-\end{center}
-Now we still only have one face, however it doesn't have as nice a boundary as they did in the cube.
-However if we look at all of space excluding $A$ and $B$ then we still get a valid space by our definition.
+
+We can start going through the faces of the above graph drawing.
+We clearly see that $ABDC$ bounds an area that contains to vertices or edges.
+This means that this area is a face.
+We can see that $EABF$, $EACG$, $GCDH$, and $FBDH$ all have the same property on their interior.
+There is however one final remaining face.
+This face is bordered by $EFHG$, and is called the outer face.
+This is all the infinite space outside the bounds of the graph.
+Every plane drawing of a graph will have an outer face.
 
@@
 		\item Every odd element in the sequence is a vertex.
-		\item Every even element in the sequence is an edge that connects the vertex before and after it.
+		\item Every even element in the sequence is an edge that connects the vertices before and after it.
 		\item A walk always begins and ends with a vertex.
@@
 
-Now the sequence $BeGjF$ is a walk as we can think of starting at vertex $B$, walking down $e$ to $G$, then down $j$ to $F$ and  finishing.
-The sequence $AaBaA$ is also a walk as we could start at $A$, go down edge $a$ to $B$, then back up $a$ to $A$ again.
-The sequence $CfEi$ however isn't a walk as it doesn't end with a vertex.
+Now the sequence $BeGjF$ is a walk, as we can think of starting at vertex $B$, walking along edge $e$ to vertex $G$, then along edge $j$ to vertex $F$ and  finishing there.
+The sequence $AaBaA$ is also a walk as we could start at vertex $A$, go along edge $a$ to vertex $B$, then back along edge $a$ to vertex $A$ where we finish.
+The sequence $CfEi$ however isn't a walk, as it doesn't end with a vertex.
 
@@
 \begin{definition}[path]
-	A path is a walk where a vertex and edge can not appear twice in the sequence.
-\end{definition}
-
-You could think of a path as you start at some vertex and start building a path as you talk your walk. You aren't allows to have your path intersect with itself, so you always
-
-So for example with the above graph $BeGjF$ is not only a walk, but also a path. The sequence $AaBaA$, while it is a walk, it however is not a path as both edge $a$ and vertex $A$ are used twice.
+	A path is a walk in which no vertex or edge can appear twice.
+\end{definition}
+
+For example with the above graph $BeGjF$ is not only a walk, but also a path. However, the sequence $AaBaA$, while it is a walk, is not a path as both edge $a$ and vertex $A$ are used twice.
 
@@
 \begin{definition}[cycle]
-	A cycle is a walk, of length greater than one, where a vertex and edge can not appear twice in the sequence with the exception of the first and last vertex which must be the same.
-\end{definition}
-
-The definition for cycle is quite similar to that of a path, it effectively is a path that loops back to where it started at the end.
-The stipulation that a cycle must be "of length greater than one" simply means that the walk $A$ (just the vertex $A$ and nothing else) is not a cycle.
+	A cycle is a walk, of length greater than one, in which no vertex or edge can appear twice, with the exception of the first and last vertex which must be the same. 
+\end{definition}
+
+The definition of a cycle is quite similar to that of a path.
+It effectively is a path that loops back and ends where it started.
+The stipulation that a cycle must be ``of length greater than one" simply means that the walk $A$ (just the vertex $A$ and nothing else) is not a cycle.
 Examples of a cycle would include $AbCgHkFcA$, $AbCfEoA$, and $FkHmJnIlGjF$.

### 2022-11-09 Combinatorics/CatalanNumbers/document.tex
fixed typo

@@
 	\section{Introduction to the sequence}
-	Our Catalan group is defined as a sequence of $a_1, \ldots, a_n+1$ of non-negative integers such that $\sumfrom{i=1}{n+1}{2^{-a_i}} = 1$ and for all $2 \leq j \leq n+1$ the number
+	Our Catalan group is defined as a sequence of $a_1, \ldots, a_{n+1}$ of non-negative integers such that $\sumfrom{i=1}{n+1}{2^{-a_i}} = 1$ and for all $2 \leq j \leq n+1$ the number
 	$2^{a_j} \sumfrom{i=1}{j-1}{2^{-a_i}}$ is an integer.  We will call any sequence that fits these rules a beveridge sequence.
